\documentclass[12pt, openany]{book}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{hyperref}

% Configure the document
\setmainfont{Roboto}
\titleformat{\chapter}[display]{\normalfont\huge\bfseries}{\chaptertitlename\ \thechapter}{20pt}{\Huge}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{\leftmark}
\fancyfoot[C]{\thepage}

% Begin the document
\begin{document}
\chapter{Prologue}

\textit{In the beginning, there were only the Gods}.
\textit{Aeons untold passed as they drifted aimlessly through the Void, until they grew bored with this state of affairs. In their infinite wisdom they brought into existence Creation, but with Creation came discord. The Gods disagreed on the nature of things: some believed their children should be guided to greater things, while others believed that t}\textit{hey must rule over the creatures they had made.}

\textit{So, we are told, were born Good and Evil.}

\textit{Ages passed in fruitless argument between them until finally a wager was agreed on: it would be the mortals that settled the matter, for strife between the gods would only result in the destruction of all. We know this wager as Fate, and thus Creation came to know war. Through the passing of the years grooves appeared in the workings of Fate, patterns repeated until they came into existence easier than not, and those grooves came to be called Roles. The Gods gifted these Roles with Names, and with those came power. We are all born free, but for every man and woman comes a time where a Choice must be made. }

\textit{It is, we are told, the only choice that ever really matters.”}

\textit{– }First page of the Book of All Things

The sun was setting on a field of corpses.

Black passed by a group of orcs building a pyre, nodding absently when they stopped piling up logs to salute – green eyes swept over the bloodied plains, taking in the devastation the Legions of Terror had wrought. Camp fires were already burning in the distance, sprawled across the hills, and by the sound of it the officers had already distributed the night’s ale rations. He would join them in time, but for a little longer he felt the need to stay here. To stand in the middle of what a decade of planning had brought forth. Callow’s standing army had been annihilated today, over two thirds of their number slaughtered before they broke ranks. The Wizard of the West had fled, his power broken. Good King Edward’s head had been popped off like a bottlecap by an ogre and the Shining Prince had been mobbed by a company of goblins until one drew a red smile across his throat. The Kingdom of Callow’s strength had been crushed in the span of an afternoon, and Black would see to it that it never recovered.

“It’s getting dark out, Black,” the voice came from behind. “You should return to camp.”

It never ceased to amuse him how a woman the size of Captain could be so eerily quiet. Even decked out in full plate, the olive-skinned woman had been noiseless in her approach. If not for the other senses that his Role afforded him, he would never have sensed her closing in. Turning to have a look at his right hand, Black raised an eyebrow when he was presented with the sight of Scribe standing next to the woman in question. Unusual of her to wander onto a battlefield, even one where the fighting was long over.

“Soon,” he agreed. “Scribe, you have a report?”

The plain-faced woman fished out a scroll from the bandolier hanging across her shoulder and handed it to him without a word. Breaking the seal absently, Black unfurled the parchment and scanned the lines. A moment passed until the barest hint of a smile quirked his lips.

“That should keep the Procer occupied for the time being,” he murmured. “By the time the fighting dies down we’ll have the border secure.”

Handing back the scroll to Scribe, he returned his attention to the battlefield. The companies assigned to the thankless work of burning the bodies would have to work through the night, at this rate. He’d have to see about arranging a rotation when he returned to camp, if sufficiently sober soldiers could be produced. A tall silhouette striding forward purposefully caught his attention as the dark-skinned man it belonged to deftly sidestepped a pair of orcs carrying a log twice the size of a grown man.

“You could have told me we were having an after-battle get together,” Warlock teased as soon as he was close enough to be heard. “I’d have brought a few bottles, though admittedly the scenery’s a little morbid for my tastes.”

Black rolled his eyes, though he caught Captain discreetly suppressing a smile. Scribe eyed Warlock with the same mild bemusement as always, as if she couldn’t believe the charmingly smiling man standing in front of them had been the one to call down a rain of hellfire on the enemy barely an hour earlier. Not an unusual reaction: sorcerers with that kind of power were rarely so jovial.

“Happenstance,” he replied. “We’ll be heading back to camp soon enough.”

Warlock cast a look around, looking for the fifth member of their little band and coming up empty.

“Ranger’s already gone?” he asked.

“As soon as the battle was done,” Captain informed him.

The dark-skinned man grimaced.

“I didn’t think she would actually…” he said, trailing off after a sideways look at Black’s face.

“What’s done is done,” the Black Knight cut through, and that was the end of that.

The four stood in silence for a long moment, watching the night slowly crawl over the fields of Streges.

“Ten years,” Black finally said.

“Six, for the earliest ones,” Scribe disagreed quietly.

With a last look at the battlefield, the Black Knight turned away without a word and started for camp. Warlock slung a friendly arm over Captain’s shoulder, murmuring something that drew a smile from the much larger woman as Scribe methodically adjusted her bandolier before following. The Dread Empire of Praes may have won the war, but the clock was already ticking. The Legions of Terrors had made a lot of angry orphans through the afternoon’s bloody work, and in time that would mean one thing –

Heroes.
\clearpage
\chapter{Chapter 1: Knife}

“\textit{How many Praesi does it take to change a lantern’s wick?}
\textit{A legion to conquer all the candlemakers, a High Lord to sell the wicks down south and then we’re taxed for being in the dark.”}
– Overheard in a Laure tavern

The punch landed right in my eye, rocking me back.

I cursed and took a few steps back, ignoring the smug smile on my opponent’s face as the crowd went wild. \textit{Shit. That’s turning into a black eye for sure.} I’d need to shell out some of my winnings to get it fixed if I didn’t want to spend a few hours lectured by the Matron again. And that was assuming I won – if I lost, I was going to be short on funds for a while. The man started circling me like a murder of crows around a rotting carcass, unhurried but intent, and I brought up my fists. The bandages wrapped around my fingers were still flecked with blood from the few hits I’d landed earlier in the fight, but the ridiculously large fighter going by “Fenn” had shrugged those off too easily for comfort. If this turned into an endurance slugging match, I wasn’t going to win: the man had at least fifty pounds on me and he looked like he’d been carved out of a slab of solid muscle. I was faster than him, but he knew that – it was the reason he stayed on the defensive, letting me land hits in exchange for getting in one of his own. \textit{And his hurt me a lot more than mine hurt him.} “Come on, Foundling,” a woman in the back yelled. “Wreck the bastard!”

I spat out a mouthful of the blood pooling in my mouth and moved forward: the longer this went on, the larger his advantage got. I needed to end it quick if I was going to have even a slight shot at winning. Added a little spring to my step to see if it would make him flinch, but the big bastard was serene as a pond. It was a shame groin shots were illegal, since one of those would have gotten him moving for sure. I flicked a jab at his jaw but Fenn let it pass, pivoting to get a little closer. \textit{Got you.} My fist buried itself in his stomach viciously, drawing a strangled grasp as I danced away back out of his reach. The part of the crowd that had put money on my victory cheered while from the rest came a cacophony of jeers: I let the sounds wash over me, refusing to pay attention. I’d been too aware of my surroundings when starting out at this and it had cost me some easy victories, but I’d learned from my mistakes. “Saw your last fight, Foundling,” Fenn grunted as he tried to close the distance. “You sure you don’t wanna throw this one too?”

If that was his idea of trash talk, then he was swinging a stick at steel. I feinted a jab to his ribs to keep him on his feet and circled to get a better angle. I \textit{had }thrown the last fight, as it happened. I’d been winning too much lately, which made for bad odds when betting on myself. After taking a beating from a no-name newcomer, though, the balance had swung the other way: I was going to make a killing if I managed to beat Fenn today. Enough to pay tuition at the College, even after the organizers got their cut and another lump sum was set aside to keep the city guard looking away.

“You afraid of a girl half your size, Fenn?” I smiled back, pushing a sweat-drenched lock of hair out of my field of vision. “You should slip the healers a few coppers so they can fix up your manhood.”

Now \textit{that} got a reaction. The stocky man’s eyes narrowed and he grit his teeth. It was funny, the way most of the fighters who tried to bait me were so easy to bait themselves. He wasn’t stupid enough to up and charge me – he wouldn’t have the reputation he did if he lost his head this easily – but he went on the offensive the moment I have him an opening. I guess it didn’t matter how predictable you were when you hit like a horse’s kick. Apparently my little comment had gotten a fire going in Fenn, because when he swung at me it was the fastest he’d been so far: I barely managed to slap away his fist at the last moment and he still grazed my jaw. \textit{If that had landed, I’d be out cold on the ground.} I got in close enough that I could smell the sweat of him and threw a haymaker, but it didn’t even faze him: not enough force behind it. He took the hit and tried to wrestle me down, much to my panic. Getting into a grapple with a man that size would be… bad. \textit{Shit shit shit.} I landed a desperate uppercut right in his chin and felt a few teeth come loose, which bought me a moment. I got in a kick on the side of his knee and it gave. He dropped into a half-kneel and that was my in.

I’d done this before and it would be brutal but Radiant Heavens I was not going to \textit{lose} – I rammed my knee into his gut and Fenn dropped. Another kick sent him sprawling to the ground, and now the fight was as good as won: I stomped down on his ankle and it broke with a sickening crack. Fenn let out a hoarse scream and I felt a twinge of guilt but mercy was the kind of thing the Pit beat out of you. I was about to cave in a few ribs with another stomp when he raised his hand and panted out his surrender. For a moment all I heard was the sound of blood pounding in my ears but it passed and the numbness turned into the clamor of the masses going wild. I wiped the blood dripping off the corner of my mouth with the bandages around my hand and made my way out of the earthen pit where I’d just broken a man’s bones for gold. Well, gold in a manner of speaking: they usually paid me in Imperial silver denarii, which somehow made the whole thing feel even more wretched. The fatigue settling into my bones left me disinclined to mingle with the gamblers who’d struck good betting on me, though I forced a smile anyway. 

A tall orc pushed his way through the crowd to slap me on the back, the double row of pristine fangs inside his mouth turning what was supposed to be a grin into a horrifying display. It was rare to see orcs at fights like these: the only greenskins in Laure were part of the Legions and they tended to steer clear of the illegal stuff. Not to mention that even two decades after the Conquest legionaries were far from popular in the city – the kind of people that the Pit attracted was the kind that wouldn’t think twice about slipping a knife in a legionary’s back in a dark alley. \textit{Good luck with that}, I thought as I extricated myself from the greenskin’s enthusiastic congratulations. The orcs were taller and more broadly built than humans, generally speaking, and their thick greenish skin made them damnably hard to put down. Anybody stupid enough to tangle with three hundred pounds of trained killer deserved whatever was coming to them.

Booker was in the back of the warehouse, set up at her usual table. There were no windows in the Pit – glass had gotten even more expensive since the latest tax hitch – and the handful of oil lamps spread over the place cast more shadows than light over the corner of the place she’d claimed as her own. People gave her a wide berth, in part because she had a thoroughly nasty reputation and in part because of the pair of grim-looking bodyguards standing behind her. I’d thought Booker was a Name when I’d first heard it, but it was just an affectation: she couldn’t even do magic, as far as I knew. Her only power was having a large amount of thugs on payroll, which in her line of business was admittedly more useful. She smiled when she saw me coming, light catching on her handful of gold teeth. “Good show today, Foundling,” she said. “Way to make the old country proud.”

I snorted at that. Booker’s skin and hair were as dark as mine: we both had Deoraithe blood running through our veins. Still, I was an orphan and she was Laure born and raised – neither of us had ever set foot in the northern duchy or spoke even a word of the old tongue. Not that I was complaining about the misplaced sense of kinship: fifteen year old girls like me didn’t usually get to compete in the Pit. I’d gotten my foot in by playing on the Deoraithe reputation of being solid in a fight. \textit{They held the Wall for five hundred years, before the Conquest.} Even now the duchy most of them lived in was the only part of Callow without Imperial governors. I’d read about some kind of deal being cut with the Empress, though I couldn’t remember specifics.

“I try,” I grunted. “You got my winnings?”

Booker chuckled and slid the denarii across the table. I counted them – the only time I’d made the mistake not to she’d short-changed me – and frowned when I realized there were only twenty-one.

“We’re missing four,” I told her flatly. “I’m not going to fall for that twice, Booker.”

Her bodyguards pushed off the wall and started looming in response to the hostility in tone, but the dark-skinned woman grimaced and flicked a hand to dismiss them.

“Mazus upped the prices again,” she explained. “Everybody’s cut is smaller, even mine.”

While I didn’t believe for a moment that Booker’s profits had seen any change, I had no problem at all believing that the Governor had decided to squeeze out a little more gold from the Pit. The Imperial Governor for Laure had begun his third term of service by announcing that all the temporary taxes of his last terms were now permanent, after all, and there wasn’t a single pie in the city where he wasn’t shoving in his fingers. I nodded, disgruntled, and slipped the silvers in the leather bag where I kept my change of clothes. “Zacharis is in the back, if you want to get your eye fixed,” Booker told me. “You know the drill.”

She’d already stopped paying me attention before she finished speaking the sentence, not that I was going to complain. Booker wasn’t exactly the kind of company I cared to keep, not that I kept much to start with. I slipped past the bodyguards without bothering to glance at them, heading through the threshold into the dingy little backroom where the Pit’s mage plied his trade. Zacharis was a man in his twenties, his skin pale and constantly flushed. The half-empty bottle of wine next to the armchair where he was snoring was the reason the man was associated with an illegal fighting ring at all: he was a drinker, and in exchange for the better part of the money he made fixing up fighters Booker let him go through as many bottles as he wanted. He reeked of wine again, I noted as I got close enough to shake him awake, but at least this time there was no stench of vomit lurking behind it. Zacharis blearily opened his eyes, running a fat red tongue against his lips. 

“Catherine?” he croaked out. “I thought your fight was tomorrow.”

I resented the fact that he insisted on calling me by my first name instead of Foundling, but not enough to make a scene. I could have gone to the House of Light for healing – and gotten it for free, too – if I had the stomach to wait through the lines but the priests there had this unfortunate tendency to ask \textit{questions}. Better to suffer through a few minutes of the drunk’s company and his sloppier healing than have a sister showing up at the orphanage to tell the Matron I was getting into fights again. “Tomorrow’s now,” I told him with a sigh. “Are you sober enough to cast?”

He muttered a reply I couldn’t quite hear and rolled up his sleeves, which I took as agreement. His eyes flicked to the bottle but when he risked a glance at me whatever he must have seen on my face was enough to convince him to put the idea aside. He gestured for me to sit down on a wooden stool and pushed himself up. From the way he grimaced at that, he must have had the beginning of a pounding headache on his hands.

“So why is it that priests heal better than mages, anyway?” I asked him, trying to force him to focus on the here and now.

The look he shot me was fairly condescending. Zacharis uttered a few strange syllables and his hand was wreathed in yellow light – he kept it hovering an inch over my black eye, letting the spell sink in.

“Priests cheat, Catherine,” he informed me. “They just pray to the Heavens and power goes through them, fixes whatever’s broke. No real cleverness needed. Mages have to understand what they’re doing – throw magic around someone’s body without a plan and healing’s the last thing you’ll get.”

That was… not as reassuring as I’d thought it would be. Trusting that Zacharis knew what he was doing became something of an uphill battle, after actually meeting the man. \textit{Still, if he was a complete screwup Booker wouldn’t keep him around.} Gods knew he had to cost her a fortune in liquor, however cheap the swill he drank was. 

“There,” he said after a moment, taking away his hand. “As pretty as I can make it. Don’t get punched again, the flesh is more fragile than usual.”

I nodded my thanks, picking out seven coppers from my bag and dropping them into his open palm. He hesitated, then fished out a pair and handed them back to me. I shot him a surprised look.

“You’re getting close to sixteen, right?” Zacharis said. “Can’t have much more than a few months left before the orphanage puts you out. Keep those, every coin will count when you’re on your own.”

That was oddly touching, coming from a man I could barely stomach on the best of days.

“Thanks,” I muttered, abashed at the sudden generosity.

The pale mage smiled bitterly. “Go home, Catherine. Pick up a trade instead of getting mixed up in messes like this. There’s a reason they call it the \textit{Pit}, you know.”

He reached for the bottle and popped the cork, taking a swallow as he turned his back to me. I fled the room and then the warehouse itself: the less time I spent here the better. Besides, we were getting close to the evening bell and I had a real job to get to.

I was already Lakeside so it was a short walk to the Rat’s Nest. 

The quarter looked worse by daylight than it did at night: no darkness to hide the dirt and the misery, I supposed. The streets down here were tight and cramped, unlike the wide paved avenues of Fairway where all the richer sort lived. Even when Laure had been the capital of the Kingdom of Callow instead of just another governorship the Lakeside Quarter had been a dump. Or so I’d been told – the Conquest had happened over two decades ago, a few years before I’d been born, so I had to take it on faith. Still, I had a feeling it was worse than it used to be. The Guilds might have been raking in gold since they’d fallen into Governor Mazus’ pocket but everybody else was feeling the weight of the ever-increasing taxes: once-abandoned warehouses were now filled with people who’d had their homes and shops seized because they couldn’t pay on time, little more than refugees in their own city of birth. \textit{If he keeps strangling trade the whole city might end up scrabbling in the dirt down here}, I reflected as I tiptoed around a small pool of mud. My boots were old enough as it was, they might not survive being another cleaning in one piece.

Besides, Harrion wouldn’t let me barmaid if I was going to track dirt all over his floor. He already disapproved of my fighting in the Pit, not that he’d ever said anything: he just had a way of sending me home early whenever I showed up with bruises that were too obvious. Hopefully I’d have time to rinse off in the back before he could see the blood still on my lip: the end of the month was never busy at the Rat’s Nest, so he might be napping in the rooms upstairs instead of keeping an eye on the common room. \textit{Which means I might have Leyran for only company tonight}, I frowned. Harrion’s son was a few years older than me and convinced he was the most charming man since the Shining Prince. Bit of a layabout, and he had a way of spending more time talking with the patrons than actually getting them their drinks – especially whenever by some miracle an attractive woman ended up at the Nest. He was harmless, as far as idiots went, but if he ended up inheriting the tavern he’d likely run it into the ground. I took a shortcut through Tanner Tom’s backyard to shave a few minutes off of my walk, if only so the sweat I was still drenched in didn’t have too much time to settle.

I didn’t have a key to the back door, but it was unlocked. I wiped my boots on the already dirty rug I was pretty sure had been stolen from a merchant down by the harbour and dropped my bag on the dirt floor and headed for the bowl of water by the table in the corner. The background noise filtering in from the door to the common room made it clear there were already a handful of patrons, though the song the minstrel was playing was even louder. I winced when she bawled out a particularly off-key couplet, picking up the rag inside the bowl and wiping my face clean. I used the polished copper plate hung up on the wall to make sure there was no blood showing on my face, cursing under my breath when I realized that the blood clot on my lip wasn’t going anywhere. The dark-skinned girl looking back at me from the surface looked like she’d seen better days, I had to admit. 

I’d never been what you would call pretty – chin too strong, cheekbones too angular – but the way my dark locks stuck to the top of my head had me looking like a drenched urchin girl. A few strands of hair had come loose from the ponytail I kept them in so I shook loose the wooden clip that kept it together and shoved it in my pocket. The water had the rag cool and pleasant, so I rubbed it along my neck and collarbones just for the refreshing feeling. The woollen shirt I’d worn in the pit was flecked with blood so I took it off and shoved it back in the bag, slipping on my only good clothes: the dyed cotton blouse was a pleasant blue, the symbol of the Laure House for Tragically Orphaned Girls sown over the heart. I’d have to be careful not to spill any beer on it: laundry day at the orphanage wasn’t for a few days yet and the Matron checked out clothes every morning. Nudging my bag into the corner, I pushed the door and entered the Rat’s Nest proper.

The tavern’s common room was exactly as pretty as the place’s name implied: rickety wooden walls salvaged from wrecked ships and a dirt floor that turned into mud wherever drinks got spilled too often. There was a wide fire pit circled by stones in the middle of it, surrounded by a ring of tables where half a dozen patrons were chatting quietly over drinks. Only two humans, I saw. Three orcs still in legionary armour were sharing a table with a yellow-eyed goblin sporting officer’s stripes on her shoulders. Or at least I thought it was a her: it was hard to tell the gender under all that green wrinkled skin. The sight of the three big orcs standing at least three feet taller than the scrawny goblin yet hanging on her every word drew a small smile out of me, though my attention shifted as soon as our minstrel began a new song.

“\textit{Boot goes up and boot goes down:}

\textit{There goes their callow crown} 

\textit{And no matter how high the walls } 

\textit{We’re all gonna make them fall-”}

There was a small cheer from the table full of soldiers. Ellerna had decided to pander to her audience tonight, it seemed. The Legionary Song wasn’t exactly a popular ditty in Callow. Not that it was surprising, considering it referred heavily to the Conquest. There was no sign of Harrion anywhere but Leyran was lounging in one of the corner tables, smirking at Ellerna whenever she glanced in his direction. \textit{Ugh. }He’d been trying to talk her into sharing one of the upstairs beds since Harrion had first hired her, and while she’d been lukewarm at the prospect at first these days she seemed inclined to give in. \textit{Bad call, Ellerna. He’s not looking to marry, no matter what his father wants. }The man in question noticed I’d come in a moment after and gestured for me to come closer. I crossed the room, throwing a smile at the pair of women I passed by on my way through. Leyran offered me the closest thing to a roguish smile he could manage, passing a hand through his short-cropped hair as I claimed the seat across from him.

“Catherine,” he greeted me. “Punctual as always.”

\textit{How you manage to come in late for work when you live in the same building is beyond me}, I refrained from saying.

“Leyran,” I replied instead. “My apron’s still under the counter?”

He shrugged. “Right next to the cudgel. Dad wants to talk to you first, though. He’s in his room upstairs.”

Huh. I grunted in acknowledgement and pushed myself up. It was still a few days early for Harrion to need my help with the accounts, so it couldn’t be that. Might just be he needed me to work some numbers for him – half the reason I’d been hired at the Nest was that I knew my letters and numbers. The benefits of being raised in an Imperial-funded institution, I supposed. The stairs creaked under my feet and led me right to the corridor where four doors stood closed: two for the family, two up for renting. Harrion’s own room was where he kept all of his papers, so I’d been there before. Rapping my knuckles against the door, I waited for a moment before pushing it open. A pair of candles was the only source of light in the cramped room: a bed and dresser were wedged in the left corner, with the bare skeleton of a wooden desk facing them. Harrion himself was seated on a stool at the desk and the old man gestured for me to come in without turning.

“Catherine,” he grunted. “I need you to read something for me.”

The owner of the Rat’s Nest was a skinny man with a balding crown of hair, dressed in plain brown wool – he was looking at a piece of parchment I couldn’t quite make out, glaring at the letters like they’d personally offended him. I’m not sure he’d have been able to make them out even if he could read: his eyes weren’t what they used to be, and he’d always balked at the cost of getting a pair of spectacles made. Used to Harrion’s gruff manners by now, I leaned over his shoulder and took a closer look at the parchment. It was an official document, I saw quickly enough: there was a golden wax seal on it that bore Laure’s coat of arms. I skimmed the first few lines, since they were mostly ceremonial claptrap, and got to the meat of the matter: the Governor’s office was sending an official notice by that the end of next month all establishments serving liquor would need to be affiliated with the proper guild or face additional taxes.

“They want to fold you into the Brewer’s Guild,” I voiced. “Otherwise you get another tax hitch – though they don’t say how large.”

“Fucking Mazus,” Harrion cursed. “Fucking Praesi and fucking Empire,” he added after a moment.

I’d heard a lot worse – and more inventive – serving drinks downstairs, so the language hardly fazed me. I could see where he was coming from, too. I’d been told the Guilds had once been a boon, when Callow had still existed, but since Laure had gotten an Imperial governor they’d become little more than a polite protection racket. They collected membership fees every month and required a certain amount of product to be delivered at the guildhall for “quality control” – in exchange for which they were supposed to protect the interests of their members and regulate the trade. The Governor had flipped the situation around by buying out the Guildmasters he could and arranging accidents for those he couldn’t, making them just another finger in the Imperial hand that was choking out Laure.

“The tax might end less costly than a membership,” I said after a moment, at loss for what else to say.

Harrion let out a derisive snort. “They’re greedy, not dumb,” he replied. “The taxes are going to be savage, girl, you can count on it.”

I threaded my fingers through my hair, letting out a sigh. “You won’t be able to afford keeping me on, will you?”

The balding man had the grace to look embarrassed. “Maybe on the busy nights, but not as often as now,” he admitted.

I would have liked to blame him, but it wouldn’t have been right. It wasn’t his fault, was it? He wasn’t any happier about the situation than I was, and it wasn’t like there was anyone to appeal to. Governors answered directly to the Dread Empress, and I doubted that Malicia gave a shit about the fact that her buddy Mazus was being a robber lord all the way out here. As long as the tributes came on time, what did she care? \textit{It’s not fair, but you don’t get fair when you lose wars}, I thought. I felt my fist clench, though I forced it to loosen after a moment. Things like this were exactly why I needed to go to the College. If I got high enough in the ranks of the Legion, if I amassed enough power and influence, one day I’d be in a position to fix this. To send fuckers like Mazus to the gallows instead of watching them throw banquet after banquet up in the palace.

“Should I stay until the end of the month, at least?” I asked.

Harrion nodded tiredly. “I’ll try figure something out, Catherine,” he said. “I know you’ve been saving up for something.”

I smiled but we were both aware the words were an empty gesture. I’d been running the Nest’s numbers for a year now, and there was only so much gold flowing through the place. I went back down the stairs, trying to figure out a way out of this mess. I might be able to scrape enough together if I started fighting in the Pits more often, but that carried risks of its own: losing was always a possibility, and the more I won the harder it would get to make good betting on myself. Booker had implied once or twice that she’d be willing to take me on as an enforcer, but that was a slippery slope. \textit{I’ll sleep on it}, I decided, putting on my apron. I still had a job, for now, and I wasn’t one to shirk honest work when I could get it.

On calm nights like this one I spent as much time cleaning as I did actually getting patrons their drinks. The larder had remained more or less in order since the last time I’d taken the time to arrange it, though, and none of the beer barrels were leaking. I found myself idly passing a rag on the counter for at least a quarter bell before something caught my interest. There were a handful of regulars I was on friendly terms with but my clear favourite among them was Sergeant Ebele – I couldn’t help but smile when she came in. She was tall, taller than most orcs even, and her skin was even darker than mine. In the hotter parts of summer I could almost pass as just particularly tanned, but she was black as charcoal in that way only northern Praesi could be. There was a little scar by the side of her mouth that kept her lips in a perpetual half-smile, which turned into a broad grin when she saw me. I’d already filled her tankard by the time she’d claimed a table, and I wasted no time in bringing it to her.

“You, my sweet,” Ebele said after taking a long pull from her beer, “are a true delight. This place would go to the dogs without you to keep it going.”

A shadow passed on my face at the thought that soon enough that would be the case, but I pushed through.

“Just finished your watch, then?” I asked eagerly.

The sergeant had a friendly disposition that I rather liked, but what I enjoyed the most about her was that after a few drinks she took little prodding to start telling stories about her service with the Legion. She was a veteran of the Conquest, one who’d been on the front lines at the Fields of Streges and the Siege of Summerholm – as well as part of the quick but brutal civil war inside the Empire that had preceded their invasion of Callow. She talked about that part less, though. I got the impression it had been a pretty brutal affair. \textit{And if someone who was at the Fields thinks of something as brutal, I’m inclined to take her word for it.}

“Oh yes,” Ebele muttered. “Hence why I’m here drinking away my sorrows. If I have to hear Goren snicker one more time, I’ll have to strangle the idiot. Be a dear and get me a pitcher, will you? I don’t intend to be able to walk out of here on my own.”

I snorted and disappeared into the larder, filling a clay pitcher to the brim at the tap. One of the few things that redeemed the Rat’s Nest from all the other hole-in-the-ground taverns was that the Harrion didn’t water the beer. It tasted like dead vermin, sure, but at least it didn’t taste like dead vermin marinated in water. Half of Ebele’s tankard was already gone by the time I returned, which boded well for getting stories out of her – though hopefully she wouldn’t keep going at this rate, because her sing-song accent got harder to decipher when she slurred her words.

“Come sit with me, lovely Catherine,” the sergeant grinned when I set the pitcher down. “This place is as dead as can be.”

A quick glance around confirmed as much. Besides the patrons who’d already been there when I came in – and who were already topped off – there was no one else. Including, I noted wearily, Leyran and Ellerna. I tried not to think too much about that. “It’s still pretty early,” I agreed. 

The Nest would get busier the closer we got to the midnight bell, but that wouldn’t be for a while yet. Ebele suddenly leaned forward, taking a closer look at my face.

“You were mage-touched, and recently at that,” she observed, tone surprised.

I blinked. Had Zacharis messed up his spell? There shouldn’t be any visible marks.

“I got into a fight,” I admitted. “How can you tell?”

The dark-haired sergeant’s smile turned rueful. “When you see enough mage-healing you learn to pick up on the signs. Whoever did yours was a little rough around the edges, but it’s good work.”

Huh. Point for Zacharis, I supposed. If he could cast that well hungover, he must have been a fairly good sorcerer when sober. \textit{If he was ever sober.} Ebele paused, appearing to consider her next words, and I prepared to swallow a sigh. People really needed to stop telling me not to get into fights – now more than ever, considering I wasn’t going to be making much of anything from the Rat’s Nest.

“Did you win?” the scarred woman asked.

I grinned. “Beat his ass into the ground,” I replied.

“Good girl,” Ebele chuckled approvingly. “You should consider the Legions, if you want to get into real scraps.”

“I’m saving up for the College,” I admitted. “Hoping to make it there by next summer.”

The sergeant’s hairless brows rose. “The War College? Ambitious of you, though I suppose it’s less expensive since Lord Black pushed the reforms through.”

I’d been born before the reforms – they preceded the Conquest – so I only had a vague sense of what she was talking about. I’d never gotten any real details out of someone about what the reforms actually were, though everyone agreed that they’d radically changed the Legions of Terror. The name she’d dropped caught my attention, though. Well the \textit{Name} if you wanted to be accurate:\textit{ }Black Knight\textit{.} The man who’d led the Calamities in the destruction of the Kingdom of Callow, over twenty years ago. I knew he was still alive and up to no good somewhere in the Empire, but the existence of people with Names had never felt quite real to me. Heroes and their darker counterparts were the kind of people that lived in legends, not in my reality of pit fights and serving drinks.

“You ever meet any of them?” I asked. “The Calamities, I mean.”

Ebele’s half-smile twitched in amusement.

“In person? Only the one,” she said. “Before the Conquest I was part of the Second, when it moved to kick in High Lord Duma’s door.”

The sergeant took a long pull from her tankard.

“My company ran into some of his personal household troops during our push to his demesne – nasty fuckers, with mages and a dug-in position. Could have wasted three hundred people easily to crack that nut, and we couldn’t just leave them sitting on top of our supply lines.”

I leaned forward. Which one of them had it been? Probably not the Black Knight, or she would have mentioned it earlier, and since Captain was famously never far behind him she was probably out too. I doubted Assassin would have stopped for a chat, but maybe Ranger? I hoped it had been Ranger. I’d always liked the stories about her best.

“So we’re starting to set up a palisade around them,” Ebele continued. “Waiting for reinforcements and all that – then out of nowhere, this man strolls up to us. Claps our captain on the back, tells her to get the company ready because they’ll be moving again soon.”

A man? That meant…

“So the captain asks him who the Gods Below he thinks he is, and he gives her this shit-eating grin. ‘Call me Warlock. That scheming bastard sent me to clear you a way,’ and off he goes.”

Warlock. They called him the ‘Sovereign of the Red Skies’, whatever that was supposed to mean – Praesi liked to tack on fancy titles to everything, it was like a cultural compulsion. Came from the centuries of unrepentant villainy, probably.

Ebele’s tone suddenly turned serious, the mirth in her eyes snuffed out and replaced by awe and just the tiniest smidgeon of fear. “We never got close enough to see exactly what he did,” she murmured. “But not even a quarter bell after he disappeared the whole enemy garrison went up in a column of red flames. When we marched through later that night, the whole place was intact. Not a stone or tent out of place, but all the armours were empty. Like the people had just… disappeared.”

I felt a shiver go up my spine. It was one thing for a mage to make fire – it was one of the easiest spells to manage – but what she’d described? That was a different matter entirely. \textit{You don’t get a Name like Warlock by learning the nice sort of spells, I guess.}

“I’ll say this about the Legions, sweet girl,” the sergeant murmured. “The constant drills are a bitch, but at least you know whenever you step on a battlefield that all the scariest fuckers are on your side.”

I nodded slowly, but before I could say anything a group of patrons walked in. I gave Ebele an apologetic shrug and got back to work.

The walk back to the orphanage was always the worst part of the night.

There were risks to bar tending in the bad part of Laure, I knew, but it wasn’t like taverns in the Merchant Quarter were lining up to hire sixteen year old orphans. I’d tried my luck more than once and been shown the door before deciding that the Rat’s Nest my golden chance. Besides, eavesdropping on drunken veterans reminiscing was more interesting than doing the same on pretentious guild members. Once in a while a patron would get grabby, true enough, but that was why we had a cudgel under the counter. They rarely needed to be told to lay off twice, and those that did limped home with a few broken fingers for their trouble. The matron back at the Laure House for Tragically Orphaned Girls was deeply offended I’d do anything as uncouth as serving drinks to ruffians, but I only had to suffer her lectures for another year before I was free. I was perfectly willing to spend half a bell in the old woman’s office getting upbraided for “consorting with unsavoury elements” if it meant that by the time I was sixteen I’d have enough to cover my tuition. Not that I’d told her that was what I was saving for: if her feathers were ruffled by my serving drinks Lakeside, she’d have a fit at learning I wanted to enrol in the officer’s school for the Legions of Terror. It wasn’t too far past the midnight bell when I finally headed out home, and making my way back to the House after dark wasn’t as dangerous as one would think, anyway: the city guard was hopelessly corrupt and in the Governor’s pocket to boot, but they were well aware that if they failed to keep order in the city then the Legions would step in. 

There were a lot of people who wanted that to happen, funnily enough: the Legions were a little heavy on the hangings, they said, but at least when Laure had been under martial law everything ran smoothly. Still, as long as Mazus remained in bed with the Guilds and kept the guards on his payroll there was nothing anyone could do about any of this. Rioting would just mean a lot of spiked heads over the city gates when the legionaries were done clearing the crowd: the Dread Empire of Praes did not brook dissent, much less open one.

That said, there was a reason the Lakeside was known as the rough part of town and I had no intention of lingering in the darkened streets. I wished I had a knife on me, honestly, but the only time I’d tried that the matron had confiscated it when one of the girls in my dormitory ratted me out. I’d never been popular with the others, and they weren’t above getting back at me in petty ways when they could. I was about halfway back when a shriek followed by the sound of struggling drew me out of my thoughts – it was coming from a side-alley, one of the myriad of dead-ends that filled this part of town. 

I peeked around the corner and felt my blood rise when I saw the silhouette of a guard pushing a girl down. Her blouse was already ripped open, but she seemed more intent on begging the man to leave her alone than fighting back. \textit{Shit.} This was the kind of thing a reasonable girl would walk away from, ugly as that reality was.

\textit{Why couldn’t I have been born a reasonable girl?}

I had no intention of scrapping with a man in armour at least a foot taller than me, but I might be able to get the other girl and run if I played this right. Unlike the guard I didn’t carry a weapon, but if I hit him hard and fast I might knock him out before it ever turned into a struggle. Reckless, maybe, but what was I supposed to do – just cover my ears and go on my merry way? I stepped into the alley as silently as I could, catching sight of a ramshackle crate full of rotting cabbage as I did. My fingers closed against the edge of it and I closed the remaining distance separating me from the guard in a handful of steps, swinging the crate into the back of his head. It broke with a satisfying crunch, putting him down as the girl he’d been pushing himself onto let out a fresh new shriek of terror. I kicked the guard in the chin to make sure he wouldn’t get back up. The girl in the ripped-up blouse was backing away from me, apparently as scared of me as she was of her tormentor. A pointless gesture, that: the alley ended in a wooden wall, there was nowhere to go but through me.

“I’m here to help,” I told her soothingly. “Come with me, we need to get out of here before-”

I never got to finish the sentence, as a vicious hit to the temple sending me tumbling to the ground. The world spun but I tried to push myself up only to come face to face with a bared blade. I looked up into the eyes of a second guard, this one wearing sergeant stripes on his shoulders. His face was grim as he kept the tip of his short sword less than an inch away from my throat.

“Joseph,” he said calmly, “are you all right?”

The man I’d hit with the crate rolled over with a groan, getting back on his feet gingerly.

“The bitch did a number on me,” he spat. “That’s going to leave a bruise for sure.”

“Be glad she wasn’t carrying a knife, you idiot,” he retorted.

“He was trying to rape the girl,” I wheezed. “Why the Hells am I the one getting hit?”

A flash of disgust went through the sergeant’s face, but he refused to meet my eyes.

“You said you’d stop doing shit like this,” he spoke, ignoring me in favour of staring down his colleague. “You promised, Joseph.”

‘Joseph’ waved him off.

“No one would have cared if she hadn’t run into me, Allen,” he replied. “We can just break a few fingers to teach them manners and go home, our patrol is almost done.”

The sergeant – Allen, apparently – sighed.

“Look at her blouse, Joseph. That’s the heraldry for the Imperial orphanage sewed up over her chest. She shows up home with broken fingers and people are going to ask questions,” he said.

The would-be rapist’s eyes widened in fear.

“Fuck,” he cursed again. “What do we do? I can’t go to jail, who’s going to feed my kids? Bessie doesn’t even have a job.”

I snuck a glance towards the girl. She was huddled in a corner, shaking life a leaf and trying to hold her ripped clothes together. There was an absent look in her eyes, like she was there but not really \textit{there}. No help coming from that direction, then. This… wasn’t looking too good.

“We’ll have to kill them,” the sergeant said flatly. “No blades, that would lead to too many questions. We came across their bodies during patrol, no witnesses and no suspects.”

And the Hells with that. I moved fast, slapping away the hand that held the sword as I tried to hoist myself back up to my feet. It loosened his grip but he rammed the cross guard of the sword into my shoulder – I was already halfway up by then so it staggered me back a step, screwing up my footing. I tried to push down the panic welling up in my chest, but the awareness that I was stuck in a dead-end alley with two armed men larger and stronger than me wasn’t exactly helping. I scratched the sergeant’s face as he tried to wrestle me down, my nails drawing blood on his face and a hiss of pain from his lips. It wasn’t enough: he’d dropped his sword at some point and he slammed me against the wall, forcing down my struggling hands and moving his legs so that I couldn’t get a decent angle to kick him.

“Joseph,” the man said in strained voice. “Get the other one. But first promise me this is the last time. We can’t keep on doing this.”

Joseph licked his lips, nodding nervously.

“Yeah, it’s the last time,” he muttered. “I mean, I didn’t want anyone to get \textit{killed} over this.”

A moment later the sergeant’s hand settled on my throat and started to squeeze. I tried to punch him and wrestle away his hand, but he was stronger than me and I was trying to breathe but-

“Should never have stepped into the alley, girl,” Allen said. “These aren’t days for playing hero.”

“Always a mistake, gloating before the business is done,” a voice commented mildly.

There was a streak of movement and an enormous silhouette moved out of the dark, slapping down Allen effortlessly and picking up the other man by the scruff of the neck. I gulped in a mouthful of air greedily, coughing a handful of times before I was finally self-possessed enough to look around me. The girl was still cowering in a corner, looking catatonic, and a man was kneeling next to her. He wrapped a thick dark cloak around her shoulders before rising back to his feet, eerie pale green eyes meeting my own. He was pale-skinned and decked in plain steel plate, though he’d moved as if the pounds of metal he was wearing were light as a silk shirt. My eyes flicked to the sword at his side before turning to the other new presence in the alley. It was a woman, or at least vaguely shaped like one: she stood at least three feet taller than I and twice as wide, keeping the struggling Joseph up in their air by the scruff of the neck without any visible strain. I couldn’t see whether she was armed: her cloak covered her body up to her neck. I pushed myself up, forcing down a cough and uncomfortably aware that the green-eyed man was staring at me. Allen looked like he was about to crawl back to his knees, so I kicked him in the chin with a twinge of vicious satisfaction.

“Staying down would be the wiser choice, sergeant” the man said. “You might find the consequences of further resistance unpleasant.”

“Thank you,” I croaked out at the strangers. “I thought I was done for.”

The man dipped his head in acknowledgment.

“Captain,” he spoke up without even looking at the gargantuan woman, “if you would silence our other friend?”

She drove her fist in Joseph’s stomach faster than my eye could follow, getting a gasp out of him that was almost a retch, and then knocked him hard enough on the temple that he slumped. She’d never stopped holding him up during any of this, and still didn’t seem particularly inconvenienced when she slung his unconscious body over her shoulder. Allen let out a strangled noise.

“I know who you are,” he wheezed out. “You’re the Black Knight. Sir, \textit{we’re on your side}!”

I took half a step back, feeling my stomach twist up in unashamed fear. Hitting a guard from behind had been something, but if the sergeant was right then I was less than ten feet away from the godsdamned boogeyman. \textit{Shit, of all the people who could have walked into the alley. }The green-eyed man had a body count that would make most butchers retch – there wasn’t a man or woman in Callow that didn’t know the Name. And if that was really \textit{the} Captain holding up the other guard, then I was all sorts of screwed: the stories said she’d once killed an ogre with a single hammer stroke. Gods, looking at her now she had to be at least eight feet tall.

“No,” the Knight murmured. “You really aren’t.”

An armoured foot whipped out and the sergeant joined his accomplice in the realm of dreams.

“If memory serves we have a safe house a few blocks down, Sabah,” he added after a moment. “Let’s keep them there for the moment.”

Captain raised an eyebrow.

“We’re not taking them to the guard?”

“Mazus would hear of it before the hour was done,” the Knight replied. “No need to give him any advance warning.”

“And the girl?”

They both glanced at the victim, still huddled in her corner and shaking like a leaf under the Black Knight’s cloak.

“Have one of the men bring her home,” he decided. “She’s had quite enough excitement for the night, I think.”

The behemoth of a woman saluted, the would-be rapist still slung over her shoulder, and picked up the sergeant’s foot. She dragged him across the ground none too gently and crossed the corner.

“Are you-” I croaked out, throat still sore from the choking, “are you really him?”

The dark-haired man smiled, though it did not reach his eyes. They were cold as ice, their eerie shade of green sending a shiver down my spine – I knew people with green eyes, but none quite as pale as his. They looked the way I imagined a fey’s would, and there was no denying the touch of strangeness there was to him. He hadn’t even replied but just the weight of his attention made me feel like a rabbit in front of a wolf, like my life could be snatched right out of me in the blink of an eye. I guess some people would be cowed by that, but I’ve always \textit{hated }feeling afraid. The other girls at the orphanage had never understood why I kept going up to the roof and standing on the edge when everybody knew I was afraid of heights, but they were missing the point. I’d kept going \textit{because }I was afraid, and I’d refused to stop even when they’d started whispering to each other about how I was going to turn into a gargoyle if I kept standing there glaring at the ground. I wasn’t fool enough to think that fighting through a childish fear of heights and staring down the smiling monster in front of me was the same, but the principle was the same. My fear did not own me – I owned it. I met the Black Knight’s eyes, refusing to flinch even as his smile stretched wider. \textit{You might be a wolf, but I am no rabbit.}

“Am I the Black Knight?” he murmured. “Yes, among other things.”

The weight I’d been feeling disappeared as swiftly as it had come into existence and I let out a breath I hadn’t known I was holding. Had he been doing it on purpose, or had all of that just been in my head? The fear hadn’t felt natural, even less now that it wasn’t choking me up.I was wary of giving the man many name but it would have been rude not to, after the way he’d just saved my hide.

“I’m-”

“Catherine Foundling, of the Imperial orphanage,” he finished, and my blood ran cold.

How did he know my name? Had I been marked for death for some inscrutable reason? I hadn’t done anything illegal, as far as I knew, or associated with anyone stupid enough to go against Imperial authority. No, I reassured myself, if he wanted me dead he wouldn’t have intervened when the sergeant was choking me. Then how-

“Haven’t you heard, my dear?” he spoke with a sardonic twist of the lips, “I know everything.”

I knew on an intellectual level that what he said was impossible but right now, standing in the dark alley by the unconscious bodies of two men who’d been slapped down effortlessly, I could almost believe it. “You’re not in any trouble, regardless.”

“Gotta say, you’re not selling that impression very well,” I replied before I could help myself.

I winced as soon as I processed the words that had come out of my mouth. \textit{Splendid notion, Catherine, let’s mouth off to the guy who could run you through and not even be questioned about it. I need to get punched in the head less often.} To my relief, he chuckled.

“You’ll have to take my word for it, I suppose,” he replied.

I wasn’t sure exactly what that was worth, but I wasn’t in a position to argue.

“I’ll require your company for a little while still, I’m afraid,” he continued.

I frowned.

“What for? You told… \textit{her},” I said, hesitant to actually use Captain’s Name, “that you weren’t handing them to the city guard yet.”

I couldn’t imagine what use he could have for me aside from a witness, and even then he hardly needed that. If the Empress’ right hand thought some people needed killing, they died. It was as simple as that, and anybody fool enough to protest was likely headed in the same direction. Black smiled, and not for the first time that night a shiver went up my spine.

“I’ve come to believe, over the years, that those who are wronged should have a say in how that wrong is redressed.”

With a last glance towards the girl whose name I had never even learned, who was already being helped up by a silent silhouette in a dark cloak, I followed him out of the alley.

The place was as close as he’d said, not even long enough of a walk for me to start thinking about anything but how nervous I was feeling.There was nothing distinguishing the safe house from any actual house in the neighbourhood, except of course for the dozen of armoured soldiers in heavy plate standing in front of it silently. So much for subtlety, then. Not that I was complaining: not even a full patrol of the city guard would feel up to tangling with those guys. Or girls, maybe? It was hard to tell with the way the helmet’s visor covered their faces and the plate obscured their body shape. I knew who they were, anyway. 

They were called the Blackguards, because Praesi had this strange fixation with shoving the word black into everything. They were the Knight’s elite bodyguards and the veterans from the Fields of Streges I’d eavesdropped on said every one was supposed to be the match of ten fighting men. They said that about a lot of people, though. The Conquest had been so overwhelmingly one-sided of a war that I thought one of the ways Callowans dealt with the trauma was by putting the conquerors on a pedestal. He went through the door after affording them a nod and I followed him without a word.

Captain – who was nowhere in sight – or one of the faceless soldiers I’d seen standing outside must have lit the candles inside, because there was a handful of them dispersed around the room. There was a ratty bed in the corner and a table flanked by a pair of chairs, but besides that the furniture was sparse. Nothing worth robbing unless you were truly desperate. The guards had been tied up and gagged, propped up against the wall in the back. Both were awake now, and neither of them was doing all that good of a job at hiding their terror. 

The Black Knight ignored them and I followed suit, taking the other chair after he seated himself. The candlelight allowed me my first clear look at the man and I took the opportunity shamelessly. How many occasions to see the man up close was I going to get? He had one of those ageless faces that could put him anywhere from his mid-twenties to his mid-thirties, which was a pretty spry look for him considering word had it he was nearing sixty. Roles did that sometimes, slowed aging or kept you looking the same. I still wasn’t all that clear on what he wanted, but if he wasn’t going to say anything then I had a few questions of my own.

“So, what will happen to them?”

Black drummed his fingers on the table, the shadows cast by the candles on his face twisting about as if they’d come to life.

“They’ll be handed to the city guard for trial and punishment. Since Laure is no longer under the authority of the Legions, Imperial law takes precedence. Attempted rape should fetch them a minimum of five years in a cell – less for the good sergeant, given that he was only an accomplice.”

Five years. That was… They’d tried to \textit{rape} her, and when I’d stopped them they’d tried to kill me so they’d get away with it.

“That’s it?” I said. “After all they did, they spend five years in a prison eating badly and then they’re back on the streets?”

He raised an eyebrow.

“You underestimate the unpleasantness of Laure’s penitentiaries, but in essence you are correct.”

“It’s not enough, for what they tried to do – for what they would have done, if we hadn’t been lucky enough for you to show up,” I growled.

The pale-skinned man I’d heard so much about growing up eyed me in silence, his face unreadable. The stories simmered in the back of my head, each less believable than the last. \textit{He once rode a dragon. His sword feeds on the souls of the innocent and that’s why he never lost a duel. He sees the future and reads the minds of his enemies. He conquered Callow in a month by turning his entire army into werewolves. The orcs worship him like a god and he’s king of the goblins.} There’d been a story about how he had the blood of giants running in his veins, but given that he fell way short of six feet tall I felt safe dismissing that one. Hopefully the mind-reading was the same kind of deal, because as far as I was concerned no one belonged inside my head but me.

“There’s another way,” he finally said.

Slowly, carefully, he unsheathed the knife hanging at his belt and put it down on the table. I eyed the blade warily, the edge of it looking wicked sharp even from where I was sitting.

“Do you know what separates people who have a Role from people who don’t, Catherine?” Black asked.

I shook my head.

“Will,” he said. “The belief, deep down, that they know what is right and that they’ll see it done.”

My throat caught. Was he implying what I thought he was?

“So tell me, Catherine Foundling,” he murmured, his voice smooth as velvet. “What do you think is right?”

He spun the knife so that the handle faced me, the touch of his fingertips deft and light.

“How far are you willing to go, to see it done?”

I could feel the eyes of the two gagged guards on me, but I ignored them. I met the Knight’s stare squarely, my heart thundering in my chest. The lives of those two men had just been dropped in the palm of my hand, and if I wanted to snuff out the light in their eyes all I had to do was squeeze. Could I really do that? Did I have the right to take justice into my own hands? It would be murder to kill them, every moment I’d ever spent in the House of Light told me as much. \textit{Five years}, I remembered. \textit{Five years, and then they’ll be out there again}.

My fingers closed around the knife. 

I rose to my feet and Joseph’s eyes widened in fear when I knelt in front of him. There was nothing in the room, nothing in the world besides the two of us. My palm felt clammy against the knife’s leather wrap, but I tightened my hand and pushed down his gag. If I did this, if I was really going to do this, I had to know. I could feel the Knight’s gaze on me but this wasn’t about him. It was about me, about the decision I had to make. All my life I’d told myself I would somehow manage to get power and that I’d used it to \textit{fix} things. To make it all better. And now here I was, gifted the power of life and death over two men in the form of a few inches of cold steel.

“You’ve done this before,” I half-asked, half-stated.

He looked ashamed for a moment, but there was something in his eyes that caused disgust to well up in me. Like he didn’t understand how foul what he’d wanted to do was.

“Look,” he said, “I didn’t meant to. It was just, the way she was dressed… I mean, what kind of a decent woman goes about at night-”

I slit his throat.

It wasn’t a conscious decision. For what he said and what he’d done, I’d decided he deserved to die – my hand had done the rest without any need for prompting. Edge parallel to the ground, slicing across the major arteries just like the butcher did it to pigs in the marketplace. Maybe if I’d gone at the House of Light more often I would have let him go to prison, but all I could think was – what would happen, when he got out? The next time he cornered a girl in the middle of the night, I wouldn’t be there. I watched as the blood gurgled out out of his throat and he looked at me like I’d somehow betrayed him. I wondered if I should be feeling anything. Sadness, regret, maybe just nausea at the sight of death unfolding. \textit{He probably wouldn’t have made it as quick for her}, I thought. The sergeant looked resigned when I turned towards him. He took a deep breath and closed his eyes. 

My cut was cleaner the second time.

I stayed there kneeling for a while, blood dripping off the blade. Funny thing, killing someone. You’d expect there to be more of a fanfare to it, thunder in the distance or the weight of the disapproving Heavens pushing down on your shoulders. All I felt was a little numb. The palm of my hand was a little bruised from the way the knife’s handle had pushed back when slicing through, and there was blood spray on my blouse. \textit{So I’m a murderer now. Not how I saw my evening going, I’ll admit.} The jest was tasteless but I smiled anyway, because feeling like a heartless bitch was still better than this… apathy that had taken me.

“Is this how it always is?” I asked, eyes still on the cooling corpse of the sergeant and the red smile I’d etched across his throat.

“When you make the decision cold?” I heard the Knight speak from just behind me. “Yes.”

I nodded and a moment later didn’t resist when he helped me get up to my feet.

“They deserved it,” I told the man, looking into his eyes.

He did not disagree.

“They deserved it,” I whispered to myself.

He steered me towards the door and I could have cared less about our destination as long as it got me away from that house. The night air felt cool against my face and I heard one of the Blackguards enter into the house but I refused to pay any attention to it.

“I have a question for you, Lord,” I said after a moment, my voice feeling like it was a stranger’s, coming out of a stranger’s body.

“Call me Black.”

“I have a question for you, Black.”

“I’m listening.”

“You’re a monster, aren’t you?” I spoke softly into the night, looking at him from the corner of my eye.

He smiled. “The very worst kind,” he replied.

I don’t know what it says about me, but for the first time since I’d walked into the alley I felt safe.
\clearpage
\chapter{Chapter 2: Invitation}

\textit{“Before embarking on a journey of revenge, dig two graves. One for the fool and one for all those pesky relatives.”}
– Dread Emperor Vindictive the First

I took me a moment to remember where I was when I woke up. 

\textit{Who knew that slitting a pair of throats would take that much out of you,}

\textit{Not that it changes anything. I made the decision, and made it for my own reasons.}\textit{Not too sure how I should feel about that.}

So. What now? 

I was starving, so I might as well see if I could get a meal of this. I didn’t get the feeling that this whole business was done, but what more could the Knight want from me? \textit{No, that’s the wrong way to think about this.} If he wanted something, he’d get it: I didn’t have the power to stop him. What I needed to think about was what I could manage to get out of this mess. It wasn’t like I was going to run into anyone that high up the Empire’s ranks again anytime soon, so I had to find an angle. I’d bought this opportunity with blood, so I’d be damned if I didn’t make it count. The Black Knight had a lot of pull in War College, I remembered hearing – which made sense, since he more or less commanded the Legions the cadets were being formed to join. Maybe if I played my cards right I could talk him into getting me a place in this year’s classes. At the moment I had almost enough to cover my tuition, but the trip to the Wasteland was another expense, and not a cheap one. I was pretty sure a word from the Empress’ right hand would take care of that swiftly, though. The only other obstacle I could think of was that anyone wanting to go into Praes proper from Callow would need papers, but for once being an orphan would be an advantage: the orphanages were an Imperial institution, so every one of us had been registered at the Governor’s office. 

Most Callowans still weren’t registered, since forcing it after the Conquest would have caused the kind of civil unrest that the Empire had aimed to avoid, but it was becoming more common as time passed- there were all kinds of restriction on the kind of offices you could hold if you weren’t. A lot of the older generation muttered under their breath that having your name on Imperial record couldn’t possibly end well, and to be honest I wasn’t sure if they were wrong. I’d served drinks and talked to enough legionaries that I no longer believed that they were always one moment away from malevolently setting fire to the city and dancing in the ashes – they had a better reputation than the city guard, these days – but those records were made for people back in Ater, the Empire’s capital. From what I’d heard of the nobles that dwelled in the City of Black Gates they were not the kind of people you ever wanted to have your name. Even other Praesi spoke of them with distrust.

My blouse was still bloodstained from last night, I saw as I inspected my reflection in the mirror hung up on the wall. There were flecks of dried red on the blue in the shape of the blood spray that had been two men’s lives and I didn’t feel like walking through the streets with that damning mark on my clothes. It looked like they’d thought of everything: there was a long-sleeved shirt and a pair of trousers neatly folded on the dresser. I changed unhurriedly and slipped on my boots before leaving the room, procrastinating out of apprehension. Bad habit, I knew, but given the circumstances I was willing to let it slide.

A short flight of stairs down brought me to the inn’s common room. It was deserted, which was unusual at this time of the day: there should have been travellers from outside the city trickling in and regulars huddled around their usual tables. Laure had been the capital of the Kingdom of Callow, before the Conquest, and even under the Empire it remained one of the wealthiest cities around. Whose pockets that wealth ended up in was another story, but given that we were a major trade centre the good inns should be packed around this time of the year. No trace of the innkeep either, just a lone woman sitting at one of the tables by the hearth. She had a stack of paper around her and was writing on a sheet of parchment, dipping her quill with clockwork regularity. She hadn’t raised her head from her work as I made my way down the stairs, so she must not have heard me.

“Take a seat,” she spoke calmly, eyes still intent on the parchment.

… Or maybe she had. I claimed the chair across from her, not sure where I was supposed to go from here.

“The innkeeper will be along momentarily with breakfast,” the stranger said.

I nodded, then felt foolish when I realized she hadn’t so much as looked at me yet.

“I’m-” I started.

“I know who you are, Catherine Foundling,” she cut in indifferently.

I raised an eyebrow.

“This is starting to be a pattern,” I said. “What should I call you?”

“Scribe.”

\textit{And that’s you shouldn’t mouth off to strangers. Again.}\textit{very}

“Ma’am,” he greeted me. “Lady Scribe, are you sure I can’t offer you tea or wine?”

“That won’t be necessary,” she replied.

It was reassuring to see I wasn’t the only one she wouldn’t raise her head for. The man slunk back to his kitchen after a respectful bow, leaving me to dig into my first meal of the day. It wasn’t the fanciest of fares, but it was fresh and I was starving: I’d never eaten a better meal in my life. By the time I was polishing off the last of the sausage Scribe finished whatever it was she was doing, signing at the bottom of the parchment with a flourish before resting the tip of her quill against her inkwell.

“Black should be back before the evening bell,” she told me. “He’ll be wanting to speak to you.”

I didn’t reply immediately, partially because I wasn’t sure how I felt about the most famous villain of our age wanting to speak to me again but also because I was studying the woman sitting across from me. She was rather plain-faced in appearance, with ink-stained fingers and a diminutive stature. \textit{Though given we’re about the same height, maybe I should have used more flattering phrasing.} She lacked the presence Black and Captain had shown yesterday, the way they could fill up a room just by standing in it. I would have been skeptical she even had a Name, if not for the way she’d effortlessly picked out my presence earlier. There was something tightly contained about Scribe, and I reminded myself that a Name didn’t have to involve fighting to be dangerous.

“Any idea what he wants to talk about?” I asked.

“The matron at your orphanage has been notified you’re still alive,” she replied, ignoring the question entirely. “She was getting worried.”

I let out a vaguely thankful noise. I didn’t dislike Matron Nelter, even if her lecturing sometimes got on my nerves. She didn’t approve of my working at the Rat’s Nest, sure – and would have thrown a fit of epic proportions if she’d been aware I fought in the Pit – but then the Laure House for Tragically Orphaned Girls had a history of setting up its wards for work more glamorous than serving drinks. Girls usually left the orphanage with enough education to pick up a trade or serve as tutors for noble children. That she took the time to get on my case meant that she cared, in her own way. Scribe seemed to have decided our conversation was over, because she pulled out a fresh sheet a parchment from the pile and dipped her quill. As it turned out, she was right about the Knight being back soon: I’d finished the sausage and I was halfway through a mug of tea when he strolled into the common room.

“Good evening, Catherine,” he greeted me cheerfully. “Scribe.”

“Black,” the plain-faced woman replied, and I had to give her points for the amount of guts it took to snub the godsdamned \textit{Black Knight} in favour of a sheet of parchment.

“The numbers confirm it?” he asked, apparently used to her cool indifference.

“Yes. Not that it matters, given the confession. Captain?”

“Having a talk with Orim as of this moment.”

Some of that had gone over my head, but the last name was one I recognized. General Orim – Orim the Grim, his legionnaires called him with a fond smile – was the head of the Fifth Legion, which served as Laure’s garrison. I finished the last of my tea, waiting for my turn.

“Catherine,” Black said after a heartbeat, turning to face me, “you…”

He paused.

“Look like you have a question?” he finished.

“This is going to sound a little strange,” I prefaced myself. “But I mean, I’ve heard stories and I think it needs to be asked. Could save a lot of trouble down the road and all.”

He raised an eyebrow, remaining silent.

“So, uh, just to be sure,” I said. “You wouldn’t happen to be my long-lost father who put me in an orphanage so I’d be safe from his enemies and is coming to get me now that I’m old enough to take care of myself?”

To my mild horror, I drew a laugh out of the monster sitting across from me. He seemed genuinely amused by the question, so I guessed I was still an orphan. \textit{Thank the Heavens for that}, I thought. Still, that meant I was now drawing a blank as to why he’d taken an interest in me.

“No,” he replied, “I’m afraid I had no hand in your conception. Besides, one is never quite old enough to deal with the kind of enemies I have.”

“I can imagine,” I said, though I really couldn’t.

Couldn’t think of a lot of people who’d worry the man sitting across from me, truth be told. There was only one Duchess left in Callow and the woman in question was Deoraithe, who didn’t really want anything to do with the rest of the country. The idea of her leading a rebellion against the Empire was pretty laughable, and there were no other nobles left with enough pull. The First Prince of the Principate, maybe? Rumours had it she’d finally put an end to their civil war, so they were probably going to start looking at their neighbours again.

“Speaking of questionable individuals,” he said, “I was hoping we might have a word on the subject of the Governor.”

I raised an eyebrow.

“I’m told most of the words I’d use for him aren’t supposed to be spoken by proper ladies.”

“Are you?” he smiled. “A proper lady, that is?”

I snorted. So he wanted to talk about Governor Mazus, huh. I could do that. He might not like what I had to say, but I could do that.

“He’s probably the most hated man in the Empire,” I told him honestly. “Nobody speaks up because if you do the guards come knocking at your door, but I don’t think there’s a lot of people in Laure who wouldn’t shank him of they thought they could get away with it.”

Black let out a thoughtful noise, sipping at his cup.

“I was under the impression he was on good terms with the Guilds, at least,” he said.

I shrugged.

“With the amount of gold he’s been throwing at the guild masters, that’s kind of a given,” I replied. “The few that didn’t want anything to do with him met unfortunate accidents and their replacements were a lot more cooperative.”

“Unfortunate accidents?” he probed.

“He’s not even being subtle about it,” I scowled. “Tara Goldeneye – she was in charge of the Spicer’s Guild and told him she’s rather go broke than take his bribes – drowned in a bathtub that barely had a inch of water in it. And don’t even get me started on the city guard.”

“I take it incidents like yesterday aren’t unheard of?”

“They do what they’re supposed to, mostly,” I conceded. “But it’s an open secret they’re his thugs and they tend to get rough when they collect the extraordinary taxes.”

His lips thinned.

“Ah yes, the famous taxes. He’s been making quite a stir back in Ater with those.”

“Funny the way they’re all temporary but somehow never go away,” I grunted.

The taxes were the main reason Mazus was so hated. Everyone expected whatever Praesi the Empress appointed Governor to try to turn Laure into his personal fiefdom, but after a decade of the Legions running the city people had become used to the people in charge being even-handed. As long as you didn’t make a mess or commit a crime, the legionnaires didn’t really care what Callowans did. Mazus poked his nose in everything, and the nose was usually followed by a hand that grabbing for more gold. 

Food prices had been steadily hiking up for the last few years, and I’d heard people complain that merchandise that wasn’t guild-approved was tariffed heavily. And since the guilds took a take of anything they approved – which Mazus got part of, of course – just the cost of joining could put smaller merchants out of business. More than being unfair, the whole thing infuriated me because it was \textit{stupid.} Laure saw nowhere as much business as it had a decade ago, and these days at least half of the people at the Summer Fair were locals. The man was so focused on squeezing everything he could out of the city that he didn’t realize he was strangling it.

“It’s sheer idiocy,” Black agreed, and I nearly jumped out of my skin.

Could he actually read minds, of had I said any of that out loud?

“Your face said it all,” the green-eyed man told me with an amused smile.

My pulse quickened. I wasn’t entirely sure he was telling me the truth. But he was agreeing with me. \textit{Why? }Wouldn’t more gold for the Empire be good from his point of view, regardless of how Mazus got it? Even if the situation ended up blowing up in the Governor’s face, the Legion garrison would be enough to put down the riots. I had a dozen questions on the tip of my tongue, but I wasn’t so sure I should ask them. He’d been reasonable so far, almost affable actually, but it wouldn’t do to forget that the man across from me had brought an entire kingdom to its knees. 

Maybe another girl would have thought that the way he kept smiling meant he was my friend, but I didn’t have any of those to confuse him with. And yet, I could feel that same old itch under my skin. The need to know \textit{why }instead of stopping at “this is how it is”, the compulsion to understand the way everything around me worked. And he’d been the one to make this a dialogue, hadn’t he? He could have made it an interrogation – Hells, he could have asked someone better informed than a sixteen year old orphan girl – but for some reason he’d taken pains to prevent this from being one-sided.

“If he’s an idiot,” I spoke up against my better judgement, “then why is he Governor?”

Nothing about the Knight’s face visibly changed, but there was a distinct feeling of… satisfaction to him. The kind people got when they were proved right about something.

“Mazus wasn’t actually expected to make anything of himself here,” he said. “It was a purely political appointment.”

“The Empress wanted to reward him for something,” I guessed, “so she gave him the richest city in Callow to rule.”

“It wasn’t a reward,” Black replied, “it was a bribe. His father is a High Lord and after the Conquest we needed to appease them.”

I blinked in surprise.

“Appease them?” I burst out. “She’s the \textit{Empress, }why would she need to appease anyone?”

The green-eyed man finished the last of his wine and put the goblet aside.

“You’re thinking of power as an absolute, but that’s a false perception. If the matron of your orphanage put on a crown and proclaimed herself Governess of Laure, would that somehow grant her authority over the city?”

“I’m guessing that’s a rhetorical question,” I replied drily.

He hummed in agreement, warming up to his subject.

“It’s the same with Malicia. Sitting on the throne doesn’t mean all of Praes obeys her every whim. She needs the backing of other people with power or her authority remains little more than a polite fiction.”

His tone of voice wasn’t all that different from the one the better tutors the orphanage hired used when they spoke about their favourite subject, which was just… odd. The image of the middle-aged scholar in charge of our lessons didn’t interpose all that well with that of the villain in front of me.

“So she needs all the High Lords on her side?” I asked.

A sardonic smile quirked his lips.

“That would be quite the achievement, given the way they hate each other almost as much as they hate her,” he murmured. “No, she simply needs enough of them under her thumb that the others think rebellion isn’t feasible.”

“And the best way to get the people she needs on her side is to give them a nice Callowan city to get taxes from,” I frowned. “Even if that means the people who live in it get stuck with a bastard like Mazus.”

“More or less,” he agreed. “The crown receives a certain part of the taxes he collects, which has been a much larger amount of gold than anticipated for the last few years. Questions have been raised, as a consequence.”

I raised an eyebrow.

“The Empress isn’t pleased she’s getting more than she thought she would?”

Black’s eyes turned cold.

“Gold doesn’t grow on trees, Catherine. Concerns have been raised about how well Laure is doing under that kind of a burden.”

I let out a thoughtful noise.

“You’re worried you’re strangling the golden goose,” I mused.

His hand waved dismissively.

“That’s part of it, of course, but ultimately it’s a minor issue. The real problem is that he’s been causing unrest.”

“Not that the idea of the Legion putting down a riot isn’t all kinds of horrifying,” I said, “but aren’t they there exactly to deal with that kind of thing?”

I grimaced at myself, a little worried by how easy it had been to slip into the Imperial mindset. I planned to go into the Legions myself, sure, but I’d made that choice with the idea in mind that when I rose up high enough in the ranks I’d be able to prevent the very kind of thing I was talking about. Black poured himself a fresh cup of wine, silently offering to do the same for me. I shook my head. I wasn’t that I disliked wine – I’d tried it a few times at the Rat’s Nest and found I enjoyed some kinds – but I’d just eaten breakfast and it couldn’t be that late anyway. Praesi started drinking early, though, so I wasn’t exactly surprised he was on his second cup.

“They could suppress riots easily enough,” Black conceded. “But there would be consequences.”

Should I, or shouldn’t I? \textit{Hells, wouldn’t even the most insolent thing I’ve said to him yet.}

“I didn’t think dead Callowans was something you’d worry about all that much, sir.”

I took pains to keep my tone polite. It was one thing to tug the dragon’s tail, another to stick out your tongue at him at the same time.

“I abhor waste,” the Knight replied, apparently nonplussed I’d just implied he was an unrepentant mass-murderer. I supposed I wasn’t the first to do so. “And all killing the rioters would accomplish is driving the resentment underground.”

He put aside his cup.

“The problem is broader in scope, Catherine. Take two nations, of roughly the same population. One annexes the other, but has no real legitimacy in doing so other than force of arms. How does one keep the annexed nation from rebelling?”

I wasn’t sure why he was keeping the names of Praes and Callow out of his hypothetical exercise given how glaringly obvious it was what we were talking about. Detachment, maybe? I guess it was easier to talk about… unpleasant measures if I wasn’t outright talking about my countrymen. Still, that was a mighty thing fig leaf.

“Use the Legions – I mean, the conquering nation’s armies – to turn the screws on anybody who steps out of line. Hang enough people and nobody’s going to pick a fight with you,” I said after a moment.

In some ways it was a lot easier to rule when you were Evil. Pesky little concepts like justice or not murdering your way out of situations weren’t something you had to worry about.

“Ah, rule through fear,” he mused. “That works, to an extent. It’s a delicate balance to maintain between having people fear you enough they won’t revolt and them being so terrified they think they have nothing to lose. Which is why, when someone does drive the people to that level of terror, it is necessary to step in.”

It clicked into place, like one of those fancy metal puzzles they sold in the marketplace.

“Mazus,” I realized.

“The policy of the Empire is to \textit{use} Callow, not abuse,” Black said. “The Governor is doing more damage than he knows.”

I kept the mild sense of disgust that caused in me away from my face. \textit{Who even says something like that?} Yet even of that was still fairly evil, as far as policies went, at least it wasn’t stupid. I’d pick having in charge a competent monster over a vicious idiot any day.

“You really think riots in Laure could spread all over?” I asked.

“The key to the Empire maintaining control over the lands it conquered isn’t fear, my dear, it’s apathy. As long as the common people can go about their business and live their lives mostly untroubled, what do they care who their taxes go to? The Governor is making people care about who rules them again, and that is a very dangerous thing.”

“Huh. That explains a lot, actually,” I admitted.

For one, it finally shed light on why the Legions of Terror – who took their cues from the Black Knight – had been so hands off compared to Mazus’ tenure as ruler of Laure. That the Governor wasn’t exactly an ally of the Empress also accounted for why the legionnaires never let an occasion to stick it to Mazus’ cronies go by. I’d put it down to a mixture of disliking the man as much as we did and basic decency but it made sense there were also politics at work behind the scenes.

“There’s also a subtler danger, and that one is the reason I came here personally,” Black added after a moment.

I raised an eyebrow, curious but deciding I’d pushed enough for the day. I didn’t know how much rope he was willing to give me, but I had a feeling I’d already drawn enough to hang myself with.

“Think of it as a story, if you will,” the green-eyed man murmured. “A city, once the capital of a thriving kingdom, now ruined and oppressed. Its people are crushed under an ever-increasing burden and there is no hope in sight. Enter…”

“The hero,” I finished just as quietly.

\textit{Shit.} That did have the potential of becoming a nasty situation. Just like if you left dry firewood piled up long enough eventually there’d be a spark that set it on fire, if a city like what he’d just described was left unattended too long eventually a Role would emerge to fill the void. Would the hero beat the Black Knight? I doubted it. The last seven to try hadn’t, after all, and I’d heard the one from five years ago hadn’t even been about for a week before Assassin got him. If he riled up the people in the city enough, though, he could do a lot of damage before being put down. This was on another level, though – the Knight wasn’t even fighting a hero, he was making sure the situation where a hero would be created never came to be.

“Heavens wept,” I said softly. “No wonder you kill them every time. The arrow’s nocked long before you let the sparrow fly.”

Black’s smile turned sharp as a knife.

“Just because I’m winning doesn’t mean I won’t cheat.”

“So why are you telling me all this?” I asked, waving my hand to encompass the whole conversation. “Wouldn’t that make me a liability? You don’t seem like the kind of person that leaves loose ends behind.”

He picked up his cup and sipped.

“Because you remind me of someone,” he replied. “And because after you accompany me to the banquet, I will have an offer for you.”

I scowled at the presumption I’d just go with him. It wasn’t like he wasn’t right – even if he didn’t have the authority to force the matter, I was already curious enough to agree – but rubbing it in my face that I didn’t have much of a choice just made him an ass.

“A banquet?” I grunted. “Sounds fancy. Should I be bringing anything?”

“It’ll be the Governor’s banquet,” he mused. “So if nothing else, I’d bring the knife.”
\clearpage
\chapter{Chapter 3: Party}

“\textit{I see I’ll have to take drastic measures to ensure intelligent conversation around here.”}
– Dread Empress Maledicta II, before having the tongues of the entire Imperial court ripped out

“So, aren’t we a little underdressed for a palace visit?” I asked.

I was still wearing the shirt and trousers they’d had laid out for me in my room – and I was uncomfortably aware of exactly how well it fit. Did I want to know how they’d gotten my size? \textit{Probably not}, I grimaced. I’d had enough shocks over the last few days as it was. Still, the dark grey cotton was more comfortable than anything I’d worn in a while. Hopefully I’d get to keep it after tonight, regardless of what the man’s “proposition” was.

“Armour goes with everything,” Black replied dryly.

He was still wearing the same plate set as last night. Now that I could get a good look in sunlight I was sure it was, well, regular steel plate. It could have been enchanted, of course – probably was – but it wasn’t the dark obsidian or whatnot you’d have expected a man in his position to wear. His belt buckle didn’t even have a skull on it! That \textit{had} to break some kind of Imperial regulation.

“I guess it does, if you’re out to stab people,” I muttered, eyes watching his face closely to see if that got a reaction out of him.

Nothing. Not all that surprising: I was pretty good at picking up on tells in fights – I’d had to learn, to make it as far in the Pit as I had – but the social stuff had never been my strong suit. A regrettable lack of awareness and natural predisposition for insolence, our etiquette tutor had called it. I’d called him quite a few less polite things behind his back after that lesson, not that it made what he’d said any less true. We were drawing attention, I saw from the corner of my eye. People ducked into their houses and locked their doors when they saw two dozen soldiers escorting a pair of strangers – Scribe had stayed behind – if you were Lakeside or even Marketside, but we’d left both of those behind a while back for the sprawling avenues of Whitestone. This whole part of Laure was noble properties and guildhalls, all built in the pale sandstone that was the place’s signature. 

It hadn’t expanded in the last few hundred years, mostly because nobles had passed a tricky little bit of law to keep everyone else out: every addition to the quarter had to be built with the stone from the original quarry that had made up the other buildings and, what did you know, that quarry had gone dry over a century back. Whoever had come up with that probably thought they were clever – I mostly thought they were an asshole. Wasn’t that always the way with nobles, though? You got a title and a little land, then all these funny ideas started creeping in. Ideas like having a separate watch just for the Whitestone, and these were the very men and women staring at us right now. They kept their distance, of course, but there were more and more of them gathering every time we passed by a cluster of chainmail-decked cronies.

“They gonna give us trouble?” I grunted as we passed what must have been at least twenty nervous-looking watchmen.

Black cocked his head to the side.

“That seems unlikely,” he murmured. “At best they’ll try to send warning to their owners in the palace, but as it happens the entrance to it has already been secured.”

I felt my brows raise.

“There’s gotta be at least one of those with a sweetheart that works as a cook or a chambermaid,” I told him flatly. “They’ll know where the servant entrances are.”

The pale-skinned man granted me an amused look.

“And legionaries should be barring those gates as well, Catherine.”

Ah. Of course he’d have thought of that. Renowned evil strategist and all. I looked away so he couldn’t see my cheeks flush.

“And here’s Sabah,” he mused out loud. “Everything is going as planned, it seems.”

The latter sentence he said with an odd tone, like he was making a joke. I didn’t quite get what the humorous part was so I just shot him a quizzical glance. I didn’t think I’d met a Sabah before, but the silhouette that popped around the corner of Peony boulevard was easily recognizable. The olive-skinned woman better known as Captain still disdained wearing a helmet, but today she wasn’t sporting a cloak – it was painfully easy to see exactly how tall and broad she was. Definitely over eight feet, and with more muscles to her frame than any orc I’d seen, and orcs were built \textit{big}. Just the sight of her was enough to scatter the few watchmen still sticking around, though she ignored them and headed straight for us.

“Black,” she greeted him. “Miss Foundling.”

Her voice was deep, though the sing-song Praesi accent was still recognizable under it. I nodded back, taking the occasion to get a closer look at her. Strong nose and deep-set blue eyes with delicate eyelashes that seemed almost out of place on a face that, well, brutish. She looked more like an overgrown caricature of a person than someone real, and the enormous hammer hanging off her back did little to dispel that appearance.

“Orim has his legionaries in place?” the Knight asked mildly.

She nodded.

“He was unusually eager to lock down the palace,” she noted. “Mazus managed to get on his bad side.”

That certainly explained why the legionaries I served drinks too rarely had anything good to say about the Governor. That kind of dislike tended to trickle down the ranks, and I’d gotten the impression that General Orim was a fairly popular leader. \textit{So they covered all the ways in and out of the palace.} Now the real question was, what for? That strange little talk I’d had with the Black Knight back at the inn had left me with the impression that Mazus was on the outs with the Empress. She was bound to have other means to discipline the man than sending her right hand to do the job, though. A pointed letter with the Imperial seal on it would have done it just as well, and without involving all the cloak-and-dagger business that was going on right now. \textit{Is he getting his governorship revoked?}That would be pretty ideal, as far as I was concerned. Laure would go back under martial law until the next Praesi bookend from the Wasteland arrived, and with a little luck the next idiot up in the palace would be more competent than this one. \textit{They wouldn’t have gone through all that trouble if that was all they’d planned, though,} I decided. \textit{Not unless they expected trouble.}

“Now don’t you just look like you’re planning murder,” a voice mused, breaking me out of my thoughts.

Both Black and Captain were looking at me, split somewhere between curious and entertained.

“That’s a bit rich coming from you, sir,” I replied, my mouth forming the words before my mind could intervene. Captain snorted, and hopefully that meant I wouldn’t get murdered in broad daylight.

“The girl’s not wrong,” she gravelled. “I’ve never seen you looking like you’re not up to something sinister.”

The Knight wrinkles his nose in distaste. “’Sinister’? Wekesa’s a bad influence on you. And to think you were so respectful when we first met.”

The gargantuan woman rolled her eyes and I clenched my jaw so my disbelief wouldn’t show. I’d never seriously imagined I’d end up meeting any of the Calamities, but the few times I’d thought about it there’d been a lot less… ribbing involved. Banter was something \textit{people} did, not whatever they were. Besides, weren’t heroes supposed to be the witty ones? The best villains got was monologues, in the stories, or maybe a disbelieving line about how absorbing power from the eldritch abomination bound in stone couldn’t \textit{possibly} have gone wrong. I pinched myself discreetly, just in case Zacharis had messed up my healing big time and I was having a particularly realistic fever dream. Captain took a look at the sky and frowned.

“We need to get a move on, to get here before the little shit’s guests are drunk,” she grunted.

Had she just called the Imperial Governor of Laure a little shit?

“I think you might be my favourite villain,” I told the woman very honestly.

The Praesi’s lips twitched.

“We should keep her,” she gravelled at Black. “Everybody’s been too afraid of you to mouth off since the Fields.”

“Someone forgot to inform Warlock, clearly” the Knight muttered. “But you’re right – we might have to kill a few to get them in the proper state of mind if they’re too sloshed.” 

And just like that, it felt like someone had poured cold water down my back. The casual way the green-eyed man had just referred to murder had jarred me back into reality. \textit{Villains. Funny and almost likeable, but still villains.} I’d seen beggar cripples Lakeside with missing limbs or a body entirely covered in burns gotten during the Conquest, through the handiwork of those two nonchalant people standing next to me. \textit{Just because they hate the same people as me doesn’t mean we’re on the same side.} It wouldn’t do to forget that. I was joining the Legions to exploit the system the Empire had built, not became another component of it. I kept my discomfort away from my face and followed the two of them when they started strolling towards the palace, the Blackguards doing the same without a word.

It was a little eerie how silent they were, actually. I couldn’t recall a single one of them saying anything, or seeing one of their faces under the helmets. 

There were rumours that all servants and bodyguards to the Imperial nobility had their tongues ripped out, but I had a hard time believing that. People peddling those stories were the same kind that said the reason the Dread Empress was so beautiful was that she bathed in the blood of the innocent. \textit{Which is all kinds of stupid.} First off, there was bound to be a limited supply of innocents in Ater. Second, a bathtub-full of blood was a \textit{lot}. Unless they had some sort of special spell to drain blood from people – which I wouldn’t put past Praesi, on second thought – that meant killing at least three adults every time, and unless the Empress wanted to go through the rest of her day caked in dry blood she’d have to take another bath after. Seemed like a lot of trouble for a dubious reason, especially since beauty wasn’t exactly a requirement for ruling. Emperor Nefarious, who’d been on the throne before Malicia, was said to have been a particularly ugly old man with a hook nose.

“I hear you fight in one of the rings,” Captain gravelled suddenly.

I eyed the tall warrior in surprise. Hadn’t expected the woman to try to get a conversation going again, but I supposed that even after my unpleasant realization from earlier chit chat was still better than walking all the way to the palace in silence.

“I, er, do,” I agreed. “Though I wasn’t aware you guys knew about those.”

Captain frowned.

“Why wouldn’t we?” she asked, glancing at Black.

“Fighting rings are illegal under Callowan law,” he told her.

“Huh,” the warrior grunted. “Barbaric.”

I held back a scowl. \textit{Not sure I want to hear that from a woman whose homeland practices human sacrifice. }Still, it had come out of the blue that the Imps were aware of the Pit. The reason the fighting rings were underground was because they were \textit{illegal}, after all. Booker wouldn’t have bothered to pay off the guards otherwise. Clearly Mazus must have known there were some, since he got a cut, but there was a difference between knowing about the Pit and knowing about the fight lineup.

“So Booker pays you off too?” I asked.

“In a manner of speaking,” Black replied. “You could say we own her.”

“Wait, if you guys run her then why is she paying off Mazus? Wouldn’t that cut into your profits?”

“You’re assuming that our people and the Governor’s are the same.”

Huh. I was reluctantly amused that Booker was getting fucked over by the Praesi on two fronts, truth be told. She’d always seemed so in control: it was a pleasant surprise she was being handled the way she handled just about everyone else.

“Anything else you guys are running on the down low?” I asked.

The Knight smiled but kept silent. I frowned.

“You wouldn’t bother with small-time stuff like a fighting ring if you didn’t have the bigger dogs on a leash,” I realized. “Shit. How much of the underworld do you actually own?”

Black’s smile broadened and he turned to Captain. “Told you she was sharp,” he said.

The armoured woman nodded, studying me with a strange look on her face, but the compliment did little to stymie my curiosity.

“The Thieve’s Guild, for sure,” I muttered. “The Smugglers too?”

The green-eyed villain shrugged. “We have a working relationship with all of the so-called “Dark Guilds”,” he admitted. “Though I could do without the melodramatic titles they grant themselves.”

That was more than a little ironic, coming from a man who’d named his personal bodyguards the \textit{Blackguards }and dressed them up according to a colour theme.

“That doesn’t really make sense to me,” I grunted after a moment. “The Empire’s the \textit{law}, why would they work with you?”

“You’re thinking in terms of legal and illegal,” Black simply replied. “You should be thinking in terms of Good and Evil.”

Oh. Put like that it made a little more sense. I supposed the kind of people who ran Laure’s less savoury parts would see people like the Calamities as natural allies. And yet, this was still Imperial territory. Why would they allow anyone to run thieves and thugs on their ground, even if they got a cut? “Merchants they rob still have that much less to pay taxes with,” I pointed out.

Captain seemed to have lost interest in the conversation, eyes wandering as she surveyed the streets. Couldn’t really blame her: we’d kind of wandered away from me fighting in the Pit. 

“When Laure was ruled by King Robert,” Black said, “the Thieve’s Guild still existed. Correct?”

I nodded. That was common enough knowledge – word had it the Thieves had been in business since the the first house in Laure had been built. Likely that was just a band of criminals giving themselves a mystique, but there was no denying they’d been around for ages.

“And yet, like all his predecessors, he aggressively pursued it’s dismantlement,” the Knight continued. “The reality of it is that there is no city in the world where such activities don’t take place. Trying to eradicate them would simply drive a band of individuals highly proficient at sneaking about in the arms of the first hero to show up.”

I rubbed the bridge of my nose. The way the man thought was starting to give me a headache.

“So you make a deal with them,” I guessed. “They don’t steal from the Empire and you look the other way?”

“There are quotas,” Black replied. “And all killings of public figures had to be vetted beforehand.”

There was a sort of pragmatic sense to it, but it still raised my hackles. The Empire wasn’t even observing it’s own laws. The Praesi weren’t so much keeping order as they were making what already existed more orderly. \textit{What’s the point of having all that power if you don’t use it to fix the parts of the world that need fixing? }Thankfully, I was spared any more small talk by the fact that we’d finally arrived at the palace. 

The Royal Palace was all arcs and windows, built in dark grey granite instead of the sandstone that infested the rest of this part of the city. There was no stone of that kind in Callow itself – word had it it had been built from the remnants of the flying fortress of a Dread Empress when it had crashed over the old palace. It was an impressive mass, and I couldn’t help but stare as we passed by the large ponds that dotted the front of it in arcane patterns. There was a low wall circling the entire thing with a large gate in the middle, but the people keeping watch at the entrance were not city guard: a dozen legionnaires were standing at attention in front, decked out in full kit.

“I guess now’s as good a time as any to ask why you brought me along,” I said as our group headed towards them.

Black hummed. “We’re going to ask a few pointed questions to the Governor,” he replied.

I raised an eyebrow. “So I just stand there in silence and observe?”

“On the contrary,” the Knight murmured. “You’re welcome to interrupt as much as you like.”

Well, wasn’t that ominous. “You’re testing me,” I grunted,

“Life is a test,” the green-eyed man replied easily.

I rolled my eyes. “I hope you didn’t have to meditate under a waterfall to come up with that one.”

Captain snorted, though the conversation was cut short as we passed the legionaries. They saluted in silence as we strolled by, taking a paved avenue to the palace proper. The entire place was deserted: I’d have expected servants to be milling about every which way while the Governor was receiving guests, but we were entirely alone. There was light and the sound of chatter trickling out through the open windows, gone as soon as we entered the torch-lit corridors of the inside. Black had come to the head of the party, taking one turn after another without hesitation: this wasn’t his first time here, I guessed. Spent most of my time eyeing the painting and sculptures that covered every open space, noting that more than a few of them were in the Free Cities style – painted marble, usually of naked people in twisted-up poses.

“Ah, here we are,” the Knight mused out loud as we arrived to a pair of closed wooden doors.

The noise of chatter and laughter coming from behind it made it clear we’d arrived at the banquet hall. Yet another staple of the Kingdom that was now just another trophy in the Governor’s hands. “Captain, if you would do the honours?”

The gargantuan woman stepped forward, laying the palms of her hands against the wood and \textit{pushing. }The massive doors swung open briskly, hitting the walls with a booming crack. There must have been at least fifty people inside, servants aside. Men and women dressed in colourful imported silks, drowning in jewel-incrusted gold: most of them over forty, though I could see a handful of younger ones. There were three long tables forming a U, the man of the hour having taken residence at the head of the crowd: his dark-skinned stood out starkly across the pale Callowans in attendance. Idly I rubbed my thumb on the pommel of the knife strapped at my side – I wasn’t sure whether Black’s mention of bringing it had been a joke or not, but I certainly felt safer standing this close to the pack of cronies with a weapon at my hip.

The noise was snuffed out of the room the moment we walked in, the eyes of every single guest in attendance glued to the Knight’s face. A few glanced at Captain and fewer at me – it was a little irritating to be dismissed so blatantly, but I had a feeling I’d be the one getting the last laugh tonight.

“Out,” Black simply said. “All of you.”

I’d never seen a room clear so quickly before. I could feel the same strange \textit{weight} I’d felt last night when he’d stared me down in the alley, but this time it wasn’t directed at me. It was like swimming just outside of a current: the pull was there, but it wasn’t dragging me in. All those peacocks dressed in silk and carrying enough gold in rings and necklaces to feed a family for a decade were hurrying out without even bothering to pretend they weren’t terrified. There was something darkly satisfying about seeing the rich and powerful of Laure jostling each other in their haste to get out the door as fast as they physically could. I didn’t hide my smile. \textit{I’m not here to make friends, and even if I was there’s no one here I’d want to count as one.}

“So it’s a Name thing, the way you mess with people’s heads,” I mused. “Seems like a useful trick.”

The green-eyed man shot me an amused look.

“A fairly basic use of my power,” he replied, looking over the fleeing throng, “but I won’t deny it can be entertaining on occasion.”

It couldn’t have been more than thirty heartbeats when the only people left in the once-crowded banquet hall were Black, Captain, the Governor and myself. I took the occasion to have a closer look at the ruler of Laure, now that I was actually in the same room as the damned man. Governor Mazus was a tall man in his late thirties, dark-skinned like so many of the Praesi were. His hair was cut short and his beard cropped close, framed by the long gold earrings dangling from his ears. His robes were a riot of green and gold silk, and I was willing to bet diamonds to piglets that some of the stitches on them were actual gold thread. There was polished quality to the Governor, like every detail of his outfit and appearance had been attended to carefully. \textit{He can certainly afford the servants to do it.}

“Amadeus,” the Governor said, outwardly unaffected by the interruption as he leaned back on his chair while loosely holding a sculpted silver goblet. “An unexpected pleasure. I would have prepared a more fitting reception, if you’d sent word ahead of your visit.”

The ice in Black’s eyes could have frozen boiling water.

“There are very few people who get to call me by that name, Mazus,” he replied very quietly, “and you were never one of them.”

There was no hiding the flinch that went through him at that, though the aristocrat’s face went blank immediately after as if to pretend it had never happened. I took notes: one of these days I was going to manage to get a flinch out of assholes without raising my voice too.

“Ah, of course,” the Governor said. “I’ve had a little too much wine, it seems. To what do I owe the privilege of your presence, Lord Black?”

“The taxes you owe the Tower are late, Governor.”

Mazus let out a regretful sigh.

“As I already informed Her Most Dreadful Majesty, the convoy was waylaid by bandits. I’ve already drafted extraordinary taxes to remedy to that, but the burned Callowans are being obstructive. Borders on treason, really.”

\textit{Not that it matters, given the confession}, Scribe had said back at the inn. The pieces were starting to come together, and what I was beginning to think was going to happen to Mazus was enough to smother the cold rage that flared up when he called it \textit{treasonous} that the people of Laure didn’t want their children to starve. I could have let the smarminess go, but really why bother? Black had already as good as said he wanted me to interrupt whenever I felt like it.

“Really?” I said. “Bandits attacking an Imperial tax convoy? He’s supposed to buy \textit{that}? They’re outlaws, not idiots. They’d be swimming neck-deep in legionnaires before the month was done.”

The aristocrat narrowed his eyes at me, apparently unused at that kind of insolence coming from one of the people he ruled over.

“I care little if you pick up stray dogs off the streets, Lord Black, but perhaps you should muzzle this one before she gets her tongue ripped out.”

Oh, he did \textit{not} just say that.

“Call me a dog again and I’m going to strangle you with your own intestines, you filthy Praesi prick,” I promised, meaning every word of it.

Mazus sputtered.

“You’re-”

“Callowan?” I interrupted. “A girl? Nobody important? All true. But if I were you, the thing I’d worry about is \textit{carrying a knife}.”

“I’d take that warning seriously if I were you, Mazus,” Black mused from my side. “I’ve known her for a day and she already has a body count.”

He sneered.

“Raising a hand to an Imperial Governor will get you drawn and quartered, girl. Your bravado does you little credit.”

“Unless, of course,” Black murmured, “said Governor has committed high treason.”

Mazus paled.

“That’s a serious accusation,” he replied after a moment. “Making it without proof would have consequences.”

“Oh, we’re still talking in hypotheticals,” the Knight demurred. “But if say, a hypothetical governor were to report his due to the Tower had been robbed, it would be possible that the Empress would get curious and send people to look into the matter.”

“Sounds like she’d be a little ticked off,” I contributed with a hard smile. “Hypothetically.”

“The Empress has little patience for those who cross her, much less those doing it so gauchely,” the green-eyed man agreed. “Now, imagine that these bandits were found, and that when… properly motivated, they had a story to tell. Would you care to guess what that story is, Catherine?”

“Someone paid them to rob the convoy,” I grunted, the words flowing out easily. “Someone who’d then get a cut of the gold and buy their silence with the rest of it.”

Black smiled, lean and mean.

“A little too clever to be a dog, don’t you think?”

I stepped closer to the tables, grabbing an empty goblet and a pitcher of wine before pouring myself drink. I wasn’t going to lie to myself and pretend I wasn’t enjoying every moment of this – it was payback for every time we’d had half-portions at the orphanage because food prices had hiked up, retribution for every time I’d seen the city guard rough up a shopkeeper late paying his taxes.

“People will say anything under torture,” Mazus finally said. “I look forward to your trying to convince a court it’s enough to have me put away.”

I frowned, but took a sip of wine – fruity and strong, probably not from Callow. Figured the bastard would be drinking imported stuff. Black wasn’t an idiot: he wouldn’t have strolled in here so confidently if Mazus was going to get away with it all, and I was more than willing to wait another few moments to see that veneer of confidence stripped away from the man’s face.

“The Empress had taken a personal interest,” the Knight said coldly. “There is no need for a trial when the sentence has already been determined.”

The Governor sneered. “This will be the ruin of her, you imbecile. My father will whip up the Truebloods in a frenzy when word gets out.”

“Really?” I choked out with a laugh. “That’s your defence – wait ’til my dad hears about this?”

“He has something of a point, Catherine,” Black said. “Or he would, if High Lord Igwe wasn’t already under arrest himself.”

It was the second time that night I saw Mazus blanch, and it was every bit as delightful as the first.

“You’re mad,” the Governor whispered.

“Ever a subject of debate, I’m assured,” the dark-haired man replied with a bland smile. “Truthfully, Mazus, I’m suprised. You’ve always been a little slow but this? How did you think it was going to end?”

“With me Chancellor,” the other Praesi snarled. “It’s just a matter of time until one of us claims the Role, you filthy upstart. You can’t \textit{destroy} a Name.”

“You can’t buy one either,” the Knight replied. “Though that hardly matters now. Tell me, Catherine, how should a ruler deal with treason?”

I shrugged, feeling the weight of the Governor’s gaze on me.

“I’m told Imperial policy about that involves heads and pikes,” I mused. “Though that always struck me as a little tacky. It’s not like you can tell \textit{whose} head it was, a few weeks in. The crows tend to take care of that.”

Mazus slowly forced his spine to straighten and his hands to stop shaking.

“Fine,” he sneered. “I was caught. So be it. Unlike peasants, my breed knows how to go when the game is up. Have the mahogany chest in my rooms fetched, I’ll drink the deathleaf extract with my wine.”

Black laughed and unlike the few laughs I’d heard from him before this one was a wintry, sharp thing.

“You don’t seem to understand your situation, Mazus,” he smiled. “You belong to us, now. Your life, your death – all ours. And you’re not dying a dignified death sitting on your throne. It’s the gallows for you, Governor of Laure.”

The Blackguards fanned into the room at Captain’s order. Mazus tried to get up, eyes white and wild, but by the time he’d pushed back his chair there was a pair of plate-wearing soldiers grabbing his shoulders.

“No,” he screamed. “Black, you can’t – you wouldn’t dare-”

They dragged him out of the room, his screams of protests echoing even as he disappeared into the corridor. I put down my goblet of wine, leaving it half-full. I felt a little guilty at the waste, but considering the banquet tables were full of food I was hardly the worst offender tonight.

“So,” I said calmly. “Now is when you make your pitch, I’m guessing?”
\clearpage
\chapter{Chapter 4: Name}

“\textit{Power is mostly a matter of making the right corpses at the right time.”}
– Dread Empress Malicia the First

My words echoed in the now-emptied hall, and I had to hold back a wince when I realized how confrontational I’d sounded. Matter-of-fact, maybe, but there’d been a distinctly accusatory undertone to my voice I wished I could take back – not because I hadn’t meant it, but because pressing the green-eyed man standing in front of me seemed…. ill-advised. \textit{Too late to put the pot back together, though. Might as well go all out.}

“So first you talk me into killing the guards,” I noted. “They had it coming, sure, but would I have made that call if you weren’t egging me on? Not so sure. So now here I am, hands bloodied and not quite sure where to go from there.”

I paused, expecting a falsely-offended denial. Black remained silent, though, and his face was still as a pond on a windless night: anything I’d see on there would be nothing more than a reflection of my own expectations. The Knight glanced at Captain, who was looming by the door, and offered her a half-nod. She left the room without a word, closing the massive doors behind her. The sound of the wooden gates closing shut in her wake was oddly sinister.

“You were getting to a point, I believe,” Black prompted me, reaching for a glass and pouring himself a drink.

I steeled my spine and pushed on. “You might have done all that for the shits and giggles – I mean, I’ve heard weirder about villains – but you took me here tonight. Had me front and centre the whole time you were playing with a man I’d cheerfully stab given half a chance. You’ve got an angle at play, and it involves me agreeing to something.”

The pale-skinned man pulled back a bench and sat astride it with cool elegance, gesturing for me to do the same. I could have circled the room and sat across from him, but that would have been playing his game and I’d done quite enough of that tonight. I kicked back the Governor’s padded seat and plopped myself onto it with the closest thing to nonchalance I could muster with my heart beating in my ears like it currently was. I was all too aware I was playing with fire at the moment, but what else could I do? Some part of me felt backed into a corner, and I’d ever only reacted one way to that: come out swinging, sometimes yelling as loud as I could.

“You’re right, to an extent,” Black acknowledged, shooting me an amused look at my choice of seat. “But also wrong. What you so quaintly call my “pitch” started the moment I came across you in that alley.”

I frowned. Now that I thought of it, what were the odds that he’d run into me \textit{just} when I was stuck in a losing fight? The guards hadn’t seemed like they’d been sent there on purpose, but how hard could it be to –

“I did not, in fact, arrange your little scuffle,” he interrupted my thoughts, tone flat.

I kept my face blank. “You could be lying.”

“I am a splendid liar,” he agreed pleasantly. “But I don’t bother when the truth serves my purposes just as well. As for happening upon you in that particular moment – well, coincidences are hardly unusual when one has a Role like mine.”

“To take the mantle of a Name is to embrace the strands of Fate,” I quoted quietly. It was rare for the House of Light preachers to have a sermon on the subject of Roles, but compared to their usual fare it was interesting enough that the sentence stuck out easily in my memory. Black’s eyes turned cold.

“Fate is the coward’s way out, Catherine,” he spat out. “It is the denial of personal responsibility. Every decision I have made was my own choice, and all consequences that come from it are on my head.”

“Considering the kind of things you’ve done,” I quietly said, “I’m not sure that’s a selling point.”

The flash of anger I’d seen in him was gone as quickly as it had appeared, replaced by the usual indifferent facade. \textit{Did I just see what he actually looks like under the mask, or did I just happen to find a delicate subject? }Neither option was particularly comforting.

“I don’t expect you to love the Empire,” he said. “You’ve lived your entire life under its boot, and that is not a comfortable place to be.”

“You don’t get fair when you lose the war,” I replied, echoing my thoughts from yesterday.

He took a sip of wine, making a face at the taste. “I had an interesting conversation with Scribe, on our way to Laure. She believes that the denarii you have stashed at the orphanage are so you can leave the city and start over elsewhere.”

I wish I could say I was surprised he knew about the money, but given that he’d addressed me by my name the first time we’d ever come to face I really wasn’t. He must have had someone in the orphanage – it wouldn’t even be hard to accomplish, the Laure House for Tragically Orphaned Girls was an Imperial institution to start with. Why, though, was a better question. Why would the Black Knight pay any attention to the goings-on in one the city’s orphanages? 

“And what was your guess?” I asked instead.

“Scribe’s one of the most intelligent women I’ve ever met,” he mused, “but she’s never had a home, you see. She doesn’t understand what it’s like, to see a place falling to pieces and need to fix it.”

I met his eyes, green to brown, and he smiled.

“You’re saving up for tuition at the War College,” Black spoke into the empty room, his quiet voice somehow managing to fill the emptiness. “You’re nearly done, too – a few more months and you’ll have enough put aside for both the semester and the trip there.”

A shiver went up my spine, and this time there were no Name tricks to blame for it. Two days I’d known the man, and already he’d already pegged what I wanted perfectly. My hand fell down to the dagger at my hip, thumb rubbing the pommel almost without realizing it. The feeling of the wrapped leather against my finger grounded me, a physical sensation to chase the almost eerie atmosphere the scene had taken.

“That’s the plan,” I agreed, managing to keep my voice steady by the grace of the Heavens. “I was under the impression that the Legions take Callowans too, now – or was I wrong?”

“You are correct,” he replied. “Though few ever take the opportunity. So why would you?”

I shrugged. “I have a talent for scrapping. Seems like I’d be a good fit.”

I wasn’t good enough of a liar to get away with an outright lie, but a half-truth might manage to pull through. There were other ways to get higher up in the ranks of the Empire, after all, even for Callowans. I’d chosen the Legions as my path up because, at the end of the day, fighting was my talent I was most confident in. The green-eyed man sighed.

“Catherine, I’ve done you the courtesy of not taking you for an imbecile,” he murmured. “This conversation will go much more smoothly if you afford me the same.”

Ah. So much for that, then. He seemed more irritated than angry at my attempt – I supposed lying wasn’t much of a sin, by Praesi standards.

“Fine,” I grunted. “You want to hear the truth? I think the way the Empire rules over Callow is fucked. At best you’re brutally fair, at worst you get types like Mazus who think it’s their gods-given right to do as much damage as possible. I don’t give a shit whether we pay our taxes to the Tower or not, but someone has to rein in the idiots when they get vicious and the Legion is my best bet to get into that place.”

The man’s lips stretched into that mean little number he’d pulled out on the Governor earlier. \textit{Well, I had a good run. I’ll try to give him a scar to remember me by before my body gets dumped in the lake}, I decided, fingers tightening around the knife.

“Most people sharing your opinion would try to become a hero,” he said instead of unsheathing his sword.

I snorted. “And what, try to restore the Kingdom? We’re fresh out of royals and even if I managed to dig up some claimant getting him on the throne would be a bloody mess. How many thousands would die, fighting the Empire? More than it’s worth. And let’s not pretend you wouldn’t burn everything to the ground on your way out.” I offered a grim smile to the monster. “I’d just be good sense, for you lot: make us a weaker target from when you invade again, a few years down the line. Since you’re not doing us the favour of crumbling by yourselves, I’d better make peace with the fact that the Empress is in charge – she’s not going anywhere.”

The black-haired killer set down his cup and let out a low, almost lazy laugh. I scowled at the sound: I hadn’t been joking, and this wasn’t exactly a laughing matter.

“I was wrong,” Black said, though he didn’t sound like he was admitting an error. “You never could have become a hero. You lack the mindset for it.”

I bared my teeth. “And to think you gave me all that sweet talk about ‘what separates people who have a Name from people who don’t.’ Way to break my heart.”

“Allow me to make up for it, then,” he replied. “I’d like to offer you a job.”

Ah, and there it was. The end game he’d been driving his cart to all this time.

“I’m a little curious as to what you’re actually going to offer,” I admitted. “Training with the Blackguard? You’re bound to have potential recruits with less baggage.”

“I am,” the Knight murmured, “looking for a Squire.”

He didn’t have to raise his voice to make the capitalized letter clear. A Name. Shit. He was offering me a Name? Could he even \textit{do }that?

“I thought people with Names picked themselves,” I croaked out, mouth suddenly gone dry.

“They do, to an extent,” he agreed amiably. “But you have the potential, and given the… intertwined natures of that Role and mine, I have a degree of influence over the nomination.”

I didn’t think he was lying, not that I really believed I would have been able to tell if he was. \textit{Well, at least it looks like I’m not getting my throat slit. Not immediately, anyway. The evening’s already looking up.}

“And what do you want in exchange?” I asked, trying to keep the suspicion out of my voice.

The green-eyed man sighed. “I’m not a trader hawking over merchandise, Catherine,” he replied. “As Squire you would be my apprentice, in a way. My responsibility. I wouldn’t have made the offer if I didn’t believe you would be an asset.”

My mind spun and I closed my eyes, overwhelmed by the possibilities he’d just opened. If I had a Name… I’d bypass the Imperial hierarchy entirely, just by saying yes. Squire wasn’t exactly the most powerful of the Names out there but it would lead to something else and until then I’d be at the side of the second most powerful person in the Empire, learning all I could. All the ins and outs of the court, all the war tricks and connections that I wouldn’t get from books or even the instructors at the War College. \textit{I might be in a place to do some good in a decade instead of three. Less, if I somehow distinguish myself.}

“You want the answer now,” I said, the tone half-question and half-statement.

“One way or another, I’ll need your decision before you leave this room,” he acknowledged.

Heavens forgive me, but I wanted this. Wanted it so very badly. That was the part that was making me balk, though: I wasn’t this lucky, never had been. There must have been something in it for him I couldn’t see yet, some clause or trap I’d only grasp when it was too late.

“And if I say no?”

\textit{One girl found floating by the docks, missing a throat.} Wouldn’t be the first time someone dumped a body in the Silver Lake, wouldn’t be the last.

He shrugged. “You return to the orphanage. I’ll see to it that you’re put on the rolls at the College, with the first season’s tuition paid. I’ll look forward to your service in the Legions.”

“And that’s it? After all this, I’d still get to walk away clean?”

The Knight peered at his cup, swirling the dark wine inside with a negligent flick of the wrist.

“Some of my predecessors would have thrown a threat in there to motivate you,” he admitted easily. “Something along the lines of ‘should you refuse me, I will burn alive everyone in the orphanage and make you watch’.” He smiled ruefully. “Most of them were killed by their Squire, as it happens. I will not repeat their mistake: I will not deceive you, Catherine, or force your hand. What would be the point? I already have followers and equals – as well as a superior, if only the one. What I want is an apprentice, and an unwilling one would be nothing more than a burden.”

There’d been a sermon in the House of Light, once, about devils. The sister preaching had told us that the real ones, the dangerous ones, didn’t bluster about stealing innocent souls and breaking their word. They gave you exactly what you wanted and let you find your own way to the Hells with it.

“You realize,” I rasped out, “that it wouldn’t change anything. Even with a Name I’ll still want to change things.”

I hated the way it sounded like I wanted to accept his offer, true as it was. 

“Mine is not the side that concerns itself with how people that gain power use it,” Black replied. “By all means, reform the Empire as much as you want – as much as you’re able to, anyway. If you have the ability to accomplish something, it is your right to do so.” 

Damn me, damn him, damn this whole night and the one that came before it. It all sounded so \textit{reasonable} to me, but that was how they always got you wasn’t it? Was it arrogance, to think that if I didn’t step up to fix Callow no one else would do it? Maybe I was just a self-deluded little girl, playing a game whose rule I didn’t yet understand and pretending I knew what it was doing\textit{. But it doesn’t matter, does it?}The only question was whether I wanted this badly enough to make a deal with the monster sipping at his wine, and I’d known the answer to that before I ever set foot in the palace. \textit{This is how it starts, isn’t it? How villains are born. When you decide that something is worth more than being Good.} My fingers clenched and unclenched. I took a deep breath and let it out.

“So how does this work? Do I sign a contract in blood and summon a demon?”

Black did not smile, and I was almost grateful about that – if he’d been smug about this, treated it like he’d beaten me, I didn’t know what I would have done.

“Normally,” he said, “a conscious decision is enough to begin the process. By wanting to be the Squire, you reach for the Role and make yourself closer to it.”

“Normally?” I repeated.

“There’s a shortcut, for those so inclined,” he told me.

I met his eyes for the second time that night, unflinching. Even if this was a mistake, I would own it. I owed myself that much.

“What do I need to do?”

He smiled. “Try not to die.”

In the blink of an eye he was on his feet, moving quickly – much too quickly for someone wearing plate – with his sword was in hand. I felt the tip of it punch through my lung before I could so much as scream, and the last thing I saw before the darkness took me was those eerie green eyes looking down on me.

I opened my eyes under water.

My hands scrabbled for something solid to hang on to and sank into thick mud, still managing to push up my torso enough that I wasn’t swallowing what looked murky swamp water. I spat out something green and vaguely leafy, retching at the taste of scum water in my mouth. Before I could try to get on my feet I was compelled to notice that there was \textit{still a sword jutting out of my chest}.

“He stabbed me,” I wheezed out in disbelief, my breath coming out panicked. “He just fucking stabbed me, out of nowhere. \textit{Who even does that?}”

“Well,” a woman’s voice drawled lazily. “You know. Villains.”

My eyes spun towards the source of the noise, skimming over a darkened panorama of tall thin trees and greenery-covered waters – it was hard to tell, in the gloom, but I was fairly sure that the girl looking down on me from jutting stump was… well, me. Older, maybe, bearing a long pink scar across the nose and wearing legionary armour but there was no mistaking the face.

“Ugh,” I groaned. “This is going to be some kind of symbolic soul-searching quest, isn’t?”

“That implies your soul is a swamp,” the girl pointed out mildly. “Maybe you should get out more. You know, make some friends. Laugh once every few moons.”

I scowled. “I’m not taking advice about my social life from a dubious Name vision.”

I tried to push myself up to a sitting position – my fingers were sinking deeper into the mud, and the rest of my body slowly following – but the sharp pain I immediately felt served as a reminder that there was \textit{still a sword jutting out of my chest.}

“Oh, right,” the smug brat mused. “Let me get that for you.”

She jumped down from the stump, wading into ankle-high water to get to me. I was about to ask her to pull it out gently when I saw her look me over and pensively raise a foot.

“Don’t you dare,” I warned her. “Don’t you godsdamned-”

She put down her boot on my breasts and closed her fingers around the hilt of the sword, giving a brutal push with her knee that dunked my head back into the scum water. I pushed myself out into a sitting position a heartbeat later, retching out more of the disgusting green stuff and really wishing I hadn’t been opening my mouth to cuss her out when she’d pushed me under.

“This is a pretty good sword,” she observed. “Goblin steel, better than the standard issue stuff.”

“And that makes getting stabbed with it better \textit{why}?” I heaved.

“If it were rusty you could have gotten lockjaw,” the doppelganger commented.

Not even a bell into joining up with the Empire and I was sitting half-drowned in a metaphorical swamp, getting sassed by some sort of – probably evil – magical double. \textit{I’ll note Black didn’t mention this part in the recruitment speech}, I thought, trying to force my soaked hair into some semblance of order.

“Might be wise to get onto the stump,” the other me said. “I’m pretty sure there’s snakes in the water.”

“That just burning figures,” I cursed, hastily getting on my feet and slogging my way out of the danger – the doppelganger offered a hand to help me up, and I warily took it. I couldn’t see a weapon on her, but I didn’t know what the rules of this place were yet. \textit{If there are any.} Closing my eyes, I tried to think hard about a sunny meadow and waited a moment.

“What are you doing, exactly?” my voice interrupted me.

“Are we still in a swamp?” I asked, keeping my eyes closed.

“Nah, it’s some sort forest now.”

Hope welled up in my chest and I opened my eyes to the smirking rictus of the doppelganger. Did I really look like that when I smirked? Huh. No wonder people in the Pit went for my face so often.

“You lied,” I acknowledged wearily, glaring at the smelly wetlands still surrounding me.

“Shocker,” the double replied dryly.

“Did I draw the short straw when they were assigning spirit guides?” I muttered.

The doppelganger looked kind of offended.

“I’m a great spirit guide,” she contested. “Ask me a question.”

I wiped my face with the back of my hand. “What can I do to end this quickly?”

Her perfectly plucked eyebrows rose. “Ask better questions.”

I snatched the sword back out of her hands with a glower – I didn’t have a scabbard to put it in, so I just rested the point on the stump and awkwardly leaned on it.

“Right, not a guide then,” I grunted. “Are we going to have to fight? Because I’m not really feeling in the mood for anything but a bath right now.”

“I’m just here to point you to the next part, really,” the doppelganger said. “See that hill in the distance?”

I took a look where she was pointing, vaguely making out an upwards slope on what seemed to be solid ground. There was some sort of structure I could glimpse, and I squinted to see it better. That was when she socked me in the jaw. Back into the water I went, landing with a splash and an aching mouth.

“Lied again,” the double told me cheerfully when I resurfaced. “We’re gonna fight.”

“I don’t know what part of me you’re supposed to represent,” I spat out, bringing up the sword I’d somehow managed to remain clutching, “but I’m going to drown you.”

“That’s the spirit,” she grinned, rolling her shoulders. “See what I did there? Spirit. It’s funny because I’m a-”

I took a swipe at her ankles, hoping she’d give me the satisfaction of being a bleeder, but she leapt onto another stump.

“In the interest of full disclosure,” the double continued, “I was also lying about the snakes. I know, I have a problem. You have one too, though, right behind you.”

My first instinct was to snarl that I wasn’t going to fall for that twice, but after a heartbeat instead I stabbed blindly behind me – the blade hacked into flesh and I spun to push more weight into it, eyes widening in surprise. The decomposing corpse that had been about to lay a hand on my shoulder fell into the water still twitching, leathery skin pulled taut around rotting teeth.

“I have a zombie in my soul,” I forced myself to acknowledge, voice sounding faint to my own ears. “Gods, maybe I \textit{do} need to make some friends.”

“So,” the doppelganger called out from the tall branch she’d managed to hoist herself onto while I wasn’t looking. “Three guesses as to whether that’s the last one and the first two don’t count.”

I glared at her. “The only upside to this is that if you rise from the dead after I’m done with you I’ll get to off you twice,” I replied through gritted teeth.

“Meh,” she shrugged. “You’re all talk. If you weren’t, you would have stabbed Mazus in his wretched throat – we both know the Knight wouldn’t have stopped you.”

“Well,” I mused as I cast a wary eye out for anything else coming out of the waters, “at least now I’m sure you’re not the Good twin.”

“Nah, prissy bitch doesn’t come down here,” the girl replied. “Says she doesn’t like the smell.”

Gods Above, there really were two of them. \textit{This just keeps on getting better. }Nothing else seemed to be crawling out from under the surface, so I moved back towards the stump to get better footing. I didn’t like the idea of staying in the mulch either: it seemed right up her alley to have been lying about having lied about the snakes. Hopefully I wouldn’t have to follow her into the branches – I wasn’t sure what path up she’d taken, and I’d never been great at climbing. Not like there were a lot of trees in Laure.

“So that’s your trouble with me?” I prompted. “Not enough murdering people at the dinner table?”

She crouched on the branch, grinning down with pearly white teeth.

“My issue is that you’re a bleeding heart, Cathy,” she drawled. “You’ve got all those pretty notions about how things should be, but when the hard choices are gonna come you’ll \textit{flinch}. You have a chance to get some real change going but you’re going to end up choking on that self-righteousness.” She waved her hand theatrically. “That’s gonna end up with us \textit{actually} bleeding from the heart, and I just can’t have that.”

“So I should just go around stabbing everyone who does things I don’t agree with?” I replied. “That sounds like a winning plan.”

“If you \textit{had} a winning plan, I wouldn’t mind,” the doppelganger smiled mirthlessly. “But you’re not trying to win. You’re trying to be right.”

In a single, smooth movement she leapt from the branch and barrelled right into me. I was taken by surprised enough that I couldn’t bring up the sword in time. \textit{Shit.} We both splashed into the water – which had happened since the beginning of this little jaunt too often for my tastes already – while clawing at each other, trying to make sure we ended up on top. She managed to edge me out, but she left her face open so I knocked her teeth it with the sword’s pommel – she pushed me away, crawling up to her feet as I did the same.

“Now that’s more like it,” she laughed, spitting out a fat gob of blood from the corner of her lip. “Swing that thing like you mean it.”

“You’re insane,” I growled. “There’s no point to this.”

“There’s no point to any of it,” she smiled. She flicked her wrist elegantly, producing a knife from somewhere in her sleeve. \textit{I know that knife.} I’d owned it for less than two days, and already I would have recognized it anywhere: the first time I’d used it wasn’t something I’d ever forget. 

“There’s only one choice in life, Squire,” my doppelganger said with a flash of teeth. “You can be someone who makes things happen, or someone things happen to. Let’s find out which you are, shall we?”

She came at me swinging. There was nothing practiced or elegant about – she was just a girl with a sharp edge trying to claw out my throat. I stepped around her, letting her momentum carry her through as I swiped at her leg with the side of the blade. Too awkwardly placed: it bounced off the steel greaves. I’d never been taught how to use a sword, and it showed.

“Put your back into it, would you?” the double chided me. “Otherwise we’ll be at this all night.”

I ground my teeth, keeping a lid on my temper. I’d taunted people into making stupid mistakes often enough to recognize when someone was trying to do the same to me. The doppelganger leaned it with a quick half-step, blade headed straight from my throat, but the strike was too wild. Too much strength into it, not enough control: she was wasting movements. My fist impacted with her chin and she rocked back, but she slapped away the side of my sword when I tried to bring it to bear. The sharp edge bit into the leather gloves she wore, drawing a thin trickle of blood as she stepped back and started circling around me. “First blood to me,” I spoke quietly.

She laughed. “Last blood’s the only one that matters,” she replied, and rushed forward again.

I was ready for her, this time: I caught her wrist as it came down for my neck, fingers digging painfully into the cold wet mail as I struggled to hold it back. She tried to headbutt me but I lowered my face in time and she rammed her forehead into the top of my head instead. The double was the one who recoiled in pain, and that was the opening I needed – awkwardly, using the sword more like an oversized needle than a weapon, I rammed the point into her jugular. Blood sprayed out and she fell to her knees, gasping. I looked down into her eyes coldly.

“My turn with the speeches,” I ground out. “You lack focus. You lack discipline. You’re just lashing out at everything: all you can do is break things until you end up broken too.”

She gurgled out a laugh, a bloody smile stretching out her lips.

“What are you laughing at?” I asked.

“You didn’t flinch,” she rasped.

She dropped all the way into the water, face-first, and I had to flip her over to wrench out the blade. Threads of red were already appearing in the murk but I took a moment to catch my breath, clutching the sword. My free hand came up to wipe the sweat off my brow, though there was no salvaging the shirt and trousers that had been through the muck thrice. I was not looking forward to the walk to the hill, but at least I wouldn’t be hounded all the way there. The sound of parted waters was heard from up ahead as a silhouette emerged from the water, shambling upright. Then another. Then another.

“\textit{Come on},” I complained. “I didn’t even say it out loud!”
\clearpage
\chapter{Chapter 5: Role}

“\textit{Where have all the good men gone? Graveyards, mostly.”}
– Dread Emperor Malevolent III, the Pithy

Running struck me as the better part of valour in this one.

The first undead I’d put down had been a bit of a pushover, sure, but there were more coming out of the water every moment and fighting in the muck was going to get exhausting. I wasn’t sure what would actually happen if I died here, but Black’s last words were probably as much a real warning as sarcasm. One of the shamblers got close enough to reach for my arm but it was ridiculously slow – small favours – so I hacked away at the head with a two-handed swing. The flesh and bone split like an overripe fig and the thing went back down to wherever the Hells is had crawled out of, sinking into the water. I flicked a glance at my back, grimacing when I saw that even those few moments had been enough for the rest of the bastards to gain on me. \textit{There’s gotta be fifty, at least?} And the swamp seemed intent on continuing to hemorrhage undead every time I blinked, so I definitely couldn’t afford to get bogged down. My mouth still tasted like scum water so I spat to the side as I pulled my way up onto the stump, looking for a way out of this mess – somehow I had a feeling that climbing up a tree and closing my eyes wasn’t going to cut it.

The structure in the distance still stood in the same place as earlier. It was shaped like a tower, I thought, though I couldn’t see how high up it went. What I \textit{could} see was that the hill it stood on was outside the swamp and currently lacking my zombie friends. It was probably a trap, I reflected, but still better than getting pulled apart by a horde of moaning imbeciles. There was a flicker at the edge of my sight and I almost flinched: something was trying to catch my foot. The edge of my sword caught the wrist halfway there, though, and I blinked in surprise at the undead recoiled with a shriek. I… shouldn’t have been able to do that. I was quick, but I knew exactly how quick I was – I’d learned it anew with every fresh set of bruises in the Pit. I was familiar with the hateful little moment when you saw a hit coming but knew you wouldn’t be fast enough to block it, and this was one of those. But instead my body had reacted immediately, with no heartbeat between the realization of the need to move and the movement itself.

“Name,” I whispered, a little awed. 

I wasn’t even the Squire yet, wouldn’t be for a while if I’d understood the gist of what Black had said, and already I could do things like this? No wonder heroes were said to take on entire fortresses filled with soldiers without a second thought. \textit{No wonder villains take on entire groups of heroes.} Silhouettes were already rising up ahead, littering the way to the hill in an attempt to keep me surrounded, so I jumped back down into the swamp and got moving. The zombie who’d almost caught me had been entirely silent: it had emerged from the waters without a sound and given no warning before striking. Adding to that the fact that it had tried to slow me down instead of kill me? It meant that they were getting smarter about this. The longer I stayed here, the harder it would get. \textit{It also means my soul is being kind of a bitch about this}, I grunted to myself.

I pushed through the muck as fast as I could. Even here was only ankle-deep, so I was a little quicker than my pursuers – though not by wide enough a margin to get comfortable. Another one rose from the mud to my right so I ducked around a tree to make a little space. I would have looked rather ridiculous, I imagined, if anybody had been around to see me. Even pushing myself I was barely as quick as someone taking a walk on solid ground and the slow-witted undead were only a threat because of their number. Not exactly the kind of struggle you wrote epic poems about. I managed for what seemed like an eternity to avoid any of them before realizing that I was playing into their hands: I was going through more effort going around them than I would actually getting into a fight, as the rivulets of sweat running down my neck were already proving. Spitting out one of the grittier curses I’d overheard down at the Docks, I squared my shoulders and rammed myself straight into the knot of shamblers barring the way ahead.

I rammed the tip of the short sword into the throat of the closest one and it came free as I wrenched the blade out, but the other two were already on me. What looked like it might have been a woman at some point sank her teeth into my arm and I hissed in pain – I knocked her loose by hitting her temple with the pommel of the sword, struggling to keep the last one away with my free hand. The zombie gave, though several of her teeth remained stuck into my flesh. Could you get an infection from a Name vision? Gods, I hoped not. Cutting away the reaching arm of the last undead was the work of a pair of measured swings as I ducked around the woman trying to bite me a second time, and then the way was clear enough for me to push through. There was a fallen tree a little up a head that allowed me to put more distance between us when I climbed up on it, though the wood was wet and the footing tricky.

A glance at the hill up ahead told me I was maybe halfway there, so I gritted my teeth and got back to work without taking a moment to catch my breath. 

The bite wound on my arm throbbed, and that clinched my decision of not getting into any more fights with knots of them. I wasn’t used to fighting with multiple opponents, and I couldn’t afford to take a wound every time I ran into a pack. I stuck to hacking down lone undead as I ducked and weaved through the trees, always keeping an eye on the hill: the last thing I needed was to get lost in this godsdamned swamp. I took a scrape on the face when one of them jumped out from behind a tree, fingernails clawing as I rammed the sword into its chest. It was light, but I’d been very lucky it hadn’t been higher up: I’d fought with blood in my eyes before, and that was always a messy business. The closer I got to the hill the thinner in the ground the undead became. Less and less knots, and then they stopped rising entirely. By the time the water had turned into mossy wet earth, there were none in sight. Dropping to my knees, I leaned up against a tree and took the chance of closing my eyes for a moment.

Gods, I was exhausted.

The Pits hadn’t been like that at all. I’d only ever done one fight a day, and they’d never gone on this long. The opponents had been more dangerous, but they’d never ground me down by sheer force of numbers. If I’d slipped up even once, down in the waters, it would have been over. 

“Fuck me,” I whispered. “Weeping Heavens, I hope the Good twin isn’t going to make this a fight.” 

I pushed myself up and waited another few moments to catch my breath. I was close enough to get a good look at the hill now, and the tower on it. White stone, though not a kind I recognized, and it kept going up higher than I could see through the top of the trees. Hopefully my soul wasn’t enough of a jackass to make it so I had to walk up sets of stairs covering that height, though considering the kind of shit it had been putting me through so far I wasn’t exactly counting on it. The way out of the outskirts of the swamp was quicker now that the ground was mostly solid: I took the long way around a handful of ponds just in case there was anything lurking in there, but to be honest I was too happy I wasn’t being dogged by the burning undead horde to really complain about the tediousness of getting out of the bog.

My first surprise came when I finally got out of the trees: the tower kept going up. All the way into the sky, and then it connected to some sort of sprawling city that covered the gloom for miles. The whole thing was upside down, with the tallest stone spires looking to me like they should be falling down any moment now. Just looking at the thing was putting back the itch under my feet that I’d associated with my old fear of heights. Even as I continued closing the distance I could barely see where the stones making the tower started and the next one began: it would have appeared to be made of a single block of rock to anyone not taking too close a look. There was a yawning doorway squat in the middle and a pair of armoured knights stood by it, perfectly still. The suits of armour were empty, I saw as I got closer, made of what looked like silver. I raised a brow at that. Silver? That was the stupidest thing I could think of to forge armour with, except maybe gold – it was soft metal, any halfway decent blade would cut through. The halberds they were holding were steel, though, and that was another story entirely. Warily, sword still in hand, I kept an eye on their weapons and hazarded a step between them. Immediately the halberds came down, barring my way in.

“Well,” I mused, “so much for the easy way. There’d better not be an endless flood of you fellows inside, because I’d like to believe my godsdamned \textit{soul} is a little more original than that.”

“You don’t need to fight them,” a voice interrupted me. “You just need to leave that… \textit{thing} outside.”

There was a woman standing just past the doorway, and for the second time I got to have a look at an older version of myself. No scar on her this time, and she wore pristine white robes instead of armour. Her hair was cut short in a way that had never suited me but looked fitting on her: her face was more mature, the cheeks thinner and her nose not as prominent. She was also currently glaring at my sword like it had been used in the murder of her extended family.

“Yeah,” I informed her flatly. “I’m not handing that over. Not when you’ve got your little friends there with the halberds.”

My new doppelganger frowned. “I have no weapons, and they’ll stay outside,” she replied.

“And I’m supposed to take your word on that?”

“If you want to enter the tower,” she told me, and I recognized the tone she was using.

I’d used it quite a few times myself, when I was letting a potential threat know I wasn’t going to budge on something. Was it worth the risk? I didn’t know how hard to put down the knights would be, and I wasn’t exactly at my best right now – the throbbing on my arm where I’d gotten bitten was a constant reminder of that, never mind the weariness in my bones. The bog-bitch had called this one the “Good” twin, though, so maybe taking a chance was the way to go. Still… Moving quicker than I’d ever thought I could, I impaled the closest knight through the breast plate, pinning it to the surprisingly soft stone behind it. I stepped away, hands raised in peace, as the other one raised its halberd.

“Weaponless, see?” I told the other woman with a smile.

The older double frowned but conceded the point with a nod, stepping aside as I entered. The inside of the tower was empty except for a single seat in the middle of the room: old gnarled wood, light brown and well-polished. Not that it felt that way: the walls were covered in colourful mosaics. They depicted daily scenes from what I recognized to be my life – lessons at the orphanage, evenings at the Nest, even fights in the Pit. The tower walls went all the way into the distance, ending in a breath-taking view of the city I’d glimpsed earlier from above. The itch came back, but I pushed it down with the ease of practice: that particular fear was one I’d already mastered, and I had no intention of allowing it to crawl back into my life. Past a certain point the walls were still blank, I assumed to make room for the rest of my life. I squinted as I tried to make up one of the scenes higher up I couldn’t recognize, but the lighting inside wasn’t good enough. I did have a guide, though.

“That one,” I asked pointing at the object of my curiosity. “What does it show?”

The other girl shot me an unimpressed look.

“That time you peeked at Duncan Brech through the cracks while he was changing,” she said.

I chuckled. “And that warrants an entire scene? He’s not \textit{that} good-looking.”

Good Twin didn’t seem to share in my amusement: she ignored me and headed for the chair, claiming the seat gingerly and leaving me to stand around like a supplicant. I sighed. And here’d I gone, foolishly hoping that she wouldn’t be as much of a pain as the other one.

“So,” I grunted, “out with it. Before I stabbed the other one she took issue with how ‘soft-hearted’ I was. What’s the axe you’ve got to grind?”

“The axe \textit{we} have to grind,” the double corrected calmly. “All that you see here, all that you’ve been through so far – it comes from you. We’re voicing your doubts, nothing more.”

“That makes me responsible for the bloody zombies, then?” I muttered. “That’s a whole new level of self-loathing.”

The white-robed girl smiled mirthlessly. “You have this belief that nothing worth having can be had easily. Your adventure in the swamp is a reflection of that.”

Interesting, but not what I’d come here for. If I’d wanted to be lectured, I’d have taken a seat in the Matron’s office and told her I’d been fighting in the Pit.

“Fascinating insight,” I told her flatly. “Changes everything. I don’t suppose that’s enough to knock off this part of the dream?”

A flash of anger went through her eyes, and I was almost satisfied I’d gotten anything but condescension out of her.

“One would hope you’d take the fate of your \textit{soul} a little more seriously, Catherine Foundling,” she thundered, her voice echoing in the empty tower.

“I would take this seriously if I thought what I learned here meant anything,” I replied, taking delight in remaining calm in the face of her anger. “But it doesn’t. It’s just a chore I have to get done before I return to consciousness and move on with my life.”

“Yes,” she spoke, forcing herself back into a semblance of serenity. “Your life. As a villain in service to the Dread Empire of Praes.”

I frowned. “That was always the plan,” I reminded her. “Now I just get to skip a few steps by having a Name instead of slowly climbing the ranks in the Legions.”

“If you don’t understand how taking up a Role changes everything,” she said, “then you are a fool. You are binding yourself to Evil. To uphold its laws, champion its cause.”

“Not to put too fine a point on it,” I grunted, “but the Empire’s laws are the \textit{only} laws, at the moment. And let’s not pretend I’m going to champion anything I don’t want to champion, because if you’re really part of my soul you should know better than that.”

The doppelganger leaned forward, a fervent light in her eyes. “There is another law. The one you were taught at the House of Light. Do good. Uphold right. Protect the innocent, fight for a righteous cause.”

“You want me to be a hero,” I realized. “That’s… I don’t think I even have the words to tell you how \textit{stupid} of an idea that is. Let’s forget for a moment that my body’s in near proximity to at least two of the Calamities, though that should be enough in and of itself. Heroes try to “liberate” Callow all the time, Idiot Twin. \textit{It doesn’t work}.”

I took a step forward.

“They try, maybe stir up a town in the south, and then they \textit{die}. Assassin gets them, or the Legions, or Hells I’ve even heard Black put down a few himself. \textit{Some don’t even make it into Callow itself before they get caught}.”

“You’re already here,” she replied. “You know Laure, know your people. All they need is someone to raise the standard, and they will rally.”

“They’ll riot,” I corrected. “And they’ll be dispersed. Then I imagine my head will look mighty righteous, spiked alongside theirs over the city gates.”

“That’s your answer?” she growled. “It’d be too \textit{hard}? Too hard, not to become another tool of the Empire instead of doing the right thing?”

“I’m all for doing the right thing,” I replied flatly. “As long as it’s not also the dumb thing. This isn’t a story, you twit. We’re living this. If we fuck up, real people are going to die and we’ll die with them having accomplished \textit{nothing}.”

“Better to accomplish nothing than to accomplish bad things,” she told me.

And that was where we split apart, I realized. The other one down in the swamp had thought that just killing everyone who deserved killing was going to be enough, but that was a child’s way of thinking. There were always going to be more people like Mazus, more petty tyrants drunk on power and greed. Just removing them wasn’t enough: you had to change the system behind them, the machinery that let them rise so high in the first place. This one, she thought that just being Good was enough. That because you were doing the right thing you’d win, in the end, and the villains would be sent packing and everyone would rejoice. That wasn’t what happened, in real life. Sometimes you couldn’t beat Evil, and the only way to change things was to be patient and clever.

“Doing nothing is worse than being Evil,” I told her, striding forward. “Getting people killed because you won’t compromise is worse than being Evil. I’m going to change things – maybe not all of them, but enough. And if that means getting my hands dirty, I can live with that. I don’t have to be a good person to make a better world.”

She opened her mouth but I was already upon her and my fingers closed around her throat.

“No,” I growled. “You’ve said enough, and \textit{we are done here}.”

–

For the second time in two days, I woke up in a room I was unfamiliar with.

Hopefully the passing out wasn’t going to be a staple of my tenure with the Empire, because it was already starting to get old. The bed I was in was more fit for a family of four than my own meagre frame, and by the feel of it I’d been tucked in under actual silk sheets. \textit{Well now. Long way from the orphanage aren’t we, Catherine Foundling?} I sighed and allowed myself to luxuriate in the feeling of them for a moment, laying back my head on the pillows and refusing to open my eyes. I felt… surprisingly good, actually, except for the dull throbbing where I’d gotten bit during the dream. My senses felt sharper, like I’d just gotten a really good night’s sleep instead of gone through a Name vision of dubious symbolism. After a few breaths the novelty of it faded away and I pushed myself up, startling the servant tidying up by the window where the sun was filtering in. A young man, Callowan if the skin tone was any indication and wearing the palace livery.

“Lady Foundling,” he bowed, looking like he’d gotten caught with his hand in a jar full of honey. “A thousand apologies, I did not mean to wake you.”

“Lady Foundling,” I repeated, somewhat bemused. “Fancy that. If I’d known all I needed to become a noble was stab someone in a dream, I’d have done it a while back.”

The servant looked rather alarmed at that, though he took pains not to let it show too obviously. “Lord Black left orders that he be informed as soon as you woke, my lady,” the man said, keeping his eyes fixed to the floor. “I beg your leave to do so. Clothes have been laid out for you by the bath.”

A bath? \textit{Didn’t expect to sink into the lap of luxury this soon after going bad, but I’m not complaining.}

“You,” I gestured vaguely, “go and do that, I guess.”

The servant excused himself again and left the room after a bow, closing the door behind him. 

“Lady Foundling,” I repeated, chuckling to myself.

The title seemed more like a bad joke than anything else. Foundling wasn’t a real name: it was what they slapped next to an orphan’s name on the ledger when they got dropped off. \textit{Like putting a coat on a pig.} The siren call that was the mention of a bath got me on my feet, sliding off the bed with another small sigh of pleasure. I really needed to look into getting sheets like those, if I ended up settling down anywhere while I was the Squire. I padded to the window on bare feet, shedding the now sweat-soaked shirt I’d been put to bed wearing and dropping it on the floor. I’d never taken to wearing breast bindings: wasn’t curvy enough to need them, since whichever of my parents had been Deoraithe had cursed me with their typically slender frame. \textit{My parents, huh. }It’d been a while since I’d thought about them. I had no idea who they’d been – were, for all I knew – since the House for Tragically Orphaned Girls didn’t keep records for me to break into. I’d been dropped off a little after the Conquest, though, so probably not a dead soldier’s child.

The view out of the window was lovely, looking down straight on a well-tended garden of sculpted hedges and exotic flowers. There were a few gardeners already at work, but I didn’t really care if one of them got a look through the window: there’d been little enough privacy in the dormitories that I’d gotten over that sort of shyness long ago. I ran pensive fingers against the window panes, enjoying the way the coloured glass turned my fingers green and red. \textit{Imported, has to be.} The Glassblower’s Guild didn’t do work like this, so it was likely from the Principate. The servant had mentioned my freshly acquired teacher’s instructions that he be told when I woke, so after a moment I moved towards the doorway facing the bed. I’d never had a chance to use a real bathtub before, so I wanted to make the most of it. The other room was all panelled wood and white marble, with a large pool in the middle that appeared to be a Miezan bath. \textit{Huh. Didn’t think those got popular here before the Praesi came.} I dipped a toe in the water and found it just short of boiling. I raised an eyebrow: hopefully there was a spell involved in keeping it at that temperature, because otherwise it would have been an outrageous waste of wood.

I slipped out of the trousers and threw them out the doorway. There were marble benches under the water so I slid in on one and rested my back against the edge of the bath – it must have been built for people taller than me, because it came up to my neck. The warm water felt like the best thing in the world, after the last few days, and I dunked myself in just to feel it wrapping up around all of me. I emerged a little ways off and came to face with a handful of small glass vials. 

They were clear so I could see they were full of salts and oils: I grabbed the closest one and took of the cap, bringing it up close for a whiff. Something herbal. Lavender, maybe? I’d never really taken an interest in herbalism. I shrugged and poured a little over my back, rubbing it in and spilling some in the water for good measure. A few moments later I was positively reeking of the stuff, so I’d likely been a little heavy-handed. I dunked myself back under the water to rinse it off before deciding that was quite enough indulgence for the day: the promised clothes were on the other side of the bath, neatly folded, so I paddled in that direction. I hoisted myself out and grabbed the cleaning linen laid out next to them, eyeing what I’d been provided curiously. Thick leather breeches, made from the skin of an animal I wasn’t familiar with, and a white woollen shirt. The new addition was the thick padded jacket that looked like it would reach to my knees: I’d seen Sergeant Ebele come in wearing one, a few times. She’d called it an aketon – legionaries wore them under chain mail to prevent chafing. \textit{Looks like I’m going to be getting armour soon.}

It was surprisingly easy to put on, designed to I could tighten the laces in the front without anyone’s help. I supposed it would have been a little absurd for the Squire to require a squire of her own, I reflected with a snort. When I came back to the bedroom it was to find there was another occupant: Black was lounging on an ornate chair by a Proceran \textit{bureau} I hadn’t even noticed, idly flipping through a book. He raised an eyebrow when he saw me.

“It suits you,” he commented.

“It’s summer,” I grunted back. “I’m going to cook alive.” A moment later the memory I had of him resurfaced and I pointed an accusatory finger. “You – you jackass. You stabbed me.”

He seemed to ponder that for a moment before shrugging.

“Only a little bit,” he replied.

I’d never wanted to deck someone in the face more than I did that man in that moment. “That’s what you’re going with?” I growled. “\textit{Only a little bit?}”

“If the fact that you’re not screaming and bleeding out of your eyes is any indication,” he mentioned, “then it was a complete success.”

“That was an option?” I asked faintly. “You could have mentioned that before.”

“Yes,” he admitted frankly. “I could have.”

Fucking villains. Even if I was technically one now, \textit{fucking villains}.

“Just to make sure – the swamp and horde of undead, that’s normal right?” I asked, seating myself at the edge of the bed.

His eyebrow rose even higher. “Swamp? Unusual. I went through a labyrinth myself, though I’m told the experience tailors itself to the person going through it.”

Gods, it was kind of depressing that the best my soul could come up with was scum water and zombies when it came to Name visions. 

“I’d consider it a good thing that your experience was rather martial in nature,” he told me. “Your Name’s abilities are likely to be related.”

“Well, that’s something at least,” I grunted. “I’m not feeling all that different, so I’m guessing that means I’m not the Squire yet?”

“About halfway there, as much as these things can be measured,” the green-eyed man said. “There’s other contenders, but none of them should be quite so far along.”

“Other contenders?” I repeated.

“Close your eyes,” the Knight instructed. “Focus. You should feel something in the back of your mind, like someone watching you.”

I obeyed. For the first few moments there was nothing, but after a while there was… a sensation. It wasn’t like he’d said, more like an itch that wasn’t quite on my skin but still belonged to me. I frowned and tried to push the feeling, and suddenly it unfolded on me.

“Three others,” I said, opening my eyes. “And some fourth thing that’s not quite the same.”

He hummed in agreement. “Try to keep your finger on the pulse of that feeling as much as possible, from now on.”

I frowned. “Why?”

He smiled. “Because as of this moment, they all want to kill you.”
\clearpage
\chapter{Chapter 6: Aspect}

\textit{Funny, isn’t it? No matter what language they speak, everyone sounds the same when you pull out their fingernails.”}
– Dread Emperor Foul III, “the Linguist”

The pile of books slammed on the table.

“The Most Illustrious Histories of the Inimitable Dread Empire of Praes”, volume I to III, made up up the top layer and I lost interest after checking that ones right under were a study of the Licerian Wars. Gods, those bred like lice. I’d had to read seven treatises about the fall of the Miezan Empire already – every two-bit scholar seemed to think that their own take on why the Baalites had won was unique and unprecedented, all while shamelessly stealing from each other’s work.

“I’m assuming you want me those read those and not, say, bludgeon someone to death with the pile?” I asked dryly.

“Very perceptive of you,” Black noted. “We’ll be leaving for Summerholm this afternoon, but before we do we’ll go over the shape of your days for the foreseeable future.”

“And apparently that shape involves…” I peered a little closer at one of the books close to the bottom, “A close look at Praesi agricultural practices? Are you sure I can’t get you to reconsider the bludgeoning thing?”

The Knight frowned. “Dry reading, I will concede, but a necessary one.”

Considering I’d never even seen a farm in my life and I doubted he’d ever done more than ride past one, that was one statement I wasn’t willing to swallow without a fight. I raised an eyebrow.

“Are we going to be doing a lot of farming in the next months, then? Have you ever \textit{been} on a farm?”

He shot me an amused look. “I was raised on one, as a matter of fact. My father was a freeholder on the Green Stretch.”

It took me a moment to place the name, digging back to the handful of geography lessons I’d breezed through. It was what they called the crescent of fertile land in the Wasteland, right next to the Blessed Isle. I’d heard that it was the only part of Praes where people intermarried with Callowans, which made sense given my teacher’s distinctly pale skin tone. Still, the idea of the leader of the Calamities plowing a field was all sorts of hilarious for many reasons. \textit{I’m sure those fields were oppressed like no field before them,} I chuckled to myself.

“Freeholder?” I repeated after a moment, mangling the unknown word. “That’s different from a regular sort of farmer, then?”

Black claimed a space on the bench across from the table. The banquet hall was just as deserted as it had been two nights ago – I’d apparently slept through a whole day, and managed to miss Mazus’ hanging for my trouble – though the polished wood had long been cleared of food and plates. I’d already set aside the hearty breakfast the palace kitchens had provided me after wolfing down two servings and half a pot of tea: Name visions apparently worked up quite an appetite. I took the high road and decided not to comment on the fact that the green-eyed man already had a cup of wine in hand before noon bell had even rung.

“Land in Praes is usually owned by the nobility,” he explained, “Namely, the High Lords or their lower counterparts. People who work the land rent it from them, and have no real say over what happens to it. The Green Stretch has no noble domains on it.”

I raised an eyebrow. “That seems unusually enlightened, for the Empire,” I commented.

He snorted. “The Stretch is the breadbasket of Praes – the north of the Wasteland barely produces enough grain to feed itself, much less sell a surplus, and the south is a literal desert. Any noble with significant holdings in the Stretch would be able to starve the Empire at will.”

Ah. That made a little more sense, in a depressing sort of way. “I’m guessing freeholders rent their land directly from the Empress?”

He nodded. “In a sense. There’s a single fee when taking possession that lasts for the lifetime of the freeholder. It has to be paid again if the land is inherited, but the Tower is typically hands-off with the entire region.”

I’d always thought of Praes a single unified entity, but the more I learned of it the more it became apparent it was anything but. How many of the blunders in the way Callow was being run came not from stupidity but the need to appease High Lords, I wondered? And how could a woman with Empress Malicia’s reputation tolerate her hand being forced by idiots?

“Why are there even High Lords anymore?” I finally asked. “I mean, they’re the obvious contenders for the throne – so why hasn’t the Empress killed them all and turned the entire Empire into freeholds? I mean, if the way your conversation with Mazus went is any indication you’d be all for riding that horse.”

Black’s fingers drummed against the table thoughtfully. “After we won the civil war, I advised Malicia as much. If I’d had my way, we’d have nailed the lot of them alive to the gates of their little kingdoms and broken the aristocracy so thoroughly there wouldn’t be a noble in Praes for another thousand years.”

“And yet here they are,” I pointed out quietly.

“She disagreed,” he told me. “Argued that the ensuing chaos would destabilize the Empire for decades. And that since there would always be opposition to her reign, it was better to know who her enemies were – and that she could beat them, if she needed to.”

The way he spoke the words was strange. He wasn’t espousing the position himself, merely parroting someone else’s opinion. The lack of conviction showed.

“You still think it should have been done,” I half-guessed, half-stated.

“Yes,” he agreed. “But she’s always seen more clearly through the politics than I have, so I’m trusting her judgement. I do have a certain tendency to try to… simplify problems.”

Meaning nail said problems alive to the gates of their “little kingdoms”. Weeping Heavens, the very image… He’d mentioned a superior, during his recruitment speech, and the conversation was making it very clear who that person was. Not that there’d ever been any doubt. Legionaries at the Nest spoke of the Black Knight with admiration, but they spoke of the Empress with awe.

“There will be other times to discuss the inner workings of the Empire,” Black said, changing the subject. “Preferably after your readings have acquainted you with the basics of its cultures. Your priority will be these three books.”

He gently tapped the spine of three particularly beat-up looking manuscripts in the middle of the pile. One of them bore script I didn’t recognize – they looked more like those magical glyphs mages sometimes used than letters – but the other two were in something I could read. Two words: the first one read \textit{Taghrebi}, the other one \textit{Mthethwa}. Languages, the both of them.

“I thought people in the Empire spoke Lower Miezan?” I asked. 

It was the tongue we were using for this conversation, and the only one I spoke. It was the only one I’d ever needed, frankly: I’d had some lessons on Old Miezan, but that was a purely written language now. The Deoraithe in the north still spoke the same tongue they’d spoken since before the birth of the Kingdom and some of the lands in southern Callow still spoke tribal dialects, but everyone understood Lower Miezan. Even people from the Principate, who’d never even traded with the Miezans, usually understood it. Though that was most likely because the tongue they spoke was so hellishly complicated no one else wanted to learn it.

“They do,” Black agreed. “It became the most commonly spoken tongue when we were still a province. But if you are to ever command Praesi soldiers, you’ll have to understand the languages they were raised to – if only so you know what they’re saying when they’re not using Lower Miezan.”

I grunted in irritation. He had a point, not that it made the prospect of learning two entirely new languages any more inviting. It didn’t help that I had a feeling I’d be learning both at the same time.

“What’s the third one?” I asked instead of continuing to bask in my disgruntlement. “Are those glyphs?”

“They’re written Kharsum, though I’d have been surprised if you could recognize them.”

“Kharsum,” I repeated in disbelief. “You want me to learn \textit{orcish}?”

“\textit{Kharsum},” he corrected me sharply. “Remember the proper name. And it is not the only orc tongue, only the most common dialect.”

“Am I learning goblin too, while I’m at it?” I complained.

Black smiled mirthlessly. “I’ve worked with goblins for over fifty years now, and I still don’t know enough of it to hold a conversation. They don’t teach it to outsiders.”

Curiosity pushed aside my indignation for a moment, though it was a close thing.

“So they all what, speak other people’s tongues?”

“Even goblins from the most backwards tribes are bilingual by the time they can walk,” the Knight informed me. “On average, they speak four languages – most Matrons speak seven, including a few who can speak Proceran.”

“That’s insane,” I grunted. “The amount of time that must take…”

“Is less than you’d think, if you start young enough,” he cut in. “Besides, you have an advantage none of them have.”

Huh. That was new. “If you say “a talented teacher” I won’t be held responsible for my actions,” I warned him.

He chuckled. “No, though that \textit{is }an advantage. Unless I’m mistaken, at least one of your three aspects will make this easier on you.”

I raised an eyebrow.

“You mean that whole “Three Sins” thing is actually true?” I asked.

He blinked in surprise.

“Three Sins?” he repeated, sounding somewhere between puzzled and curious.
“And on all those who take up the banner of Evil, the Heavens will bestow three sins, planting the seed of their downfall in the name of Justice,” I quoted from memory.

Sermons at the House of Light were usually on the boring side, but that one had caught my attention: it was always more fun to hear about what the villains were up to than getting edified on the importance of the seventeen cardinal virtues.

“Your priests always did have a way with words,” he noted amusedly. “Though I notice they don’t mention heroic Roles have their own aspects.”

“So aspects instead of sins,” I mused. “I can buy that. What are they for?”

“They define your Role,” he told me, tone serious now. “They’ll change from one incarnation to the next, to some extent, but some aspects are as good as set in stone. \textit{Conquer }is a staple of the Role of Black Knight, for example.”

“That means what, exactly?” I replied with a healthy dose of scepticism. “That you’re good at conquering things?”

“The more closely attuned you are to your aspects, the larger the portion of your Role’s power you can access,” he smiled. “So when “conquering things”, as you so aptly put, I become… \textit{more} of what I am.”

“So why aren’t you always conquering something, then?” I asked. “Wouldn’t you be pretty much invincible?”

“That particular brand of logic has been popular with some of my predecessors,” he agreed. “But in the end there’s only so much power to access, and staying too close to your aspects tends to lead to tunnel vision. Not to mention the other side of the equation.”

“Heroes,” I murmured. “Why do I have a feeling that for every Evil role with \textit{Conquer} in it, there’s a Good one with \textit{Protect}?”

“Because I rarely suffer the company of imbeciles?” he suggested.
I gave him a flat look.

“Please, sir, there’s no need to gush – I’ll get embarrassed,” I deadpanned.

He didn’t manage to take a sip quite quickly enough to hide his smile.

“So what are my aspects, then?” I asked.

He shrugged.

“Only you can answer that. It will come to you in due time. \textit{Learn} is a typical one, which is why I believe that throwing off the proverbial cliff when learning languages will yield the best results,” he said.

So he wasn’t being entirely unreasonable about this. Still, \textit{orcish}. “I didn’t even know orcs had a written language,” I admitted, eyeing the not-glyphs inscribed on the book’s spine.

“It actually predates all other written tongues on this continent,” he commented. “The arrival of the Miezans set them back centuries, in that regard.”

That had always been the problem with the Miezans, as far as I could tell. They’d built amazing structures and done wonders with magic that no one had managed since, but they’d had this nasty tendency to stomp down on subdued cultures to make sure they didn’t rebel. Orc slaves had been a prized commodity of the later Empire, with the way they could handle larger amounts of hard labour – and clans that didn’t like their children being taken away had the screws turned on them, sometimes all the way to extinction. It was a lucky thing the First Licerian War had sparked before they could venture into the maze of petty kingdoms that later became Callow, because otherwise I wasn’t sure what my homeland would look like today.

“At least tell me I’m going to be learning something that’s actually \textit{interesting},” I pleaded.

He snorted. “Readings will be done on your own time,” he informed me. “As of tomorrow, you’ll be waking up at dawn for sword lessons with either myself or Captain.”

I grinned. Now \textit{that} was a little more up my alley. “Much softer sell, this one.”

He shot me an amused look. “I expected as much. After your midday meal you’ll have until the afternoon bell to yourself. Between that and evening bell I’ll be handling the aspects of your education that can’t be learned from books.”

That was also sounding promising. “And that means?”

He hummed. “We’ll be travelling this afternoon, so I suppose now would be the best time to have today’s lesson. Grab your knife, we’ll see about getting you a proper mount.”

Walking around in an aketon was an unusual experience.

The heat I’d gotten used to quick enough – though the accompanying sweat I could have done without – but the sensation of having a thick layer of additional protection covering me from my neck to my knees was a little surreal. Some part of me wanted to throw myself at a wall just to see if I’d bounce, though rationally I knew I wouldn’t. It was my second time making my way through the halls of power of my native city, so I made a point of taking in the scenery as I followed Black through the maze-like corridors. Tapestries of hunts and battles dotted the scenery wherever paintings did not, and I noted with quiet amusement that no one had seen fit to take down the ones depicting victories of Callowan royals over the Empire. There was even one particularly glorious one that depicted Dread Emperor Nefarious getting his ass whipped by the Wizard of the West during his failed invasion, on the very Fields of Streges where Black had inflicted a crushing defeat twenty years later. I somehow doubted Nefarious had actually dropped his crown while fleeing the battle, but the sight of the woven scene warmed my heart anyway. There were warmly-coloured wood panels covering most of the walls, elaborately carved around the edges, though they came less and less often as the Knight led me towards the western wing of the palace.

“So we’re headed to the stables?” I asked.

He didn’t seem particularly inclined towards conversation at the moment, but when had that ever stopped me with anyone?

“We are,” he replied absently. “The Royal Stables no longer provide for the king’s personal retinue of knights so they’re not as well stocked as they used to be, but we should find what we need regardless.”

“I feel like I should point out I’ve never ridden a horse,” I provided helpfully. “I don’t think I’ve even gotten closer than a stone’s throw to one.”

He glanced at me sideways as we passed a threshold through what seemed to be an annex to the kitchens – though a ridiculously spacious one.

“That’s a suspiciously specific unit of measurement,” he said after a moment.

“Wanted it to kick a guard,” I admitted shamelessly. “Poor sap.”

He raised an eyebrow. “The guard?”

“The horse, of course,” I grunted back. “The guard was asking for it.”

A shadow of a smile flitted across his face as we entered a paved courtyard – the sudden transition into sunlight blinded me for a moment. \textit{But not}, I noted, \textit{as long as it would have a week ago.} Two heartbeats hadn’t even passed before I’d gotten used to the change of scenery, and the oddity of it sent a shiver up my spine that had nothing to do with sweat. \textit{And I’m not even the Squire yet.}

“You’ll also see better in the dark,” Black murmured from my side. “Though nowhere as well as goblins do.”

“My quota of creepy realizations for the day is reaching full load,” I informed him. 

He hummed. “Perhaps you won’t enjoy the lesson very much, then.”

“Well that’s not ominous at all,” I deadpanned. “Are you going to leave this unaddressed like the funny line about everyone wanting to kill me? Because I’m still waiting for an explanation on that one.”

“All things in due time,” he replied with a serene smile I really wanted to take a hammer to.

I smelled the Royal Stables before I saw them: manure and animals had a distinct stench to them, especially in large concentrations. \textit{You’d think that by now a mage would have figured out a spell to get rid of the smell of shit.} The stables themselves were made of the same grey granite as the rest of the palace, a long row of stalls where upwards of fifty horses were barred in. There was a groom feeding a stallion some hay in the distance, but he took a single look in our direction and made himself scarce as quickly as humanly possible.

“So, a gelding?” I prompted as we got close enough for me to have a look at the mounts. “I hear they’re easier to ride for beginners.”

The horses I saw in the stalls had little to do with the ones I’d seen in the streets pulling carts: they were bigger and taller, warhorses instead of workhorses. Some of them had distinct enough appearances I was pretty sure they were specific breeds, though for the life of me I couldn’t name one. The Procerans had some kind of mount called destriers, maybe? I knew Callow’s cavalry had been famous, once upon a time, but given how the knights had largely gotten wiped out during the Conquest they weren’t something you saw much anymore.

“The horse’s temperament shouldn’t be much of an issue,” Black replied. “I was informed that one of the Bedlam chargers had taken sick, but – ah, there he is.”

The horse had a dark chestnut coat, though it was matted with sweat. I guessed it must have stood over five feet tall when standing up: it was hard to tell with it lying down. It’s eyes were closed and it was breathing unevenly.

“I’m not going to have to nurse it back to health, am I?” I asked warily. It was a beautiful animal, but I knew nothing about horses and I’d rather not end up killing my first mount through a stupid mistake that someone better acquainted with the species wouldn’t have made.

“The stablemaster gives him one chance in three to last the month,” he told me. “It has a bad case of pigeon fever – abscesses under the skin. Painful way to die.”

I grimaced. Now that I was taking a closer look, I could see it was getting a little thin: I could glimpse the rib bones through its coat, and if I wasn’t mistaken its chest was swelling.

“You want me to heal it?”

I knew some Roles could do that. Bring back people on the brink of death, or even a little beyond the line, but I’d been under the impression that those were the heroic ones like Healer or Priestess. Black shook his head.

“We’re going to kill it.”

I blinked in surprise as the words took a moment to sink in. “We’re going to \textit{what}?”

“You did not mishear me,” the green-eyed man said calmly.

“Look, if this is some kind of test… I already offed two people this week and seriously considered a third, so I really don’t see the point in-”

“We will then raise it from the dead,” Black continued evenly, as if I hadn’t interrupted.

I was too taken aback to muster a proper glare. “This is seriously fucked,” I finally managed to grit out. “Necromancy? That’s capital E…” I trailed off.

“Evil,” he finished quietly. “Yes, Catherine. That is the side you’re standing on, now. That is the choice you’ve made.”

I tried to muster up a response to that, but my thoughts were too scattered. I wasn’t sure why killing a horse I’d never seen before somehow struck me as more morally dubious than slitting the throat of two actual human beings, but it did. They’d been horrible people, sure, but they’d still been \textit{people}. The House of Light’s official stance was that animals didn’t have a soul in any meaningful way so killing one wasn’t exactly a sin either, but… 

“Fuck. You could have given me a softer learning curve than jumping straight into \textit{raising the dead},” I spoke through gritted teeth, hesitant and hating that I was feeling that way. “You know, let me dip my toes in with cackling and monologues before taking the metaphorical leap.”

“Monologues are for amateurs,” Black informed me. “If you have the time to make a speech, you have the time to kill the hero. That said, this \textit{is }a soft learning curve. You’re not meddling with the horse’s soul, merely animating its body with necromantic energy. Morally speaking, it’s no different from felling a tree to make a cart – you’re making a means of transportation out of something that used to be alive.”

“You’re skipping the part where I’m killing it first,” I grunted.

The dark-haired man shrugged indifferently. “It would die anyhow. If anything you’re saving it from weeks of unnecessary pain by putting it out of its misery now.”

“So why didn’t you just have the Blackguards bring in some dead horse, if any corpse will do?” I asked.

I wasn’t sure whether that would be better or worse, actually. It’d be easier to distance myself from the whole thing if I’d never seen the animal alive, but I’d also feel like an actual necromancer. You know, some sorcerer creep in a run-down tower having his minions bring him bodies to make unholy abominations out of.

“You wouldn’t be able to raise it,” Black said. “You’re too fresh into your Role to manage something of the sort – you’ll need a connection to the corpse. Besides, better quality of corpse will make a better undead.”

I closed my eyes and took a deep breath, my fingers closing around the handle of the knife at my hip. I’d always known I’d need to cross some lines, to get ahead in the Empire. Gods, I’d as good as renounced any chance of getting into the Heavens after I died just by claiming a Name on the wrong side of the fence so this was positively trifling in comparison. \textit{Like felling a tree to make a cart,} I told myself, the words coming as cold comfort.

“Will it be painful?” I asked, opening my eyes. “For the horse, I mean.”

“It won’t even wake,” Black replied.

I knew people who hadn’t died half that peacefully. “So what do I need to do?” I grunted, letting go of the knife.

“Lay your hand on its coat,” the Knight instructed quietly. “I’ll do most of the work, you just have to get a feel for what’s happening.”

I knelt in front of the horse, awkwardly reaching for the side of its neck. It didn’t even stir. Black crouched next to me and laid a single finger on its forehead, narrowing his eyes almost imperceptibly. There was no crackling of energy or flash of light – this wasn’t magic, I thought, not the way mages used it anyway – but suddenly there was a \textit{weight} pushing down on my shoulders. The horse went cold, the sensation of it against my fingers giving me goosebumps. The way it felt was… hard to describe. I’d gone swimming in the Silver Lake, last summer, from one of the shallower beaches. The sun had been pounding down all afternoon so the waters close to the surface had been pleasantly warm, but the depths my feet reached to had still been cool. It felt a little like that, if the warm waters were the rest of Creation and all of my body was in the depths. The power didn’t feel twisted or unnatural, the way I would have expected Evil at work to. It was just \textit{other}, in some fundamental way.

The horse took a last breath, then stilled. 

Black’s brows furrowed. “And now for the tricky part.”

The power inside the horse tightened like a rope in response to the Knight’s will and the corpse twitched: my fingers dug into the corpse’s flank as I focused all my attention on what was happening, willing myself to miss not a single moment. There was a sharp pricking sensation on my palm, like I’d been jabbed by a needle, and my awareness of the corpse unfolded like a sixth sense. I could feel the chords that animated the horse and they were \textit{mine} as much as any of my fingers: I willed it and the charger rose to its feet. I didn’t know how horses were supposed to move, how their limbs were supposed to work, but the corpse did and I drew on what it had been while still alive.

“Well done,” the dark-haired man murmured as he rose to his feet.

I realized with a start I was already up – when had that happened?

“It will need a name,” Black prompted me.

I pondered that for a moment. I could name it something heroic or inspiring but that would have been something of lie of sorts, a denial of what I’d just done. \textit{Call a spade a spade.}

“His name,” I announced, “is Zombie.”
\clearpage
\chapter{Chapter 7: Sword}

\textit{“A single strike parts a champion from a corpse.”}
– Praesi proverb

Dawn had come much, much too early.

I put on my aketon and fastened my bootstraps regardless. I’d been told the ache in my everywhere would die down when I settled into my “riding legs”, whatever the Hells that was supposed to be, and apparently Zombie was making it much easier on me than an actual horse would. Not that it felt like it. I dragged my ass down to the common room of the inn we’d ended up in and picked at my porridge half-heartedly, forcing myself to swallow mouthfuls of the increasingly lukewarm slop. I wasn’t that hungry at the moment, but a I knew that if I didn’t fill my stomach now I’d feel ravenous in a matter of hours. Captain was the only other person sitting at the table, methodically tearing through her second bowl without a word. Even while eating her eyes were never restful, always moving and scanning the corners of the inn’s dining room – the habits of a lifetime spent serving as my teacher’s bodyguard. With a grimace I put down my spoon and admitted that this was about as much food as I could force myself to swallow at the moment. Besides, I had questions to ask and this was as good a time as any: Black was nowhere in sight but I was due to begin my first sword lesson soon.

“So,” I spoke up, “the Sixth Legion.”

Captain eyed me curiously but didn’t reply. I hadn’t expected her to, really: even after only two days of travelling with the gargantuan warrior I’d gotten a decent read on her personality. She wasn’t the type to talk unless asked a direct question, not unless she was with an old friend.

“I know their cognomen is \textit{Ironsides},” I continued, “but besides a mention of how they held the left flank at Streges, the books don’t say more about how they got it.”

A cognomen was what we mere Callowans would call a nickname, thought the books had given me the impression that there was a little more to it than that. I’d taken the time to look up the legions that served as Summerholm’s garrison, after being told it was where we headed. The Sixth and the Ninth – \textit{Ironsides} and \textit{Regicides}. The second was fairly straightforward, but the first not so much. Captain put down her wooden spoon, resting it against the rim of the bowl.

“They broke a charge of the knights of Callow,” she gravelled out, her tone making it clear she expected this to be a tell-all explanation.

“That’s, uh,” I said, “good on them I guess? You’re saying like that’s a really impressive thing.”

The tall woman mulled over this a moment before speaking.

“You were born after the Conquest,” she finally said, “so you don’t understand the way wars used to go. You only heard of the Legions after we started winning.”

“I know the Empire tried to invade a few times before,” I defended myself. “I was taught about how Emperor Nefarious got his ass handed to him by King Robert before Black and the Empress got put in charge.”

“Don’t take it as a criticism,” Captain grunted. “The Legions went through reforms decades before you were born. Things were different back then. It used to be that the Empire didn’t fight Callowan armies on an open field unless we had them four to one.”

I couldn’t help but let out a whistle at that.

“That seems a little excessive,” I told her.

“We still lost about half of the time,” she gravelled. “Before the Fields, the only way a legion ever held against a charge by Callowan knights was by packing the ranks so tight they got bogged down.”

I winced. You didn’t need to be a master tactician to understand that that particular tactic was going to involve a lot of dead legionaries.

“So the Sixth are badasses who spit in the face of enemy charges,” I said. “The name’s already starting to make more sense.”

“There’s more to it than that,” Captain gravelled. “Istrid – the Sixth’s general – is an orc. So is most of her legion.”

“And that changes things because?” I asked.

“Greenskins weren’t allowed to be legionaries until the reforms,” the large warrior grunted. “Just auxiliaries that the Black Knights used as meatshields to take the heat off Praesi soldiers. And when the knights charged \textit{them}…”

“They broke, and they broke hard,” I finished quietly.

It was easy enough to imagine the greenskin legionaries I remembered patrolling the streets in Laure, only without the armour and the large shields. I’d seen enough frescoes of Callow knights in the House of Light to know they were large men and women in full plate riding war horses decked in the same: it would have been like running a sharp knife through butter.

“And so there was Istrid and her legion of orcs, after a thousand years of her people being run down like animals,” Captain spoke quietly. “Standing down those knights from behind a line of shields, and this time \textit{they were not the ones to break}.”

“Ironsides,” I murmured, trying out the word with a new kind of wonder.

I’d probably met cripples in the streets of Laure who’d been part of that ill-fated charge, I told myself. It was a sobering thought, but it didn’t quite manage to take away the mystique of the tale Captain had just spun with her curt sentences. That was the thing I hated – loved – the most of these villains I was travelling with: when you listened to them talk, they didn’t seem so much like the villains anymore. There was a twisted sort of justice to the Sixth Legion managing to be on the other side of slaughter, for once. \textit{We’re raised on stories of Praesi monsters, but I wonder what kind of stories they heard while growing up?}

“Don’t focus too much on Istrid,” Captain spoke quietly. “Sacker’s the more dangerous one between the two.”

“Ninth Legion – cognomen \textit{Regicides},” I recited from memory. “One of their companies killed the Shining Prince, right?”

“They all wear red war paint on their throat to show how the idiot got his throat slit,” she chuckled. “It’s what she’s remembered for, but it’s not why she’s dangerous. She’s slated to take Ranker’s place when she retires, and you need more brains than brawn to make it to Marshall.”

“So she’s smart?” I guessed.

“Cleverer than a snake and twice as mean,” Captain grunted. “She’s a patient one, too – balances the way Istrid can get a little too eager for blood. It’s why they’ve been paired together.”

I grimaced. Coming from a woman who was on first name basis with the Dread Empress and the Black Knight, ‘twice as mean’ was a statement to take seriously.\textit{ So let’s add General Sacker to the list of people I’ll need be very, very careful around}.

“Speaking of Summerholm,” I segued in the most casual tone I could muster. “D’you have any idea why we’re headed there?”

Captain shot me an unimpressed look, so apparently not as casual as I’d hoped.

“Some kind of Name thing for you,” she gravelled. “Squires are so bleeding dramatic. Getting Amadeus settled into his Role was a pain too, though, no reason you’d be different.”

I raised an eyebrow. “Your Name was easier?”

“I was born into mine, back when I was the Cursed,” she grunted. “By the time I became the Captain, no one was dumb enough to challenge me for it.”

I eyed the gargantuan warrior frankly – she was already wearing her armour, and even without her hammer peeking over her shoulder she looked like a one-woman battering ram. “I find that pretty easy to believe,” I admitted.

She snorted and returned to her gruel, making it pretty clear she considered the conversation over. I tried to do the same, but nearly spat out the stuff when I realized how cold it had gotten during our little chat. Shoving the spoon back in, I pushed myself up and nodded my goodbye to Captain before heading for the door. The inn we were at – the Soldier’s Rest – wasn’t big or rich enough to have a real stable, so the horses had been tied to a row of posts right outside. Zombie stood perfectly still next to Black’s mount, his chestnut coat lacking the subtle rise and fall that the horses of the Blackguard showed every time they breathed. Just by coming close to it the eerie awareness I’d come to have of the necromantic construct unfolded in the back of my mind again: it felt like he was a puppet whose every individual string I could pull on at any time. That wasn’t the eerie part, though: I \textit{knew}, somehow, how all those strings interacted. How pulling on the part that animated the left forward leg would affect the rest of the body, what parts I needed to tug on to set him to a trot or a full run.

It wasn’t like I’d ever studied horse anatomy, either. I had no real explanation for how I knew any of that except that my Name itself knew – and wasn’t that just enough to send a shiver up my spine?

“You’ll get used to it,” the voice came from behind me.

I tamped down the urge to jump out of my skin. Black’s idea of a sense of humour apparently involved sneaking behind me at every occasion. How the man managed that in a full suit of armour was beyond me. \textit{Probably involves some kind of Name bullshit.}

“To raising things from the dead?” I replied, turning to look at him. “Gods, I hope not. That strikes me as a bad habit to form.”

The dark-haired man stood alone. No sign of any of his bodyguards, or even Scribe. \textit{Not that she’d say much of anything even if she was around.} The plain-faced scrivener made Captain look positively chatty in comparison.

“I’m referring to the things you don’t know how you know,” he replied. “Names provide what you could call a… second set of instincts. Part of growing into yours is learning which parts to use and which parts to ignore.”

My eyes fell to the scabbarded sword he held in his hands. A short sword, much like the one strapped at his hip. Not quite Legion-issue – the pommel was inlaid with silver, though from this far I couldn’t see what it depicted – but close enough for training purposes. Without any warning, he tossed it at me. My hand came up before I’d even processed the sight, snatching it out of the air like we’d choreographed the whole thing.

“The reflexes are useful, so I think I’ll be keeping those,” I acknowledged. “I take it that’s going to be mine?”

He nodded. “Goblin steel, straight from the Imperial forges of Foramen. You won’t find anything of better make on the continent.”

I raised an eyebrow. “Not even dwarven stuff?”

The Knight snorted. “As if they’d ever sell anything but the mass-produced stuff to surfacers. Dwarven weapons are common because they’re cheap, Catherine, not because they’re quality material.”

I raised a hand in a gesture of appeasement. “Alright, alright. No need to go all Praesi pride on me.”

The silver inlays made up a grinning goblin’s head, as it happened. The smaller greenskins might not have the kind of fangs you could see in an orc’s mouth, but the leering goblin was showing an impressive set of canines. I shoved the scabbard into the leather straps made for it on my belt, wriggling it a little to make sure it fit properly.

“No shield?” I asked.

There was one hanging off his back, fastened by a clever metal contraption I’d taken a look at the other day. A large rectangular piece of plain steel, unadorned by any heraldry: it was similar to what legionaries used, the kind Sergeant Ebele had called a \textit{scutum}.

“It’s waiting for you where we’ll practice,” he replied. “You’ll go without armour for today, but as soon as the armour Scribe requisitioned arrives you’ll be doing this in full plate.”

Joy. The aketon already made me feel like I’d gained twenty pounds, actual armour was going to turn me into Creation’s clumsiest upright turtle. I followed Black when he led the way around the inn – didn’t see what was so different between the ground in front and in the back, but it was too early to ask questions. Besides, the whole place was identical in every direction as far as I could tell. The two hundred miles between Laure and Summerholm were flat farmland with no city to speak of in between. The main road was good paved stone, at least: it’d been built by the Praesi after the Conquest, in case they ever needed to move troops quickly between the cities. People called it the Imperial highway, since from Summerholm it connected through Streges and its infamous fields to the Blessed Isle – and from there, across the Wasaliti River to the Wasteland itself. There was a field of beaten earth behind the inn’s wooden walls, and there was my shield: an actual legionary’s scutum, painted dark red, though I noticed it lacked a legion number. I picked it up and tested the weight: twenty pounds, maybe a little more? It’d get tiring to hold up until I built up my arm strength. The horizontal grip was good cedar wood and I tied up the leather straps hanging off of it to my wrist – put there to make sure it wasn’t easy to knock out of my fingers, I figured. Black was standing at ease on the field when I finally turned to face him, shield held up to cover his side and sword already in hand.

“So,” I said. “Teach me swordsmanship.”

He smiled. “I’m not going to teach you anything of the sort.”

“That seems a little counterproductive,” I commented.

“Swordsmanship,” he continued, “is the tame sport they teach noble children. It’s a matter of forms and rules, as useful on the battlefield as a blunted blade.”

The tip of his sword rose to face me.

“I’m going to teach you to \textit{kill}, Catherine,” he said. “Kill well and quickly, while giving as few openings as possible.”

“Hurray,” I replied flatly. “Long live the Dread Empire, other assorted patriotic slogans. Can we start now?”

Still, even as I gave him the flippancy that little bout of melodrama had deserved, I straightened my spine and brought up my shield in a rough approximation of the way he held it. This was the sort of lessons I’d actually been looking forward to – even more now that I’d started learning the blinding headache that was spoken Kharsum. Only one night in and I was already much more amenable to the Miezan point of view of stomping that whole “other cultures” business into the ground. He actually looked a little offended I’d been largely unaffected by his impromptu spot of theatre, though he got over it quickly enough.

“The two most important parts of any kind of fighting,” he said, “are distance and footwork. Your fighting in the Pit should already have taught you the basics of distance, though you’ll need to adjust to the range of your sword.”

I frowned but nodded. Girls my height who got into fights either learned to deal with the fact that most opponents would have more reach and upper body strength than them, or they learned to enjoy the taste of blood in the mouth. The short sword wasn’t much of an upgrade, in that regard. Most people I’d end up fighting would have a sword too – and outside Praes, longswords and two-handers were the most popular weapons. \textit{Except for the Free Cities, I guess.} That whole lot had a fixation with pikes and spears, though to give praise where it was due their phalanxes were supposed to be fearsome on the field.

“Shield up,” Black barked, and my arm rose immediately – mostly out of surprise.

I’d never heard him raise his voice before. The suddenness of it had my blood rushing through my veins while he advanced towards me, eyeing my stance critically.

“You’re right-handed,” he said, “so your left hip and leg should be braced against the back of the shield. Otherwise, \textit{you’re open}.”

His sword whipped out faster than my eye could follow, swatting aside my hastily-placed scutum. The tip of his blade came to rest on my throat for the blink of an eye before he took a step back. I swallowed. That wasn’t a practice blade he was using: if he’d pushed it an inch further in, I’d be dying on the ground. Squaring my shoulders, I put the godsdamned shield up the way it was supposed to go. The upper edge came all the way up to my chin and the sides covered my entire body – it was reassuring, to have that length of steel between me and his blade. The position felt awkward, to be honest. The foot in front pointed towards Black but the one in the back had to be horizontal if I wanted to have any stability: swinging my sword would be tricky.

“Better,” the green-eyed man conceded grudgingly. “Now for the sword. Grasp the grip and press forward as you lift it out.”

It ran against my instincts to do it that way, but I could see the sense in it: it kept everything but my upper arm under the cover of the shield. I rotated my elbow down and brought the sword up, letting it rest to the side of the scutum. \textit{Ah}, I understood suddenly. Of course swinging would be difficult: the sword wasn’t supposed to be swung. It was meant to stab forward in short thrusts.

“Legionaries fight on three lines,” Black said. “Low line goes like this.”

He crouched behind his shield, letting it cover him all the way up to right under his eyes. The tip of his sword was knee-height.

“Mid line goes like this,” he continued, rising up and bringing the sword up to his hip.

He took a short step forward and I eyed him warily. My newly-acquired Name reflexes had been of no help whatsoever last time he’d attacked.

“And high line like this,” he finished calmly.

His arm went back and the tip of the sword came to breast-height like a serpent poised to strike. I nodded sharply.

“Good,” he smiled. “First we’ll spend some time having you go through those motions.”

He stepped back.

“\textit{Low line},” he barked out.

I flinched at the sudden sound but crouched. I \textit{would} learn this, and learn it well.

Several eternities later – or, more realistically, about two hours – I found myself pulling the cork out of a waterksin and gulping down the contents greedily. We’d acquired an audience somewhere between the stabbing drills and the footwork ones. If I had to hear \textit{steady timing, maintain the distance} one more time, someone was going to get stabbed. And I had a sword now, so I meant business. Captain, who’d been the one to hand me the skin in the first place, patted me comfortingly on the shoulder.\textit{ Gods, even her hands are huge. She must have ogre blood or something, humans don’t usually get that big.}

“The first few weeks are always the hardest,” she told me. “You’re not doing bad at all.”

I took her word for it, though I couldn’t find it in me to agree out loud. I’d been in enough fights to know that I was good in a scrap – \textit{very }good, even, for my age – and it had been a while since I’d felt as clumsy and slow as I had today. I was aware that comparing my own movements to the effortless way Black moved even in plate wasn’t a reasonable comparison, but it wasn’t stopping that nagging voice in the back of my head from making it anyway. \textit{And I’ll be worse when I get my own armour. }I felt my fist clench and took another swallow to hide my grimace. I was definitely doing another set of drills tonight, preferably somewhere no one would be able to see me making a bumbling fool of myself. When I passed the skin back to Captain I found her scrutinizing me with those too-perceptive eyes of hers, and without saying a word she patted me on the back a last time before heading towards Black. The Knight was talking in low voices with Scribe, reading a folded parchment she’d handed him after he’d announced we were taking a break.

“Black,” she called out as she strode across the field. “Anything urgent come up?”

Green eyes flicked towards me before he replied. “Nothing new.”

Captain grinned, tossing the waterskin towards the wall and rolling her shoulders.

“Let’s have a bout, then. You’ve been putting the girl through the mangle, so at least show her what she’s headed to.” The gargantuan woman pulled the war hammer hanging off of her back, twirling it one-handed like she was holding a twig instead of a massive wrought steel bar. “Been a while since we had one, anyway.”

Well now. That sounded like it had potential. Seeing the Knight getting smashed by that hammer a few times would do wonders for my mood. The green-eyed man snorted.

“Fair enough. Terms?”

“Let’s keep Names out of it,” Captain replied. “Would defeat the point to go all-out.”

“Would also wreck most of the countryside,” someone muttered from my side.

I glanced and saw one of the Blackguards had come up to me. There were a handful of them milling about the place, though together they didn’t make up more than a dozen people. Where the rest had gone to, I had no idea. The man who’d spoken pushed up his visor to show his face: couldn’t have been older than thirty, with brown wide-set eyes and the dark skin tone typical of northern Praesi. \textit{Soninke}, I corrected myself. \textit{They call themselves the Soninke.}

“They get messy, I take it?” I prompted him.

It was the first time one of the Blackguards had struck up a conversation with me, so I fully intended to keep it going. Hells, it was the first time I’d seen one of their faces: they kept to themselves to the extent I’d started to wonder if they were avoiding me.

“The last time they had a spar without holding back, Captain knocked down a tower and Lord Black threw a whole statue at her,” he informed me cheerfully. “Hilarious at the time, of course, but the local baron was less than pleased.”

I chuckled. “I don’t think we’ve been introduced,” I said. “I’m-”

“Catherine Foundling.”

I scowled. “I really wish people would stop doing that.”

He grinned, showing off pearly white teeth. “I’m Lieutenant Abase,” he introduced himself, offering his hand. I went to shake it but he made some sort of strange clicking sound with his tongue and moved my hand up to his forearm.

“You’re not a civilian,” Abase told me. “Use the warrior’s salute.”

I raised an eyebrow but clasped his arm like he’d showed me. \textit{Praesi and their rituals. I’m surprised they can use a chamber pot without doing a special dance first.}

“So,” I mused. “Any particular reason this is the first time I actually speak with one of you?”

“We’re quiet types,” the lieutenant replied drily. “And wary of strangers. Lord Black has several men’s worth of enemies.”

Wary of me, huh. Not sure whether I was offended or flattered. Still, I must have done something right, to finally rank words today. I was about to ask exactly what that was when movement at the edge of my field of vision interrupted me: Captain and Black were putting distance between them, striding to the edges of the dirt field. Scribe stood in the middle, looking superbly bored with the whole affair.

“Try not to blink,” Lieutenant Abase said. “You’ll miss it.”

\textit{Miss what?} I wanted to ask, but Scribe was already speaking.

“On my mark,” she announced. A heartbeat passed, then she brought down her hand.

I blinked – probably because the lieutenant had brought it up in the first place – and in the fragment of a moment where my eyes closed, Captain crossed half the field. She left behind foot tracks and a spray of dirt where’d she been standing an instant before, barreling through the distance almost faster than I could see. Black had not yet moved, standing still with his shield up and his sword in mid-line, but the moment Captain got close enough to bring her hammer down he calmly sidestepped around the strike and pivoted so he’d be facing her back. The armoured woman’s weight and momentum carried her forward even after she landed on the ground, carrying her a few feet further down the field as she turned to face the Knight.

“Shit,” I whispered. “Did she really just jump thirty feet forward in heavy plate?”

“Quick on the offensive, today,” Abase noted, unruffled by what we’d just witnessed. “She must have been getting bored.”

“Weren’t they supposed to not use their Names?” I asked him. “What she just did is, like, physically impossible for a normal person. Just seeing it would give my numbers teacher a headache.”

“They’re not using them \textit{actively},” the lieutenant clarified. “Lord Black’s shadow isn’t moving and Captain is, well, still using her hammer.”

He didn’t elaborate further on either of those interesting tidbits, and I decided not to press him any further – not because I wasn’t curious, but because what the people in question were getting up to had claimed my full attention. Captain was attacking relentlessly, swinging the two-handed war hammer like she couldn’t feel the weight of it at all. And yet, she wasn’t the one controlling the flow of the fight. Black moved little and carefully, rarely more than a step at a time: he stepped barely out of the arc of her strikes and then swung around so he was facing her back. He’d yet to attack, but just the threat of him doing so was forcing Captain to keep moving. The sight of them was almost comical, from where I stood: the two of them were dressed in similar-looking plate, sure, but the olive-skinned woman stood at least three feet taller than him and had broader shoulders to boot. Neither of them wore helmets, so I could see that while a faint smile tugged at Captain’s lips my teacher’s face was expressionless. His pale skin made it creepy: he looked like he was wearing a mask made of marble. After another miss, Captain took a step back and raised her hammer high.

“That should do for the warm up,” she grunted before striking the ground.

There was a dull boom and the ground shook like it had been hit by a catapult stone: dirt sprayed everywhere, clouding my sight of the battlefield for a moment. When they came into sight again, Black was ducking under a vicious-looking swing. He ventured a kick to her knee but Captain danced back, the hammer coming back to swat him on the backswing. His shield came up to take the hit but the metal crumpled under the force and the impact was enough to throw him back a few feet.

“You’re getting slow in your old age,” she told him.

The dark-haired man shrugged and discarded the now-useless scutum. “You’re getting mouthy in yours,” he noted amusedly.

And then he went on the attack.

I’d seen him move like that once back in Laure, when he’d decided that stabbing me in the chest was an acceptable way to end a conversation, but seeing it from a distance was an entirely different matter. When Captain was at her quickest I could still make out a blur, but with him it was like he just… appeared in another place. Stepping inside the warrior woman’s guard almost absent-mindedly, he swept his blade across the space where her throat had been a moment earlier: if she hadn’t taken a step back at the last moment, her blood would have been spilling in the dirt. She brought down her hammer’s handle on his shoulder, but he spun around and smashed the pommel of his sword into her elbow. She grunted and the impact loosened her grip, but Black was already moving again. He spun again and stomped down on the back of her knee, forcing it down as his blade went for the side of her neck. Captain managed to bring up the hammer’s handle at the last moment and block it, but hers was not a weapon made for defence and it showed. Not that it mattered, given their difference in strength – the instant she got her footing back, Captain pushed him off without any visible effort.

It was what he’d been waiting for, unfortunately for her.

He drew away as she pushed, letting her pass through and steadying his arm in the high-line guard he’d spent half an hour showing me earlier: he thrust straight into the back of her neck. It was a killing blow, or it would have been if he’d pushed it all the way through. Instead he stopped after pricking the skin, stepping back and sheathing his sword with a flourish as Captain cursed in Taghrebi. I recognized the plural of goats somewhere in there, and to be honest I was kind of glad I had no idea what the rest of it meant.

“And that’s a kill,” Black spoke, the lack of smugness in his tone so flamboyant it looped around back to smug.

Captain grunted and let her hammer rest against the ground, fingers coming up to touch the minute wound on her neck. “That makes what, two hundred for you?”

“And still one twenty-one for you,” he agreed. “The gap is widening, it seems. Are you sure \textit{I’m} the one getting slower?”

“You’ll need to beat Ranger at least once before you get to gloat,” she growled back.

I let out the breath I hadn’t known I’d been holding as the two of them continued to bicker amiably. So that was what it looked like, when legends fought. And not even a serious fight, I reminded myself.

“Triple drills,” I muttered to myself. “Triple drills, even if my limbs fall off.”
\clearpage
\chapter{Chapter 8: Introduction}

“\textit{Note: orc buoyancy is limited. Avoid fighting the damnable rebels near shoddily-built dams in the future.”}
– Extract from the journal of Dread Emperor Malignant II

They called Summerholm the Gate of the East.
Should the Legions manage to bypass the Blessed Isle – as they had a handful of times in the past – it was the only walled city between the Empire and the heartlands of Callow. It was the one city the Praesi \textit{had} to take, since it commanded the only bridge across the Hwaerte River. As far as I knew, the Wastelanders had only managed to conquer it twice: once during the Conquest and once over seven hundred years ago, under Dread Empress Triumphant. While my teacher had managed to reduce its walls through clever use of goblin engineering, Triumphant had simply made them obsolete by sailing her flying fortress right over them. I could see why she would have gone to such an extreme, now that I was in sight of those very fortifications. The side of the city we were facing was the least fortified, but even here the walls ran two concentric circles of stark granite over fifty feet tall. Crenelated bastions ran the length of them, most showing the silhouette of a siege engine, and even as close to sundown as we were there were soldiers manning them. \textit{Legionaries instead of the Royal Guard, though. Not that they’re any less well-trained – the opposite, if anything.}
“They look like they’re expecting an army any moment,” I commented as I guided Zombie towards Black with a tug of the reins.
His own horse was also a necromantic construct, I was sure of it – there was a certain… smell to that kind of power that I was beginning to pick up on – but it was hard to tell what it actually looked like under all the steel it was covered in. With all the weight that meant I was pretty sure his mount could double as a battering ram in a pinch, though that would do to the horse under it did not bear imagining.
“Summerholm has always been the keystone to warding off invasions,” he replied. “It continues to serve that purpose, if under a different banner.”
I snorted. “And who’d be doing the invading, exactly?”
For better or worse, the Empire’s hold on Callow was unchallenged. There’d been no major uprising since the Conquest, and with Procer embroiled in that particularly nasty civil war of theirs they’d had other things on their mind. That left the Free Cities to the south, who’d only ever managed to stop attacking each other when they were being invaded, and the fanatically isolationist elves to the north hiding in their forest.
“There’s always someone plotting nefarious designs around here,” Black replied drily. “It’s something of an occupational hazard.”
I rolled my eyes. I had a feeling there was more to it than that but my teacher declined to elaborate any further on the subject though, so I elected to let the matter go. I’d bring it up again when I’d acquired a better education on all things Praesi, of course, but until then there was no real point to it. Besides, we’d gotten close enough tot he city that I could see the Legion camps sprawled all around it. The official roster of soldiers for a legion was four thousand fighting men, I dredged up from my most recent readings, though the \textit{Praecepta Militaria} had stated there were usually about as many camp followers, merchants and servants trailing in their wake. It would have been impossible for a city the size of Summerholm to lodge two legions comfortably, so a pair of semi-permanents camps had been established outside the walls.
“Weeping Heavens,” I muttered, “It’s like a second city.”
However many civilians the Sixth and Ninth legions had started out followed by, the number had swelled out of control since. The central areas where legionaries slept were cleanly outlined according to regulations, overlooked by earthen walls and watchtowers, but around them small towns had sprouted into existence. Dingy huts made of wood and baked clay from the river banks made up up some of it, but there were twice as many pitched tents of all colours. Some avenues large enough for troops to go through had been established, but the rest of it was a messy labyrinth of small lanes. We were maybe an hour away from sundown but the place was teeming with activity, from the small courts were merchants were selling their wares in improvised market stands to the clumps of families making their evening meals in massive iron cooking pots. There was even a man trying to guide a herd of goats into a pen, though one of the does kept getting away to bleat plaintively at a very amused legionary.
“Summerholm is where Praesi and Callowans mingle the most,” Black spoke as our party started down the slope towards the camps. “All trade goes through it, so it’s fast becoming one of the richest cities in the Empire.”
“And there haven’t been any tensions?” I asked. “I heard the siege got pretty rough, towards the end.”
Summerholm hadn’t been sacked, not exactly – Legion regulations stated that rapists were hanged and looters lost a hand if caught with stolen property – but the final assault on the walls had been costly enough that no one on the Empire’s side had been particularly inclined to mercy when the surrender had been given.
“Rebuilding the city accrued some good will,” Black murmured. “And leaving eight thousand men and women in the prime of their life as garrison means that mixed race marriages were an inevitability.”
He paused for a moment.
“You’re not wrong, however. Summerholm is the pulse of Callowan sentiment towards the occupation: any rebellion with a chance of success will have its seeds planted here. Our agents have been keeping a close eye on things.”
\textit{Our agents.} I’d avoided questioning Black on where he was learning all these things he wasn’t supposed to know so far, but since he was bringing up the subject…
“The Eyes of the Empire,” I said. “That’s what your spies are called, aren’t they?”
They were famous among Callowans, a shadowy threat to match the very visible one posed by the Legions. Everybody had a story about how one of their cousins or a friend of a friend had been snatched in the dark of night by the ruthless men and women who bore the lidless eye tattoo. I was pretty sure I’d seen one in the Nest, once. Well, either that or a man with a deplorable fondness for hooded cloaks. Black’s lips stretched into a sardonic smile.
“Ah, the Eyes,” he mused. “One of Scribe’s better ideas, that.”
I frowned. “What’s that supposed to mean?”
“I have a great deal of spies in Callow, true,” he acknowledged. “So do Malicia and quite a few of the High Lords. But I assure you none of them go around hiding their face or bearing an incriminating mark.”
“But there \textit{are }people like that going around,” I pointed out. “If they’re not yours, whose are they?”
“Oh, they’re mine,” Black replied. “But they’re not meant to actually gather information.”
I closed my eyes and rubbed the bridge of my nose. The way the man thought gave me headaches, but there was a twisted sort of sense in what he was saying.
“So while everyone is paying attention to the shady people looming in the corners…”
“No one thinks twice about the waitress serving drinks just close enough to eavesdrop,” he finished amusedly. “Every resistance movement in Callow worth the name checks prospective members for the eye before letting them in. Letting them catch a few ‘attempted infiltrators’ every year lets us slip in agents when we really need them.”
My teacher was kind of a bastard, I reflected, but I couldn’t deny that he was a \textit{clever} bastard.
“And nobody’s ever seen through that?” I asked.
“Once you give people what they expect to see,” he shrugged, “they rarely bother to dig any deeper.”
I grunted, chewing over that particular tidbit in silence. He’d offered it almost off-handedly, but it seemed to be the way he approached a lot of things – playing on the assumptions of his enemies, making them think they had it right while preparing the knife in the back. Everything surrounding Names had a pattern to it, almost formulaic steps that every child learned from the cradle through stories of heroes and villains: people who adhered to those steps, whether consciously or not, became predictable in a way. It was something I could use to my own advantage, if I paid attention closely enough. Putting the thoughts aside, I returned to more immediate matters.
“So your agents in Summerholm,” I probed, “have they mentioned anything interesting?”
I already knew I’d have a welcoming committee waiting for me in the city: the three bundles of pressure in the back of my mind felt too close to be anywhere else. The fourth bundle, the weird one, was still a little ways off. It got stronger every day, though, which I took to mean it was headed in our direction. Black had avoided telling me too much about what awaited me in Summerholm, so far, but I had no idea whether that was because he was a cryptic jackass by nature or because there would be…. consequences if he did. Still, stumbling blind into the situation blind was a decent way to head for an early grave: I’d be much more comfortable going in with an edge, any edge. The dark-haired man graced me with a steady look.
“There are two major resistance movements in the city, at the moment,” he finally said. “The Sons of Streges – disaffected veterans, mostly – and a splinter group of the former Thieves’ Guild. My agents in both of them have stopped reporting.”
The tone was flat, a stark contrast to the way he usually seemed to take everything half-seriously.
“You think they got caught,” I said.
“They are either dead or held captive,” he stated. “There are ways through which they would have contacted the network, otherwise.”
I frowned. If a single agent had been caught it could have been a simple blunder on the person’s part, but every single one of them?
“Magic?” I questioned. “Truth spells are rare, but they’re not exactly unheard of.”
He shook his head. “There is no such thing as a reliable truth spell,” he informed me. “At best they can increase the odds of catching someone in a lie – and given how esoteric that branch of magic is, very few mages ever bother to study them. There are, as far as I am aware, none who have in Callow.”
It went unsaid that his awareness was as far and wide as it was feasible for someone with the resources he had at his disposal to manage.
“I’m having a hard time believing every single one of your spies screwed up at the same time,” I told him.
“So am I,” he said quietly. “Which means we may have a hero on our hands.”
Well, \textit{fuck}. “That’s bad, right?” I asked. “Because it sounds bad. I thought you caught these types before they ever got in a position to do stuff like this?”
“Once in a while, one slips the net,” Black admitted. “Normally they out themselves shortly after by taking a stand for justice in some backwater village, but this one has made no ripples at all.” He frowned. “Or, more likely, made them somewhere they went unnoticed.”
I grimaced. “Careful or lucky?”
“I’ve found the more dangerous heroes are a little of both,” the Knight replied. “The infestation is still limited to a single Role, I believe – if they’d assembled a whole party it would have been noticed – so we’re dealing with a very specific type of hero.”
“That already sounds more manageable,” I said. I didn’t know if I had it in me to stab a Bard, honestly. The were always charmingly ineffective in the stories, it would have been like kicking a puppy. “So, some lone wolf kind of deal?”
“A gritty avenging type, I’d wager,” Black replied. “They crop up with unfortunate regularity.”
So, three strangers who wanted my head on a pike, Role shenanigans and a hero on the loose. Evidently, my first visit of Summerholm was shaping up to be a memorable one. I let silence fall down and our party headed for the camps, riding off the main road into the countryside.
People came to greet us before we got into the camp proper.
A dozen legionaries in heavy plate were escorting a orc woman going without a helmet. On foot, all of them – the Legions didn’t really have cavalry to speak of, except for the Thirteenth. Captain pulled up at my side and I shot her a quizzical glance.
“Istrid,” she simply gravelled as the legionaries got closer.
Black dismounted and I followed suit after a heartbeat, standing a back as my teacher strode towards General Istrid. The general’s skin was almost more brown than green, I noticed: she looked like she’d been carved out of rough old leather, though that was common enough in the older orcs. There was a wide scar on her cheek that pulled at her eye, fixing her face in a mocking rictus that looked impressively firece on someone in full legion gear. She was one of taller greenskins I’d seen, though not quite as broad-shouldered as most orcs her size would be: still, she towered at least two feet above me. \textit{And above Black too}, I noted with amusement.
“Warlord,” she growled in Kharsum, offering up her arm the same way Lieutenant Abase had shown me a few days back. The word she’d used wasn’t the one I’d read in the books I’d been given, but the pronunciations was fairly similar – I suppose it might have changed since the manuscript had been written, or she could have been using a slightly different dialect. Black clasped her arm without hesitation.
“Istrid,” he greeted her in the same language, tone fond. “Couldn’t wait for us to make it to your tent?”
“I got bored,” she replied unashamedly. “You took your sweet time coming.”
“There was a situation Laure that needed seeing to,” the Knight spoke mildly.
The orc officer barked out a harsh laugh. “Heard about that. Finally hanged the fucker, huh? Been a long time coming.”
\textit{Ha!} I was already feeling rather better disposed towards General Istrid – anyone who wanted to see Mazus swinging from a noose couldn’t be all bad.
“Good things come to those who wait,” Black told her.
“Now you’re sounding like Sacker,” Istrid growled. “You two will be the death of me. Never mind that – Captain, that you hanging around in the back?”
The woman in question patted my shoulder and moved to join them, leaving me to stand with the ever-silent Blackguards and Scribe. Black’s band of bodyguards was no longer as silent as it had once been around me, but they’d reverted to silent statues as soon as we’d come in sight of Summerholm. I glance towards Scribe who had, I saw, also dismounted. She was standing closest to me, and since it didn’t seem like my presence would be noticed any time soon I ambled in her direction.
“They seem pretty friendly,” I said.
She wasn’t a very talkative woman, Scribe. The most I’d ever heard her say was that handful of sentences the first time we’d met, and since then she’d always seemed so busy I’d hesitated to try and strike up a conversation. No parchments in her hands now, though, and it wasn’t like I had anything better to do.
“They’ve known each other for a long time,” she replied, to my surprise. “Istrid’s clan was the second to side with Black, when he was still the Squire.”
Huh. That certainly explained why they were still catching up like old friends sharing drinks instead of heading to the general’s tent.
“Known her for long too, then?” I asked.
I knew precious little about Scribe, except that she’d been around Black since before the Conquest. None of the stories I’d heard mentioned her except in passing, and it wasn’t like she’d surrendered any information about herself since we’d met. I knew disappeared for a few hours everyday and came back with fresh new correspondence, but where and how she got the letters remained a mystery. The plain-faced woman shook her head. “I came later.”
\textit{Like squeezing blood out of a stone}, I thought. I shuffled awkwardly on my feet and tried to think of something to say, but was saved at the last moment by an outside interruption.
“Catherine,” Black called out. “Introductions are in order.”
I shot Scribe a mildly relieved look and headed for the cluster of old friends. General Istrid sized me up as I walked without even the pretence of subtlety and I straightened my spine out of habit. She wouldn’t take a stick to my fingers every time I slouched to make sure I had proper posture the way the House matron had, but then again I had a feeling that making a bad impression on the commander of the Sixth Legion would have more dire consequences than throbbing knuckles.
“Istrid,” the Knight said, “Meet Catherine Foundling.”
The tall orc frowned, then turned to look at him. “She looks like Wallerspawn,” she said in Kharsum.
I scowled, partly at her blatant dismissal and partly at the word she’d used – Waller was a term orcs used to mean Deoraithe but it wasn’t exactly a polite one. “Half,” I replied in the same tongue, painfully aware that my pronunciation was tetchy. “That a problem?”
That certainly got her attention. “Well,” she drawled, showing a row of sharp teeth, “at least you’re not shy. You sound Callowan, girl – where’d he dig you up?”
“Laure,” I replied. “You end up meeting all sorts of interesting types, when stabbing people.”
The general barked a laugh. “Ain’t that the truth. Well met, Catherine Foundling.”
She offered her arm to clasp and I reciprocated, somehow managing to keep my nerves off of my face. The general seemed a lot taller now that I stood in front of her and that rictus on her face hadn’t gone anywhere: she made for a rather intimidating sight, and the story of her staring down a charge of Callowan knights was still fresh in mind. \textit{Possibly she scowled at them and they decided they had better things to do somewhere on the other side of the Tyrian sea.} \textit{Gods know I kind of wish I did.}
“Let’s not make Sacker wait too long,” Captain spoke up as I stepped back. “Odds are she already has eyes on us.”
“Sucker’s bet,” Istrid grunted before turning to address her legionaries. “Stable the horses and find somewhere for the Warlord’s retinue to stash their gear.”
A chorus of salutes was her only reply and I handed off Zombie’s reins to an olive-skinned woman with sergeant’s stripes when prompted. General Istrid led the way to one of the avenues I’d glimpsed earlier, followed by Black and Captain – I glanced back to see if Scribe was following us, but she’d disappeared into thin air when I wasn’t looking. \textit{Wait, wouldn’t have had to pass next to us to} g\textit{et into the camp?} A large hand settled on my shoulder, gently steering me forward. “She does that,” Captain gravelled. “It’s part of her Role to stay in the background. She’ll pop up again when she’s needed.”
How much of my not noticing Scribe had come from her being quiet and how much had come from the effects of her Role, I wondered? I muttered something that could pass as agreement and let the matter drop. Sundown was almost on us, and as a result activity in the wider camp had died down: the improvised markets were closing and people were trailing out of the camp and heading towards the gates of Summerholm.
\textit{I suppose it makes sense that not all of them stay here after nightfall.} For another group getting through the crowds quickly might have been an issue, but everyone was giving us a wide berth. Nobody was quite so bold as to point fingers in our direction, but quite a few people seemed to recognize Black and Captain – whispers bloomed in our wake wherever we went. The weight of the attention made me uncomfortable: the feeling of the three other potential Squires hadn’t gotten any closer, but I had more than them to worry about now. There might very well be a hero somewhere in the masses, and if they were looking for a target I was painfully aware that I was the easiest one available. I was not, after all, so deluded as to think that half a Name and a week’s worth of training with a sword and board would make me a match for a veteran of the Conquest like General Istrid. The grip on the short sword at her hip was well-worn, and she walked like someone who thought of their weapon like an extension of their limbs.
We encountered two patrols as we delved deeper into the impromptu town, both of them stopping to salute as we passed by. More and more legionaries stood watch as we got closer to the actual Legion camp – well, one of them anyway. The standards spread out everywhere all bore the Sixth Legion’s number in Miezan numerals, so it was pretty obvious this was theirs and not the Ninth’s. By the time we made it to the large pavilion that apparently served as General Istrid’s council room, night had fallen. Torches were already burning, though they were hardly needed considering how many cooking fires there were out there: the trail of smoke in the sky must have been visible for miles. The inside of the pavilion was empty except for a large table of polished wood surrounded by comfortable-looking chairs. There was only one person inside: a small goblin woman, under five feet tall and so heavily wrinkled her face looked like a mask. General Sacker, I assumed. She looked almost half-sleep, her yellow eyes were half-lidded even as she gave me an once-over before turning towards my teacher.
“Lord Black,” she murmured from her seat, bowing her head ever so slightly.
She was so quiet I almost missed the words, but the green-eyed man nodded back without missing a beat.
“General Sacker,” he replied, “It’s been too long.”
She inclined her head again.
“Gods Below,” General Istrid interrupted with disgust, “the both of you sound like you’re attending a feast at the Tower. I’m going to need a drink, if we’re doing the fucking Praesi rituals.”
“Finally,” I muttered, “someone’s willing to say it out loud.”
Istrid shot me an amused look as she poured herself a cup some sort of amber liquor from one of the carafes on the table. When I returned my attention to the others, I found that General Sacker was looking at me – and there was no longer anything half-asleep about her demeanour as she studied me. I’d always heard calculating eyes referred to as cold and cool, but if anything the yellow gaze pinning me seemed to burn with focused intensity. \textit{Clever as a snake and twice as mean}, Captain had told me.
“You’re from Laure,” General Sacker spoke in the same whisper-thin voice. “Interesting. Orphan?”
I wasn’t sure who the question was addressed to so I glanced at Black, but he’d already claimed a seat and was pouring himself a drink from the same carafe as Istrid, paying no attention to the conversation. \textit{Worst mentor ever.}
“I am,” I confirmed warily.
Sacker nodded to herself. “Calloused hands, mhm. Fighting rings? Illegal in Callow, I do believe.”
Her tone didn’t make it clear whether she approved or disapproved.
“So I’ve heard,” I simply replied.
I had no idea what her game was, but it felt like she was toying with me and I very much disliked the feeling of it. My first instinct was to bite back, but I pushed it down. There was the fact that Captain had specifically warned me about her, of course, but there was more to it than that. General Sacker was \textit{old}. By far the oldest goblin I’d ever met and that made her very, very dangerous – most of their kind never made it past thirty five, and looking at the general I guessed she was pushing forty. Older goblins were notoriously frail and sick but Sacker was still not only in command of a legion, but of a legion holding one of the most important fortresses in the Empire. She was, in short, \textit{not someone I wanted to fuck with}.
“You can mess with her head later, you vicious old bat,” Istrid broke in cheerfully, apparently not caring about any of that in the slightest. “We’ve got fresher corpses to eat, like our little hero problem.”
General Sacker pursed her lips.
“There’s not definitive proof that we have a-”
That was when the pavilion exploded.
\clearpage
\chapter{Chapter 9: Claimant}

“\textit{Gaining power’s a lot like scaling a tower, Chancellor. The longer you do, the more likely you are to fall.”}
– Dread Empress Regalia the First, before ordering her Chancellor thrown out the window

I was swatted down by the hand of an angry god, fire licking at my face.

The world went silent and dark until I realized I’d closed my eyes: when I opened them I still saw spots of colour but the fear of having gone blind that had taken me for an instant left my frame. Everything around me was smoking or on fire: the top of the pavilion had been outright blown away and the rest of the cloth was twenty feet away, cheerfully burning. I pushed myself up, noticing with a grimace that the elbow joint of my armour had been partly melted by the heat. The damned ringing in my ears made it hard to focus on anything, but when I passed my hand over my face I felt with dismay that part of my eyebrows was missing. My fingers came away covered in soot but I pushed concern over my appearance way down the priority list: whoever had just attempted to kill every one of us might still be around, and the second shot might be a little more accurate.

Black was already up and about, helping up a prone and shaky-legged Istrid as Captain hovered around him protectively. I reached for my sword, checking wearily wether the heat had damaged the scabbard – no, it still came out just fine. \textit{Good. Now, time to disembowel whoever was responsible for that. My eyebrows are like, my one good feature.} Someone kicked my ankle and I felt it through the aketon, only now noticing that my left greaves had somehow been blown away during the impact. I snarled and look down only to find General Sacker staring back up at me peevishly. I gaped at the sight of her: half of her face was gone, a wasteland of blackened flesh with hints of meat peeking through. One of her eyes had popped out of its socket, not that she seemed to care in the slightest. She snapped her fingers in front of my face several times and –

“-can’t hear me at all, can you? Typical Callowan, all bark and no-”

“Now let’s not make this a cultural thing,” I rasped out. “Do you hear me talking about how goblins always look like they’re up to something shady?”

She slapped me. I snarled at her and reached for my sword before common sense could kick in. T\textit{hat little-}

“Just making sure you’re not in shock,” she grinned malevolently at me, baring a mere handful of broken yellow molars.

“Maybe I should make sure of the same,” I told her through gritted teeth. “You know, just in case.”

She swaggered away towards Black without replying, though how someone who’d lost half their armour – and face – in the blast could manage a swagger was beyond me. \textit{Don’t kick the Praesi general, Catherine. It’ll be very gratifying, but there’ll be Hells to pay afterwards.} I followed Sacker, making a point of getting ahead of her through use of my Heaven-gifted longer legs.

“– put the camp under lockdown. I don’t want anyone getting out,” Black instructed Captain.

“They’ll be long gone,” the gargantuan woman replied. “But there might be a-”

“I’ll survive without you dogging my shadow for an hour,” he spoke, tone flat and emotionless. “\textit{Go}.”

She went without further protest, stopping to look me over as she passed me by before moving on with a silent nod.

“Fuck,” I heard Istrid gasp as she leaned on Black’s arm. “Been a while since I’ve been on the receiving end of one of those.”

I looked around and found that, strangely enough, a single chair had been left untouched by the carnage except for being knocked over. I strolled away to pick it up and place it next to General Istrid, acknowledging her grateful glance with an inclination of the head.

“So, out of curiosity,” I rasped out. “Did someone just drop a godsdamned comet on us? Because that’s a bold opening move, not gonna lie.”

“No. Goblin munitions,” Black replied.

“Sharpers,” Istrid specified in a growl. “They always mess with my hearing.”

“A bad batch,” General Sacker murmured. “Otherwise I wouldn’t be standing right now.”

The tall orc seemed to notice that half of her colleague’s face had been kissed by fire just then, a flicker of surprise and dismay going through her eyes.

“Well,” she gravelled after a moment. “How many eyes do you really need, anyway? You can get an eyepatch that matches Grem’s.”

Sacker palmed what remained of her face, looking pained for the first time that night. I ignored the byplay, mind already spinning. Goblin munitions, huh. I knew a few things about those, though not as much as I’d like. \textit{Sharpers blow, if you’re too slow. Smokers choke, and then you croak. Brightsticks blind, and none too kind.} Children in the Laure had a whole game made up around the rhyme, a sort of morbid take on what Imperial sappers had done to the enemy during the Conquest.

“Sharpers wouldn’t kill a Name without a good spot of luck, would they?” I suddenly asked, looking at Black.

A heartbeat passed as the cogs between those unsettling green eyes turned and arrived at the same conclusion I had.

“We weren’t the target,” the Knight stated. He glanced at the two generals thoughtfully.

“If I wanted to create a right mess in Summerholm,” I spoke up, “first I’d off the people commanding the garrison and then-”

He grimaced. “The Governess.”

Legionaries had finally arrived on the scene and immediately my teacher pulled one of them aside, sending him to check on Governess Kansoleh with a few curt sentences. Only after that did he return the full weight of his attention to me.

“There will be no lesson tonight,” he said. “I trust you’ll manage an evening by yourself?”

“I’ll find a way to keep myself busy,” I replied neutrally.

It suited me just fine, as it happened: lately I’d been going with the current a little too much for my tastes. While I didn’t doubt that at some point I’d be introduced to the three bundles of murder in the back of my head in a formal capacity, I had no intention of waiting that long to get a closer look at people who were supposedly out for my blood. Surrendering the initiative was starting the fight on the defensive, and I’d always been an attack-minded kind of girl. The Knight paused to meet my eyes, a long moment passing before he snorted.

“Talk with Scribe,” he said. “She’ll see to it you have what you need.”

\textit{I really need to find a book on Names}, I decided.\textit{ If he can’t read minds, I think that would actually make it creepier.}

Displaying his usual level of helpfulness, my teacher had not deigned it necessary to tell me \textit{where} Scribe was.

Thankfully, I lucked out when I asked a legionary to direct me to wherever the Blackguards had been settled. None of them were actually in the temporary barracks – if I’d had to guess, I would have said they would have started running towards Black as fast as they could the moment they heard the explosion – but the woman in question was kneeling on the ground in front of a low table already covered in parchments. I tried to get a glimpse, but none of it made sense to me: it was gibberish in a mix of Kharsum and Mthethwa, as far as I could tell. \textit{Cyphered, most likely.} The flat indifference she was displaying in her own quiet way was at odds with how close to Black I’d thought she was – wasn’t she worried even a little bit? A sharper wouldn’t kill a bloody Calamity, but it could have wounded him pretty badly.

“No one died,” I told her. “Black’s not even wounded – General Sacker got the worst of it.”

“I know,” Scribe replied, adroitly dipping her quill in the inkwell.

I might as well have tried to empathize with a statue. A particularly unconcerned statue, even. Pushing down a sight, I knelt across the table from her.

“I’m going to be heading out into Summerholm,” I said. “I need a few things before I do.”

I wanted a quiet look, not a melee in the streets of a city that had just gone into high alert, and that meant no armour and no Praesi clothes. I was keeping the sword, inconspicuous as it would be, because screw going unarmed in a city with a hero loose in it – especially a hero that considered blowing up people a valid tactic. Scribe pointed to my left and I followed the finger to a bundle of clothes resting on a shelf. 

“Bullshit,” I replied flatly. “How could you possibly have known I would need those before I even did?”

Scribe glanced up. “I’ve had those set aside since we left Laure,” she simply said.

I was starting to hate that I was playing a game where everybody seemed to know the next ten moves except for me, I thought with a scowl. It came in useful more often than not, sure, but it also left me with the sensation that I was being herded towards a finish they’d already planned out for me. What was I going to do, though, complain my needs were being seen to \textit{too} well? \textit{Yeah, I’m overdue something reckless. Been walking down roads they paved for me a little too much.} Without a word I shed my armour and the still-singed aketon underneath, slipping on the woollen trousers and short-sleeved blouse that came with it. Good make, both of them, but not so expensive as to warrant a second look.

My old boots had been preserved and it was a glorious feeling to wiggle my toes inside the used leather instead of the steel-capped stuff I’d been given before we moved out of Laure. I already felt a little more like me and a little less like a doll dressed up in Evil clothes. With the goblin-steel sword and my knife on either sides of my hips I was fully equipped for murder if it came down to it, which if Black’s line about the intention of the other Squire claimants was accurate it very well might. There was also a leather purse with some coins in it, which might come in useful: about twenty silver coins, with the Marchford crest on them. They wouldn’t be as widely accepted as Praesi denarii – Countess Marchford was well-known to short the precious metals in her currency – but they’d certainly attract less attention than a Deoraithe girl running around with a purse full of Imperial silver.

“I’m heading out,” I told Scribe. “Have fun doing… whatever it is you’re doing?”

The plain-faced woman hummed in response, which seemed to be the sum of the attention she was willing to grant me. I walked out of the barracks, already focusing on the other claimants as I did: one of them had gotten a little closer, as it turned out. 

I smiled grimly: time to check out the competition.

Outside of the Sixth’s military camp, the tent city was a lot like a hornet’s nest that had just received a good kick. Legionaries had pulled back to their fortifications and now refused to allow anyone through – at least coming in, I had no problem getting out except for a few suspicious looks – which had not gone unnoticed by the civilians. The explosion itself had not been a cause for panic, since any halfway decent mage could manage something just as loud, but the way the legions had reacted in the aftermath made people nervous. Yet not, I saw, nervous enough to shut down all activity for the night. The sea of torches and camp fires shed light in a way that made the labyrinth of tents look like actual streets instead of empty spaces, and while people went about their business quietly they were still very much out and about. I kept to the shadows as I tried to narrow down where the closest claimant actually was, something made increasingly difficult by the way he or she kept moving away when I got closer. It occurred to me for the first time that the… sensation might go both ways – if I could tell when they were close, could they do the same?

That could make this whole spying business unfortunately difficult, if it were true.

I might as well assume it was, given how my luck tended to run. Which meant his was no longer about sneaking around: it was about cornering a quarry. I found myself wishing I’d paid closer attention to the layout of the camp, but what little I remembered from earlier would have to do: I was somewhere to the left of the legion fortifications, I knew that much, so now I just needed to drive the stranger into a place where there was no crowd to hide behind. Ignoring the huddled families casting curious looks in my direction, I closed my eyes and tried to sink deeper into my Name like I had when I’d helped Black raise Zombie. It was harder without his own power to act as an anchor for mine, but this was also less… complex to accomplish. It was like my Name \textit{wanted }me to know, and it required focus more than direction. The other claimant was a little north of me, moving towards the larger avenues, and I would have none of that: the less people around for this, the easier it would be to pick out my quarry. I moved in between and the presence backed off.

\textit{Yeah, they can definitely feel me too.}

I ducked around a tent, moving as fast as I could without outright running, and the sensation kept giving ground. Twice it tried to circle around me, but I was quicker: as soon as I got in the way the presence back-pedalled, staying out of my sight if not out of my mind. How long we played this game of cat and mouse I wasn’t sure: night had fallen a while back, and the smoke from the fires made it hard to get a good look at the moon. It was a tedious business, but I grit my teeth and did it anyways – it was a long, methodical grind to force the claimant somewhere I’d be able to look at them, but as long as I remained calm and methodical it was just a matter of time. Eventually, we ended up close to the edge of the camp. There were fewer fires out here but Black’s earlier prediction had come true: I saw better in the dark than any human should. I felt the presence pause as it neared the open ground and a feral smile stretched my lips. \textit{Where are you going to run now, my pretty? }I put a spring to my step and moved towards the now-still claimant, slipping between tents as quick as I could to make sure they wouldn’t have time to try and circle around again.

The presence in my mind was suddenly snuffed out.

The surprise nearly made me stumble, but I caught myself at the last moment. My hand drifted to my sword, and with a sinking feeling I struck me that I hadn’t been the only one playing a game tonight. Here I was, far away from any witnesses and alone in the dark with only my sword for company.\textit{ I wasn’t running the bastard down, }I realized\textit{, I was being baited.} And I’d fallen for it like a farmer buying magic beans, which added insult to the very real risk of injury.

“Well,” I muttered to myself, “no need to be coy about this.”

I drew my sword and wished I’d taken my shield with me, even if it would have made me stick out like a sore thumb. The tents surrounding me had seemed like nothing more than irritants getting in my way, earlier, but now every one of them could be cover for someone wanting to slit my throat. My nice little moonlit walk was taking a sinister turn, but I forced myself to take a deep breath. \textit{Fear is sloppiness. Fear is the fault line in solid stone. Fear is the enemy’s mind, drawing blood before his sword. }The words stilled my heartbeat and I let anger flood my veins instead. I might have fallen for my enemy’s trick, but I was not without fangs of my own.

“So,” I called out into the silence. “Are you going to make me wait all night?”

There was no warning except for a flicker of movement at the edge of my sight – the shape moved fast, faster than I’d seen anyone without a Name ever move, but I’d been waiting for it. In a flutter of robes my enemy struck, scimitar coming low for my leg. I managed to bring up my sword down in time, the angle awkward but good enough to stop the blade from scything into my flesh. I only got a quick look at whoever was attacking me before they leapt back before a tent, ducking out of sight: long dark robes that hid the body shape and some sort of clay mask over the face. Taller than me, but not real way to tell if it was a man or a woman. The claimant did not attack again, silence falling in their wake. I tightened my grip around the handle of my short sword taking a careful step back as I considered my options. Did I want to turn this into a death match?

I was reluctant at the prospect of killing three strangers, even if it got me a Name, but this particular stranger did not seem to be overly burdened by the same moral objections. Taking out one of the contenders early appealed to the fighter in me – one less person to worry about – but I’d been given to understand that I was already ahead of the curve when it came to claiming my Name. Killing one of the claimants on my first night in Summerholm might drive the remaining two to work together against me. \textit{And I don’t know if I could handle that. If this bastard’s disappearing trick is any indication, they have a few cards up their sleeves I didn’t even know were in the deck.} They came from behind, this time. Thank the Heavens for those robes, otherwise I wouldn’t have heard it coming: I turned around and struck blindly, hitting nothing but air but forcing the claimant to move around my swing. The clay mask and its creepy leering rictus looked back at me silently as my opponent tried to slice up my wrist. I got the pommel in the way but the masked claimant’s scimitar slid down and bit into my fingers – I drew back with a curse, trying to kick them in the crotch as they melted back into the dark.

“Fuck,” I swore again, taking a look at my hand.

It stung like a bitch but the cut wasn’t deep: I wasn’t at any risk of losing the finger. It was bleeding a lot, though, and that was dangerous if left unattended – worse, it was making my grip slippery. \textit{And that’s why we wear gauntlets, Catherine}.

“First blood to you, you creepily silent masked ambusher,” I conceded out loud. “Still, to quote-”

I felt someone moving behind me again and bared my teeth. This time the blade came for my throat and I ducked under it, burrowing my fist in my opponent’s abdomen with great relish. The pained groan I heard even through the mask was sweeter than any hymn and before they could step back I slammed the pommel of my sword right in their mask. A chip fell off of the cheek and they rocked back – after a moment of hesitation the stranger ducked out again before I could press my advantage, dodging the point of my blade by less than an inch.

“-to quote a really unpleasant acquaintance of mine, last blood is the only one that matters,” I finished, falling back into a low guard.

I’d wondered why someone who was so intent on surprise would have first struck after I’d invited a hit. It was after they attacked the second time I’d understood why: the robes made noise when they moved too fast, so they’d taken advantage of the sound of my voice to cover it. It had made the third strike easy to predict, though I doubted it would work again. I checked my hand again, grimacing when I saw the blood was soaking my grip and dripping to the ground. I couldn’t let this go on for too long, the more it dragged out the larger my opponent’s advantage got. \textit{All right, the time for subtle is done. It’s never been my specialty anyway.} If my enemy was using the environment we were in to their advantage, then there was an obvious solution: break the godsdamned environment. I kicked the stakes keeping together the tent closest to me, ignoring the angry yells that came from inside as it fell and I cut through the rope holding up the one next to it.

To my opponent’s credit, they were on me before I could bring down a third. I slapped aside the scimitar coming for my kidney with the flat of my sword, moving in close. The masked claimant tried to push me back, but to my delight I discovered I was stronger than them: when I shoved back they stumbled, immediately giving ground as I pursued. From the corner of my eye I saw people coming out of the tents, faces turning from angry to fearful the moment they saw people with swords in hand. An older man grabbed his daughter by the hand and legged it, which brought a hard smile to my face. They were getting legionaries, most likely, and chances were good those would side with me over my opponent. The stranger must have thought the same, because they stopped backing away and returned on the offensive.

I knew how to handle them now, though. \textit{I own close range, you quiet bastard. We’re dancing to my song now.} I kept pushing forward, watching for the blade and driving my opponents into tents as they tried to put a little distance between us. The masked ambushed was in the tricky position of having to keep an eye on me as they stepped back, though, and after a moment they stumbled over a stake. That was the opening I’d been waiting for – the point of my blade missed the throat but slid into their shoulder. I was forced to step back by a wild swing of the scimitar, but I laughed: now the both of us were bleeding, and that wound was a lot worse than mine.

“Cow,” the stranger hissed through the mask in Taghrebi, the voice distinctly male.

He hadn’t said cow, exactly – the actual word he’d used meant \textit{bull’s daughter}, though the meaning was the same. Very roundabout language, Taghrebi.

“Goat-husband,” I replied cheerfully in the same tongue, drawing on the extensive repertoire of insults Captain and Lieutenant Abase had been teaching me when Black wasn’t paying attention. His fingers touched the wound and came back red: I raised an eyebrow when he used the blood to trace a line across the clay mask. 

“Would it be culturally insensitive to ask what in the Hells you just did?” I mused out loud.

“This isn’t over,” the boy hissed again, and Weeping Heavens why did villains always say shit like that before trying to run away? He might as well have sent me a written warning he was about to flee. He turned to make his escape but \textit{screw} that: my schedule was tricky enough without having to watch over my shoulder for a vengeful masked jackass waiting to pounce at any moment. Our very dramatic confrontation turned to a very ridiculous foot race in the dark. Now and then he tried to duck around a tent and do the melting-in-shadows trick he’d pulled on me during the fight, but it seemed to fail if I had an eye on him while he was doing it.

He was trying to get back towards the crowd where he could hide among the crowd, but that kind of thing was harder to manage when I knew exactly what he was trying to do. He must not have known the layout of the tent city much better than I did, because our little race took an unexpected turn when he took a left into an alley that ended into a stone wall – a legion supply house, by the looks of it. He slowed when he realized he’d run into a dead end, turning to face me. I could see him pant through his robes, the red stain on his shoulder soaking the dark fabric further every moment. I was in slightly better shape, though not by much: fight in the Pit tended to be on the short side, and they rarely required much running.

“Well,” I gasped out, catching my breath. “I was aiming for a talk, but I suppose shanking you in a dark alley will have to do. In all fairness, you started it.”

I brought up my sword into the middle line and slowly strode forward.\textit{ }People were at their most dangerous when cornered, I knew, and so I stepped lightly. Barely three feet in front of me, a small clay cylinder landed in the dirt – there was a fuse on tip of it, nearly done burning. The children’s rhyme drifted to the surface of my thoughts almost mockingly: \textit{brightsicks blind, and none too kind.} “Shit,” I cursed feelingly, closing my eyes just before it blew. 

Looking straight into the flash was a good way never to see anything again, and even through my closed pupils the explosion light was horribly painful. Colours swam in my eyes and all I could think of was that I hadn’t seen the masked bastard throwing anything but I knew of at least one person with access to goblin munitions with a vested interest in seeing the both of us dead – I turned so that I’d have a tent at my back, refusing to give my ambusher a clear shot at me even as I half-faced the new threat. I heard two sets of steps coming down the alley, and when my vision cleared there were two people looking back at me. One was a goblin, the strangest-looking I’d ever seen: there was not a speck of green on her skin, all of the flesh bared by her chain mail a shade or red nearly orange. Next to her a tall Soninke girl with a white veil over her face was eyeing me curiously, a long spear propped up against her shoulder. It looked like a bridal veil to me, but she was no Callowan: to the Soninke, white was the colour of death. I felt the masked jackass move behind me and my eyes flicked back to him, my sword rising back to middle-line immediately.

“Now that we have your attention,” the goblin jeered. “Why don’t we all have a nice little talk?”

I didn’t need to reach for my name to know who those two were. \textit{Well}, I thought to myself.\textit{ I did want to check out the competition.}
\clearpage
\chapter{Chapter 10: Menace}

“\textit{Threats are useless unless you have previously committed the level of violence your are threatening to use. Make examples of the enemies you cannot control so those that you can will be cowed. This is the foundation of ruling.”}
– Extract from the personal memoirs of Dread Emperor Terribilis II

“Do not get between me and my prey, fools,” the masked man growled.
“Are you trying to talk trash after running away from me for, like, half an hour?” I gaped. “I only hit your head the once, your brains can’t possibly be that scrambled.”
The tall girl with the spear smirked. “Now now, it’s not his fault – desert vagrants are born with only half a mind,” she contributed.
I tried not to look too obviously amused. Apparently the Miezan occupation hadn’t done as much to curb the age-old distaste between Soninke and Taghreb as some of my books had implied.
“\textit{Humans},” the red goblin sneered. It was an impressive sneer, even compared to the unmourned Governor Mazus’. I bet she’d practiced it in front of a mirror. “You cant get back to your games after we’re done talking.”
“Let’s not be hasty, Chider,” the Soninke replied. “It’s not really murder if she’s doing it to a sand rat.”
Well, that had gone downhill fast. I could sympathize with wanting to mock some of your fellow countrymen – I \textit{did }know an uncanny amount of jokes about southern Callowans – but she seemed to genuinely believed what she’d just said. \textit{Right, Praesi. Not the most morality-oriented people, generally speaking.} With a sigh I sheathed my sword, keeping a wary eye on the masked wonder.
“Considering you just threw a brightstick at us – which was pretty rude, for the record – it might be a good idea to move before legionaries come have a look,” I suggested.
Someone using goblin munitions after the same had been used in an attempt to off two generals would lead to all kinds of unpleasant questions, and I was beginning to get curious about what it was the two fresh additions to this little party wanted.
“Assuming jackass over there is willing to talk at all,” I added as an afterthought, noting my ambusher still had his scimitar in hand.
“We claimed a fire pit not far from here,” the goblin – Chider, apparently – mentioned, turning red-rimmed eyes to my now-silent opponent. “I offer you the shelter of my fire, stranger.”
The last words she’d spoken in Taghrebi instead of Lower Miezan, using a phrasing I wasn’t familiar with. My Mthethwa was a lot better, mostly because I’d practiced it more. My ambusher’s mask dipped by a fraction and he slipped his scimitar back in its scabbard.
“Speak the words,” the still-nameless Soninke said sharply. “Guest right goes both ways.”
The man hissed at her, though he went still when the spear left her shoulder to point in his direction. I would have taken a step back to get out of the way even further if I could – I was definitely up for a spot of masked bastard stabbing, but the goblin was still a wild card. She had a haversack slung over her shoulder, and I’d bet piglets to diamonds that there was nastier stuff than brightsticks waiting under the leather.
“Fine,” he spat. “I take shelter in your fire, hearth-keeper.”
“That’s better,” the veiled girl smiled, her teeth barely visible through the sheer fabric.
“Is Praesi cultural fun times over yet?” I asked politely. “Because we really need to get the Hells out of here, if we don’t want to spend the rest of the night in Legion custody.”
“A Callowan that speaks sense,” Chider commented. “Now I’ve seen everything.”
What was it with goblins and insulting me? Did I smell in a way that pissed them off?
“Wow,” I retorted with a hard smile, “a mouthy goblin. Never seen one of \textit{those} before.”
The Soninke unconvincingly tried to turn her snicker into a cough. Chider shot her a disgusted look and strode away. Not friends, then, just allies of circumstance. Good, it would have been tricky to deal with them if they were intent on sticking together. I had, after all, already stabbed my only other prospective ally. I made to follow the goblin, carefully keeping my distance from the man in question. The tall girl waited for me, offering her arm to clasp when I got close enough.
“Tamika,” she introduced herself as I grasped it.
“Catherine,” I replied. “So what’s all this about, anyway? I thought this whole thing involved a lot more fights to the death and a lot less talking.”
Tamika shrugged. “The goblin wants to have a meeting before we dance the dance, and I see no reason to refuse her.”
She was pretty cordial, for someone who’d just casually mentioned she wanted to kill me. Chider’s fire was easy enough to find, not far around the corner. She was already sitting on a stone besides it, prodding the burning wood with a long branch – our arrival was welcomed by a fresh new rendition of her earlier sneer, though this time she’d didn’t bother to insult me. This was, I guessed, as close to friendly as she was going to get. I claimed a log for myself, taking a moment to have a look at my hand while everybody was settling down. The bleeding had stopped, though I had a feeling that flexing my hand would tear the cut right back open. I’d need to have it looked at, if I didn’t want it to go bad. \textit{Unless Names mean you can’t take sick anymore}, I mused. \textit{I’ve certainly never heard of a hero laid low by fever, not unless the wound was cursed.}
“So I hear you’re the one who arranged a get-together,” I addressed Chider when the silence got too heavy. “Why?”
The red-skinned goblin prodded the fire one last time before throwing the branch in.
“There’s a hero in Summerholm,” she said, to the surprise of no one around the pit. “That means we have another way of solving our dispute than killing each other.”
Tamika made the same weird clicking sound with her tongue that Lieutenant Abase sometimes did.
“Hunting a hero is not something undertaken lightly, goblin,” she said. “Besides, there are people in the city with better claim to that life than us.”
“If you mean Black,” I grunted, “then I’m pretty sure he’d approve of us taking care of the problem.”
There was a moment of perfect silence as all three of them turned to stare at me.
“Then it is true,” the masked man said. “You came here with the Carrion Lord.”
\textit{Another title? Weeping Heavens, like he doesn’t have enough already.} I straightened my back, meeting them stare for stare.
“Rumours move fast around here,” I replied, declining to actually confirm the assumption.
From the way Chider’s eyes narrowed at the words, that particular fact had not escaped her notice.
“Spilling each other’s blood will only weaken the Empire,” the goblin said. “This is a better way.”
“Spilling the blood of the weak can only strengthen the Tower,” the masked man retorted immediately, tone contemptuous.
“That’s a funny thing to say, considering you’re the one who’s bled the most,” I smiled at him.
His hand drifted towards his scimitar, but before he could reach it Tamika cleared her throat.
“Take that out and you won’t live to see morning, Taghreb,” she told him in a very friendly tone.
The man scoffed, but after a moment he backed down. Proud, then, but not completely stupid. Just mostly.
“What’s your name, anyway?” I asked. “The things I want to call you won’t cut it in polite company.”
“Rashid,” he told us, as grudgingly as if I’d asked for his firstborn. “Remember it, for when the devils ask you who sent you to the Other Place.”
“I’m Catherine, in case you hadn’t overheard,” I told Chider, ignoring the man. “So you want us to make a pact, then. A truce until one of us manages to get the hero?”
“Precisely,” the goblin replied. “I do not ask for your cooperation, merely that you stay out of my way.”
“I could agree to that,” I mused. “Seems pointless to have a go at each other when there’s someone out there who wants all of us dead. Tamika?”
The Soninke rolled her spear between the palms of her hands, face expressionless.
“It would be a worthy test of my skills, to measure myself against a hero rather than one of you,” she finally said. “This truce would extend no further than the death of our common enemy, yes?”
I wasn’t exactly happy that the dark-skinned girl was looking for an escape clause before she’d even agreed to the terms, but it was still better than nothing. It wasn’t like I hadn’t been intending to keep a close watch on my back the whole time, anyway.
“Is that a yes, human?” Chider probed her.
Tamika shrugged. “I accept those terms. May the Gods devour whoever breaks them.”
Everyone’s eyes turned to Rashid. It was irritating that the mask prevented me from reading his expression, but I supposed that was rather the point of wearing it in the first place.
“This was a waste of my time,” the man replied with undisguised scorn. “I will hunt this hero, but you are all my enemy.”
He rose to his feet, robes stained red.
“We have unfinished business, Callow girl,” he said in a tone that he probably thought passed for sinister. “We will see each other again, I promise you that.”
I sighed as I watched him stalk away into the night. My fingers clenched around the hilt of my sword as I considered whether or not I should follow him: we were more or less done here and the idea of just letting the bastard go didn’t sit right with me. I’d already killed people for lesser reasons than the one he’d given me, after all, and his wound had to have weakened him. \textit{I might not get an occasion like this again.} I was about to politely take my leave when I saw the two others were staring me down.
“I know what you’re thinking about,” Tamika smiled pleasantly. “Don’t.”
“You’re not the one he wants to stab in the back,” I replied. “You don’t get a voice in this.”
“He’s still protected by guest-right until dawn comes,” Chider murmured. “Let’s not make this any messier than it has to be.”
The implied consequence of breaking said guest-right was clear, though if they thought whispered threats would be enough to cow me they had another thing coming. What did I care about whatever Praesi thought was honourable? I’d work with the Empire, with every monster and murderer who’d slaughtered their way to power, but that sure as Hells didn’t mean I’d do it following their every custom. What was the point of playing a game by the rules, when it was rigged for you to lose? \textit{That said, is getting another shot at the bastard worth alienating these two?} I weighed my options carefully. Chider I thought I could handle, if I managed to get up close fast enough. She’d think twice about using munitions if the both of us were in their range. The Soninke was the one who gave me pause – spears weren’t a weapon that saw much use outside of the Free Cities, but the comfortable way Tamika carried hers suggested a degree of familiarity with the weapon that was very, very dangerous. In contrast, I had barely a week of sword lessons under my belt. \textit{Pick your fights, Catherine.} Letting Rashid go was a pain, but getting into it with the other claimants on ground I hadn’t picked while still wounded was a good way to get myself killed – especially if they worked together, which they very well might.
“Until dawn, then,” I conceded, making a mental note of looking into Taghreb guest-right and all it entailed.
I couldn’t afford to get trapped into situations like this often, and I had a feeling it would only get worse when we got to the Wasteland. With a somber nod I took my leave of the other claimants and begun the long walk back to the Sixth Legion’s camp. I might as well grab some sleep before I got back to work.

By the time I got to the now-closed gates I’d realized I hadn’t thought this whole thing all the way through. Getting out had been easy enough, which not that I took the time to think about it was rather surprising: he’d ordered a lockdown of the camp. Then again, he would have had the time to send a messenger to make sure I’d go through unmolested while I spoke with Scribe. It seemed ungrateful to complain that my teacher had anticipated my needs, but there was something about the whole set up that rankled me. Every move I’d made so far, the Black Knight had anticipated – approved of, even. \textit{And that’s the part that bothers me.} I didn’t trust the green-eyed man, when it came down to it. I was beginning to like him, much as that thought would have horrified me a month ago, but not enough to forget who and what he was. I was still unclear on what he wanted from me, and the more time passed the more I was beginning to understand how much of a liability that was. \textit{There’s no place for a man like him in the kind of Callow I want to make, and he’s too smart not to be aware of that.} Which begged the question of why he’d taken me as an apprentice, and why he was still backing me when I’d as good as admitted I wanted to take an axe to Imperial authority in Callow.
There was an angle at play I wasn’t seeing, and until I caught it I had to assume that every action I took he approved of furthered his plans as well as mine.Building a power base of my own would have to be my first step. I’d always known how I would go about that, fortunately: I needed a command in the Legions of Terror, the larger the better. Ideally I’d need to be assigned to one of those garrisoning Callow, where I’d be able to use my soldiers to quietly remove the more troublesome elements of Imperial occupation in my sphere of influence. That plan was why I’d been so interested in claiming a Role in the first place: Names tended to make age issues irrelevant when it came to accumulating authority. History was full of young Named leading armies and ruling cities. Instead of spending two decades steadily climbing through the ranks while accumulating experience, I might be able to get a real command in just a few years. There were two bumps in the road, though.
First, I couldn’t do any of this with Black looking over my shoulder the whole time. The idea that the man who’d masterminded the Conquest would allow me to quietly turn Callow into a semi-independent vassal state was absurd. I’d effectively be undoing half of what he’d accomplished by annexing the Kingdom in the first place. \textit{Which means that at some point I’ll either have to kill him or become trusted enough to be given an independent command.} I was more inclined to the second, as it happened: the Black Knight was the most famous monster of our age, but he was also a thoroughly rational creature. There was no guarantee that whoever replaced him would be as… even-minded. Besides, managing to kill him in the first place would be tricky. I certainly had a better shot at managing the deed now that I was headed towards a Name of my own, but the heroes he hunted down with alarming regularity had Names too. How did one get the trust of a man like Black, though? I needed to figure that out, and quickly.
My second problem was that the Empire was at peace. Officers still got promoted when their predecessors retired or died of mundane causes, but my best chance at a position of real power was being granted soldiers to deal with a problem. None seemed in the cards right now, which meant that even if I inherited a legion it was unlikely to be loyal to me personally – my authority would flow from Black or the Empress, and if I ever went against them the legionaries would balk. \textit{What I need is for Praes to raise a new legion, one that will look to me for orders instead of anyone else.} A legion made up mostly of Callowans would be ideal, but the odds of that actually happening were so low as to be insignificant. I needed to learn Praesi ways then, enough that the soldiers would see me as one of their own. A\textit{nd that’s exactly what Black is having me do, which is worrisome in its own right.} Was that his angle? Making me swallow Imperial customs one mouthful at a time until I was nothing more than a Praesi with Deoraithe colouring? \textit{What better tool to keep Callow in the fold than one of their own, with the power of a Name backing her}. It sent a shiver up my spine, the idea that the man could have thought that far ahead.
I put aside the train of thought when the legionaries keeping watch at the gates hailed me. It was clear they’d been told to expect me just from the way they recognized me when they got close enough for their torches to shed light on my features. I was allowed in without any trouble and the sergeant in charge informed me that I had a bed waiting for me in a pavilion next to the barracks where the Blackguards had been settled. It was a quick walk, and now that I wasn’t stuck in a tense stand-off with people who might or might not want to kill me I was beginning to feel tired from the night’s events. Not exhausted – my body moved just as surely as it had when the sun was up – but I could feel my focus wane. The pavilion the sergeant had mentioned stood out from the surrounding tents by sheer size – no cloth for this one, though, only heavy flaps made of leather. There was a light lit inside, and I was about to enter when I felt something pulse in the back of my head. The fourth feeling, the strange one. How had I not noticed earlier? I must have been more tired than I’d thought.
“Thank you for seeing me at this hour, Lord Black,” I heard a girl’s voice say.
“Your request garnered enough curiosity to earn you an audience, Heiress,” I heard my teacher reply.
I peeked through an opening in the leather. Black was leaning back in a chair, the usual glass of wine in hand as he sat across a Soninke girl. She was, I noticed, strikingly beautiful. She couldn’t have been more than a year or two older than me, but her skin was smooth and flawless. I couldn’t see her eyes from where I stood, but I could make out high aristocratic cheekbones and elegantly style eyebrows. The riding leathers she wore were dyed in red and gold, perfectly tailored to fit an hourglass figure I could only envy. With those long legs and eye-catching curves, she was a serious contender for the most stunning girl I’d ever seen. It took a moment for what the green-eyed man had called her to sink in. \textit{Heiress.} I could feel the capitalized letter on the tip of my tongue, bearing that strange weight spoken Names always did. There was simply no way I was going to interrupt this, not if they hadn’t noticed me. I was in no way above eavesdropping on a potential enemy, which I was pretty sure this Heiress was. The girl in question lounged in her seat with all the elegant laziness of a large predatory cat, her sipping at her own goblet doing little to hide the way she was studying Black.
“I’ve looked into her, this… student of yours,” Heiress said. “She does have potential, true, but you cannot deny I have more.”
Black was smiling, the same always did when at his most dangerous. From the sudden wariness in the Soninke’s body language, she seemed to be just as aware of that as I was.
“Can’t I?” he murmured, tone sardonic.
“I have looked into her, Lord. She’s a nobody. A Laure orphan with a reputation as a brawler and nothing else to her name. There are thousands like her all over Callow,” she replied, a hint a frustration creeping into her voice.
Rude. I was under no delusion that I was unique, but there was a little more to me than a \textit{reputation as a brawler}.
“I am, inarguably, smarter than her,” Heiress continued. “I know how the Empire works, and I have real combat experience. I led the troops that suppressed -”
“That group of bandits at the edge of your mother’s lands, I’m well aware,” Black interrupted her. “You show promise as a commander, though I note you never attended the College.”
“Neither did you,” Heiress retorted flatly.
She met his eyes squarely and I had to give her points for guts, if nothing else.\textit{ Now would be a good time to tell her that she’s not actually smarter than me}, I silently urged him on, not bothering to repress my scowl. \textit{Any moment now.}
“Catherine shows promise in other ways,” he said instead, and I made a mental note to take some kind of petty vengeance on him at some point.
Seriously, he could have put a little more enthusiasm in that. I didn’t think it likely he’d give me the boot and take the Heiress under his wing instead – he’d already invested too much in me, whatever his reasons – but this was turning out to be a remarkably one-sided debate.
“Enough to justify passing over all the things I can bring to the table that she cannot?” Heiress challenged.
Black’s smile widened ever so slightly as he leaned forward, the atmosphere in the room shifting instantly.
“They \textit{have} trained you well,” he murmured, voice smooth as silk. “Just enough insolence to pique my interest, self-confident without stretching into the arrogance I so dislike in you nobles.”
Heiress’ eyes widened for a heartbeat and then her face went perfectly blank.
“Lord, I-”
“Am not nearly as good at this game as you seem to think you are,” Black broke in sharply, and the words rang of steel. “Did you think it was the first time the Truebloods tried this? That they had never before sent one of theirs with a little talent my way?”
The dark-skinned girl went still and my teacher’s smile turned ugly. I let out a shaky breath, feeling the weight of his Role suffocating the tent even from where I stood. \textit{Heavens Ascendant. I am never going to get used to that.}
“No one rules forever, Lord Black,” Heiress managed through gritted teeth, the white of her eyes showing as she pushed through the terror permeating the room. “And you may have beaten the Heir back when you were the Squire, but she is not you. \textit{And I am not him}.”
He laughed.
“Go home, girl,” he said. “Weave your plots, marshal your soldiers. And when you do, remind your mother of the last time we crossed paths – that pike over the gates of Ater is still missing a head, and I am ever a patient man.”
She stood, back ramrod straight, and strode away with barely veiled fury. I hurried away from the flaps as quietly as I could, stepping into the shadows a moment before she crossed. Heiress paused just outside the tent, casting a cold look around her. Her gaze passed over the spot where I’d hid without pausing, though, which I took to mean it was too dark for her to see me. A heartbeat later she was on the move again and I let out a breath I hadn’t known I was holding. I waited for her to be entirely out of sight before entering. Black was still in his chair, looking irritatingly unsurprised to see me enter.
“Let’s skip the part where you reveal you knew I was eavesdropping the whole time,” I grunted. “I’m not in the mood for smugness.”
“As you wish,” he mused. “Clever of you to listen in – very talented girl, Heiress. You’ll need all the advantages you can get.”
“So if you really think she’s all that, why did you pick me to be your Squire?” I asked, claiming the same seat she’d been in.
He poured himself another cup of wine, raising an eyebrow to silently ask if I wanted the same. I shrugged in agreement – the taste was growing on me, thoughtI doubted I’d ever drink it by the barrel the way so many Praesi did. \textit{If anyone had told me a month ago I’d have the Black Knight pouring me wine, though, I would have directed them to a healer. After stepping away slowly.}
“You’re taking this as a criticism of your abilities,” he noted. “You shouldn’t. Heiress has been tutored in everything from politics to war from the time she could first speak. That she is more competent than you is a reflection of her privilege, not of your own faculties.”
I took a sip from the cup he handed me, wondering whether or not I should press the subject. \textit{What the Hells, why not? What do I have to lose?}
“It would be easier for you to train someone who’s already been taught those things, though,” I pointed out. “I’ll be playing catch up for a while yet.”
“That she has already been taught is not a point in her favor,” Black replied.
That seemed like a good thing until I put another moment’s thought into it.
“So you’re sticking with me because I’m what – more malleable?” I scowled. “Easier to manipulate?”
He sighed.
“I will address this once, because I doubt you would have brought it up if you had not already been thinking it,” he said. “I will not lie to you, Catherine, or deceive you.”
I was about to butt in but he raised his hand and I paused, frowning at the fact that I had actually paused.
“Not out of a sense of honor or altruism,” he continued, “but simply because it would be foolish in the long term. It’s the way these things go, you see – if I deceived to you, you would inevitably find out I did at the worst possible moment and then avenge yourself in a way that would lead to my downfall. The amount of my predecessors that died because they failed to learn that simple, easy lesson is staggering.”
If he’d tried to sell me that he would never steep so low or that the teacher-student bond was something sacred I wouldn’t have trusted a word of it, but this sort of… enlightened self-interest? Yeah, I could buy that. The more I spoke to Black the more I was beginning to understand that everything he did he thought of in terms of costs and benefits – like a bookkeeper, if bookkeepers invaded neighbouring kingdoms and put people’s heads on pikes. And wore plate. And rode undead horses. \textit{Gods, I really hope there aren’t any bookkeepers like that out there. Creation is a scary enough place as it is.}
“I’m glad you recognize I’m smart enough for \textit{that}, at least,” I muttered peevishly, still not willing to let that particular gripe go anytime soon.
He drummed his fingers on the table in response to that, and from the look on his face it looked like I’d actually managed to irritate him. Huh, I’d never managed that before. In a twisted way, it almost felt like a victory.
“Petulance is bad habit,” he said. “She’s \textit{had} to be smarter than you to survive. The Imperial Court is the most lethal environment on the continent short of an actual battlefield. Last year the High Lordship of Okoro changed hands eight times in the span of three days, all of them through assassination. Her mother is a brilliant woman in her own right, one who managed to survive Malicia’s ascension to power without loss of influence \textit{while openly supporting the opposing faction}. Her every move, her every word is measured – underestimate her even for a moment and she will have your throat slit without batting an eyelash.”
I would have liked to dispute that, but I couldn’t help but remember the cold look in Heiress’ eyes when she’d left the tent. I’d won enough fights by being underestimated that it wouldn’t do to forget how costly a mistake that could be. \textit{Alright, then. Tread carefully around her. People don’t get Names by picking out flower arrangements and hers does have an ominous ring to it.} I responded to Black’s sharp gaze by a nod and he seemed satisfied I’d been properly cautioned.
“You still haven’t told me why you picked me,” I finally said.
The dark-haired man gazed at his cup, swirling the wine in it with a slow flick of the wrist.
“I’m told you never made friends with anyone at the orphanage,” he replied. “Why is that?”
“I, uh- what?” I blurted out.
Well, he wasn’t wrong, but to hear it put like that was a little mortifying. It wasn’t like everyone at the orphanage had hated me or anything, though I guess a few of them had, but I’d never made a close friend the way some of the other girls did. I’d always figured I was just a loner, and while that made me a little odd there were others like that in the orphanage so it wasn’t \textit{that} odd.
“I guess I never really had anything in common with them,” I admitted. “I don’t think they were wrong to want the things they wanted, but I just… didn’t. It was frustrating, the way they didn’t understand why I was like I am, so after a while I stopped trying.”
“And that angered you, didn’t it?” he murmured, “That they \textit{just wouldn’t get it}, no matter how many times you tried to explain.”
I shrugged with affected nonchalance, trying not to show how close to home he’d hit. And he was right, Gods help me. It still stung, the way they’d looked at me like I was insane when I’d said I wanted to change things. That I wanted to become someone who could make sure no one like Mazus ever got as powerful as the Governor had been. I used to think that I just wasn’t articulate enough, that if I’d found the right words maybe I could have bridged the gap I could feel I had created between us, but as I got older I stopped believing it. Even I knew there were some walls out there I couldn’t ram my way through.
“They never understand,” he murmured. “Even if they love you, they never quite understand.”
He looked almost sad, and for the first time since I’d met him I could believe he was as old as he was supposed to be.
“I chose you,” he mused, “because I remember what it’s like, that feeling in your stomach when you look at the world around you and you know you could do \textit{better}. That if you had the authority and the power, you wouldn’t make the mistakes you see the people who have it make.”
He took a long drink of wine.
“Is it madness, to get frustrated when they don’t see the things that seem so obvious to you? I truly don’t know. Gods know I’ve been called mad often enough, and I’m sure in time you will be called the same.”
He met my eyes with a sardonic smile.
“The things Heiress knows, you can learn. You will learn. But that indignation you’ve got boiling under your skin? That’s not something that can be taught. And it’s exactly why you’ll beat her, when the time comes.”
He set down his cup.
“Go to sleep, Catherine,” he said, rising to his feet. “Tomorrow promises to be eventful.”
\clearpage
\chapter{Chapter 11: Sucker Punch}

“\textit{Ha! And I bet you didn’t even see it coming!”}
– Dread Emperor Traitorous the First

I took a sip from my tankard, forcing myself not to grimace at the taste.

The ale here was worse than the Nest’s, which I wouldn’t have believed possible until actually drinking this stuff. Finding an inn that was low-brow enough for someone of my means but still saw enough traffic to be worth my time had taken most of yesterday’s afternoon, but I believed the effort to have been worth it: the Lost Crown was a breeding ground for discontent if I’d ever seen one. The evening bell hadn’t rung yet but the common room was more than half full – and not a single man or woman in it had come without a weapon. Every single one was Callowan, most of them were over forty and quite a few had scars. Not the kind you got in the back alley fights I was familiar with, but the kind you got when someone had done their level best to kill you and barely come up short. \textit{I’d bet apples to rubies that nine of ten were Royal Guard during the Conquest.} It was a good thing that the purse Scribe had provided me had been full of Marchford silver, because if I’d used denarii here I would have gotten my throat slit before the night was out. 

I drew mistrustful glares, of course, though not as many as I would have expected. My sword’s grip had been covered in a weathered leather wrap that hid the damning silver goblin’s head, but the sight of a girl my age with a weapon of that quality had been enough to warrant cautious looks. My one advantage, the thing I’d been banking on, was that I was of Deoraithe colouring. \textit{And when have any of the People made truce with the Enemy?} Callowan children were raised on stories about the unflinching brown-cloaked wardens and the way they hunted orcs all the way back to the steppes when they dared to come in sight of the Wall. That the Duchess of Daoine had bent the knee in the wake of the Conquest had not been enough to ruin that reputation: people remembered that the northern duchy was the only part of Callow where no Imperial Governors ruled. Daoine was as good as a kingdom of its own, these days, and though it paid tribute to the Tower even the Legions tread lightly that far up north. The last of free Callow, whispers called it.

“You want me to top that off?” the innkeeper suddenly spoke up, jarring me out of my thoughts.

Toothless Thom was a balding, gregarious man. His name was a bit of an exaggeration: he still had most of his molars, though admittedly some of them were chipped. He’d taken an ogre’s war hammer to the face at the Fields, as he’d been eager to tell me. \textit{Lucky I had my shield up,} he’d confided. \textit{Otherwise I’d be called Headless Thomas and my idiot brother would have gotten the inn.} The place had been called the Guard’s Rest, once, but Thom had changed the name when he’d come from the war. That a man who’d been at the battle where Callow’s royal line had been ended had called his inn the Lost Crown made it perfectly clear where his sympathies still lay.

“No,” I told him. “Want to keep my head clear. I have a question for you, though.”

The older man raised an eyebrow. “That so,” he said, tone neutral.

“I’m looking for work,” I said. “Purse is getting a bit empty.”

He shrugged. “I ain’t hiring, though some of the taverns by the fortress are.”

“Not that kind of work. I’m looking for a ring.”

He shot me a considering look. “There’s one under the Lucky Pilgrim. It ain’t that hard to find.”

“I’ve already been,” I admitted.

I’d gone for a look earlier in the day. Bigger place than the Pit had ever managed to become, with a court under the tavern itself where people went at each other with fists and weapons. It wasn’t, however, the kind of place I needed.

“Lots of greenskins in the crowd,” I murmured after a moment.

Now \textit{that} got his attention. I drank a mouthful of ale to hide how nervous I felt – I’d never been the best of liars, so I’d decided to stick to the truth as much as possible. If I got caught, though… There were a lot of former soldiers in the crowd around me, and if they decided I was a Praesi spy then my odds of getting out with all my innards on the inside weren’t looking too good.

“What’d you do in Laure, Cat?” Thom asked.

“Served drinks when I could,” I replied. “Fought in a ring when I couldn’t.”

“You’re a little young for that,” he noted.

“I was ranked third in the Pit,” I retorted, and I didn’t have to fake my pride in that. “Would have been first by now, if I’d stuck around.”

“Your parents must have been proud,” the balding man snorted.

“Orphan.”

“Raised in an Imperial orphanage, then,” he spoke, tone turning sharp.

“Didn’t stop the fucking Governor from taxing us,” I replied just as sharply.

I met his glare with one of my own, refusing to back down, and after a moment his gaze softened.

“No offence meant, kid,” he said.

“None taken,” I grunted back.

“So why’d you leave, if you were doing so well?” Thom probed, changing tracks.

“Mazus’ cut kept getting bigger and mine kept shrinking,” I groused. “Heard things were better here.”

“Lot more greenskins here than in the capital,” the innkeeper pointed out.

“Lot more veterans too,” I answered the unspoken question.

The balding man chewed on that for some time, eyeing me all the while.

“I might know of a place,” he admitted. “Ain’t exactly a ring, but close enough.”

I raised an eyebrow. “It pays?”

The innkeep offered me a toothless smile. “In more ways than one. You’ll need to strip first, though. With my daughter in the room.”

I kept my face straight but inside I was grinning like a fool. It had been a gamble to try to get my foot in the door on the second day, but it looked like it had paid off. And a good thing too – I couldn’t have kept this game up for more than another day before moving on. I could still feel the other claimants in the city, and the longer I waited the further ahead they got in their own hunts. More than that, I had a liability to worry about that neither Chider nor Tamika did. The masked imbecile hadn’t made a repeat appearance yet, but how long could that possibly last? Getting into a fight with someone so obviously Praesi would shut down this avenue of investigation, and at the moment I was coming up empty on other ways. Thom called over his daughter, a slender blonde girl in a conservative blouse who split her time between the kitchen and serving drinks. She had rather striking grey eyes, I noticed. Rare, for a Callowan: blue and brown were much more common.

“Elise,” the innkeeper spoke, leaning in close. “Keep an eye on our little friend while she changes, eh? She’s going to be joining our cousins for drinks.”

The girl nodded, steering me towards one of the rooms in the back.

“Lucky you,” Elise said, closing the door behind me. “This is the first meeting since the Governess died.”

I made a noncommittal noise, hiding my excitement. \textit{Meeting. That sounds promising. }I\textit{ }took off my woollen shirt before opening my belt and slipped out of my trousers, dropping them next to me on the ground. I was about to take off my socks when she raised a hand.

“That’s enough,” she said, taking a step to look at my bare back.

Those pretty eyes of hers, I noted, lingered on my arse longer than was strictly necessary. Or proper. I wouldn’t have minded the attention in other circumstances – she was a comely one, if not exactly my type – but this wasn’t really the time or the place. I dressed again as soon as she gave me a nod of approval, shifting my scabbard so it rested comfortably against my hip.

“Nice sword,” Elise mused. “Where’d you get it?”

“It was a gift,” I replied.

She wiggled her eyebrows. “Generous lover?”

I choked. “Oh, \textit{Gods no}. A teacher, I suppose.”

“He must have liked you. I’ve been meaning to learn how to use one – maybe you should show me how good you’re at handling yours, one of these days,” she said, smiling wickedly.

Ah, Callowan girls. So much more straightforward about our interests than coy Proceran ladies or haughty Free Cities maids. I doubted Elise would be as eager to get me into a dark corner if she knew I intended to ram a sword into the local hero’s belly, but there was no need to draw suspicion by turning her down. Besides, it \textit{had} been a while for me. Between the Pit and my evenings at the Nest, I hadn’t had much time to pursue the softer things in life – and I doubted that would change anytime soon, given how Black loved to pile ever more work on my shoulders.

“I’m sure that would be quite the evening,” I replied, a smile tugging at my lips.

“Only one way to find out,” Elise smirked, opening the door and striding away into the common room.

I closed the door behind me, pretending not to notice the amused look Thom shot me. There was a man sitting on the stool I’d occupied, studying me without even pretending not to. Late forties, I’d guess, and his thick salt and pepper beard didn’t quite manage to cover the handful of scars adorning his face. His hair was thinning, though there was enough left that it lent him a dignified look.

“You’re \textit{Cat,} I take it,” he ground out when I walked up to them.

“That’s me,” I agreed. “And you are?”

“Remaining nameless, even if you don’t have the fecking eye,” the man growled. “This is shite, Thom. Nobody can vouch for her.”

“We need new blood,” the innkeeper spoke in a low voice. “You know they Imps have been keeping an eye on veterans since the Governess got offed. Besides, the boy can have a look at her.”

\textit{The boy}, I repeated silently. \textit{Now, isn’t that interesting? }Even if I learned nothing else of worth tonight, that particular tidbit had made my gambit worth it.

“I asked for work,” I told both of them. “Not the keys to your secret clubhouse.”

The grizzled man spat in his empty mug. “On your head, Toothless,” he finally said. “Come on, girl, we’re going for a walk.”

I smiled at him pleasantly. “Well, since you ask so charmingly.”

We left through the back, after the still-nameless grump slapped a younger woman on the shoulder and she joined us. She didn’t introduce herself either, cautiously eyeing me through her bangs as she kept a hand on the hilt of the bastard sword at her hip. The sky was beginning to darken, so we kept a steady pace: since the assassination of Governess Lindiwe the city had been put under martial law and curfew was strictly enforced. Anyone out after sundown without authorization papers would be arrested, and anyone resisting arrest would be put to the sword without hesitation. The city guard was no longer the only force policing the streets, either: the Sixth Legion sent regular patrols and the Ninth had occupied all gates.

“So where are we headed?” I asked when the silence became more tedious than tense.

“The Royal Foundry,” the woman informed me, rolling her eyes when the man glared at her. 

“I thought the Empire owned that now,” I frowned.

“They occupied the main one, the one that provided for the Royal Guard,” the swordswoman explained. “The Legions never bothered with the ones that provided for the local troops, since they make their own weapons.”

Ah, that made a certain amount of sense. The Legions of Terror were armed with equipment forged in the south of the Wasteland, in Foramen. Exceptions could be made in time of war when there was a pressing need for resupply, but usually they preferred waiting for the armaments and armour coming straight from the Imperial Forges. There’d have been no real point in taking the smaller foundries, after the war: the main one would serve just fine for the maintenance work required by the occupying legions.

“Enough with the history lesson,” the jackass growled. “Quiet until we get there.”

The younger woman offered me an apologetic shrug, but she complied. The outer city of Summerholm was different from Laure. Unlike Callow’s old capital, which had grown over the years as the wealth and people flowed in from the rest of the Kingdom, Summerholm had clearly been designed. The streets were of the same width everywhere, wide enough that bowmen on the walls circling the inner city could have a clear shot at anybody down here. Watchtowers, now occupied by legionaries, loomed over every choke point. More than once we passed by dead-end streets full of arrow slits, killing fields in the making for anyone taking a wrong turn. The Gate of the East had not been made with commerce or industry in mind: it was more castle than city, built so that it could be turned into a death trap for invading Praesi armies. The knowledge that even after twenty years of occupation the people born in the city likely knew the ins and outs of it better than the Legions did nothing for my peace of mind.

“We’re here,” the grizzled veteran announced abruptly. “Get in before we’re seen.”

The Royal Foundry was nothing spectacular to look at, which I supposed was rather the point. The building was solid old wood, with a metal spike above the door where a sign must have hung at some point – there was none now, though. The door was unlocked and the swordswoman pushed it open without knocking while our cheerful companion cast mistrustful looks around the empty street. I followed her in, squinting as my eyesight got used to the poor lighting inside. The large cast iron furnace that took up the better part of the left wall was lit, glowing even though the forge on the other side of the room was dead and cold. \textit{Expensive way to light the place.} I followed the more pleasant of my guides as she headed for a room in the back, already hearing the low murmur of conversation from where I stood.

The area we entered must have served as a stockroom, back when this place was still active: there were empty weapon racks for weapons and armour all over the place, some tipped down to serve as impromptu seats for the two dozen people occupying the room. I drew a few curious looks when I came in, but nothing like the degree of cautious hostility I’d been expecting. \textit{They only bring people they trust here, then,} I mused. \textit{But if that’s the case, why bring me?} I didn’t think this was a trap, but I was definitely missing \textit{something}. Like back in the Lost Crown, everybody but me was far past thirty: there was an even enough spread between men and women, and though none of them wore armour they all had a blade of some kind. \textit{And they look like they know how to use them}. If I wasn’t mistaken, I’d just been brought to a meeting of the Sons of Streges – Black had mentioned they were largely made up of disaffected veterans. The Sons were always the only resistance group I had a real chance of getting in touch with: the other one was made up of former members of the Thieves” Guild, and I had a feeling they’d be both much more secretive and much harder to find. The bearded man came in, scowling at me as he stopped by the door.

“Take a seat, girl,” he grunted. “We’ll start when the Swordsman gets here.”

“It’s true, then,” I murmured, trying to sound surprised. “There’s a hero in Summerholm.”

“You’ll get to meet him soon enough,” the veteran replied. “He’s a perceptive lad, the Lone Swordsman. Caught five spies already. If he says you ain’t one, you ain’t.”

I nodded, keeping my face unconcerned \textit{Shit. Shitshitshit.} Lone Swordsman didn’t sound like the kind of Name that would lend itself to truth-telling, but if he’d already outed agents placed by Black then he must have a trick of some kind. I took a deep breath, sitting down on a sideways rack. If the trick was just that he could tell when someone was lying, then I might be able to talk my way out of this mess. I hadn’t been sent by Black or any Imperial authority, technically. I wasn’t loyal to the Empire either, so it might be possible to work with that. \textit{But if he asks me whether I intend to kill him I’m fucked.} I closed my eyes and slowly got a grip on my panic, taking steady breaths. I wasn’t out of options yet. 

My first instinct was to position myself close to the door so that I could turn this into a running battle if blades came out, but I discarded the option. I was being watched, and making that sort of move would be as good as outing myself. Would I be able to take the hero in a fight? Maybe. His Name seemed centred around swordsmanship, though, which did not bode well for me considering I had a grand total of eight days of sword lessons under my belt. \textit{And I definitely can’t take both him and the Sons at the same time.}

Stupid of me to expect that if they had a trick to find out spies they wouldn’t use it on every possible occasion instead of only when they thought they had a leak. On the bright side, that meant the process was unlikely to be painful or particularly powerful: it wouldn’t be used as often if it were. Could heroes tell when they were in the presence of a villain? I couldn’t find this Lone Swordsman the way I could my rival claimants, but I wasn’t the Squire yet. There was no real way to tell what kind of abilities his Role would allow him to access, even now that I knew his Name. My private debate was cut short when the man in question entered the room through a back door, not that it had been going anywhere productive.

Even if the room hadn’t gone respectfully silent the moment he’d entered, I would have known I was looking at a hero. He couldn’t have been much older than seventeen, darkly handsome with messy black hair and vivid green eyes. His face was one made for brooding, all angles and windswept locks, and his long brown leather coat did nothing to detract from that impression. \textit{A leather coat. Gods. Why wasn’t he clapped in chains the moment he passed through the city gates? If he was any more obviously a hero he’d have his Name tattooed on his forehead. }The longsword at his hip did not glint in the light, the metal pommel swallowing the ambient light whole and giving nothing back. \textit{Enchanted? That could be trouble}. He moved with the certainty of an older man, and all the other people in the room straightened their spines unconsciously when they saw him.

“No need to get up on my account,” the Swordsman said, raising a warding hand at the few people who’d gotten to their feet. “We’re all equals here, my friends.”

“Some more equal than some,” a woman in the back called out, but it was said fondly.

“We all have our burdens to bear,” the hero replied easily. “But we’ve shared in one victory already, and I promise you that more are to come. The Black Knight himself is in the city, and that is an occasion we won’t be getting again anytime soon.”

I let myself fade into the background as the Lone Swordsman strode into the middle of the room, commanding everyone’s attention with a kind of effortlessness I could only envy. Was it natural charisma on his part, or a side-effect of his Name? Whatever it was, veterans twice his age were hanging on to his every word.

“We still have half of the munitions from the raid on the Sixth Legion’s armoury,” he said. “And with those backed by a little cleverness, I propose to put down the monster who brought ruin to the Kingdom.”

Murmurs of approval went through the room at the declaration.

“It’ll take more than goblin alchemies to kill that man,” a voice cut through the noise, cold as ice.

Leaning against the wall on the far side of the room, an older man built like an ox was frowning. His head was shaved but auburn whiskers covered the side of his face, leading into a thick beard of the same colouring. 

“I was there when he killed the White Wizard with Warlock’s help,” the man spoke flatly. “Half a bridge he dropped on those two, and they walked out of the wreckage like it was light drizzle.”

“We already know munitions can kill Named,” the Swordsman replied. “The Empire proved as much during the Conquest.”

“They can kill run-of-the-mill Named, maybe,” the man grunted. “You’re dealing with the bleedin’ Calamities, boy.”

“I am not a run-of-the-mill hero, my friend,” the green-eyed boy said very softly. “I swore I would see the Kingdom restored, and I will see that oath through to the bitter end.”

\textit{Oh, gag me.} Did he think that making some kind of dramatic promise over someone’s grave would actually help him kill the likes of Black? I stopped and thought about it for a moment. \textit{Hells, it actually might.} \textit{Roles take to that kind of theatre like a duck to water. }Whether the doubter was actually convinced or just cowed by the uncomfortably emotional display on the Swordsman’s part was up in the air, bur regardless he objected no further. The crowd was against him, anyway: they were eager for blood, and their success with the Governess had only whet the appetite.

“Before we get to the planning,” another man spoke up, and with a start I recognized my earlier guide’s voice, “we have new blood for you to look over.”

Everybody’s eyes turned to me and I fought down the urge to shrink on myself. It was time for my moment of truth, though hopefully not a literal one – that could get messy.

“So,” I said as I pushed myself up, wiping dust off of my trousers. “How’s this going to work? Do I need to strike a pose? Word of warning – if poetry is involved, I’m definitely not your girl.”

The Lone Swordsman smiled, which made him look like someone was pulling up his lips forcefully. Not a great smiler, this one.

“Just come a little closer,” he said. “What’s your name?”

“I’m going by Cat,” I told him, watching his face to see if it registered as a lie.

If it did, this was going to go downhill very quickly. The hero frowned.

“What colour is the sky, Cat?” he asked.

“Depends on the time of the day,” I pointed out.

Someone snorted, though they hastily turned it into a coughing fit. The Swordsman sighed and patiently waited for me to give an actual answer.

“Blue,” I said.

The hero’s frown deepened.

“That’s strange,” he said.

“People usually wait to know me a few days before making that comment,” I replied.

“I can’t read you at all,” the Lone Swordsman murmured. “That’s never happened before.”

“If I had a silver for every time I heard that line-”

I didn’t see the strike coming, but I felt it. There was a blur of movement and my body reacted on its own, my sword swinging out of its scabbard and ringing against his own before it could come any closer to my head. There was a moment of painful realization where it struck me that I had moved much, much too quickly for mundane human.

“Well,” I mused, pushing back his blade. “This is awkward.”

“Traitor,” someone hissed.

“Technically,” I corrected the voice, “I’m the only person in this room \textit{not} committing treason.”

Two dozen blades coming out of scabbards were my only response. Tough crowd.

“Now,” I spoke, voice calm and steady as I backed away. “I know what all of you are asking yourselves right now. Is that girl a spy?”

Two of the rebels were blocking the door, I saw from the corner of my eye.

“The answer to that question may surprise you,” I continued.

There was a heartbeat of silence.

“Is it yes?” someone called out from the back. “Is the answer to the question yes?”

It was not, I reminded myself, appropriate to start cracking up before your desperate final stand.

“Shut up, Beric,” someone growled. “Obviously the answer is yes.”

“You guys never let me win anything,” Beric complained.

Beric, I decided, was going to die last. He’d earned it. The Lone Swordsman brought up his sword and fell into a stance I didn’t recognize.

“You’re surrounded, villain,” the hero said. “There’s no one around to hear you if you call for help. Surrender and you might yet live.”

I felt safe in assuming that diplomacy was not one of his aspects.

“Ah, but you have it the other way around,” I replied haughtily, trying to stand as tall as my diminutive stature allowed for. Why was everyone always so tall? “It is, in fact, all of you who have fallen in my trap. Surrender now and will spare you most of the torture, unless one of you gives me lip.”

The Swordsman scowled. “You’re full of shit,” he growled.

Given that there were two Named in the room, it seemed fair that that was the precise moment where the back of the room exploded. Most of the Sons of Streges were thrown to the ground by the impact and I had to take a knee. Smoke and dust had been blown everywhere, I might as well have been standing in the middle of a sandstorm as far as visibility was concerned. I could make out a silhouette in the smoke, too tall to be a goblin and not broad enough to be an orc.

“Rashid,” I called out. “If that’s you, then for the first time in your life I think you actually need to be commended on your entrance.”

Tamika came out of the smoke instead, black-veiled and grim-eyed. Her spear was nowhere in sight but she held a crossbow in her arms, pointed at the Lone Swordsman.

“I’m guessing Chider’s somewhere in this mess?” overhearing the sound of fighting out of sight as I asked the Soninke girl.

The hero sneered and half-turned so he’d be facing both of us.

“She’s coming,” Tamika agreed calmly, speaking in Mthethwa. “I feel like I should apologize, Catherine.”

That was the part where I was supposed to ask \textit{what for}, I assumed. Instead I threw myself to the side and the bolt sunk into the wall. The Lone Swordsman eyed the both of us warily.

“What in the Burning Heavens is going on?” he asked.

“My plan is working,” I lied.
\clearpage
\chapter{Chapter 12: Squire}

“\textit{Now kneel, fools, and witness my ascension to GODHOOD!”}
– Last words of Dread Empress Sinistra IV, the Erroneous

There was a heartbeat of silence before Tamika cocked her head to the side.

“Your plan?” she asked.

“Don’t encourage her,” the Lone Swordsman cursed.

I smiled condescendingly, casting an eye around me to find a more defensible position. If a monologue was going to buy the time I needed, then I was more than willing to chew the scenery for a while.

“I’m glad you asked, Tamika,” I announced. “You see, while it may appear that this is sheer bloody chaos, the whole situation was in fact-”

The scimitar came within an inch of my throat and I back-pedalled in panic, swinging my sword at the now-visible silhouette of Rashid. \textit{Right. There’s a reason long-lived villains don’t make speeches.} The bastard was still wearing his mask and without a word he stepped back into the smoke, disappearing in the blink of an eye. Ah, wasn’t that going to be fun? With this kind of visibility, he had no practical limit on how many times he could pull his stealth trick. While I’d been busy trying not to get my throat cut, the veiled Soninke and the hero had apparently had a breakdown in negotiations: Tamika’s crossbow was on the ground, abandoned as she tried to fend off the black-haired man with her long dagger. She was, I noted with a degree of satisfaction, failing pretty badly. The strange sword scored a long gash across her face, ripping away the black veil. It sung\textit{ }when it drew blood, letting out a loud keen as the edge of the metal flashed red. I flinched at the sound, at how \textit{wrong} it sounded. That thing was definitely enchanted, and not in a nice way. The crossbow wielder wasn’t going to fight her way out of this one, I assessed. The long-haired Soninke girl wasn’t half bad with her dagger – no doubt better with it than I’d be – but the Lone Swordsman was in another league entirely. He moved more like a machine than a man, calmly and methodically powering through Tamika’s defence to inflict increasingly dire wounds. 

I considered joining the dance, but that seemed like a recipe for death by Rashid. Bringing up my sword, I wiped the sweat off my brow and moved towards the foundry in the front. For all that I’d been villaining my way through this encounter with blatant lies and poor misdirection, I had no intention of letting this devolve into some sort of climactic melee involving all my enemies. I would, for one, probably lose. I was pretty sure I was already tapping in the Learning aspect of my Name – the fact that I’d never needed to read a page twice to remember it flawlessly indicated as much – but it hadn’t helped me much when it came to my swordsmanship. All I had to see me through a fight was those unusually quick reflexes and a history of knowing the taste of blood in my mouth. Not, I decided, the stuff victories were made of. There was another way to deal with this mess, though: I stood less than thirty feet away from a lit furnace and most of my enemies had helpfully bunched up inside a flammable building. \textit{So let’s set the place on fire and hide by the exit to stab anyone coming out in the back. }Not the most honourable of plans, but honour was for people powerful enough to afford that kind of luxury.

I somehow managed to leave the room without a masked interruption, losing sight of Tamika and her heroic opponent – I had to step over the corpse of my female guide from earlier in the process. Her neck had been hacked halfway through, I saw with mild horror. \textit{Rashid’s work, no doubt.} That was when my cunning plan hit an obstacle: standing by the furnace, Chider was looking back at me with an unreadable expression on her face.

“So,” I spoke up, moving so that a table occupied my back, “I don’t suppose you’ll be willing to hold to the truce?”

Chider shrugged, her leathery face pulling taut.

“It’s nothing personal, Callow-girl,” she replied in Lower Miezan. “The money was just too good to pass on.”

\textit{Money?} Who would have-

“Heiress,” I realized. “Heiress bribed you three to take me out.”

“I don’t know if she got to Rashid,” Chider noted, “Though I don’t think she would need to. But she found Tamika and me, yes. Not sure what you did to tick her off, but she’s willing to sink a small fortune into seeing you dead.”

I scowled. I’d yet to meet the girl face to face and I was already starting to hate her guts.

“You understand she’s playing all of you, right?” I said. “She’s going to be rivals with whoever ends up being the Squire, so she’s trying to meddle in the claiming.”

“She probably thinks she is,” Chider agreed, “For some reason she seems to think you’re the most dangerous of the four of us and who knows? She might even be right. But I don’t mind her getting what she wants, as long as I also get what I want.”

“And that’s my corpse?” I grunted, already preparing to duck for cover when the munitions started flying.

“I want to be the Squire,” Chider corrected sharply. “I don’t really care how I get there. There’s never been a goblin Squire, Callow-girl. Or a Black Knight, or an Empress. The tribes have done more for Praes than all of the High Lords put together, but even now all we can aspire to is being \textit{followers}. If I have to kill a few humans to remedy that situation, so be it.”

I could sympathize with that, I really could. I knew what it was like, being part of a system where the best you could ever manage was being slightly above the bottom of the barrel. But her way apparently involved my being a corpse, and that wasn’t really a point I could compromise on.

“We don’t have to fight, you know,” I told her. “I’m still willing to make truce until the Lone Swordsman is dead.”

Chider grinned, all teeth and malice. “Silly girl, I’m not going to \textit{fight} you.”

She reached inside the satchel at her hip and brought out a clay ball the size of her fist. I ducked behind an anvil, but the expected sharper never came. I blinked and the glimpse I’d had of the munition drifted to the surface of my mind, clear as spring water. Creepy, that – my memory had never been that good, and there was no way I should have been able to see as many details as I had. Sharpers were clay balls, yes, but usually they had a stick protruding out. This one hadn’t had anything of the sort. It wasn’t a brightstick either. A smoker? I’d never seen a diagram of those, so I wasn’t sure what they looked like. My answer came in the form of a roaring furnace: there was a deafening blast and a burst of green light. I snuck out a look from behind the anvil and saw the whole front of the foundry was burning. Eerie green flames were spreading further with every passing moment, and of Chider there was no sign. The furnace was on fire, I noticed. The \textit{metal furnace} was on fire. \textit{Green flames, burning metal? Oh fuck me.}

“Goblinfire,” I gasped into the empty room, backing away with haste.

That clay ball hadn’t been a smoker, it had been godsdamned goblinfire. The most heavily restricted substance in Imperial territory – just possessing some was enough to earn you a hanging – and Chider had just casually tossed a ball of it into an open flame. Nobody except the goblins knew exactly what goblinfire was, but the Conquest had taught Callowans to fear the sight of the green flames: it burned \textit{everything}, including water and even magic. Seven days and seven nights it would keep burning, impossible to put out until it stopped on its own. There were still parts of Laure where the ground was nothing more than blackened glass, where the substance had been used when the Legions took the city. If any of it touched me, the best I could expect was to be turned into a blackened husk for the rest of my miserable existence. \textit{Well, I guess I’m not leaving by the front door}, I grimaced. Which meant going back into the very melee I’d tried avoiding. New plan, then: get the Hells out of here before the Royal Foundry got turned into the closest thing to the actual Hells that could be managed on Creation. Possibly stab someone if I got an opening, but no need to take stupid risks. Appearing reckless was useful – \textit{being} reckless was a death sentence for a girl in my position. Naturally, the moment I’d settled on a fresh course of action was when Rashid chose to make his appearance. Stepping out of the doorway, the masked boy’s robes fluttered as he strode forwards me. His scimitar was coated in blood and chunks of bone, though it looked no less sharp for it.

“I told you we had unfinished business, Callowan,” he hissed in Taghrebi. “I’ve been looking forward to this.”

“Really, Rashid?” I complained. “We’re going to have a duel to the death in the middle of a foundry full of \textit{goblinfire}? Couldn’t we at least move to the other room?”

“And risk one of the veiled wretches stealing my kill?” he chuckled. “I think not.”

Apparently that was enough banter for him, because he struck without warning. No tricks this time, no attempt to take me by surprise: the curved sword came for my neck, though I slapped it away with my own blade before it could come anywhere close to drawing blood. He’d apparently found a healer in the last two days, because the wound I’d inflicted on the night we first met didn’t seem to be slowing him down.

“Fine,” I ground out through gritted teeth as I pushed back his scimitar. “The hard way it is.”

I made to sweep his leg but he spun around me fluidly, blade flashing out to swipe across my unprotected back. I hissed at the pain and swung my sword to force him away, already feeling the blood welling up in the wound. \textit{Shit. I really hope that wasn’t poisoned.} He darted away, carefully choosing his distance and stalking around me like a crow circling a corpse. From the corner of my eye I could see the green flames continue to spread, swallowing everything in their way. I brought up my sword in middle-line, flattening my profile so he’d find me harder to hit. All of this would have been much easier with a shield, and I once more cursed that it would have been a dead giveaway to the Sons if I’d come bearing one. His footing shifted minutely, but I had no intention of letting him go on the offensive again: I struck first, point aimed at his sternum. 

Not fast enough, though. Half a step back brought him just out of my range, and when my blade retracted he followed it in a single fluid movement. The scimitar flashed again, coming for my sword-arm much faster than I’d believed him to be capable of. Angling my pommel up took the better part of the hit, but the edge still ripped through a chunk of my forearm before he darted away. I swallowed a sob of pain, tightening my lips. What was happening? He hadn’t been anywhere this good last time we fought, and as far as I could tell his technique hadn’t gotten any better. He was just \textit{better}. \textit{Something about this fight is empowering one of his aspects.} That wasn’t something I could match, damn me. The only one of mine I’d figured out was Learn, and it appeared my Name didn’t consider duels to the death to be learning opportunities.

“There’s the look I was waiting for,” Rashid purred. “The moment where you finally understand your place in the world.”

For once my life, I was in too much pain to think of a proper response. I struck instead, aiming for the same shoulder I’d wounded last time, but he slapped my point away with contemptuous ease. My hand was shaking, and after being struck twice I’d hesitated too much to properly commit to the strike.

“Maybe I should just leave you in here,” the boy mused through his mask. “Bar the door and let you burn alive. I’m told the green flames are even more excruciatingly painful than regular ones.”

I tried to take a deep breath but ended up inhaling some of the smoke that was growing to permeate the room and started coughing instead. Rashid didn’t even deign to take that opening, preferring to just stand there radiating amusement. I was losing. I was losing, and I was going to die.

The truth of that sunk in and it was like the all the colours in the world where whisked out.

I didn’t have any tricks up my sleeves, and this wasn’t the kind of opponent I could talk my way out of fighting. Rashid had come here tonight to spill my life’s blood on the ground, and would not leave until he’d gotten what he wanted. He was faster than me, more experienced in this kind of fight, and every one of my heartbeats spilled more out my blood on the floor while he remained unwounded. The gap between us could only widen one way, now. \textit{I am going to die here}, I realized. This was as far as I’d managed to go, for all my grand ambitions – killed in an abandoned foundry by some idiot wearing a mask who just happened to be better with a blade. \textit{What a stupid, stupid death. }Gods, I was tired. Barely two weeks since I’d left Laure, and it seemed like it had been years. The heat of the spreading flames licked my skin and a part of me wondered if I should just let him run me through. It would be quicker death than letting him take me apart wound by wound as he so clearly wanted. 

“I had all these plans, you know,” I spoke into the silence. “To make a different world, a better world.”

“The delusions of a weakling,” Rashid replied with naked contempt. “Cockroaches are for stepping on, that’s all there is to it.”

The sheer scorn in those words felt like a slap in the face. 

“You don’t get to say that, you little shit,” I said in a low voice. “Even if you beat me here, you don’t get to say that.”

Something in my belly stirred like old embers, a heat under the surface that needed only the right fuel to burn. It didn’t care if he killed me – more than anything, right now, I wanted that dismissive prick to be wrong. It didn’t matter if I was outclassed, it didn’t matter if he had every advantage and I had less than none. I was going to make him choke on those words, choke until his face turned blue and his eyes popped out. 

Even if I bled. 

Even if I burned. 

Even if the flesh was flayed off my bones.

I would \textit{Struggle.}

Power flowed through my veins, the beat of it drowning out even the roar of the flames. I raised my sword and stepped forward.

“Oh?” Rashid chuckled. “Are we-”

I rammed my fist into his mask, shattering the clay like the cheap affectation it was. The scimitar came up but I grabbed him by throat and threw him against a table. My Name pulsed under my skin like a living thing, feeding on the fight. The Taghreb snarled and got back on his feet as I continued striding forward, striking almost too fast for the eye to follow. Slow. So slow. How could I ever have thought of him as fast? My sword came down on his wrist and blood sprayed out. His hand fell, fingers still clutching the handle of the blade. I could see his face now, see the fear appearing in those dark eyes.

“I-” he snarled, but I shut him up by punching the tip of my blade through his throat.

Fear turned to disbelief and with a flick of the wrist I tore out my sword. He dropped to the ground.

“Got stepped on,” I finished in a whisper. “\textit{Cockroach}.”

I watched the life bleed out of the boy, standing above him with my bloodied blade in hand as the flames cast their hellish green light. The moment he took his last gasping breath I felt something click inside of me, like another piece of a puzzle I couldn’t see had snapped into place. The power inside my veins dimmed, then disappeared\textit{.} The pain I’d stopped noticing slammed back into my senses and I grit my teeth as I swayed on my feet\textit{. }Tapping into the Name’s power had worn me down, and not just because it’d taken away my tiredness for a moment. \textit{And I don’t think that little burst is going to happen again. Not tonight, anyway.} With a last look at the boy I’d just murdered, I stepped into the smoke.

My eyes wanted to close and my body wanted to curl up into a ball and sleep until all of this mess had gone away and become someone else’s problem. I allowed myself the luxury of thinking about how much more pleasant my life would be, were I the kind of person who was willing to do that. Then I took a deep breath and walked towards the sound of fighting, sword raised. \textit{No rest for the wicked.}

The Lone Swordsman had two opponents, but Chider was not one of them. Tamika, blood dripping down her chin where the enchanted sword had sliced her earlier, was reloading her crossbow while she fought the hero with her spear. She was also white-veiled again, and unwounded. I blinked, making sure that my little Name episode earlier hadn’t knocked something loose in my head: there were, in fact, two Tamikas. The one who’d shot at me earlier still bore the wounds I’d seen the Swordsman inflict her, but the other one was still untouched. Rashid had mentioned \textit{wretches}, earlier, I recalled. I’d thought it was a mistake, at the time, but apparently not. 

Whatever Name trickery this involved, they were actually managing to drive the hero back: whenever the dark-haired man managed to get the drop on the one fighting him with the spear, the other one loosed a crossbow bolt at him. Whenever he tried to take out the one with the crossbow, the spear-wielder started pressing him furiously. The tactics they used weren’t particularly sophisticated and the Lone Swordsman didn’t seem to bear any wounds besides a rip in his leather coat revealing the chain mail that covered his forearms, but… Neither was he making progress. Their synchronization was too good, each attack flowing into the next with neither ever missing a single beat. None of the three had noticed me yet. Quietly, I stepped behind the one I was now naming Crossbow Tamika. She wore hardened leather but no helmet – her neck was bare, and I was done playing around with my fellow claimants. I got within three feet of her before Spear Tamika saw me. Her eyes widened, but it was too late: I was already striking and… and now I was ducking when the other one swivelled to face me and shot her bolt into the space where I’d been a heartbeat earlier.

There was no way she could have known, much less taken aim so quickly. Were they sharing each other’s field of vision? Gods, that would be a ridiculously useful trick. Spear Tamika stepped away from the hero before I could close the distance separating me from the other one, coming just close enough to be able to come to her rescue if I tried to intervene as she reloaded her crossbow. Well, that was a problem.

“Lone Swordsman,” I called out. “I have a question for you.”

“No,” he replied instantly.

“You don’t even know what I’m asking,” I complained. “I could have been offering my surrender.”

He squinted at me. “Are you?”

“We can get to that later,” I dismissed. “Evidently you’re the gritty type, but how far up the antihero scale are you?”

“As far as I need to be,” he responded gravely.

I pushed down my urge to make something out of that. Crossbow Tamika had already finished reloading, and the pair of them seemed to be considering their next target. I \textit{really} wasn’t liking the way Spear Tamika was beginning to angle towards me.

“Are you the kind of gritty that works with enemies?” I probed. “You know, for the greater good and such.”

I’d been paying too much attention to the spear-wielder: meanwhile Crossbow Tamika had calmly lined up her shot and pulled the trigger. I’d been lucky with the bolts so far, but with the last remnants of my Name’s power fading away I didn’t have the kind of speed that let me dodge those at will anymore: she missed my chest but the projectile punched into the flesh of my shoulder with a wet thunk. I let out a cry of pain, nearly dropping my sword in shock.

“Fuck,” I cursed. 

I hacked away the shaft of the missile with a trembling hand, but actually taking it out would have to wait: I was pretty sure that kind of bleeding would kill me, after how much of Rashid had already gotten out of me. The Lone Swordsman’s face was inscrutable, but if he didn’t reply in the next few moments I would have to-

“You’re Callowan, aren’t you?” he asked.

“Laure born and raised,” I confirmed.

“… only until they’re dead,” he spoke, distaste clear in his voice. “Not a moment longer.”

“You’re such a charmer,” I gasped, resisting the strange urge I was getting to roll my wounded shoulder.

The bolt was painful enough without wriggling it around in my flesh. 

“She came here to kill you,” Crossbow Tamika said suddenly, her voice sounding strangely distant as she addressed the hero.

“He’s your enemy,” the other one told me in the same tone.

“So are you,” I grunted, pushing myself into action.

The spear-wielder was the closest to me, so it was towards her I moved. Without a word she burst into motion, the tip of her spear thrusting forward in the blink of an eye. I sidestepped the strike, though it was a close thing: both my exhaustion and blood loss were beginning to take their toll, Name or not. I forced a spring to my tired limbs and passed the tip of her spear but without missing a beat Tamika whipped the shaft straight into my wounded shoulder. I dropped down on one knee, trying to turn my scream into a curse and only half-succeeding. I grit my teeth and pushed myself up, but the shaft struck me across the face and threw me down sideways. I felt my sword fall out of my grip, handle slick with blood, and as I scrambled desperately to reach it Tamika’s boot came down on my fingers. I felt the phalanges break with a sickening crack. I whimpered and watched as the spear rose, tip headed for my throat, when it suddenly stopped. Without so much as a word of warning, my opponent threw her weapon in the direction of the other duel.

I was weaponless, shit, and – and I \textit{wasn’t.}

My left hand reached for the knife I’d won by slitting two throats, the sheath hidden in the small of my back. Tamika raised her hand and dark smoke coalesced in it, forming into a spear again, but it wasn’t quite done. With a heaving cry I rose again, feeling the burn of skin getting ripped as I pulled out my hand from under her boot. She stumbled at the sudden pushback and my hand arced, the small knife a silvery blur as I drove it right under her chin. Tamika blinked wordlessly, blood gurgling as she tried to breathe. I twisted the knife and tore it out, blood spraying all over my upper body from the severed artery. The Soninke took a hesitant step back, then another, and her hand came to touch the wound as the now-materialized spear clattered against the ground. From the other side of the room a horrible scream came until it was suddenly snuffed out. I glanced and saw the other Tamika’s head rolling on the floor, the cut so perfect it took a few heartbeats before blood started coming out. I’d fallen back on my knees at some point, I realized, but my sword was within reach. I tried to pick it up with my hand but the broken fingers refused to move. 

No pain, though. Was I already beyond that? I dropped the knife and took the sword with my left hand as the Lone Swordsman calmly walked towards me. Behind me I could feel the goblinfire beginning to spread into this room, and with a wet laugh I saw green light beginning to filter out of the other exit. \textit{Chider set fire to both ends. Of course she did. }The hero seemed unconcerned as he came to stand before me – I stabbed the tip of my sword into the ground to push myself back to my feet. So much for avoiding the climactic melee. The Lone Swordsman frowned, his face still irritatingly handsome despite it. “Not a moment longer,” he reminded me.

The sword blurred and let out that horrifying keen as it spilled my blood on the floor. I could feel a trail of fire across my chest and something hard hit me in the stomach. I stumbled to the ground. My limbs felt cold. Someone was walking away and I knew who, but I couldn’t quite remember the name. Smoke was snaking its way across the ceiling in whimsical patterns and I lay there.

Dying.

I’m not sure how long I lay there. I could still hear things, but events came disjointed. A flash of blinding light and the sound of wood breaking. Three claps of thunder – or was it five? Beyond the cold that was spreading through me I could feel the most maddening itch, but I didn’t do anything about. It was like a painting almost done, but not quite. Like all it would need was a last brushstroke, and finally everything would \textit{fit}. I lay there, listening to the green flames devouring the world, and itched.

And then it clicked.

Awareness flooded back into me. I was Catherine Foundling, daughter of no one and nothing. I’d fought people for gold once, but earned only silver. I’d taken lives, and justice had come for me with a sword that cried like a grieving man. I was apprenticed to a monster but dreamed of making a world without them. A traitor to all causes but my own, and my path had brought me to this moment: bleeding out on the floor, surrounded by fire.

The other claimants were all dead, and I was the Squire.

My mind was getting clearer with every breath. It brought no comfort. The Name was roiling under my skin, finally mine, but it brought no healing with it. \textit{Evil never does.} I wanted to get up, needed to if I didn’t want to celebrate my victory by merrily burning alive, but my body refused to cooperate. I was more than half a corpse, and the endurance I’d always prided myself on was finally failing me. More than half a corpse, huh. The idea took shape in my mind, absurd in all the best ways.

“I’ve seen a corpse raised before,” I cackled to myself, hacking out a horrible laugh.

I reached for the depths of my Name, sinking as deep as I could without a second thought. It was still there, that cool feeling I remembered from the sunny afternoon where I’d made my mount. \textit{Like water so deep it’s never seen the sun.} I grasped the power, spun it into threads. Slowly, carefully, I tied knots around my limbs. It occurred to me that I was making a puppet of myself and I let out another cackle. \textit{Well, better me than someone else.} Opening my eyes, I looked at the ceiling and pulled. My left leg yanked itself up – the muscles pulled taut but held, and the right leg came to join it. Mustering the full weight of my concentration, I tugged at the largest string: my abdomen was harshly brought up, and I stood on my feet again.

“And now,” I announced to the empty room, “for my next trick…”

One, two, three, four, five. One after another, my broken fingers snapped back into place. I didn’t feel so much as a twinge of pain from the act, which wasn’t very likely to be a good sign. I balled up my hand and formed a fist before letting the strings go loose: the fingers loosened, still unresponsive to my attempts to get them moving. It would have to do. Like Creation’s most demented puppeteer, I tugged and pulled until I managed to get my sword back at my side and my knife back in its sheath. There was a hole in the wall, I noted. Apparently the Lone Swordsman had solved the dilemma of both ways out being on fire by making his own. Whatever he’d used to break through reeked of magic, but it didn’t seem harmful to me: I walked out into the alley with an indifferent shrug. The street was deserted, though close to the mouth of it I found black goblin’s blood splashed on the pavement stones. Chider’s satchel laid there unattended, spilled open by a sword strike. There were still munitions in it, I saw. Absent-mindedly I picked up a sharper, but the longer I looked at it the more my mind began to wander: I looked ahead instead, leaving the street and heading into a larger avenue.

I was near a stairway leading up to the outer walls, and up there on the ramparts I caught sight of a coat fluttering dramatically.

The Lone Swordsman stood there, brooding away into the night as the wind tousled his dark locks teasingly. I was halfway up before I realized what I was doing, and by then it was too late. Manipulating your own near-corpse apparently didn’t lend itself to stealth very well, because he turned towards me long before I was within stabbing distance. Shame, it would have been kind of a treat to just ram my sword in his back and push him off the wall.

“You,” he scowled before turning pale as he took a closer look. “\textit{What have you done to yourself?}”

I tried to reply but all that came out was an insolent gurgle. Right, still dying. That was unfortunate. I wasn’t in much of a bantering state, so I chucked the sharper at him instead. I missed and hit behind him, but the blast still knocked him off his feet. Small favours, I supposed. It took me two tries to get my sword out of its sheath – the angle was hard to visualize – but by the time he recovered from the shockwave I was on him. I tugged the strings and my arm came down, blade slamming down into his awkwardly angled parry. \textit{Too rough}, I noted as I felt the arm’s muscles tear like cheap cloth. The strength behind the strike was monstrous, though I noted with mild surprise that the edge of his blade actually cut into mine. Ultimately that came in useful: when I drew back my arm with another tug, his sword was ripped out of his hand and came away with mine. I shook it off by tugging my arm back and forth, kicking it down into the street when it clanged against the floor. I tried to speak up again but ended up spitting out a fat gob of blood as he looked upon me with horror, backing away. Still, it had the benefit of clearing my throat.

“Told you my plan was working,” I rasped.

“You \textit{planned} to become a necromantic abomination?” he said, aghast and still stepping away warily.

Not really, but it wasn’t like he could prove that. I circled around him with my sword brought up, forcing him to stand against the edge of the wall. The Hwaerte River’s dark waters ran down below, yet another defence in the arsenal of the Gate of the East.

“You’re Callowan,” he said when the silence got awkward. “We should be fighting side by side, not against each other. Why do you work for them? How can you possibly justify working for these tyrants?”

He hadn’t seemed as eager to make common cause when he’d been the one with the sword, I noted.

“Who else is there to work for?” I managed to get out, my voice so rough I could barely recognize it as my own.

He waved his arm passionately.

“Callow!” he replied. “For the Kingdom and all the people who live in it.”

“There is no Callow,” I rasped. “The Kingdom died twenty years ago. Before either of us were born.”

“If even one person fights under the banner, the Kingdom still lives,” he said, sounding like he’d just imparted some kind of great truth on me. \textit{Heroes.}

“A kingdom of one,” I spoke into a hacking cough. “All hail King Swordsman, lord of stupid causes.”

Those green eyes turned to steel and I tugged the strings to shift my footing, half-sure he was about to attack.

“There’s nothing stupid about \textit{freedom},” he hissed.

“Going to free us, are you?” I laughed. “How? By killing Imperial Governors? Nobody here’s any more free than when you started.”

“So I should kneel and lick the Enemy’s boot, like you do?” he snarled. “Never. I’d rather die.”

I could kill him. Right now, right here, I knew deep in my bones that I could kill him. I might not be able to the next time we met, but this once the story’s flow was in my favour. It was tempting, but at the edge of my mind I could make out a path. It was a dark one, strewn with ruin and the death of innocents, but hadn’t I stopped pretending to be on the side of the Heavens the moment I’d taken the knife?

“Prove it,” I rasped. “If you want your way to beat mine, then come at me again. Properly. Earn your Name, hero. Run and hide and muster your armies in the dark. Make deals you’ll regret until you have nothing left to bargain with. I’ll be waiting for you, on the other side of that battlefield.”

The Swordsman’s face went blank as I let my sword come down.

“But remember this,” I said. “Tonight? \textit{I won}.”

Faster than the eye could follow, I pushed him off the wall. He yelled something I couldn’t make out and as he fell into the dark waters and I took a step back from the brink. I let what I’d just done sink in, closing my eyes. With a life spared, I’d just killed thousands. I’d just promised cities to fire and ruin, sown the seeds of a rebellion that would rip the land of my birth – the very same land I wanted to save – apart. But I’d also bought the war I needed. Damn me, but I’d bought the war I needed. One after another, the strings holding me up gave. I flopped bonelessly to the ground, at the edge of unconsciousness. It was nice out. Cool and soothing, after all that time in the fire. I heard steps against the stone, calm and unhurried. 

“Busy night?” someone murmured.

I opened my eyes and came face to face with eerie green ones.

“I got stabbed,” I mumbled. “A lot.”

“Happens to the best of us, Squire,” the dark-haired man murmured, and I felt his hand on my shoulder before darkness took me.
\clearpage
\chapter{Chapter 13: Order}

“\textit{Mercy might be the mark of a great man, but then so’s a tombstone.”}
– Extract from the personal memoirs of Dread Emperor Terribilis II

\textit{It was dark inside the Commander’s quarters, the only light coming from the candle on the woman’s desk. He stepped behind her quietly, his Name’s power silencing the sounds of his armour as he raised his blade. The dark-haired woman stilled for the barest fraction of a moment, and Squire knew then that his chances of taking care of her quickly had evaporated into thin air.}
“\textit{Quiet or not,” the Commander spoke with a voice that bore the soft accent of the Deoraithe,“you reek of blood.”}
\textit{Squire’s blade came down but the woman spun, hand grasping for the longknife on her desk and batting the killing blow aside at the last moment. The green-eyed man sighed and shifted his footing as she rose to her feet.}
“\textit{I do hope that was a figure of speech,” he said mildly. “I bathe every few days.”}
\textit{The Commander bared her teeth in mockery.}
“\textit{Some things don’t wash off with water, Praesi,” she replied.}
\textit{His blade flicked forward, tasting the edge of her defence and finding it unfortunately steady. No less than he’d expected, of course – the woman’s Name was one that could only be earned through years of hard fighting, and not even Ranger’s tutelage was enough to overcome the disparity between their levels of experience. Even nurtured, talent could only bring you so far.}
“\textit{So tell me, assassin,” Commander jeered, “what was it that finally pushed the Chancellor to send a killer after me?”}
\textit{The longknife was a blur of sharpened steel in her hand and she stepped forward, turning a thrust into a vicious flick of the wrist when he stepped around it, dancing away before he could strike back and leaving behind a shallow cut on his cheek.}
“\textit{Was it the punitive expedition on the Red Boars?” she asked.}
\textit{Squire have ground fluidly, trying to find an angle where his sword’s longer reach would be able to come into play. It was unfortunate that his way into the quarters had meant travelling light, because fighting an opponent this dangerous without his shield was quickly becoming more than he’d bargained for.}
“\textit{No,” Commander mused, “it’s not like we’ve never done that before. Which means someone opened their damned mouth about my plan for the Lesser Steppes.”}
\textit{Squire smiled.}
“\textit{I might have heard a thing or two,” he agreed. “But you seem to operate under a misconception, Commander.”}
“\textit{Illuminate me, then, assassin,” she replied coldly.}
“\textit{Not Assassin,” he corrected her. “Squire.”}
\textit{That was when the bells started ringing. Three rings, a pause and then three rings again: the signal for a fire in the fortress. Apprentice had already started his work, then, which meant it was time to wrap this up: Grem’s clansmen would be in position soon. His opponent spat a few words in the Old Tongue. From the intonation, he would venture a guess they were nothing particularly polite.}
“\textit{So you’re one of the pups who wants to be the next Black Knight,” she growled. “You made an error in coming here tonight, boy – it’ll be my pleasure to nip you in the bud before you become a real problem.”}
\textit{Which was, he was forced to concede, a very real possibility. When she moved forward again, it was with the weight of cold anger behind her attacks – again and again he was forced to give ground, pushed out of her quarters until he was at the head of the stairs. Commander slipped under his guard when he overextended, ignoring the deep cut he carved right above her ear to close the distance and slam her palm into his chest. Had anyone but a Named done that on full plate they would have broken their wrist for their trouble, but instead her blow sent him tumbling down the stairs. About halfway down he managed to roll back to his feet, but before he could bring up his sword she nearly sliced through his jugular, forcing him to scramble back desperately. In a matter of moments she’d driven him all the way out to the inner courtyard, and now they both knew the game was up.}
“\textit{If you kneel,” she said flatly, “I’ll make it quick.”}
“\textit{If this were a story,” Squire told her, “this would be the moment where I revealed I was left-handed all along.”}
“\textit{Are you?” the dark-haired woman asked gruffly.}
“\textit{No,” he replied, sheathing his sword. “I’m a practical man at heart, you see.”}
\textit{The first arrow took Commander in the side of the throat, punching straight through and coming out the other side. Ranger’s work. The short bow volley from Grem’s clansmen followed a heartbeat later, filling her with so many arrows he could no longer make out her face.}
\textit{That’s the thing with practical sorts, Commander,” Squire told her gently. “We cheat.”}

I woke up in a room I didn’t recognize.
I could still feel the cold of the northern night on my skin, cheek still stinging where the Commander’s longknife had drawn blood. That particular sensation paled in comparison to the rest of my pains: my entire body was a raw wound, the worst of it centred around the long gash that snaked across my entire torso. I pushed myself up against the cushions, wincing as a flash of agony went through me. Tossing the blanket covering me aside, I took a closer look at the bandage-covered cut the Lone Swordsman had gifted me with: it was an angry red and would scar rather gruesomely, but at least it wasn’t bleeding. The rest of my body bore no marks, which sent a shiver of unease down my spine: I’d been healed by Zacharias enough to know that magic couldn’t heal this well without dipping a toe in unsavoury waters. I was alone in the room, I saw as I took a look around: sparsely furnished in the Callowan style, no windows and I couldn’t hear so much as a hint of noise from the outside. Everything in here smelled of blood, I noticed with a jolt of surprise. I hadn’t noticed because I’d smelled the same thing in the dream, and wasn’t that a creepy thought?

I forced myself into a sitting position at the edge of the bed, pushing down a pained groan. The identity of the Squire in my dream wasn’t exactly hard to deduce: Black still looked more or less the same, if a little older, and there was no way I could confuse those eerie green eyes with anyone else’s. There’d been too many details to the vision for it to be just a fantasy cooked up by my mind while I slept, though: even now, closing my eyes, I could still hear the low voice of the Commander and the shriek of those arrows as they fell form above. \textit{A Name dream, then.} My mind still felt too fuzzy to puzzle out exactly what was going on here, but I knew that there was bound to be a reason for it. When Black had shoved a sword through my chest, I’d ended up confronting two versions of me that could have been. \textit{So the dream shows me the previous Squire killing a hero when I just let one go. }A little heavy-handed, as far as hints went, but I was not a subtle girl by nature: it made sense that my Name would be equally as blunt. I passed a hand through my tangled locks with a grimace. Gods, I smelled awful. I needed a bath, or at least a change a clothes.

The door creaked open and Captain came in, ducking her head under the threshold. The sight drew a smile out of me: very few things must be Captain-sized, outside of wherever the Hells ogres lived.

Good,” the warrior grunted. “You’re awake.”

Barely,” I agreed. “How long was I out?”

It’s been two days since your little stunt,” she said. “You came damned close to never waking up.”

I’d suspected as much, but it still sent a shiver down my spine to hear it said out loud.

Should I sent a thank you note to the Legion healers, then?”

Captain snorted.

You tore your body up way past what they can handle,” she informed me. “Luckily we had a blood mage from the Swiftfoot tribe in camp – still took three bleedings to get you back to something manageable.”

Bleedings. Gods Above, I hoped she wasn’t saying what I thought she did.

You mean they bled \textit{me}, right?”

The olive-skinned woman graced me with a quelling look.

Don’t be obtuse, girl,” she grunted. “You had little enough of the stuff left in your veins. Black had them spill the lifeblood of three. Rough stuff, but it usually works.”

I felt my stomach sink and let out a ragged breath. Three people dead just to heal me, and Captain didn’t even seem to think of it as particularly notable. 

Who were they?” I croaked out. “The people that died to save me.”

She shrugged. “Death row prisoners,” she told me. “Never learned their names, but Scribe would probably know. Had to file some papers to requisition them.”

Requisition them, like a resource. Same as if they’d asked for a new set of armour or some sewing equipment. \textit{Like they were things, not people.} Oh, they weren’t likely to have been very nice sorts – they wouldn’t have gotten a death sentence otherwise – but at the end of the day what I saw was a Praesi spending Callowan lives like currency. Three stranger’s lives spent to preserve mine, without a second thought. Would I have agreed to it if I’d been awake, I wondered? It disgusted me that I was no longer as certain of my answer as I would have been a month ago. Captain’s presence suddenly felt intolerable, a blight to everything I was trying to accomplish. Just another cog in the Empire’s machine, grinding down the lives of the people they’d conquered. 

And yet, what could I do? For all that I itched to lash out, I was all too aware that even at my best I’d never manage to do more than scratch her armour. She was a woman who’d faced entire battalions of knights and slaughtered them effortlessly. They’d been kind, Captain and Black, so easy-going and helpful I’d ended up forgetting I was dealing with monsters. \textit{Calamities, the monsters even other monsters fear.} And the worst of it was that we were on the same side. I’d chosen, willingly, to align myself with people who saw human sacrifice as just another tool in their arsenal. The taste of bile in my mouth drowned out the smell of blood, and I suddenly felt like throwing up. It was one thing to make the decision to sacrifice lives in the abstract, but now that I was faced with the reality of it… How could I have ever thought good would come of this? \textit{Look upon the foundations of your better world, Catherine Foundling. Another three corpses for the pile, and they will not be the last.} I retched, vomiting all over the bed. The concern on Captain’s face was the most hateful sort of kindness I’d ever seen. My stomach settled after a moment and I wiped my mouth against the blanket.

I’ll talk to Scribe, then,” I muttered, shivering.

I’d remember the names, carve them deep enough I could never forget. Find out if they had families, people who’d depended on them: an insipid way of repaying a debt that ran so deep, but what else could I do? I still had my savings from the Pit and would not use so much as single speck of Imperial gold for this.\textit{ }\textit{My debt, my penance. Gods have mercy on my soul.}

You can do that later,” Captain grunted. “Put a tunic on, Black wants you outside.”

I felt too drained to tell her that all of them could go fuck themselves, as far as I was concerned.There was no dresser, but someone had neatly folded some clothes on top of the chair in the corner. I forced myself to my feet, rebuffing Captain’s helping hand when I swayed. I was in no mood to take help from Praesi. Changing my underclothes with someone else in the room was almost nostalgic, a reminder of the days where’d I shared a dormitory with the other orphanage girls. \textit{Nobody set out clothes for me then, though.} It bothered me that I’d stopped noticing luxuries like that: they crept up on you, the trappings of power. One inch at a time, until you forgot you’d ever lived without them. My lips twisted in distaste when I saw the woollen tunic I was expected to wear was dyed black. It felt like a claim was being made on me, and I’d always balked at those\textit{.} I buttoned up the collar anyway and smoothed my face out of emotions. I’d get clothes of my own as soon as I got the occasion.

What does he need me for?” I asked Captain as I finished slipping on my boots.

Just needs you to be seen out and about,” the gargantuan Taghreb replied. “Rumours are you’re dead, and people want a face to put to the fire.”

I blinked. Shit, the goblinfire.

That’s still burning?” I asked.

They managed to cordon it off,” Captain said, “but almost half the quarter went up in flames. Istrid had her legionaries evacuate the people in time, at least.”

A small relief, that I wouldn’t have to add more lives to my tally so soon after the last ones. I tightened my belt and made sure my knife’s sheath was properly placed. No sword, but that was to be expected after the Lone Swordsman’s blade cut into it.

Let’s go and get this over with,” I muttered, more exhausted than even my wounds warranted.

The inn we were apparently in was deserted except for a handful of Blackguards covering the entrance. I ignored them and followed the brown-eyed warrior into the streets. I heard the crowd way before we got to the Court of Swords. The large paved plaza had once been where the counts of Summerholm held justice, though the Imperial governess had preferred the fortress for that purpose. The name came from the way Count Harlay the Grim had taken the arms of a slaughtered Praesi army and piled them up to offer the king of the time instead of the taxes owed that year. What must have been the better part of Summerholm’s population had gathered in the Court and the sound of all those thousands whispering among themselves was almost deafening. Gallows had been erected in the centre, surrounded by a square of legionaries six men deep. Black sat astride his mount in front of the structure, Scribe standing next to him still as a statue. For once, she didn’t seem to be paying attention to anything but what was happening in front of her. 

The people parted in front of Captain like a receding tide, falling silent at the sight of the tall Named striding across the stone. From the corner of my eye I could see people pointing at me when they thought I couldn’t see. \textit{Squire}, I heard whispered. \textit{Traitor} came up nearly as often, and the epithet wouldn’t have stung as much had there not been a grain of truth to it. I kept my eyes fixed straight ahead and matched Captain’s stride as best I could. Black was in full armour, I noticed as soon as we drew close – he wore a helmet, for once, a heavy piece ornamented to look like a grinning devil.

Squire,” he greeted me, still looking towards the gallows.

Black,” I replied. “What the Hells is this?”

The restoration of order,” he said.

The gallows were no more than thirty feet away, so I could see who was on them now. There must have been fifty people standing in two lines behind the nooses, and I recognized every single one of them. Patrons from the Lost Crown, a handful I’d glimpsed in the Royal Foundry who must have survived the night.

You can’t do this,” I said urgently. “Not all of them were members of the Sons. Some just had sympathies and -”

And so were party to the assassination of an Imperial governess,” he interrupted me flatly. “High treason, which fetches the noose.”

You already knew who the members were,” I spoke pleadingly. “You could have hung them then, no need to do it now.”

Green eyes stared me down through the holes in his helmet.

They were tolerable, so long as they were harmless,” he stated. “They are no longer harmless.”

This is butchery,” I hissed. “You’ll be hated for this.”

I am already hated in this city,” he noted. “An acceptable loss, if I am also feared.”

I reached for the power of my Name but there was \textit{nothing}. Not a drop of the power I’d used to crush my enemies, even as I reached as I deep as I could.

You bound my Name,” I accused him.

Your powerlessness is of your own doing,” Black replied. “You took action that ran against your Name’s nature, and so damaged your access to it. Something related to your confrontation with the hero, I assume. No body was found.”

So you’re punishing

I am hanging traitors who took up arms against the Tower,” he corrected sharply. “I am not in the habit of wasting lives over petty lessons.”

I’d never hated anybody more than I hated the man in that moment. Sitting there on his horse, looking down on me from above. He stood for every fucking sneering Praesi I’d come across, eyeing me like I was just cattle in their herd. Pretending the laws he upheld were anything else than rules the Wasteland used to fix the game so they’d win every time.

I will have no part in this,” I spoke, voice so cold and furious I could hardly believe it was my own.

My fingers closed against the handle of my knife. His stare never wavered and I realized how absurd I must have seemed to him, the girl who couldn’t even use her Name and was still threatening to pull a knife on the Black Knight. There were two Calamities standing within ten feet of me, and even through the haze of rage that fact managed to sink in. I loosened my fingers. 

I will have no part in this,” I repeated, more calmly.

I might not be able to stop this, but I didn’t have to pretend I endorsed it in any way. I turned to leave, to go anywhere but here-

.”

I thought I knew fear. I’d felt it the night we first met, when the Knight’s power had choked the very air of the alleyway. I was wrong. Oh so very wrong. My limbs froze and my heart spasmed. Dark things lurked just out of my sight, thirsting for my death.

.”

I did. I couldn’t even think about not obeying. The monster studied me without a speck of emotion in his eyes, the almost indolent amusement he always displayed sliding off his face like water off a clay mask. There was no humanity in the thing I was facing, and finally I could say I’d met the Black Knight. The real one.

Did you think this was a game, Catherine? That actions would not have consequences?” the green-eyed man murmured. “Power cuts both ways. Authority comes with responsibility. Ambitions such as your demand sacrifice, so  .”

My body did. Even as I screamed inside, my body did. A hush went over the crowd as General Sacker scuttled up onto the gallows, giving her legionaries a sharp gesture to get on with it. Levers were pulled, the ground opened beneath the prisoners and twenty-five Callowans died of a broken neck. Thousands stood in the Court, and you could have heard a pin drop. Legionaries untied the corpses as soon as the last one stopped twitching, letting them fall down the hatches as they pushed the second row of prisoners forward. I read their faces one after another, too dazed to be properly horrified. In the middle of the line stood a slender blond girl with grey eyes. \textit{Elise.}Our eyes met and recognition flickered across her face, followed by pleading. \textit{Gods, forgive me. I didn’t know. You have to believe me, I didn’t know.} A heartbeat passed and the beautiful face turned to disgust. She spat on the ground as the noose was settled around her neck.

General Sacker gestured again and she died.

The crowd let out a long breath, and just like that it was over. Tens of thousands stood in the Court of Swords, surrounding less than two hundred legionaries, but as the last corpse dropped under the gallows they started to disperse. Cowed, just like me.

We leave with the noon bell,” Black spoke calmly. “Get back to the barracks by then.”

Without another word he rode away, his steel-clad horse obeying the unspoken commands of his Name. I staggered away numbly, my legs taking me away from the Court. It didn’t matter where, as long as it wasn’t here. \textit{Anywhere but here.} How long I wandered I couldn’t say, but I ended up at the bottom of a dead-end alley. No one else was in sight. I leaned against a wall, forehead coming to rest against the roughly hewn stone. Slowly I fell to my knees, welcoming the burn of my wound as my body stretched. I was so very, very tired. Over two hundred miles stood between me and home, and suddenly I was aware of how alone I really was. Surrounded by people who hated me, people I’d willingly set aside for the company the monsters killing them. And now here I was, without even the protection of the Name I’d bartered my soul away for.

A dry sob wracked my throat and I rocked myself slowly, closing my eyes. I’d done this to myself, feeling clever and in control every step of the way. It had felt like a dream, really. One colourful absurdity after another, Names and visions and claims. The stuff legends were made of. Maybe that was why it had come so easily to me – I couldn’t quite believe it was real, so I treated it like a story. I’d bantered with villains who’d soaked the pages of history books in blood like I was an equal instead of an ant they could step on without a second thought. Just the memory of the way I’d mouthed off on the first night was enough to chill my blood now, now that I knew I’d been speaking to the green-eyed creature I’d met in the Court instead of the lackadaisical villain I’d thought I was facing. There was no believing this was dream now. \textit{Not when I can still hear the sound of Callowan necks snapping under the rope. }Tear fell down my cheeks and I let them.

If this wasn’t worth crying about, what was?
\clearpage
\chapter{Chapter 14: Villain}

“\textit{All lessons worth learning are drenched in blood.”}
-Dread Empress Triumphant, First and Only of Her Name

We rode for Ater.

I forced myself awake for my sword lessons and kept up my readings, but I hadn’t spoken a word to Black since Summerholm. The Fields stretched in every direction around us, farms and grasslands as far as the eye could see: empty, most of them. The farmer seemed aware an Imperial party was coming through and they avoided the sight of us. I spent my evenings in silence, staring at closed books and thinking about the city I’d just left. I’d made a mistake. There were things about the way I’d reacted on the day of the hangings that bothered me, and I had no real explanation for them. Oh, I was still more disgusted than I could properly put into words. I’d taken lives before, but learning about the sacrifices had been a different matter. I’d killed for justice, when no one else was willing to give it. I’d killed in battle, when my enemies left me no other choice. That three prisoners, no matter how they’d ended up on death row, had been slaughtered like cattle to keep me alive still made me nauseous. They hadn’t died for a greater purpose, they’d died for my sake. Used up for their blood like animals. Their deaths had been unasked for, and they were not my fault, but the were my responsibility nonetheless.

As for the hangings… I could see, now that the heat of the moment had passed, that they’d been doomed to die. The Knight wasn’t wrong that they’d committed treason. Sparing them would have weakened Imperial authority and let a pack of conspirators who’d already been part of the murder of a Governor on the loose. That thought did not, however, extend to the sympathizers who’d died like the rest. How many in the Lost Crown had actually been part of the Sons of Streges? The group had been a small one, and ineffective before the Lone Swordsman had gotten involved. \textit{There certainly weren’t fifty of them, and that’s how many got the noose.} Were they innocent? No, perhaps not. But they were mainly guilty of hating the Empire, and how could they be blamed for that? If Black hung every sympathizer in Summerholm, there’d be nobody left in the city but the Legions. 

It wasn’t enough, though. There was more to it. It hadn’t helped that I’d nearly lost my life the night before and been told of death after death the moment I woke up. My hands still shook when I thought of how close I’d come to dying that night, slowly bleeding out on the floor as the hero walked away. If he’d been even a little more thorough, just a little less sure my wound would kill me… I took a deep breath a steadied my hand. The thought of going into a fight again had dread creeping up my spine, and I hated every moment of it. The whispers from the crowd had pushed me, in a way. For all that I’d pushed through as I walked, even now the memory of them stung. I’d thought I was prepared to be called a traitor by my people, I’d gone into this knowing they’d consider me one, but after actually living through it I knew I’d been anything but. Some part of me had wanted to set myself apart from what was happening, to prove I wasn’t betraying the land I wanted to save. 

My conversation with the Swordsman kept plaguing my thoughts. “\textit{How can you possibly justify working for these tyrants?” }he’d asked.\textit{ }I’d dismissed him as yet another heroic imbecile, back then, but- I frowned. There was no but. There should be no but. Why did a single conversation with a man I held no real respect for shake me so? It wasn’t like he’d made any good arguments. Just platitudes about kingdoms and banners, the kind of sentimental logic someone with no solid reasoning would use. There was something at play here I didn’t understand. I still couldn’t feel my Name, and the last time I had was in the wake of letting the hero go – they were related, in some way. I’d failed some sort of test: my Role had found me wanting in some manner. It burned me that the only person I could have discussed this with was the Black Knight, and I just \textit{couldn’t}. Putting aside that I’d knowingly tried to push a hero into starting an insurrection in Callow, just the sight of the man was enough to fill me with cold anger.

Three times, his voice had turned strange as he gave orders. Three times I had obeyed, regardless of what I wanted. That he’d casually commandeered my own body wasn’t something I ever intended to forget – and no one held grudges quite like Callowans.

The days passed one after another and I dug into the books. Most of them were history, as it turned out. Praes had been a mess before the Empire was even declared: there’d been no less than four Soninke kingdoms in the north, fighting each other over land, and in the Hungering Sands the desert tribes had slaughtered each other brutally over ever-scarce resources. They only people they’d hated more were each other: the Taghreb had frequently raided into the southernmost Soninke kingdoms, stealing everything they could get their hands on and burning the rest. Back then the goblin tribes in the Grey Eyries had been nothing more than a presence looming in the background, though they’d already been forging iron weaponry when everyone else was still using bronze. In a sense the Clans had been the force to be reckoned with, back in those days: humans tread lightly around them, fearful of the great greenskin hordes in the Steppes that descended like a flood of death every few decades. 

It was a feeble distraction, though, and the tension rose with every passing day. It had become nearly intolerable by the time we got to the Blessed Isle. The barren rock in the middle of the Wasaliti River had been the furthest Miezan stronghold on the continent, meant to be the stepping stone for an invasion of ancient Callow before the Licerian Wars put an abrupt end to those prospects. It had changed hands hundreds of times since those days, but the massive stone bridge linking the island to the ground from both sides still stood unbroken as a testament to superior Miezan engineering. The ancient fort had become a massive castle in the wake of Dread Empress Triumphant’s fall, when the Kingdom of Callow had finally claimed it as its own. Before the Conquest it had been the fortress-temple of the Order of the White Hand, the steel-clad paladins who guarded the eastern border of the kingdom. For centuries they’d been a plague on the Empire, raiding beyond even the Green Stretch. There were still songs sung about the time they’d ridden up to the Nine Gates of Ater, leaving the corpse of a Praesi general in sight of the city walls as a warning against designs to the west.

It was a ruin now, the very stone blackened and burned by the largest deployment of goblinfire in Praesi history. The Order of the White Hand had been wiped out root and stem as the opening move of the Conquest, the paladins killed to the last man and woman so that they could never rise again. It had been the moment when Callow started taking the newest Black Knight seriously, though not quite enough: two weeks later the infamous massacre on the Fields of Streges had effectively broken the better part of the Kingdom’s military strength. We rode under the broken arches of the only gate in silence, the wind hurling itself at the ruins sounding eerily like a dirge. It was said that if you listened closely you could still hear the screams of the two thousand who’d burned alive.

The sun was setting and the Blackguards immediately set to making camp under one of the larger towers, putting up the tents and starting a fire. Some of them had left the party to hunt earlier and caught a handful of rabbits they were intent on turning into stew, skinning the beasts and putting them into an iron cooking pot. I left Zombie in what must have once been the outer stables, avoiding the company of Black and Captain who were sitting by the fire. I could have just retired to my tent with a book and a candle, but after a long day’s ride I felt like stretching my legs: I wandered off into the ruins, not quite sure what I expected to find. The fortress had been thoroughly ruined, I found out. Even the inside of most structures was scorched, and not a single roof had survived the taking of the Isle. Here and there skeletons peeked out from under the debris, the bones themselves blackened and warped as a grim reminder of the dangers of goblinfire. 

I wasn’t sure why the Empire had never bothered to rebuild and garrison the Blessed Isle, truth be told. As the only way across the river it seemed like a key position to hold, but the Praesi seemed happy enough to leave it a wreck. A warning against defiance, maybe? Maybe even they were unsettled by what had happened here during the Conquest. I let my feet take me wherever they felt, eventually ending up by the southern wall. The view from there was striking. To the west fields swallowed the horizon, tinted red by the light of the setting sun, and to the east the Imperial road stretched beyond what the eye could see. It went all the way to Ater, I knew, one of the larger projects undertaken by the Empire. \textit{Dread Emperor Tenebrous}, I dredged up. He was the one to get it done. He’d seemed like a promising ruler early in his reign, until he’d made one deal too many with the Underworld and become convinced he was a giant spider stuck in a man’s body. Things had swiftly gone downhill after that.

I got bored with the sights eventually, walking down a half-ruined set of stairs to make my way back to camp. I was getting hungry, and I still had some readings to get done before I went to bed. I crossed into an open courtyard surrounded by a quartet of smaller bastions but stopped dead in my tracks when I realized I was no longer alone. Lounging on a miraculously untouched stone bench, a strikingly beautiful Soninke girl was watching me with a pleasant smile. I reached for my my sword before realizing I’d left it back in camp – I no longer wore it outside of my lessons. All I had was my knife, and even in the dying light I could see that the Heiress had a bared blade resting across her lap.

“Catherine Foundling,” the dark-skinned girl spoke amiably, her sing-song Mthethwa accent caressing the words. “It was past time we met properly.”

“Heiress,” I replied. “Didn’t think you’d be inclined to talk, after what you did in Summerholm.”

The aristocrat shrugged elegantly.

“It was nothing personal, Catherine,” she told me. “I thought you were a threat, back then. This is how the game is played, yes?”

I grit my teeth. She’d set the other three claimants – well, maybe two, Rashid likely had gotten there on his own – on me and it was \textit{nothing personal}? After a heartbeat I frowned.

“Back then,” I repeated carefully.

Heiress smiled, warm and friendly. “I know better, now. I wasn’t sure, after you let the hero go, but after that display in the Court of Swords there can be no doubt.”

My blood ran cold. There’d been nobody else on the walls, when I’d pushed the Lone Swordsman into the river. How could she- No. She might be guessing. No need to hand her leverage she might not have.

“Not sure what you’re talking about,” I grunted. “The Swordsman got away on his own – heroes do that, you know.”

The beautiful girl laughed. “Of course he did. I withdraw any implication to the contrary. Still, there’s no need for us to be enemies. I’ve come with a peace offering, you see.”

I raised an eyebrow. “I was under the impression that your Role and mine were supposed to be at odds,” I pointed out.

“We would be,” she agreed. “If you were a real Squire.”

My fingers closed against the handle of my knife.

“Would you care to repeat that?” I whispered. “I didn’t quite catch what you said.”

She waved away the threat. “Come now, Foundling – you don’t actually \textit{want} to be the Squire, do you? If you did, that deplorable scene in Summerholm wouldn’t have happened.”

“I’ve killed for this Name,” I replied coldly. “Careful, Heiress.”

“I’ve killed for good theatre seats, my dear,” the Soninke chuckled. “That’s the way of things, in the Wasteland. That’s why you’re so disgusted with us, isn’t it?”

“If you’re looking for an impassioned defence of the Praesi moral fibre,” I said through gritted teeth, “I’m afraid you’re barking up the wrong tree.”

“Oh, I quite agree with you,” Heiress told me feelingly. “You’re different, Catherine. Trying to be one of us can only hurt you. It’s why I’m offering you a way out.”

\textit{What?}

“You’re feeling trapped, right now,” the other girl told me, “but you don’t have to be. I have a ship waiting, and I can get you back to Laure safely. Or anywhere else you want to go, for that matter. You can start over without all this mess hanging over your head. Tonight. Just say the word.”

My heartbeat stilled. She was saying the truth. I knew it in my guts, she was saying the truth. If I accepted, I’d set out on a ship tonight and leave before anyone could catch me. I couldn’t go back to Laure, obviously, but I could sail down the Wasaliti until Mercantis and make my way into the Free Cities. I’d be beyond the Empire’s reach, there. Safe.

“And if I refuse?” I asked quietly.

“Are you?” Heiress murmured, pleasant smile unwavering. “Refusing?”

It was such a pretty smile she had. Shame about the way it didn’t reach her eyes.

“I think I am,” I said.

She sighed, crossing her legs.

“I’d hoped we could do this without resorting to unpleasantness,” she spoke. “Are you quite sure we can’t come to terms?”

“More sure by the moment,” I replied flatly.

“Well, then,” Heiress said, all pretence of pleasantness melting away. “As we speak, I have men surrounding your orphanage in Laure. If I give the word everyone inside will be dead by morning. The matron, the girls you shared a dormitory with, even the children. Put to the sword, every last one of them, unless you abandon your Name tonight.”

For the second time, my blood ran cold. She’d spoken her threat the way other people talked of the weather – like it was nothing particularly noteworthy, just a way to make conversation. Was she bluffing? Maybe. But she had the resources to arrange this, and she didn’t seem like the kind of person afraid to use every tool at her disposal.

“I’m not asking for your life,” Heiress told me patiently. “Merely that you get out of my way.”

“If you give the word,” I repeated. “That assumes you’re alive to do so.”

She laughed. “I have come in the fullness of my Name, Catherine. You’re powerless and as good as unarmed. And if that’s not enough for you…”

She snapped her fingers and in near-silence four silhouettes stepped out of the spreading shadows. Thick cloaks hid their features, but there was no hiding the crossbows they were pointing at me. They were spread out in the courtyard, their lines of fire overlapping only on me.

“Be reasonable, Catherine,” the Soninke said. “Surrender is the only rational course left to you.”

I closed my eyes. How many girls were there, in the orphanage? At least forty, and a third of them no older than ten. She’d kill them and not lose a wink of sleep over it, if she thought she had to. Gods, I was so sick of this. Not even a month and I was so very tired. I opened my eyes and exhaled, looking up into the sky. The moon was out. I laughed.

“Thank you,” I said.

Heiress frowned.

“I should thank Black too, I suppose,” I continued quietly. “This was a lesson I needed to learn.”

“I don’t follow,” my rival admitted.

“I’ve been thinking about this all wrong, you see. I was raised in Callow, and we see things differently. The shepherd boy picks up the fated sword, slays the dragon and is revealed to have been a prince all along.” I smiled at her. “This was never going to be that kind of story.”

Gods, I’d wanted it to. Deep down, I’d thought that just doing good things under an Evil Role would see me through this. That I could walk that line without every really dirtying my hands in a way I’d regret for the rest of my life. 

“Do it,” I said. “ Kill them. If I give in once, you’ll just use it against me over and over again.”

I couldn’t beat the monsters by being better than them. I’d never had that in me. Too much impatience, too much recklessness. That was all right, though. There was another way: \textit{be the bigger monster.}

“Do you think I’m bluffing?” Heiress asked, voice low and dangerous.

“I know you’re not,” I admitted. “Which is why I’m going to say this: if a single one of them dies, \textit{I will} \textit{make a monument to ruin of you}. All that has ever given you joy, I will turn to ashes. Everyone you’ve ever loved, I will break so thoroughly they die cursing your name. I will undo everything you’ve ever accomplished, wipe the slate of your existence so clean there won’t be a person alive that remembers you were ever born. I will take no pleasure in it, but I will do it.”

Eyes cold as ice, I bared my teeth.

“I will do it, so that the next time some smug Praesi prick tells me to surrender I can point to the wasteland that was once your home and watch them flinch.”

“You don’t have it in you,” she replied, face blank.

“\textit{Try me},” I hissed.

There was fear lurking under the beautiful mask and I relished it. It was about time those fuckers started taking me seriously.

“I could kill you, here and now,” Heiress said.

“You could try,” I corrected with a breathless laugh. “Here I am, abandoned by my Name with only a knife to defend myself. You’ve got four big men with crossbows and a fancy sword in your lap. Look into my eyes, Heiress – do I look afraid to you? You’ve stacked the odds, but have you stacked them \textit{enough}?”

She hesitated. I’d never felt more alive than I did in that moment, when that clever little wretch took a look at me standing alone in her trap and faltered. I had nothing to me but my anger, but that was more than enough. I’d fought without a Name, long before I ever met the Calamities. I could do it again.

“Kill her,” Heiress ordered, but I was already moving knife in hand.

Three strings twanged and I felt a bolt come within a hair’s breadth of my throat. \textit{Too slow.} I was on the first man before he could even drop his crossbow: I slid behind him, letting the last shot bury itself in his stomach. Laying a hand on his shoulder, I slid my knife across his throat and and let him drop to the ground. By the time I was moving again, Heiress was nowhere in sight. \textit{Stupid of you, my dear. If you’d stayed you might have won.} The second man had his sword out when I got to him, but after fighting real monsters every morning I could have laughed at how sloppy his stance was. He swung too wild and I slipped inside his guard, burying my blade in his eye to the hilt. I snatched his sword before it could drop to the ground, letting the third one come to me as the last henchman finished reloading. I flicked the tip of the blade in his direction and he backed off warily, though I circled to keep him between me and the man with the crossbow. 

He seemed reluctant to attack and I grinned when I realized why: he was afraid of me. They both were. I’d just killed the other two like it was a stroll through the market and sent their employer running without even needing to fight her. I pushed forward, letting him catch my sword in a parry – he was too eager to keep me far away, and it cost him when I dropped the sword to catch his wrist. His eyes widened in panic but before he could say a word I punched him in the belly. No armour, only soft flesh, and I pried his fingers loose of his sword before hacking into his neck with it like I was reaping wheat. I turned my eyes to the last one, bloodied blade in hand as the tip of his crossbow shook in his unsteady hands.

“Pray you don’t miss,” I said. “You’ll be dead before you get to reload.”

Steadying his hands, the man took aim carefully. Whether I could have dodged the quarrel or not would remain a mystery: before he could do anything, a hand of shadow slithered its way up his throat and started choking him. The minion pawed at it frantically, but the shadow stayed on his skin. A minute passed before he fell to the ground, blue in the face and eyes bloodshot. I cast an eye around the courtyard and saw Black sitting on top of the wall in the back, legs dangling off the edge. He seemed amused, the mask of indolence he liked to affect once more painted over his face. The dark-haired man remained silent, breaking off a piece of bread and popping it into his mouth. I strode towards the first man I’d killed, wrenching out my knife and wiping the blade on his cloak. I felt my Name stir deep inside of me as I sheathed the knife and smiled a hard smile.\textit{ Liked that, did you? Good. We’re far from done, you and I.} Slowly, I turned to face the Black Knight.

“I’ve missed enough lessons,” I said. “Let’s get to work.”

\textit{How can you justify working for these tyrants?} the Lone Swordsman had asked. I finally had my answer. \textit{Justifications only matter to the just.}
\clearpage
\chapter{Chapter 15: Company}

“\textit{I’ve found that the best way to win at shatranj is usually to turn into a giant snake and tear my opponent’s throat out.”}
– Dread Empress Vindictive III

We’d stopped for a late lunch before coming in sight of Ater. Black had pushed our usual personal lesson earlier in the day, since the evening would likely be spent introducing me at the Imperial Court, and he was spending more time talking than dipping his millet bread in the broth the Blackguards had put together.

“Early Praesi Names were divided along ethnic lines,” the green-eyed man spoke as I dug into my own bowl ravenously. “The Taghreb had the likes of the Red Fox – usually a thief, always clever – and the Grey Lion, often the strongest chief of the time. Soninke Names were associated with the rulers of their kingdoms, though some Champion derivatives arose during particularly brutal wars.”

“They’re all gone now, though?” I asked, hastily swallowing my mouthful when he raised his eyebrow at me.

“None have been seen in over a millennia,” he agreed. “Roles are usually a reflection of the people they spring from, you’ll find, and it’s been a long time since humans inside the Empire have ceased any designs of independence. Why settle for ruling a fraction of a realm, when you could claim the Tower itself?”

I could see his point. That was one of the most seductive parts of the Imperial philosophy, I’d found: in Old Callow, the throne had only ever passed between the various branches of the Fairfax dynasty. It would, theoretically, have been possible for one the duchies to topple them – and some had wanted to. The Dukes of Liesse, in particular, had never quite managed to forget that they’d been kings before the unification of Callow. In practice, though, the fact that more often than not the kingship came with a Name had seen them rule unchallenged. In Praes, though, anybody could claim the Tower if they were clever and ruthless enough. The High Lords got a turn in the seat more often than commoners, certainly, but the chronicles of the Empire were full of instances where a man or a woman with strong powers or a stronger vision had butchered their way to power. There was no Imperial dynasty: the longest a family had ever managed to claim the Tower was three generations, and they’d been wiped out to the last when the third Emperor was overthrown.

“I don’t recall hearing about any greenskin names, not since the Declaration of Empire,” I noted. “Which is weird, considering some ogres got Roles and there’s a lot less of them than orcs or goblins.”

Black set aside his bowl, offering me the full weight of his attention. We weren’t reconciled, not exactly. I would not forget or forgive the day we’d left Summerholm anytime soon, and he’d smelled the rat in the way the Lone Swordsman had managed to get away. Still, he spoke and I listened. For better or worse, the Calamity was the teacher I’d been given and I intended to learn everything I could from him. His successes, while ghastly, had still been successes. More than that, I’d planted the seeds of a war so I had better be ready to fight it when the time came.

“When it comes to the Clans,” he said, “we have the Miezans to blame for that. They systematically dismantled every aspect of orc culture. They went as far as razing the holy grounds of the Broken Antler Horde, the largest city on Callernia at the time. Roles do not come to be in a void, Catherine. There needs to be a weight behind them, a cultural imperative. Had the Clans broken away from Praes after the Declaration we might have seen a rebirth of their old Names, but the first Dread Empress managed to keep them in the fold by the skin of her teeth.”

“That’s kind of sad,” I admitted.

“Their most common Name was the Warlord,” Black murmured. “Mostly known for their propensity to put entire villages to the torch and take back their inhabitants to the Steppes as thralls.”

“Not \textit{too} sad, then,” I mused.

He chuckled. “As for the Tribes, it’s trickier matter. They were never outright conquered by the Miezans, as you know. They knelt after the first few defeats and so kept the majority of their holdings.”

“There’s not a lot about goblins, in the books you gave me,” I told him. “Some stuff about their alchemies and when they started getting interested in engineering, but even the explanation about the Matrons was a little vague.”

“That’s because there’s nearly no reliable literature on them,” Black replied. “They’re frustratingly secretive, not that they haven’t been given reason to be. Personally, I suspect that they \textit{do} have Names.”

I raised an eyebrow. “And they just what, never stepped out of the Grey Eyries? Roles are a little flashier than that.”

“They might not be,” the Knight said, “if the culture that spawned them values secrecy above all else.”

Huh. That made a twisted sort of sense, actually. For all we knew, the Matrons themselves might have been Named and just never told anyone. Roles like Assassin had aspects that allowed them to hide from scrutiny, so it wasn’t exactly unheard of. I had another question I wanted to ask, about the Name of Chancellor and how it had come to be forbidden – just laying claim to it apparently qualified as high treason – but before I could get anything out Scribe popped out of nowhere. More damningly, she managed to do it right next to me.

“Bloody Hells, how do you keep doing that?” I blurted out. “We’re standing in the middle of an open field, Scribe. The only footing here is \textit{rocks}.”

She didn’t reply, though I’m pretty sure a glimmer of amusement flashed through her eyes.

“Scribe,” the green-eyed man frowned. “You don’t usually interrupt during lessons.”

Without a word, she handed him a scroll. It was, I saw, sealed with black wax and the official Imperial seal. \textit{That looks serious.} Black broke it open and scanned the contents, face turning pale when he got halfway through.

“You’re sure?” he asked her.

“I have three different witnesses. Reliable,” the plain-faced woman replied.

“\textit{Fuck},” the Black Knight cursed, and my eyes widened. It was the first time I’d ever heard him curse. “We have those laws for a \textit{reason}, Scribe. Not even Triumphant was fool enough to break the Decree and she broke nearly every other law on record.”

Weeping Heavens, he actually sounded worried.

“What happened?”

The pale-skinned man rubbed the bridge of his nose, dropping the scroll on his lap.

“The Tower just received a Red Letter,” he said, tone grim.

I burst out laughing. “Really? The gnomes are knocking at the door? You could have at least put a little effort into the punchline.”

My mirth fell flat when neither of their expressions changed. “You’re serious,” I realized. “Are you telling me they actually exist?”

“Yes,” Black confirmed flatly. “And that’s the second Red Letter the Tower received this century. If we receive a third, the consequences would be… dire.”

“The gnomes, like the people with the huge metal armours and the flying machines that scream? We’re talking about those guys?”

“Have you ever heard of Kerguel, Catherine?” Black asked.

I shrugged. “The lost city that got sunk into the ocean by the Gods. There’s a great deal of bad poetry about it.”

“It was a real place,” the Knight told me. “One of the most powerful nations in the world at a time where the great Baalite cities were a collection of mud huts. They had an interest in natural physics and pursued it heedlessly, until one day they received a letter in a red leather sheath.”

That wasn’t the story as I’d been told it, so I listened in silence.

“The letter told them to cease their research or face extinction,” Black spoke into the quiet of the Wasteland. “The lords of Kerguel laughed and dismissed it as an esoteric joke. They laughed again, when a more strongly-worded letter came a month later.”

He paused, letting out a deep breath.

“They stopped laughing, when they lost contact with all their colonies. It was already too late by then. The Yan Tei have the only surviving records on the subject, and they say that the fleet of metal ships that came for Kerguel darkened the sky itself – it could be seen from miles away.”

“You mean they…” I trailed off.

“They sunk the island into the sea,” Black said. “Sorceries Kerguel had spent decades refining slid off the ships like water off a duck’s back. The explosions were larger than anything that’s been seen before or since. By the time the gnomes were done, there was not a living soul left on the barren rocks.”

I sat there listlessly, watching my teacher’s expression turn coldly furious.

“So you can understand how after that farming machine under Nefarious got us a Letter, I’m a little irritated that the Hearthmaker tribe was\textit{ foolish} enough to start playing with powders.”

“What are you going to do?” I asked quietly.

“They need to be purged,” he sighed. “Every last one of them, and the research destroyed. The Matrons will have a fit, but there’s no other way.”

“You could fight them,” I said. “If they’re threatening you, you must have found something they’re afraid of.”

Black smiled mirthlessly. “In the grander scheme of things, Catherine, I’m the petty warlord of a backwater kingdom. The only nation on our continent that can be considered something other than a regional power is the Kingdom Under. When one of the \textit{real }world powers tells the Empire to do something, we do it. I will not face destruction in the name of pride.”

Well, shit. When someone with my teacher’s usual level of self-confidence told you someone was out of their league, they weren’t likely to be wrong. Would the gnomes also destroy Callow, if they came? It was part of the Empire, at the moment. \textit{Hopefully I’ll never have to find out.}

“We’re going to Foramen, then?”

Black frowned. “You aren’t. It’s still too early for you to deal with the Matrons.”

I scoffed. “Can’t know if we don’t try, can we?”

“Spoken like someone who’s never been in the same room as those cunning old bats,” my teacher replied, faintly amused. “No, you’ll be going to the Academy until I’m done.”

Funny how these things went, wasn’t it? A month ago that had been the plan, and now it looked like I’d get what I’d wanted.

“Scribe,” the dark-haired man spoke. “Is there a company with a missing officer?”

The plain-faced woman replied immediately. “Rat Company. Lacking a lieutenant as of last week, still waiting on a transfer. They’re beginning war games at Spite Valley tonight.”

Black hummed thoughtfully. “Sink or swim. Fitting. Can you have a legionary’s kit brought to her on the way?”

Scribe inclined her head by an inch. “Already sent the runner.”

The Knight chuckled. “What would I do without you?”

“The same things,” Scribe replied blandly. “Just not as well.”

He turned his eyes to me and I shrugged in agreement. Wasn’t like I had anything else planned this week.

—

The War College was the only officer’s school in the Empire, meaning that every officer wanting to make a career in the Legions of Terror was expected to have graduated from those hallowed halls. There were other training camps scattered among the Empire for legionaries, of course, but anyone who wanted to enrol straight into the commissioned ranks went through the College. The institution had existed in one form or another since the founding of the Empire, though until recently admission had been restricted to the children of Imperial aristocracy – and in even earlier times, only to the boys among those. Dread Empress Terribilia the First had put a swift end to that particular brand of stupidity by using the Headmaster as ammunition for her latest catapults, much in the same way that my own teacher defenestrated the last Headmistress when she’d refused to allow “filthy greenskins” in her classrooms. 

The College itself was situated on the outskirts of Ater, a large two-story stone hall made up mostly of classrooms, but the cadet barracks and training fields took up the entire city district known as the Five Swords Lanes. Towards the end of Dread Emperor Nefarious’ reign – which could more accurately be called the beginning of Dread Empress Malicia’s – the reform and rapid expansion of the Empire’s military had forced the Legions to set up a handful of semi-permanent camps outside Ater where the vast majority of the cadets actually slept. The old College barracks were reserved for students in their final year, nowadays, and the more practical classes were taught out in the Wasteland instead of in a classroom. 

Within a week of joining, students were assigned to a company of a hundred other cadets that would serve as their mother unit for the rest of their time at the College. Given that there were around a thousand cadets in attendance, the student body was divided along the lines of ten companies. Each company had a name and a standard, typically an animal from the Wasteland, except for the company at the head of the monthly rankings: they were called only the First Company, and the competition to hold that title was nothing short of brutal. While individual cadet marks in the theoretical classes did affect company standing, the real way to rise in the rankings was to win the war games held every week in Spite Valley. 

There was an old fort in the valley the Blackguards escorted me to, a leftover from the days where the Order of the White Hand had occasionally crusaded their way east to Ater itself. After the Conquest it had stopped being garrisoned and become the main site for the College’s war games. The most basic scenarios were favoured: typically an attack and defence simulation between to randomly drawn companies, though the Headmaster was known to occasionally pit several companies against each other in wider games. The valley itself was half a day’s march away from the capital and large enough that armies in the thousands could have gone through. The fort itself was situated on a hill guarding the way to Ater, sloping down into the deeper valley where a lone watchtower overlooked deep woods and a handful of streams. After a long walk the slope rose again, leading to a circle of hills backed by a veritable forest of rocky outcroppings: that was where Rat Company had elected to make camp, among the hills. I’d been able to see the smoke from the campfires long before the company itself.

Hiking my way through the camp with the legionary garb I’d put on hours earlier, I blessed the fact that there’d been a primer on the Legions inside the pile of books from Black – Heavens knew how confusing all the terms would have been otherwise. 

The war game was being run between a pair of companies, which meant the hundred cadets on each side answered to a single captain. Under the captain there would be five lieutenants in charge of a “line” of twenty soldiers, and under each lieutenant a sergeant. Lines were expected to be able to split into two “tenths” if the battlefield required it, in which case the sergeant would end up in command of the second tenth. I felt uncomfortable in my standard-issue chain mail after having spent so long wearing a better-fitting armour, but that gear had belonged to Squire – I was ‘Lieutenant Callow’ as long as I attended the College, and she wasn’t supposed to have access to those kind of resources. I found my assigned line milling around a half-built campfire, digging into their rations gloomily. My sergeant was easy enough to spot, thankfully: a tall orc with the single red stripe of his rank sown into his shoulder pad, his skin closer to brown than green. He was talking with a particularly skinny goblin sporting the same insignia, I saw as I drew closer – they stopped as soon as they noticed me coming, the orc pushing himself up to snap a salute while the goblin merely afforded me a curious glance. “Sergeant Hakram?” I checked.

“That would be me,” the orc said in a gravelly voice. “You’re our new lieutenant, then?”

“Lieutenant Callow,” I agreed, offering my arm.

Hakram let out a pleased rumble at the gesture and clasped my forearm. “The little pipsqueak next to me is Sergeant Robber, from the Fourth line.”

“Pleasure to meet you, Lieutenant,” the goblin greeted me. “I should get back to my men before Pickler realizes I’m gone. Luck in battle, Hakram.”

“Wade in their blood, Robber,” her sergeant replied in one of the most common orc forms of farewell. The goblin scuttled away around the hill after offering me an amusingly sloppy salute.

“So which company did you transfer from, Lieutenant?” Hakram asked.

“I’m new,” I replied. “Never been in any before.”

“Gods be kind,” Hakram cursed. “The Captain’s going to have a fit. We’re already at the bottom of the rankings and now we get a greenie?” The orc paused before shooting me an almost apologetic look. “No offence meant, it’s just that a seasoned Lieutenant might have made a difference tomorrow,” he continued. “We’re up against First Company, and they get to be on defence too.”<

“None taken,” I replied, a little bemused. “First Company’s that good?”

“They haven’t lost a single game,” Hakram grimaced. “Captain Juniper’s called the Hellhound for a reason.”

“They’re pitting the best company against the worst?” I mused. “That hardly seems fair.”

“Luck of the draw,” the sergeant offered ruefully. “Ratface’s been cursing his heart out since the moment he pulled our number.”

“The Captain’s name is \textit{Ratface}?” I grinned, letting out a startled laugh. I knew that anyone who enrolled in the Legions could do it under the name of their choice, but who in the Hundred Hells would choose the name Ratface? Hakram grinned back, the sight made more than a little intimidating by his razor-sharp teeth.

“I heard the instructors assigned him to Rat Company just for the irony,” the orc said. “You should probably head out to the officer’s meeting, Lieutenant. I’ll take care of the watch rotations for the night.”

“The command tent’s on the other side of the hill, right?”

“It’s got a standard with rat skulls hanging off it,” Hakram grinned. “Can’t miss it.”

I offered the orc a salute he mirrored crisply and took the dirt trail up the hill. The legionary armour felt surprisingly light on my shoulders, after a month of traipsing around in plate, even with the thick rectangular shield strapped on my back. I missed my own sword already, but I supposed to keep a low profile while at the College and carrying around anything but standard-issue stock was a sure way to draw unwanted questions. Unlike some of the legionaries I’d read about, Rat Company didn’t seem equipped with the lever-action crossbows. They were probably meant to be an assault company, then. 

Like my sergeant had said, the command tent was impossible to miss. It was twice as large as anyone else’s, for a start, and even if I’d somehow managed to miss the standard next to it the War College’s crossed silver swords were sown into the fabric on every side. There was a pair of legionaries standing guard by the entrance but after a cursory glance at the twin red stripes on my shoulder they let me through without a word. Four armoured legionaries were crouched by a crate someone had nailed a map to, most of them looking up at the sound of my coming in. I glanced through the room, noting that only half of the lieutenants attending were human. The only attending goblin was still tracing something on the edge of the map with her crooked fingers, looking almost comically small next to the thick, muscled orc at her side. A strikingly handsome boy with grey eyes and olive skin gave me a brief once-over before letting out a displeased grunt.

“You’d be Lieutenant Callow, I expect?” he asked.

“Reporting for duty, Captain…” I trailed off, wondering if I should actually call him by the name I’d been given. It had seemed amusing when talking with Hakram, but now it was turning out more along the lines of awkward.

>“Ratface,” the captain finished curtly. “You weren’t in the College rolls before being assigned to Rat Company. Would I be correct in assuming you’re a greenhorn?”

“I’ve seen combat before,” I replied. “And not with blunted swords either.”

“Have you now?” Ratface smiled, looking anything but friendly. “Good for you. Unfortunately that’s worth shit to me, Lieutenant. I don’t care if you castrated an ogre in single combat, you’re still a godsdamned greenie legionary they saddled me with on the day before an exercise with the First Company.”

I took a deep breath, wondering if punching my superior officer in his fat sneering face on the first day of my assignment would leave a black mark on my record. It probably would, so I forced my anger down for the moment. Let him whine all he wanted, I’d show what I was worth on the battlefield.

“More dead weight,” the large greenskin lieutenant cursed softly in Kharsum. “Just what we needed.”

My eyes flashed with quicksilver anger. I only had so much patience to spend. “You’re awfully mouthy for an unblooded boy,” I replied in the same language. “Looking for a fight?” 

The orc barked out a laugh. “Hard words,” he grinned dangerously. “Keep a lid on it, greenie, it’d be a shame if I had to knock those pretty little human teeth out.”

The captain sighed, passing a hand through his short curls.

“Nauk, stop flirting with the rookie,” he said in Mthethwa, “we’ve got more pressing matters on our hands. Take a seat, Lieutenant. I suppose it’s not your fault you were assigned to us.”

Accepting the tacit apology, I gave a nod in response and went to crouch over the map with the others. The parchment laid out the cluster of hills Rat Company was camping in with the rocky outcroppings at our back as well as the valley separating us from the old fort I’d passed by earlier.

“Juniper will have the valley between us full of scouts,” Ratface announced, “but our best chance is still hitting them tonight. If we try a night assault tomorrow it’s a sure bet they’ll have had time to set up an ambush. Kilian, what did your men see when they got a look earlier?”

A short red-haired lieutenant cleared her throat and pointed out the watchtower in the middle of the valley. “There were at least two lines there setting up bonfires,” the girl murmured. “If we manage to take them out without too many losses we might actually have a shot at taking the fort.”

“My sappers have enough smokers to clog up a whole wall,” the goblin lieutenant said. “The melee for the rampart will be messy after we land the ladders, but if the lieutenant holding the wall panics we have a decent shot at punching through to the standard.”

“Nauk,” Ratface addressed the orc. “Your men will take the first wave of the assault. Callow, you’ll be right behind him.”

“Understood,” I replied.

“Sergeant Hakram knows his business. Frankly, I’d rather have him as lieutenant for your line but life is ever full of disappointments,” the captain continued. “If he tells you you’re doing something stupid, \textit{listen} to him.” After a last lingering look at the map, Ratface spat in the dirt and raised his head to look us in the eyes. “We’ll get moving two hours before dawn,” he informed the assembled officers. “Keep your lines on half-watch, I want our soldiers as rested as they can be for the fight. I’ll see you all in a few hours.” We rose and saluted, exiting the tent one by one and leaving the captain to his map.
\clearpage
\chapter{Chapter 16: Game}

“\textit{Those who live by the sword kill those who don’t.”}
– Dread Emperor Vile the First

I woke up to the sound of fighting.
Pushing away my covers I reached for my sword-belt, hastily buckling it on as I hopped from one foot to the next. Squinting to make out the source of the noise in the camp fire’s dying light, I caught a dozen silhouettes making it down the hill towards my line. Legionaries, I saw, but the insignia on their shield wasn’t Rat Company’s. \textit{A night attack on the very first night?} Reckless, but if the sounds of battle coming from the other side of the hill were any indication the enemy captain’s boldness might just have paid off.
“ON YOUR FEET, YOU LAZY BASTARDS!” I heard Hakram’s voice roar from further down, “WE’RE UNDER ATTACK!”
Grabbing my shield, I forced myself to focus and went to join my assembling soldiers. I’d thought that the assault before dawn would give me the time I needed to ease into legionary tactics, but it looked like I was going to be dropped straight into the deeper waters again. The thought brought a reluctant smile to my face as I pushed my way past the awakening soldiers to my sergeant. \textit{Business as usual, then.} When had I ever gotten to learn anything the easy way?
“Sergeant Hakram,” I called out as soon as I glimpsed his face, “Report.”
“I have no idea what’s going on,” the orc rumbled. “I got woken up when the soldiers on watch went missing.”
I eyed the enemy soldiers calmly walking in our direction with a grimace. I’d miscalculated: that was a full line, not just a dozen. The shouts and ring of steel against steel coming from where Lieutenant Nauk’s line had been camping next to mine meant that they were in just as much trouble as we were. Was Captain Juniper trying to wipe out the company on the very first night?
“The standard, Sergeant,” I breathed out in understanding. “They’re going for the standard.”
Juniper didn’t need to actually knock out every soldier in Rat Company, just bring back our standard to her victory zone. Hakram let out a colourful string of curses in Kharsum, which I chose to interpret as agreement.
“Third Line!” I called out, “Double ranks, NOW!”
We couldn’t afford to get bogged down in a melee with the enemy line, not if First Company was going straight for the win. I’d have to get my soldiers on the other side of the hill and decide if this engagement could still be salvaged.
“Lieutenant?” Hakram prompted. “What are your orders?”
My line had formed up like a well-oiled machine while I was thinking. The First Company’s soldiers had stopped halfway down the hill and formed a wedge, patiently waiting for me to charge my line into their formation. \textit{Screw that. I’m not hitting a force on high ground with most my soldiers half asleep.}
“Go help Lieutenant Nauk’s line, Sergeant,” I decided. “I’ll go for the standard myself.”
The orc frowned.
“Sir-” he started, but I cut him off.
“Hakram, there’s no time to argue,” I said. “Do it and I’ll catch up with you afterwards.”
The sergeant saluted, though he still looked sceptical.
“Good hunting, Lieutenant,” he replied, turning to get my soldiers moving.
The enemy was standing square atop the dirt path I’d used during the day, meaning I’d have to go around the sides: I slung my shield across my back on the leather strap reserved for that very purpose and went for the shadows. I’d have to be swift and quiet if I wanted to make it without getting caught, just like when I’d used sneak out of the orphanage to go fight in the Pit. The night was on my side, at least: the moon was covered by clouds, and while it might have helped the enemy sneak up on us earlier now it meant that away from the campfires I was as good as invisible. I circled as far away from the fighting as I could, but while skirting around a handful of abandoned blankets I got a glimpse of the melee I’d just sent my line into: Nauk’s silhouette stood out starkly against the flames. The lieutenant was half-naked and grappling with a pair of enemy legionaries, ignoring their blunted blades as he knocked their heads together and roared out a challenge. Hellgods, it was easy to forget how terrifying orcs could be when they cut loose. Two hundred pounds of pure muscle and bloodlust moved by the most vicious of instincts. No wonder the war parties from the Steppes had been such a thorn in Callow’s side, before the Wall was built. Shaking off the thought, I finished my trip around and got a high enough vantage point that I could see what was going on.
It was… less than promising. The standard still stood, but a melee was raging barely twenty feet from it and I could see Ratface’s forces were getting mauled. He’d managed to dig in his left flank with its back to the hill, but the centre was giving ground and there was no right flank to speak of: the line facing my men had probably slipped through the space to make sure Ratface wouldn’t get any reinforcements, if I had to guess. \textit{We’ve lost this}, I was forced to admit. Even if my own soldiers managed to get Lieutenant Nauk’s moving, by the time they punched through the line waiting for them on the hill the battle would already be over. \textit{So think}, I told myself. \textit{How can we turn this around?} Moments passed, but nothing came to mind. Whoever Captain Juniper was, she’d thought this through perfectly. An enemy legionary tore his way through the centre and ran for the standard, and before I knew what I was doing I started running downhill. A handful of legionaries from the centre pulled back and managed to tackle the soldier, but that was the beginning of the end for Ratface’s men: First Company’s legionaries poured through the openings in the rank, breaking the whole formation apart in a matter of moments.
Forcing myself to go even faster, I ignored the melee and focused on the one part of this I could actually recoup: the standard. If First Company got their hands on it the game was as good as over, but if I could bring it back to my line and pull out under the cover of darkness we might just survive this disaster. Though what I could actually manage to do with so few soldiers was… \textit{No}, I told myself. \textit{One thing at a time. }Better to focus on the things I could do than those I couldn’t. Snatching up the standard from the socket it was in, I shot the melee an apologetic look before running off the way I’d come. The way back was quicker, since there was no point in skirting around the fighting. The melee around Nauk had gotten even messier in the last few minutes, but I could see it was turning to Rat Company’s advantage: the attacking line had tightened ranks and was slowly edging back towards the hill. A good call, if I’d actually meant to have my soldiers join the broader engagement. The company’s legionaries closed rank around me as soon as they saw I held the standard, a ragged cheer coming from their formation.
“Lieutenant,” Hakram greeted me cheerfully as he pulled back from the front line. “Nicely done. How’s the situation on the other side?”
“Done,” I replied. “First Company was flipping their line when I left – they’ll be on our asses in a few moments. Where’s Lieutenant Nauk?”
“Limping about,” the sergeant told me with a vague gesture. “They managed to break his leg, so he’s using Sergeant Nilin as a crutch. I don’t suppose you brought back any healers?”
“Didn’t even see one,” I said. “I’m pretty sure the mage line was the first to be hit.”
“Fucking Juniper,” Hakram cursed. “\textit{Bashal} like this is why they call her the Hellhound.”
“CALLOW!” the yell came from behind me in the voice I recognized from earlier. “Decided to join the fight, I see.”
I turned with a raised eyebrow to see Nauk with his arm slung over a dark-skinned boy’s shoulder. Sergeant Nilin, I assumed.
“Had to pick something up,” I replied easily, hefting up the standard resting on my shoulder. The orc lieutenant eyed me cautiously.
“Ratface?” he asked.
“Probably a prisoner by now,” I grimaced.
“We hitting that line on the hill, then?” Hakram rumbled.
I passed hand through my hair, only now noticing I’d been running around without a helmet this whole time.
“No,” I decided. “We’re pulling out. How many soldiers do we have?”
“Half my line and most of yours,” Nauk grunted. “At least half a dozen wounded.”
I eyed the enemy line gathering up on the hill – the ones who’d formed a wedge earlier seemed to be joining them, and there was no way the forces just described would hold up against forty legionaries, half of which hadn’t even seen fighting yet.
“Let’s get out of here before they have time to form up,” I said. “Wounded first, I want them out of the way if this turns into a fighting retreat.”
Hakram saluted and disappeared into the mass of soldiers without another word. Not for the first time tonight, I was glad I’d gotten the tall orc as my sergeant.
“They’ll hunt us down if we go into the rocks,” Nauk spoke up, dark eyes considering as he faced me.
“That’s why we won’t be heading there,” I replied. “There’s enough woods in the valley to hide us until we have a better idea of what’s going on.”
The large – and still half-naked, I only now noted – orc looked at me for a long, silent moment.
“Sergeant Nilin,” he suddenly spoke, still looking into my eyes. “I’m ceding command of our line to Lieutenant Callow for now. Let’s get the bastards moving before we have half of First Company breathing down our necks.”
Letting out a breath I hadn’t known I was holding, I offered the orc a gracious nod before turning my attention back to the soldiers on the hill. They were nearly done forming ranks, I saw. With an ironic salute to the enemy, I followed my troops as they made their escape.

—

We hadn’t been walking for a quarter bell when Sergeant Robber popped out of the darkness. The goblin had half a dozen sword points resting on his throat in the blink of an eye but he merely grinned, supremely unconcerned.
“You guys are by far the largest group of survivors out there,” he informed me as soon as I made my way to the front of my line. “You must have pulled out early on.”
“I can recognize a lost battle when I see one,” I replied, tone neutral. “You’re alone?”
Robber whistled softly and another three goblins came out of the dark, one of them badly bruised but all of them bearing the leather satchel I knew sappers carried their munitions in.
“We’re all that’s left of my line,” the diminutive sergeant told me. “They even got Lieutenant Pickler. Got room for a few sappers in your little exodus?”
“Make yourself at home,” I replied.
Sappers. The first pleasant surprise of the night, which I rather thought we were due after the series of disasters we’d been inflicted. The goblins might not have been of much use in a shield wall, but they served an important purpose in the Legions: engineers, demolition specialists and even scouts when there was a need for it. Whatever the goblins were carrying in those satchels of theirs was worth its weight in gold, in our current situation. The other three goblins melded into the ranks without a word, but Robber remained at my side as the column started moving again. The goblin had assumed, correctly, that I’d have questions for him.
“You said there were other groups?” I asked.
“Small bands of five or less that fled when Ratface got taken,” the goblin said. “They were fleeing without a plan, most of them headed for the rocks. Juniper’s probably spreading out her soldiers to hunt them down as we speak.”
Well, so much for linking up with another group. I’d half-hoped that another officer would have managed to save a tenth and make out in the night, but to be frank I wasn’t all that surprised no one had managed. I probably wouldn’t have either, if the lines I’d been fighting hadn’t been stuck holding a vital position.
“We’re looking for safe place to rest,” I told Robber. “I know your Lieutenant sent some of your line scouting earlier – do you know anywhere we can use?”
The goblin nodded, though he looked less than enthused.
“I know somewhere from the last time we had a game. Would take us most of the night to get there, though,” he cautioned.
“The further into the valley we go the better,” I murmured. “They’re looking in the rocks, but they’re bound to catch on we went the other way eventually.”
“I hear you,” Robber said, absent-mindedly tacking on a “sir” to the sentence after a moment. “D’you know if they saw you take the standard?”
I grimaced. I’d been wondering that herself. I would have been seen when I’d first taken it, of that there was no doubt, but would they know I was in command of the missing line? Even if First Company interrogated their prisoners, no more than a handful of people would even know what I looked like.
“I don’t think so,” I finally said, “But I wouldn’t bet on it.”
“Yeah,” Robber muttered in agreement, “people who underestimate Juniper always get fucked. There’s a reason her company hasn’t lost since she became captain.”
I passed a hand through my hair, letting out a sigh. There wouldn’t be much sleeping tonight.
“Find us a camp site first, Robber,” I ordered the sergeant. “Let’s take it one day at a time.”
Bobbing his head, the goblin deftly jumped forward and called out for the soldiers at the head of the column to follow him into the dark.
The march into the valley proved to be one the most harrowing experiences in my life. I could understand why war was conducted mostly during the day now. It had been Hells on my troops to make their way through the slippery hill paths and even worse when we’d entered the forest, without even the moonlight to show us where they were going. Robber’s goblins were already proving their worth, their peculiar eyes allowing them to pick out the best paths unerringly in the dark. Twice we’d had to huddle out of sight as the goblins picked out enemy scouts, waiting in silence until First Company moved on. Some of the legionaries had suggested lighting torches after we’d crossed into the woods, but I’d nixed that idea in the bud: if Juniper had left anyone in the watchtower that was as good as marking our camp on the First Company’s maps. By the time we finally arrived at our destination, the first stirrings of dawn could be seen in the sky.
My exhausted soldiers dropped their packs and shields to the ground as soon as they could, barely bothering to spread out across the clearing Robber had taken us to. I could see why he’d choose a place like this: there was small stream running through the clearing where the legionaries would be able to fill their canteens and a handful of berry bushes I dearly hoped were edible. I’d had Hakram ask around for how many rations had been salvaged from the camp, and the amount was dangerously low. My body was urging me to follow the legionaries’ example and curl up under a tree, but I forced myself to move. There was still work to be done before I could allow myself to rest. I saw my wounded settled as comfortably as I could, cursing that we hadn’t managed to get even one mage from the battle’s survivors. I had a word with Sergeant Nilin to arrange for him to set up a watch and was pleasantly surprised to find Hakram had already done the same without my asking. I was beginning to see why Ratface had wanted the orc in command of my line.
“Grab some sleep, Lieutenant,” my sergeant told me quietly when I insisted to be added to my line’s watch roster. “Better to have your brain well-rested than another pair of eyes to watch for the enemy. You’ll be the one making the plans tomorrow.”
I agreed on the condition that he wake me up in no more than one full bell, pretending to believe his obvious lie when he agreed because I was too exhausted to argue. Setting down my bedroll close under an old oak tree, I lay down under the blanket and told myself I’d close my eyes for just a moment. There were just too many things left to do, I murmured to myself.
Darkness came.

—

It was midmorning when Hakram woke me up, by the looks of the sun. I considered reprimanding him for having let me sleep in, but I finally decided against it: if I hadn’t woken up by myself it meant my body had probably needed the rest. I blearily tied back up my bedroll and went to wash my face in the stream. The camp was buzzing with activity, legionaries clustering in small groups to talk to each other in low voices: I got a handful of salutes on my way, which I nodded back to. The cold water finished waking me up, clearing away the last dregs of sleep. I broke a piece of the rations I’d brought with me on the flight last night and tore hungrily into them, deciding I’d go pick some berries later to finish the job. \textit{After asking Robber if they’re poisonous}, I added mentally. I had no intention of spending the rest of the game moaning on the ground after managing to survive last night. I was pleasantly surprised – once again – that Hakram had roused up the other officers and was already waiting for me.
“No sign they found us” I prompted the other four as I sat on a flat stone.
“The sentries haven’t seen anything,” the dark-skinned boy I vaguely remembered being called Sergeant Nilin agreed.
“We should be safe for a day or two,” Robber told me. “I’m sure Juniper doesn’t know about this place.”
“Doesn’t mean she can’t find it, goblin,” Nauk rumbled from the ground where he’d been propped up against the tree trunk.
The goblin sergeant sneered in response but did not bother replying. I glanced at them curiously, noticing the undercurrent of hostility to the reply. From the corner of my eye I could see someone had tied a rudimentary cast around Nauk’s leg with cloth and branches, but every few moments the orc winced when he moved around too much\textit{. One less soldier to count on,} I grimaced.
“How many legionaries in fighting shape do we have?” I asked the group.
“Twenty five I’d take into the field, and Robber’s three sappers,” Hakram informed me. “We’ve got a full tenth of wounded, but most are in good enough shape to serve as sentries.”
I passed a hand through my hair, sighing. That was less than I’d hoped, frankly, but still more than I’d expected.
“We’ll split the legionaries into three under strength tenths,” I said. “Sergeant Robber will keep his sappers as a separate unit.”
“That’s all well and good,” Nauk grunted, “but what are we going to be using them for? You got a plan, Callow?”
I grimaced: it was a bit of stretch to call my idea a plan, but it was the only thing I’d come up with so far.
“We need a prisoner to interrogate,” I replied. “Otherwise we’ll just keep on stumbling about blind.”
Hakram nodded, nonplussed.
“You’ve got a target in mind, Lieutenant?” he asked.
“If I remember well from yesterday’s map, there’s a watchtower in the middle of the valley,” I said. “If Captain Juniper spread out her forces to look for us, it might be undermanned.”
“There’s bound to be at least a sergeant there,” Nilin spoke quietly.
“Robber,” I asked, “how good are your sappers at scouting?”
The goblin hummed thoughtfully.
“Not as good as a real scouting line, but still better than most,” he replied. “You want us to have a look?”
“Unless anyone else has a better idea?” I prompted. No one replied. “Well then, gentlemen, let’s get moving.”

—

“My guy counted ten,” Robber croaked from my side, the both of us in cover behind a tree. “They still have no idea we’re here.”
I smiled. Twenty might have gotten messy, given how tired my men were from running all night, but ten? Ten we could take. We’d have to go in hard if we wanted to be gone by the time Juniper’s patrols heard the ruckus, but then I hadn’t expected this to be an easy fight.\textit{ That’s never stopped me from winning before.}
“Hakram,” I said, “take your tenth around behind the hill and wait until they’ve seen us to hit them in the back.”
The tall orc flashed me pearly-white fangs and saluted before turning towards his soldiers.
“Get your asses in gear, my pretties,” he gravelled. “We’re getting us a little payback.”
There were a few hard smiles among the troops and in a matter of moments they disappeared into the foliage, the dead leaves padding their armour keeping the metal from clanking. None of my ramshackle band of survivors had taken well to last night’s stomping, and I knew they were just itching for a chance to even the score. I decided to give it a while before I got my own tenth moving – rushing it was just as dangerous as lingering, at this point. Robber leaned closer, yellow eyes alight with the most malicious of mischief.
“I’ve got brightsticks if you want to make an impression, Callow,” the goblin wheedled, grinning at the idea of setting off the mostly harmless version of the goblin alchemy in the faces of the soldiers who’d taken his lieutenant. “Nothing like a little flash and bang to start a party.”
“How many?” I asked, keeping her voice down.
“’bout twelve, and half that many cussers,” Robber replied. “That’s plenty enough for a scrap like this.”
I closed my eyes, seriously considering it. Was it worth it to use the munitions this early in the game? I might need them later on, and the fight was already skewed in my men’s favour. But they might be just what was needed to finish the fight before the patrols got onto us, and the moment Juniper’s roaming lines found us the fight was as good as done. \textit{No. I won’t let fear do my thinking for me. We’ll use them when we can make them count.} Opening my eyes, I shook my head at Robber.
“Callow –” he started.
“We’ll find a better use for them, Robber,” I interrupted him. “You have my word on that.”
The goblin fixed me with a hard stare, but after a moment he nodded.
“Aye aye, Lieutenant. Where do you want my sappers, then?”
“There’s three trails and you have three men,” I replied. “If anyone comes in uninvited, I want to know about it.”
The goblins in Robber’s heavily mauled tenth were too lightly equipped to be of real use in a melee and I had no intention of risking my last sappers in a straight up fight: I’d need every one of them when trying for the standard. Using them as sentries would have to do, even if it wasn’t the most glorious of duties. The goblin sergeant saluted in a manner so sloppy it seemed more like a mockery of the gesture before sliding his way downhill. I counted up to sixty in silence before gesturing for Sergeant Nilin to crawl up at my side.
“Lieutenant?” the dusky-skinned boy asked in a whisper.
“Get your legionaries ready, Sergeant,” I replied. “Let’s see how well they hold up when we’re the ones doing the ambushing.”
Letting him slide back down, I picked up my shield and pushed myself up. A moment later my tenth followed suit and I allowed the rank to catch up to me as Nilin’s men lined up behind us – we took a brisk pace up the hill and in an instant we were in sight of the watchtower. The sentry on top cried out in alarm but I had no intention of allowing them to form up.
“Shields up,” I roared, picking up the pace.
I unsheathed my sword and the sound of the men following suit was heard from all around me. I caught sight of Hakram’s tenth running up the other side of the hill without a sound and I laughed in delight a moment before the two sides of my ambush collided with the scattered soldiers from the First Company. A tall orc with a vivid scar running up his cheek stood before me but I slammed my shield against his, knocking him back and striking in the opening I’d made: the blunted blade hit the back of my opponent’s knee and forced him to kneel. I kicked him in the gut to make sure he wouldn’t get up, knocking him out for good with a strike to the temple. Raising my head to take a look around, I realized with a start that the skirmish was already done – most of the First Company cadets were out cold, but a handful were being held down at sword-point by my men. Hakram walked up to me grinning like a cat who’d gone through a whole birdhouse of canaries and slapped me cheerfully on the shoulder.
“That felt good, sir,” he rumbled. “Juniper’s face when she hears about this is going to be a work of art.”
I felt my own lips quirk into a savage smile.
“We’re still a long way from making up for last night, but we’ll get there,” I promised. “Do we have any wounded?”
“One of mine sprained her ankle running up the hill,” Nilin said as he walked up to us. “That’s the only one on our side – we got lucky.”
“Let’s hope our luck continues holding up,” I replied. “Grab their sergeant and let’s get out of here.”
“And the rest?” Hakram asked.
I sheathed my sword and shrugged.
“No point in interrogating them. Break an ankle on each and leave them for Juniper’s healers to fix. That should keep them out of our hair for a few days.”
Both sergeants snapped a salute and turned to bark out their orders. I grabbed a soldier by the shoulder and sent him to fetch Robber, mind already thinking on my next move. \textit{We’re not done yet, Hellhound. Not by a long shot.}
\clearpage
\chapter{Chapter 17: Set}

“\textit{I’ll be honest, Chancellor – revenge is the motivation for over half the decrees I’ve made.”}
– Dread Empress Sanguinia II, best known for outlawing cats and being taller than her

Nauk was napping when we got back to camp, resting lazily under a tree. One of his legionaries kicked him in the ribs when the war party passed by the sentries. Awaking with a growl, the orc swiped at the laughing dark-haired girl but she danced away. I raised an eyebrow at the exchange but passed no comment as I eased my armour’s straps and propped up my shield against a stone.
“Humans,” the wounded lieutenant rumbled. “You always think you’re funnier than you are.”
I felt I’d gotten enough of a handle on orc humour to know that was a joke. Still, it was always hard to tell with orcs.
“Still funnier than you,” Robber sniped as he set down his leather satchel.
Nauk eyed Robber balefully.
“You’re still conscious? Only half a victory, then,” the orc replied.
I didn’t know why those two had been at each other’s throat since last night, but frankly I was far past caring.
“If the two of you have that much fight left in you, I have a fort that needs taking,” I told them flatly. “Any volunteers?”
Robber rolled his eyes and wandered away without a word, leaving me to deal with Nauk – the orc scoffed but refused to meet my gaze. \textit{Yeah, I’m definitely asking Hakram what’s up with these two.} Our situation was bad enough already without two of my few remaining officers taking verbal swings at each other in front of the troops.
“We cleared the watchtower and dragged back their sergeant,” I informed Nauk. “I’m guessing you’ll want to be there for the interrogation?”
The orc grimaced.
“You’ll need to help me up,” he admitted. “My leg hasn’t gotten any better.”
I crouched next to him and slung his arm over my shoulder, knees almost buckling under the weight of him as I bore the other lieutenant’s mass.
“Heavens, what did you eat to get this big?” I wheezed, forcing myself upright.
Nauk grinned toothily.
“Whatever was lying around at the time,” he replied, “we’re not as picky about food as you lot.”
“You should consider trying salad,” I said, only half-joking. “I hear it’s very slimming.”
“Do I look like a bloody elf to you?” the orc grumbled as we crab-marched to the rocky outcropping I’d seen my men dragging the sergeant behind. “I might as well lick bark and frolic in meadows while I’m at it.”
“Elves eat meat too,” I informed him, tone thick with amusement.
“Give it a few years and Lord Black will have us eating the elves,” Nauk replied conversationally. “My grandmother got a bite during the Conquest, said it was more tender than lamb.”
\textit{Does it still count as cannibalism if it’s another species?} I’d have to ask Scribe, she probably knew. That aside, this was far from the first time I’d heard an orc artlessly profess trust in Black. It was proving to be a recurring pattern.
“Hakram said something along the same lines,” I replied. “He was keen on the Black Knight too. Is it an orc thing?”
I almost stumbled when Nauk stopped moving, turning to face me with an unusual serious expression.
“I like you, Callow,” he rumbled, “So I’ll give you a piece of advice. You look like Wallerspawn and talk like a Callowan, so your folks were probably on the other side during the Conquest. You might have an axe to grind and that’s your own business, but don’t ever talk bad the Black Knight in front of a greenskin.”
The orc’s dark eyes burned with an intensity I’d only glimpsed last night when I’d seen him trashing a pair of legionaries with his bare hands, roaring challenges as he knocked their helmets together.
“He raised us up, Callow,” Nauk said fervently. “He ended the wars between the Clans and told us that we could be \textit{more}. That even if we were born in a hut, we could still become generals and lords instead of being meat in the grinder. If those fucking prissy nobles in the Tower were still in charge, I wouldn’t even know how to read.”
“I was just asking,” I replied quickly, awkwardly warding him off with a raised while still balancing his weight on my shoulder. “I’ve got nothing against him!”
Nauk eyed me sceptically.
“Even met him once,” I continued, “I was around when he had Governor Mazus hung.”
The orc grinned, doubts apparently cast aside for the moment. I reflected ruefully that with every passing day I was getting better at lying while saying the truth – no doubt Black would be proud. Or at least quietly approving, which was the closest I’d ever seen him to expressing that actual emotion.
“Heard about that,” Nauk admitted. “The old families in Ater threw a fit over it.”
From the looks of it, the prospect rather delighted the lieutenant. I frowned as we crossed the last few yards separating us from our destination. That was another pattern I’d noticed: most of the cadets hated the nobility in Ater with a vengeance. I could understand the resentment, having had a lean table at the orphanage more than once because of Mazus and his cronies, but it seemed to run deeper than that. Now that I thought about it, the Legion garrison in Laure had always been a little too eager to put the city guards in their place whenever they could. I’d first stopped being scared of the large orcs in armour after seeing one run off guards harassing an old shopkeeper, back when I was seven. The legionary had even helped the old man back to his stall before leaving, I remembered. \textit{So the Legions of Terror and the nobles hate each other’s guts. Then why did Black have Mazus executed? Wouldn’t that make things worse between them?} My wayward teacher must have had a plan in mind, I guessed. \textit{Or}, I thought with a sudden chill, \textit{he’s decided it’s not worth trying to keep them happy anymore.}
That was the stuff civil wars were made of, I knew, and the prospect of a Dread Empire at war with itself was horrifying. Wars were brutal enough between Good and Evil, but between Evil and Evil? There might not be an Empire left by the time the dust settled. Putting the line of thought aside for the moment, I focused on the matters at hand: I helped Nauk sit against a rock facing the still-unconscious sergeant from the First Company and let out a sigh of relief when I dropped off the weight. The sergeant’s hands and feet were bound with thick rope I’d seen the sappers carrying around and Hakram was looming over her body with a patient look on his face. Robber was sitting cross-legged on a flat rock, flipping a brightstick in the air lazily and catching it at the very last possible moment. Hakram turned to face me, rolling his shoulders in an unconscious gesture: I could sympathize, after a night and half a day running around in legionary armour.
“Nilin’s setting up the watches,” me sergeant informed me. “Says he’ll be along as soon as he’s done.”
I nodded absently, taking a closer look at our captive. The girl was on the short side, skin the same bronze colour as Captain’s and hair cropped close in the haircut most female legionaries seemed to favour. Her armour was dented noticeably around the ribs: it must have been a nasty hit that had put her down.
“Do we know anything about her?” I asked.
“Name’s Juwan,” Robber said, stopping to play with his stick. “She’s from Thalassina, I think.”
Thalassina was one of the three great cities of the Empire, I knew, along with Ater and Foramen down in the deep south. It was the largest port in the Empire and the main hub of trade with the Free Cities.
“Let’s wake her up,” I said. “We might have to move camp and I’d rather do it before nightfall.”
Hakram knelt by the prone sergeant and slapped her none too gently. I winced: not the way I would have done it, but then I’d never interrogated anyone before. After a moment Sergeant Juwan blearily opened her eyes, squinting to get used to light before she took a look around her.
“Well, this is unexpected,” she croaked out. “I don’t suppose any of you asshats could give me a little water?”
Hakram snorted and uncorked his canteen, carefully pouring into the captive’s open mouth – he lost patience after a moment, pulling it away and closing it with a small pop.
“I’m Lieutenant Callow,” I said. “I have a few questions to ask you.”
“Lieutenant what?” Juwan replied incredulously. “Who in the Seventy Thousand Hells are you? I’ve never heard of you before.”
\textit{Seventy Thousand Hells?} I blinked in surprise, sneaking a look at Robber to make sure I hadn’t misheard that last part. The goblin shrugged.
“They believe in all sorts of weird stuff in Thalassina,” the sapper told me. “It’s all that salt in the air.”
“That’s rich coming from someone whose patron deity is called \textit{the Gobbler},” our apparently unimpressed prisoner retorted.
“Hit her, Hakram,” Nauk opined over the goblin’s retort. “They always get mouthy unless you hit them.”
My sergeant shot me a questioning look but I shook my head. In all fairness, Robber had been asking for it.
“I’m new,” I addressed Juwan. “But that’s irrelevant –”
“Oh gods,” the prisoner muttered, “I was ambushed by a greenie. I’m never going to hear the end of this.”
“Are you quite done?” I said, a tad more sharply than before.
The sergeant shot me a condescending look.
“Look, ‘Lieutenant’,” she replied. “You’re new, so it’s understandable you might not get how fucked you are. Juniper’s out there looking for you guys right now and you’ve got what… maybe a line and handful of sappers? You can’t win this.”
My face turned blank as the sergeant continued.
“Look, you managed to ambush my tenth so you did well on your first game,” Juwan told me. “You might even get transferred to a company that actually wins once in a while. We’ve got Ratface and all your mages, just surrender the standard and we can all go home tonight.”
I could feel the anger coming from the other three officers at our prisoner’s casual dismissal and I felt the stirrings of it too, deep in my gut. I passed a hand through my hair and forced myself to calm down. \textit{Don’t make decisions angry. Angry means stupid, and if you get stupid you’ve already lost.}
“Sergeant Hakram,” I said. “Hit her.”
Sergeant Hakram did.
“Now, as I was saying,” I continued icily. “I’m Lieutenant Callow. I have a few questions for you.”

—

I really wished we’d managed to keep at least one of the maps, because the vague outline Robber had traced in the dirt looked more like a Helike mural than the rendition of Spite Valley it was meant to be.
“So that rock is our position?” Nilin asked in a politely sceptical tone.
Robber rolled his eyes.
“That’s the fort,” he replied. “We’re the smaller rock.”
We let out a small noise of understanding in unison. Our captive had been blindfolded and stashed in a corner with a legionary standing guard over her, now that the questioning was over. I’d assembled the officers to hold an unofficial war council immediately after. Juwan’s interrogation had yielded enough information to make the skirmish at the watchtower more than worthwhile: the sergeant’s knowledge of troop disposition was a day old, but it allowed us to place our own position into a broader context. All of Rat Company except our motley band of survivors had been taken prisoner, we now knew, but there hadn’t been enough room in the fort to keep seventy-odd legionaries. There was a secondary prisoner camp, and that meant we’d just stumbled on a way to bring up our numbers before hitting the harder target. There was no way taking a shot at the fort with our current line and a half would be anything but suicide, but if we managed to free another tenth – or even better, a few mages – then it would be a whole other story.
“We should move to attack the prison camp as soon as possible,” Hakram said, breaking the thoughtful silence. “Juniper might post more soldiers there when she learns we already took out a tenth.”
“The men marched all night and fought not even a bell ago,” Nilin retorted, tone flat and disapproving. “There are limits to what we can ask from them.”
“The men will have to tighten their belt if they want to win this, Sergeant,” Nauk growled. “Nobody said it was going to be a walk in the park.”
“Says the guy who was napping when we came back,” Robber scoffed.
“Enough,” I intervened. “Sergeant Nilin has a point. I’d rather not attack a second time in daylight anyway, we might get followed back to camp.”
That gave everyone pause, as I’d intended it to: if even a single tenth found our camp, then that was it for the wounded and the handful of rations we’d managed to salvage. An empty stomach wasn’t the kind of enemy you could put down with a sword.
“There’ll be a least a line waiting for us there,” Hakram rumbled. “And they’ll be dug in behind fortifications, you can be sure of it.
“Juniper’s sappers are the second best in the College for building defensive positions,” Robber admitted, though it ran against his pride to do so. “They go by the book, though. If I get a look at it from a distance I could tell you what plan they’re using.”
I closed my eyes and silently weighed the risks against the benefits. Night attacks were a messy enough business without going in blind, I decided. The sapper had already proved he could get around quietly, and with the watchtower out of the equation this might very well be the best chance we’d get.
“Take half a tenth and be back before sundown,” I told the goblin. “Don’t take stupid risks, we’ll need you for the assault.”
Robber’s answering grin was malicious as ever and he saluted before pushing himself up. I turned my attention back to the “map” as he left, wondering if I was making a mistake. The prisoner camp was my best shot at getting enough soldiers to assault the fort, I knew, but that meant Juniper knew it too. Were we headed right into a trap? \textit{It doesn’t matter}, I finally decided. \textit{I} \textit{can’t win this without taking risks, and this is the most reasonable one.}
“Put the troops on half-watch,” I said, raising my head to look at the other officers. “Everybody should try to get some sleep, we’ve got a busy night ahead of us.”
Nauk grunted his assent and Nilin helped him up. Hakram was about to follow suit but I discreetly shook my head: I still had a few questions to ask me sergeant. The orc shot me puzzled look but remained seated at my side while the other two officers crab-walked away.
“Lieutenant?” Hakram prompted, raising a hairless brow.
“Robber and Nauk,” I said, going straight to the point. “What’s their problem?”
The tall orc grinned.
“You didn’t hear this from me,” Hakram replied, leaning closer, “but it so happens they’re both more than a little fond of Lieutenant Pickler.”
“The lieutenant for the sappers?” I asked, surprised.
“That’s the one,” the orc agreed. “They’re not usually that blatant about it, but without her around to keep the peace I guess the knives are coming out.”
I frowned.
“And what does she have to say about this?”
Hakram’s grin widened, showing razor-sharp white fangs.
“She might have mentioned something about how if they kept waving their genitalia around, something was bound to get stuck in a door hinge.”
I bit my lip not to burst out laughing, sneaking a look at the retreating Nauk’s back.
“I didn’t know orcs could be attracted to goblins that way,” I admitted.
“It’s not common,” Hakram replied. “But Nauk’s an odd one, and even I have to admit Pickler has a nice set of teeth.”
“Teeth,” I replied, tone flat. “You’re having me on.”
The sergeant looked somewhat offended.
“Teeth are very important,” he defended himself. “Why do you think no one’s interested in humans? You’ve all got cow teeth.”
If someone had told me a year ago I’d be sitting in the grass with an orc discussing the importance of molars in the mating habits of his species, I thought, I would have been rather dubious. Even now it felt more than a little surreal. Hakram apparently took my silence as a sign of displeasure, because he hurried on.
“No offense meant, Callow,” he assured me. “I’m sure you’ll find a nice human to eat berries and nuts with.”
“You know we eat meat too, right?” I replied, rather bemused.
He snorted.
“It doesn’t count if you roast it first,” he told me with a friendly pat on the shoulder. “You might as well be chewing bread.”
I didn’t have the heart to tell him that that was rather the point. We walked back to camp in a comfortable silence and I found my bedroll, barely closing my eyes for a moment before sinking into sleep.

—

“Only four and no patrols,” Robber said.
I clenched my fingers and unclenched them, taking a closer look at the fortifications. The outer wall was made of stacked stones and about the height of a half a man, with torches every few feet and four legionaries patrolling the perimeter at regular intervals. Behind it the First Company had built a palisade of stakes, too high for my soldiers to climb over. It hid the inside of the camp. There was only one way into the camp itself, an opening in the palisade swerving to the right and wide enough to be held by half a dozen legionaries. It was open field all the way to the first wall, I saw, and I knew my soldiers would have to take out the guards if we wanted to avoid the attack turning into a disaster. \textit{If we don’t, they’ll sound the alarm and the rest of the line will hold us off in the opening until reinforcements can arrive.} Eyeing the wooden palisade speculatively, I gestured for Hakram to come closer.
“Could you break through that if we needed to?” I whispered.
Her sergeant grimaced.
“Not without a battering ram,” the orc replied. “They’ll have put up buttresses on the other side to hold it up, it’s in the manual.”
It remained unsaid that we wouldn’t have enough room to use a battering ram without tearing down a chunk of the first wall first, and that even then we’d have to make the damned thing first. No, this was going to have to be about getting my men in through the front door. Sergeant Nilin gingerly made his way through the underbrush to me, looking as uncomfortable in the woods as I felt – he was as much a city boy as I was a city girl, I’d gathered.
“Lieutenant, Sergeants,” he greeted us in a murmur, snapping a parade-ground salute. “All of our soldiers are in position.”
I’d told the sergeants to put all almost-thirty of my men in half circle around the camp’s only way in, the three incomplete tenths waiting in silence for the signal to assault the enemy. Only Robber’s sappers had remained marauding about in the woods, but I could see them trickling back into the ranks one after the other from the corner of my eye.
“Hakram,” I said, “I’ll need volunteers to take care of the guards.”
The tall orc grunted his assent and made back towards his men.
“My sappers could handle that,” Robber countered in a low voice. “Less of chance we’ll caught, too.”
“Your sappers are going to be with the rest of Hakram’s tenth and my own,” I replied.
The goblin’s yellow eyes shone with malevolent light in the dark of the woods.
“We finally get to play with the fireworks then, Lieutenant?” the sergeant asked eagerly.
“Hit them with all you’ve got, Sergeant,” I told him.
We’d been hoarding the sappers’ munitions so far, but now was the time to use them up. I’d thought about keeping them for the assault on the fort itself, but been forced to conceded that if tonight’s rescue failed there would be no assault worth the name. Better to use the brightsticks to ensure that the enemy line was too stunned and deafened to form up properly.
“Back to your tenths, gentlemen,” I murmured. “Let’s get this wheel turning.”
They replied with a handful of salutes and I ducked around a tree as silently as I could, electing to stay ahead of my legionaries so I’d be in a better position to watch events unfold. Hakram’s volunteers were already moving, I saw, the closest one crawling through the grass as he made his way across the open field. The next few moments would define if my offensive failed or not, I knew, so I held my breath as I watched the volunteer slowly make his way towards the unsuspecting guard. The legionary pressed himself against the outer wall as the guard passed him by, silently pushing himself up and climbing over the fortification. For an instant it looked like the sentry might hear him, but then the volunteer unsheathed his sword and hit the guard in the back of the head with the pommel. The First Company’s sentry crumpled to the ground without a dull thump, and with a peremptory hand gesture I got my soldiers moving. Not a moment too soon, as it turned out, for a cry of alarm came from the other side of the outer wall. One of Hakram’s volunteers had failed. I cursed under my breath.
“Double time,” I called out to my legionaries, running across the empty field as quickly as I could manage in armour.
A dark shape passed me by, then a second, and with my jaw gaping I saw Robber and his sappers scuttling across the grass with the unnatural grace of a pack of spiders. The goblins pushed ahead of my men effortlessly, their thin green limbs moving fluidly as they tore through the distance separating them from the opening. Raising my shield up, I forced myself to catch up with them, my soldiers following suit behind me. By the time my line got to the opening Robber’s sappers had already spread out in a line and were watching a half-dressed tenth from the First Company form up.
“\textit{Abacinate},” Robber called out, his grin sharp and vicious.
All four goblins pulled out thin, elongated sticks and lit them up with the pinewood matches they carried around everywhere. They threw as one and I barely had the time to close my eyes before the brightsticks exploded, the deafening bang and bright light searing my eyelids anyways. Unlike a real brightstick those wouldn’t blind permanently, but they still stung like a bitch. I opened my eyes, already moving forward, only to see the sappers had little spheres in hand, already lit.
“\textit{Spargere},” the goblin sergeant ordered, and the sappers rolled the balls under the enemy’s shields with unerring aim.
A moment passed and then a series of explosions scattered the first rank of the enemy, sending shields flying and throwing the legionaries to the ground. Those cussers packed quite a punch, for a training version. I grinned at the goblins as I passed them, my soldiers close behind, and the legionaries threw themselves into the holes the sappers had just torn with savage enthusiasm. A dark-skinned girl around my age bashed her shield against mine, but I used the momentum of the charge to push her down anyway. Knocking out the enemy soldier with the pommel of the short sword I didn’t remember unsheathing, I pressed forward into the camp as my legionaries broke the enemy formation. The inside was nothing unusual, four lines of bedrolls where the last handful of legionaries were hastily putting their armour on. There was a long tent in the back where the prisoners were no doubt being held. Signalling for another handful of legionaries who’d broken through to follow me, I set to pacifying the rest of the camp. It was a grim business, but now was not the time to be gentle. We overwhelmed the first enemy before he managed to land anything more than a glancing hit on my shield and pressed on to charge the next two. One of my legionaries got a nasty hit on the shoulder, but in a matter of moments it was done. \textit{Four outside}, I counted mentally. \textit{Twelve at the breach, and three we just finished. If they were a full line, that still leaves…} There was a flash of flame and the legionary at my side was blown away.
“Guess I still have to work on my aim for that one,” a lone legionary in light armour mused as red-orange flames wreathed her hands for a second time. “You’d be the Lieutenant in charge of that lot, then?”
“Lieutenant Callow, third line of Rat Company,” I agreed as she raised my shield and steadied my footing. “And you’d be?”
“Lieutenant Assaye, fourth line of First Company,” the honey-skinned girl replied with a smirk. “Should have brought a mage, Callow. This is going to have to get messy.”
“I seem to have misplaced mine,” I told her flatly. “You wouldn’t happen to have some spares in that tent, would you?”
“Well look at the mouth on you,” Assaye said. “Here’s a tip, though, rookie – don’t banter with mages when they’re buying time to cast.”
The flames wreathing the other lieutenant’s hand grew in intensity and gathered into an orb that the girl sent flying right at me. I smiled. \textit{Here’s a tip for you, Lieutenant}, I thought, \textit{learn to recognize when you’re being baited.} Ignoring the primal part of my brain that was screaming at me to duck out of the way, I raised my shield and ran right into the fireball. The impact nearly blew me off my feet but I grit my teeth and pushed through the flames, closing the distance separating me from the gaping lieutenant. There was no way I was taking another one of those, so I struck the girl on the temple with the flat of my short sword before she could summon up something more vicious. Before Assaye ever hit the ground, I dropped my shield and blade with a curse to put out the flames on my shoulder pads, doing my best to ignore the fact that I was letting out smoke like a small chimney.
“I’m not sure whether that was very brave or very stupid,” I heard Robber mutter from behind me.
“I heard she castrated an ogre in single combat,” Hakram grunted back in a low voice. “Thought that was just Ratface making the best of things, but I’m starting to believe it.”
I turned around to shoot both sergeants a dirty look but they adopted the most innocent expressions they could – which, given that Robber was a yellow-eyed pyromaniac and Hakram had a set of teeth that would make most wolves balk, would have gotten them instantly convicted in any court of law.
“If you two have time to gossip,” I told them, “you’ve got time to go check up on the prisoners we’re rescuing.”
“Aye aye, Lieutenant,” Robber grinned, following Hakram’s example and saluting before he made a strategic retreat.

—

As it turned out the tent held only a tenth of prisoners, which would have been disappointing if not for the fact that there were two mages and a sergeant among them. Both of the mages knew how to heal, which was even better news: I fully intended put them to work as soon as my troops got back to camp. Robber had argued we should take a different way back to our clearing to shake off possible followers, meaning the trip back was twice as long as the one to the enemy camp: it was the middle of the night by the time my soldiers were finally able to put down their shields. The sergeant we’d rescued was a short brown-haired girl by the name of Kamilah with a nasty scar running across her cheek, and she was sitting in on the unofficial officer’s meeting I’d ordered as soon as watches were set up. Nauk was getting his leg looked at so he’d be missing this, but the orc lieutenant had shrugged and told me he didn’t mind being brought up to speed when he was back on his feet. I’d gotten the impression he was rather eager to start moving on his own again, and I could hardly blame him for it.
“They moved some of us earlier today,” Sergeant Kilian said. “To the fort, I think – I don’t recall hearing anything about another prisoner camp. We used to be a full line of prisoners.”
“I was afraid you’d say that,” I muttered.
If there’d been another camp it might have been possible to assault it to add a few more legionaries to our forces, though I doubted Juniper would have made it as easy on us the second time.
“The fort’s next, then,” Hakram rumbled.
“We have healers now,” Nilin disagreed. “And enough soldiers to keep prisoners. We could take out some of Juniper’s patrols before risking an assault.”
“We’re dealing with the Hellhound, not a godsdamned first-year,” Robber chided him. “The moment we make a patrol disappear she’ll be able to guess what part of the woods we’re in, and it’s all downhill from there.”
Nilin shrugged.
“She’ll have at least a line getting healed and she’ll be forced to leave a garrison at the fort – I say we should take our chances,” he replied.
“We’re not meeting Captain Juniper on an open field,” I cut in. “Even if we win, we won’t be in any shape to assault the fort afterwards.”
Sergeant Kilian cleared her throat.
“No disrespect intended, sir,” she said, meeting my eyes squarely, “but why are you in command? You’ve been in the company for barely two days, if I’m not mistaken.”
My own sergeant growled, but I held up my hand.
“It’s a valid question, Hakram,” I said. “Lieutenant Nauk ceded command to me when he was wounded, but now that he’s getting healed he has seniority.”
“Balls to that,” came the voice from behind me.
I turned: the orc in question was striding towards us, leg finally out of its cast. I frowned at the other lieutenant.
“Are you sure, Nauk? I like being in charge,” I freely admitted, “but you’ve been at this a lot longer than I have.”
“I would have been in that prisoner camp if not for you, Callow,” the large orc replied. “You got the standard and you’ve bloodied First Company twice. Only idiots change generals halfway through a campaign.”
The short sergeant smiled uncomfortably.
“It wasn’t meant as a criticism of your performance, sir,” Kilian said. “I just thought it was a question that needed to be asked.”
I could appreciate that. It would have been awkward for me to bring up the issue myself, anyway.
“No offence taken, sergeant,” I replied. “Take a seat, Nauk. We’re planning our next move.”
The orc plopped himself on the log and everyone politely ignored the creaking sound that came from the wood – except for Robber, who snickered and seemed about to make a comment when Hakram spoke up.
“We should assault the fort in the morning,” he gravelled. “No point in giving them more time to prepare than necessary.”
“My sappers can have ladders done by then,” Robber offered up, looking a little irritated he’d been cut off from indulging in his feud with Nauk.
“How are you doing on munitions?” Nilin murmured.
The goblin waved his hand vaguely.
“Out of cussers and brightsticks, still got enough smokers to ruin someone’s day,” he told them. “I’ll manage.”
“We’ll have only two lines for the assault,” Nauk rumbled. “That’ll be hard fighting.”
The officers looked rather uneasy at the thought, but I shrugged.
“They won’t have a full house waiting for us in the fort either,” I replied.
“Do or die, then,” Hakram grinned. “Worse comes to worse, we go out with a bang.”
Nauk looked like he rather approved of the thought, slapping the other orc’s shoulder cheerfully. I only barely refrained from rolling my eyes.
“Let’s set up a full watch tonight,” I ordered. “That makes it twice we’ve kicked the hornet’s nest – sooner or later, something is bound to follow us home. Dismissed.”
After a round of salutes, they rose and returned to their men. I remained behind, looking up at the night sky and wondering what tomorrow’s battle would have in store for us. \textit{Only one way to find out, I suppose.}
\clearpage
\chapter{Chapter 18: Match}

“\textit{Always mistrust these three: a battle that seems won, a chancellor who smiles and a ruler calling you friend.”}
– Extract from the personal journals of Dread Emperor Terribilis II

The fort at the end of the valley had stood there in one form or another since the beginnings of the Dread Empire, or so Hakram told me. Before the Dark Tower’s authority had been firmly established, it had served as a choke point to hold off roving orc clans and Taghreb raiders. In later eras it had become the last defence against armies coming from the Kingdom of Callow before they could march on Ater itself, the last stand Evil could take before Good came to knock at the front door. It had been over a century since the last Crusade, however, and in the interregnum the Legions of Terror had taken to using the fort as a defensive position in their war games.
\textit{Still, it wouldn’t do to forget that they built this for an actual war, not a fake one}, I mused. Cadets were responsible for the upkeep of the fort, meaning every company knew its workings inside out: my soldiers were no exception, though only Robber and his sappers had been able to hash out a detailed plan of it in the sand. The description they’d given me was… daunting.
The fort itself was situated on the flattened top of a hill, its walls thirty feet high and a little more than half as thick, but the true terror of it came from the outside fortifications. Right in front of the walls a ditch about fourteen feet deep had been dug and filled with stagnant water. After a thin strip of land another identical ditch had been dug and filled with jutting wooden spikes. The open field leading to the ditches was dotted with the vicious traps the legionaries had nicknamed “lilies”: pits three feet deep with a sharpened stake waiting for unwary soldiers at the bottom, hidden under a layer of branches and dead grass.
All companies had assaulted the fort often enough to know the pattern of the traps by now, but it still forced the ranks of attacking companies to break. From what Robber had told me, trainees still died in accidents regularly – it was considered a good omen for a company to not lose any freshmen cadets in their first game of the year.
“You’re sure their mages won’t shoot at us while we’re going through the lily field?” I asked Hakram.
“It’s considered bad form to do it,” the sergeant gravelled. “Companies that hate each other’s guts might go ahead anyway, but we’re not feuding with the First.”
I raised an inquisitive eyebrow at the orc.
“Who \textit{are }we feuding with, then?”
“No one,” Hakram replied, sounding rather chagrined. “We’re at the bottom of the company rankings, so no one’s bothering.”
I let out a vaguely empathetic noise.
“Rat Company’s been last for a while, then?” she asked.
“Since before Ratface took over as captain,” her sergeant agreed. “He’s done his best, but unless we manage a miracle today it’ll still be his twelfth defeat: he’ll lose his captainship.”
I kept my surprise away from my face – from the casual way Hakram had dropped that tidbit, it seemed like it was common knowledge among the rank and file. It certainly cast the captain’s hostility when I’d first met him in a new light: no wonder he’d been furious, being assigned an untaught lieutenant on the eve of a game that had his rank on the line. \textit{Not my fault he lost the last eleven, though, so he could have been less of an ass about it.}
“So, have we got an idea how many are in there?” I asked, changing the subject.
“No way to tell,” Hakram grunted back. “Gotta be a least thirty of them, but there could easily be more.”
I grimaced. Going in blind was hardly the way I would have preferred to take a crack at the fortress, but we were running out of options fast. At least Robber’s sappers had fashioned us four ladders over the night, meaning we’d be able to manage to assault multiple walls simultaneously. How much that would really help them if the enemy was as numerous as they were was arguable, but it was still better than nothing. Speaking of the devil, the goblin sergeant was swaggering his way up the hill towards us.
“That’s Lieutenant Trapper on the wall,” he announced, his tone implying that particular fact was significant.
I raised an eyebrow.
“I’m sure you have a point,” I told the goblin, “but so far I’m missing it.”
“Trapper’s only the fourth senior-most of the First Company lieutenants,” Robber replied. “So that means…”
“They can’t have more than two lines in there,” I finished thoughtfully. “Otherwise someone else would be in charge.”
Robber hummed in agreement, palming a smoker from his satchel and twirling it through his fingers. I frowned and readjusted her plans. Forty legionaries we could manage, with a little luck. It all depended on the nerve of the officers holding the walls, of course, but Robber’s deduction was the first bit of good news I’d heard all day.
“How do you know about Trapper’s seniority?” Hakram asked, breaking me out of my train of thought.
“Oh, that’s easy,” the yellow-eyed sergeant replied nonchalantly. “We know each other from the Great Goblin Conspiracy meetings.”
My sergeant barked out a laugh but after a moment of awkward silence he shot an uneasy look at Robber.
“There’s not really a Great Goblin Conspiracy, is there?” he rumbled.
“Would I tell you if there was?” the goblin replied with a wicked smile, throwing his smoker up and snatching it out of the air.
Robber saluted lazily and swaggered off back to join the tenth I’d assigned him to. I did my level best not to snicker at my sergeant, but from the disgruntled face the orc was making I guessed some of my amusement was showing. Studying the steel-capped legionaries standing on the southern wall of the fort, I decided to make a last minute change to the assault. We still didn’t know how many crossbowmen First Company’s garrison could muster, but as far as I could figure our best shot at setting foot on the walls was splitting up the enemy with multiple assaults. Nilin’s tenth would assault from the west, Kilian’s by the east and Nauk’s would take the gate. If anyone could manage to land a ladder while getting shot at by a whole line, it was the orc lieutenant. The pair of mages I’d rescued yesterday was too exhausted to be of any use, so they were hiding in the woods with the standard: I’d given them orders to hide until the games were over if the assault failed. Better a tie than a defeat, if it came to that.
“We won’t be backing Nauk at the gate,” I told Hakram. “Our tenth will hold back until we see an opening. Give our sappers to Kilian and tell her I want the whole eastern wall turned into a cloud of smoke when she assaults.”
The greenskin sergeant cocked is head to the side and eyed me thoughtfully as he tried to puzzle out the meaning behind the corrected instructions.
“You’re banking on Trapper panicking when he loses sight of what’s going on in the east and giving us an opening,” he stated after a long moment of silence.
I blinked in surprise.
“How are you still a sergeant?” I asked.
“Failed Foreign Languages two semesters in a row,” Hakram admitted. “Fucking Old Miezan. Can’t make higher than sergeant if you’d don’t pass everything.”
“Lucky for me,” I murmured.
I shuddered to think of how much harder this whole game would have been without the tall sergeant quietly covering for all the gaps in my military education. I got a pleased grin for my comment and Hakram walked away to spread my last orders, leaving me alone to watch my plan come to life.
“Let’s see how steady your nerves are, then, Lieutenant Trapper,” I whispered to myself, watching Nilin and Kilian’s troops start moving through the lily field.
The first crossbow shot from the walls clattered uselessly against the shield of one of Nilin’s soldiers in a matter of moments, though I immediately heard a sergeant barking for First Company to hold their fire. \textit{Praesi crossbows can hit a target to up to three hundred and fifty yards, effective kill range at one hundred fifty}, I recited mentally. The lessons had been a pain to learn, but I was beginning to understand why Black had put so many military treatises in the pile. The attacking tenths still had at least fifty yards to go before they would start getting shot at in earnest, but the officers were already calling up for the legionaries to form the testudo. The first rank stopped and raised their shield, the second one propping theirs up to form a roof over their heads. It would slow them down and it was nowhere as effective as if it had been full lines forming up instead of tenths, but it was still better than going in bare. Twenty yards to go, then ten and finally the order came from the enemy on the wall.
“First Company, take aim,” a sergeant bellowed.
I clenched my fingers and unclenched them, resting the palm of my hand on my short sword’s pommel.
“First Company, FIRE!” the call came.
The twang of crossbows unleashed filled the battlefield, the bolts whistling eerily as they tore through the air. From the corner of my eye, I saw one of Nilin’s legionaries get caught in the knee and fall to the ground with a yell but Nauk’s tenth was the one they were trying to take out – the orc lieutenant took a blunted bolt straight to the chest but he laughed it off and replied with an obscene gesture. Still, two of Nauk’s legionaries were hit, one dropping his shield with a yelp and the other slipping to the ground without a word, knocked out cold. The legionaries fell out of the testudo the very instant First Company was done shooting, sprinting across the lily field as fast as they could. They’d be safe for a minute or two: crossbows might be easier to wield and pack more of a punch than longbows, but their rate of fire was horrendously slow. With a little luck Kilian and Nilin would be past the ditches by the time First Company was ready for another volley.
Nauk’s tenth was already at the feet of the gates and trying to prop up their ladder but it kept getting pushed away by a pair of legionaries with forked poles. The lieutenant barked out an order and a pair of smokers spun through the air to land on top of the gate, letting out streams of thick grey smoke. Unlike real smokers it wasn’t poisonous, but it was still hard to breathe in. First Company immediately tried to throw those back but a pair of cussers followed and blew an enemy legionary straight off the rampart. Robber’s handiwork, at a guess. I winced: a fall from that high was sure to earn broken bones. Turning my attention to the west, I saw Nilin was failing at getting his own ladder up. First Company had somehow managed to set it on fire and his tenth was too busy trying to put the flames out to press their assault. \textit{Magic}. Mages always made everything more complicated. Eyes flicking to the east, I saw Kilian was making good progress. In a matter of moment she would… and there they went, the smokers had landed on the wall.
“Come on, Trapper,” I murmured. “You could lose the east if you’re not careful, and we both know you’ve got too many soldiers covering Nauk.”
A minute of tense anticipation passed as I waited with baited breath until a handful of legionaries hurried through the battlements to link up with the eastern wall. I grinned.
“Gotcha,” I said.
Turning to Hakram, I saw he was milling around the tenth I’d been holding back.
“Sergeant, get our tenth ready to move. We’ll give them a minute to get entangled before we hit the wall next to Nauk.”
“Aye aye, Lieutenant,” the sergeant saluted.
The legionaries picked up the ladder and spread in two lines of five. Fastening my helmet’s leather straps, I checked my blade a last time out of habit and made my way to my soldiers.
“We go in hard and fast,” I addressed them as soon as I was close enough. “Wounded get left behind, we head straight for the standard.”
My tenth managed an awkward salute while keeping a hand on the ladder and I took the lead, my shield already brought up. It would have been shame to get this far only to be taken out by a lucky crossbow shot. I’d already decided we’d stick to the road as long as possible before veering to the right. Nauk was making enough of a mess around the gate that First Company would have more pressing problems on their hands than my tenth. I kept the pace brisk, but there was only so fast the legionaries could go while carrying a ladder – twice I had to slow down so I wouldn’t pull ahead too much. By the time they got to the first ditch the smoke on top of the wall was starting to clear and I could see a handful of Nauk’s legionaries desperately fighting on top of it to protect the ladder they’d managed to land. \textit{Good}, I thought. \textit{Keep them busy for me, Lieutenant.} I slid down the slope and threw my shield on the strip of ground separating the first ditch from the second, picking it up as soon as I’d made the climb.
My soldiers were following close behind, Hakram exhorting them to hurry every step of the way, and in a matter of moments they’d propped up their ladder. It was a good thing every company knew how tall the walls were, I had a feeling the sappers’ ladders would have come up short otherwise. I was second up on the ladder behind a pale-skinned girl whose name I did not know and I winced when a enemy legionary popped up at the top of the battlements and unloaded his crossbow straight in her chest – the girl managed to divert her fall off of the ladder so I didn’t fall with her, but it had been made clear enough that speed was of the essence. I jumped over the edge of the battlements to be greeted by the sight of half a dozen First Company legionaries headed my way. The boy with the crossbow had already taken out his sword but he was too slow. I punched him in the jaw and threw him off the wall while taking out my blade. Hakram suddenly appeared at my back, sword in hand, and with a shared grin we ran towards the enemy. We didn’t need to win, we both knew, just delay them long enough for my tenth to make it up the wall.
Shield impacted against shield and I was forced to take a step back, but my adversary’s defence was sloppy: I landed a hard blow against the side of the helmet and turned aside a sword stroke from another legionary. Another of my soldiers joined the fight and then another, the whole tenth trickling in before too long had passed. I might not have liked Ratface, but I had to admit that the captain had drilled his legionaries superbly. First Company’s legionaries backed off when they saw they were outnumbered, one of them running for reinforcements, but I had no intention of pursuing. The whole melee had cost us only one wounded and I offered the dark-skinned legionary a sharp nod before running off towards the stairs. Keeping the map of the fort Robber had traced in mind, I knew I’d have to take my tenth through the melee on the eastern wall before reaching a way down: time to see what Kilian had managed to accomplish. The smoke on the battlements had faded away to wisps, making it easy to see the sergeant’s men were busy giving First Company a hard fight: Kilian’s tenth had wounded and had been outnumbered from the start, but they were fighting with a ferocity that surprised me. Maybe I’d underestimated how badly Rat Company’s legionaries wanted a win. My tenth took to First Company’s flank like fire to kindling, tearing through it in a matter of moments and scattering the enemy.
“You sure know how to throw a party, Lieutenant,” Kilian herself gasped as she made her way towards me, cheek badly bruised.
“It’s all about the guest list,” I replied amusedly. “Think your men have it in them to head for the standard?”
“HEAR THAT, GIRLS AND BOYS?” Kilian roared out. “LIEUTENANT CALLOW WANTS TO KNOW IF YOU’VE STILL GOT A WIN IN YOU!”
The noise of blade slapping against shields and cheers drowned out everything else for an instant, my own legionaries joining in without hesitation.
“That good enough, sir?” Kilian asked with a cheeky smile.
“It’ll do,” I agreed. “Fall into rank, we’re moving out.”
The inside of the fort was about what Robber had described: a low stone house up against the northwestern corner to house prisoners and a series of tents surrounding the wooden palisade that made up the centre. I could see over it from my current vantage point and the enemy standard was right there in its socket, without so much as a single guard. If we hurried enough I’d be able to pull out my troops before casualties got too bad. Ordering my men to pull up the ladder that had brought Kilian’s tenth to the top of the wall, I took the lead once more and started running down the stairs. I’d have to set up a cordon of legionaries to make sure we weren’t flanked.
The gate to the inner fort wasn’t even locked, my soldiers found out to their surprise: they must not have been expecting an assault. This whole thing was going off much more smoothly than I’d thought it would, to be honest. \textit{No point in looking a gift horse in the mouth}. I left the enemy standard in Hakram’s capable hands and got my legionaries moving towards the western wall: as far as I could see Nilin was making no progress on it, but we could use his ladder to escape. That was when the first hitch in my plan appeared. Yells came from the cordon I’d set up and I cursed when I saw what was going on. The survivors from the east and what seemed to be at least half the soldiers who’d been fighting Nauk were hitting my flank, the distinctive silhouette of Lieutenant Trapper haranguing them into pushing forward. The whole thing could turn into a rout in a matter of moments, I knew: all it would take was First Company breaking apart my men and then it would just be a matter of taking out scattered groups of my attackers. There was only one thing for it, I’d have to…
“Lieutenant,” I was interrupted by Kilian, “it doesn’t have to be you.”
I blinked in surprise.
“I’m not sure what you mean,” I hedged.
“Someone has to hold the rearguard,” the sergeant replied flatly. “But it can’t be you.”
“You think I can’t handle it?” I challenged her.
“I think Lieutenant Nauk was right,” Kilian retorted, meeting my eyes squarely. “You’re the one holding this together. Let me handle it, Callow – there must be a reason you got me back in the first place.”
Tempting, oh so tempting, but could I really let anyone else do this? Rat Company didn’t really need me to get the standard back to camp and claim victory. I closed my eyes, furiously trying to find another solution, but all I could think of was a pair of pale green eyes looking back at me. \textit{The only clean victories are the one in stories, Catherine}. I let out a string of curses that drew a raised eyebrow from Kilian. Sacrifice has never come easy to me, and sacrificing people under my command left an even worst taste in my mouth. \textit{But that’s why you sent me here, isn’t? So I’d learn that sometimes you being charge means making decisions like this.}
“Fine,” I grit out. “Give them Hells, Sergeant.”
Kilian saluted grimly and unsheathed her sword, heading out for the melee.
“LEGIONARIES!” she screamed. “TO ME!”
Hakram tugged at my elbow urgently and I clenched my fingers. Without another word I ran off towards the stairs to the western wall, my tenth falling in behind me while Kilian’s delayed First Company. Time to get out of there.

—

The way out had been surprisingly easy, Nilin’s tenth managing to land their ladder within moments of my soldiers hitting the wall. I’d gotten my men through and linked up with Nauk while the orc was making his own escape, having somehow managed to unlock the front gate. We’d hurried away after getting back our own standard, well aware that if we lingered too long the rest of First Company was bound to find us. The walk back to the initial camp site had become more and more leisurely as we neared their objective, though, my soldiers laughing and teasing their way up the valley. And yet I couldn’t find it in me to join the merriment. The victory had been too easy, and the more I thought about it the more this was beginning to feel wrong – it was too much of a coincidence that so many troops from the First Company would be out on patrol at the exact moment my own cadets had hit the fort. Hakram had said that Juniper liked bold strokes and swift victories, that it was likely she’d been so frustrated by them surviving that she’d overcommitted on patrols, but I was beginning to think he’d been wrong.
The way the mage line had been hit first had been bothering me for a while: if Captain Juniper meant to take out Rat Company, why hadn’t she gone for the scouts? With them silenced she might have managed to overrun the entire camp before the alarm was rung. \textit{Unless that wasn’t what she was after}, I thought. \textit{Crippling the company by taking out our healers the first night makes more sense if she was aiming to just chip at us day by day.} But on that night, when the First Company’s soldiers crept around the camp, they’d found that Ratface had ordered a half-watch and realized they could do a lot more damage than just taking the mages. Juniper hadn’t bet it all on a night assault that could easily have gone wrong, she’d taken an opportunity when she saw an opening. And if that was true…\textit{ then there’s no way she overcommitted on patrols. There’s something I’m missing here.}
“If I couldn’t find my enemy,” I mused out loud to myself, “how would I catch them?”
What did Juniper need to win? \textit{Our standard.} Just as we needed hers. But as long as Rat Company’s survivors were on the move, she might as well have been looking for a needle in a haystack: Spite Valley was full of hidey-holes, and a more defensive-minded leader than I might have elected to wait out the remaining time in one and let the game be a draw. \textit{But I showed her I wanted to go on the offensive by hitting the watchtower}, I realized. \textit{So then why were there so few soldiers guarding the prisoners?} … there’d been no senior officers among the prisoners at the prison camp, now that I thought about it. And only two mages.
Enough to patch up all my wounded, sure, but we’d still been barely forty afterwards and my two healers had been too exhausted to be of any use for the assault. I’d thought it was a coincidence at the time, that the more important prisoners had been kept elsewhere. But if that was the case, why had there been any mages at all? \textit{She was giving me those. Building up my confidence so I’d attack the fort. }So I’d taken my men to the fort, and at the cost of almost half of my force taken the First Company’s standard. Now I had only a little over a line left and I was headed back for the deserted Rat Company camp, where I’d put down the enemy standard and officially claim victory. \textit{If couldn’t find my enemy, how would I catch them}?
“I’d dictate where they have to go,” I whispered, a shiver of dread going down her spine.
“What’s that, Callow?” Nauk called out cheerfully, the standard still resting on his shoulder.
“RAT COMPANY,” I roared, “FORM UP!”
Hakram, bless his soul, instantly started slapping around the disbelieving soldiers around him until they formed a wobbly square. Nauk pushed through the shifting cadets to get at my side, a sceptical look on his brutish face.
“That just gave away our position to any patrol in the area,” he growled. “Care to explain?”
“They already know we’re coming, Nauk,” I breathed out. “Think about it – hasn’t it all been going too smoothly?”
“So we got lucky,” the orc grunted out. “It happens.”
“We haven’t been lucky, we’ve been played,” I retorted, eyes scanning the woods around us. We were already in sight of the cluster of hills where we’d camped on the first night. Was it too late? Were we already far enough into the trap that there was no backing out? If we managed to get away with both standards, we might still be able to turn this around.
“You’re thinking too hard, Callow,” Nauk growled. “Juniper’s good, but there’s no way she’s that-”
In an unpleasant concession to the universal laws of irony, that was the very moment that the soldiers emerged from the woods on both our sides. A line per flank, I guessed, and the garrison we’d escaped from back at the fort had probably been shadowing us during the whole trip, just out of sight.
“Hellgods,” Nauk spat out. “That’s all sorts of fucked.”
A handful of silhouettes appeared at the crest of the hill we’d been about to start scaling, first among them a large orc in legionary armour who idled her way down the dirt path. So there was another line waiting for us uphill – they’d probably caught Robber when I’d sent him scouting ahead with his sappers. Rat Company closed ranks, shields up and faces grim. They still had fight in them, I knew, but none one was expecting to win the battle anymore. The joy had gone out the company the moment the first enemy soldiers had come out.
“So which one of you would be Lieutenant Callow?” the lone orc called out in a smoky voice as soon as she got halfway down the hill, resting a hand on the pommel of her short sword.
I sighed.
“I’m guessing that’s Captain Juniper?” I said in an aside to Nauk.
“The Hellhound herself,” the orc grunted. “Think we could grab her if we charged?”
I snorted, shaking my head.
“Too obvious,” I replied. “She’s planned it all out so far, I doubt she missed a ploy that obvious. Guess it’s time to meet the woman of the hour.”
I tapped the soldier in front of me on the shoulder and the company parted to let me through. I made my way to the bottom of the hill before deciding it was far enough.
“So, you’re Captain Juniper,” I said. “I’d make a pithy comment about expecting you to be taller, but you’ve got at least two feet on me.”
“Funny,” Juniper replied with bared teeth. “I’ll get to the point, Lieutenant, we’re both busy girls. The Tactics manual says I should offer you a chance to surrender, since you’re both surrounded and outnumbered.”
There was a pregnant pause.
“This is where you refuse with a scream of defiance and I get to crush you lot while still getting full marks,” Captain Juniper prompted.
I eyed my opponent thoughtfully, letting another silence take hold. Juniper had chosen everything about the encounter so far: the terrain, the troop disposition, even the time of day. That little petulant voice in the back of my head was urging me to throw back the offer of surrender in the orc’s face and give her a fight to remember, but I knew better than that. Even before I’d spent a month getting taught by the most dreaded strategist of the age, I’d known better than that. Never give the opponent get what they want. \textit{If you let them dictate the flow of the encounter, you’ll lose every time.}
“No,” I decided. “We’ll surrender. No point in dragging this out, you’re right. Give me a minute and I’ll talk Lieutenant Nauk into it. Do I just give you the standards or is there a protocol I don’t know about?”
Juniper eyed me distrustfully, clearly taken aback. It was all I could do not to smile.
“First you give us back ours, then I send someone to collect yours,” she replied. “Don’t try to be cute, the moment one of you steps out of line my legionaries are charging. I’ll be waiting up the hill.”
Dismissing the idea of such wanton treachery with a vague hand gesture, I made my way back to Rat Company’s ranks. The company’s remaining officers gathered around me.
“Lieutenant,” Hakram rumbled. “You can’t seriously be considering a surrender. I know the odds are bad, but –”
“Don’t be an idiot, Sergeant,” I whispered, “I have a plan. Pick another two men to accompany me when I give the Hellhound back her standard.”
The orc hid a grin and saluted. I turned to face Nauk and Nilin.
“So, gentlemen,” I said cheerfully. “How long do you think you can hold against the bastards?”
Nauk let out a belly laugh.
“For you, Callow? We’ll last ‘till sundown,” he grinned, looking like the world’s meanest, ugliest green cat.
“A quarter hour,” Nilin ventured more pragmatically, ignoring the dirty look the orc shot him.
I clenched and unclenched my fingers, trying to limber them up. A mostly pointless gesture, but I’d found it helped me think.
“A quarter hour will have to do,” I decided. “By then I’ll have either failed or succeeded anyway. Give them Hells, boys.”
They saluted with grim looks on their faces, but there was an energy to them that had been missing a moment earlier. Funny the way even the slightest hope could fundamentally change the mood in the worst situations. No wonder heroes kept talking armies into taking doomed last stands. Hakram and the two soldiers he’d picked – the pale dark-haired girl I’d seen kick Nauk and a female orc even taller than my sergeant – caught up with me before I left the ranks.
“So what’s the plan, Lieutenant?” Hakram whispered.
“We get close, then we charge towards the victory point,” I replied in a low voice.
“Simple,” the sergeant mused in his gravelly voice. “I like it. And when we get surrounded and stabbed?”
I shot the sergeant an amused look.
“That’s also part of the plan, I’m afraid.”
I was rewarded by a handful of snickers. I’d hoped I’d stumble upon a miraculous last-minute master plan, but it seemed my brain was fresh out of those. Well, it beat surrendering anyways. Grabbing the standard the female orc was offering me and propping it on my shoulder, I took the lead and started for the top of the hill. Juniper had deployed her line just behind the crest so I could see the tip of their helms but not what they were doing: clearly the Hellhound wasn’t out of tricks yet. I would just have to trust my suicide squad would be quick enough on their feet to get out of it. We were maybe a dozen feet away from the top when I gave my soldiers a warning look and whispered “\textit{Now}.” We broke out running. I heard Juniper scream an order but refused to pay attention, my whole focus on covering the last of the distance separating her from the enemy line.
That was when the logs started rolling down.
Every one of them a whole tree with the branches cut, thick as man and heavy enough to crush anything in their path. Well, I’d chosen right when I’d decided not to charge the company up the slope, I mused with a strange degree of detachment as the first one thundered down towards me. \textit{So this is as far as I could go, then}, I thought. Beaten by a pile of dead trees after having been played like a fiddle at every turn. All the plans I’d hatched over the last three days, all of the triumphs I’d fought for – snatched away in an instant. I could already see the way it would all go in my mind: Juniper’s line would charge down the slope behind the logs and snatch the standard from my unconscious body before closing the jaws of the trap on Nauk and Nilin. They’d fight well, but in the end they’d still lose. \textit{No}, the thought came.\textit{ I’m not done. I can still do more. I am more than this. I did not come this far to be slapped down by a heap of firewood. }
I felt thunder dance across my skin and the world spun into focus. The logs tumbling down slowed to a crawl and I grit my teeth before \textit{jumping,} sailing into the air and landing behind them in a crouch. I heard Hakram’s grunt of pain and the crack of bones as a log caught him in the chest, but I kept moving. No time to look back – Juniper’s line was already charging down, but the hill had made it impossible for them to tighten their ranks. They were full of openings, and the Name I’d claimed as my own howled in my mind as I slipped behind a charging legionary, tripping him with his own standard. There was another one behind, an orc who tried to strike me down but I laughed, heady with battle-joy, and the shaft of hardened wood slapped away the short sword before whipping around to take him behind the head. I pushed forward and suddenly I’d passed the enemy line, all I needed to do was run and-
“What the \textit{Hells }was that?” Juniper snarled, impacting into my side with her shield raised.
I rolled with the fall and pushed forward as soon as my feet were back under me but the captain was there again, blocking my way.
“Me,” I replied, “winning.”
I ducked under a cautious sword stroke and unsheathed my own blade. The power was already leaving me, slipping through my fingers like sand, but I would not fail when I was so close. I could hear legionaries doubling back to take me from behind, there was no time to waste – throwing the standard behind Juniper, I unslung my shield from my back and stepped forward. The orc captain was quick, I thought as Juniper tested my shield-side with a careful probe of the blade, but compared to the people I’d been getting my clock cleaned by for the last month the Hellhound was an amateur. Shield met sword and I pushed forward again, stabbing forward only to find my own sword bouncing off the orc’s armour. Undaunted, I stepped to the side and whipped my blade at Juniper’s head. The orc’s eyes widened at the speed of the strike and she stepped back, raising her shield to counter the stroke she knew was coming. That was all the opening I’d needed: dropping my shield I ran for the victory point, dropping low to snatch the standard as I did. I heard Juniper curse from behind me but the orc was slow, too slow, and with a roar I passed by the fallen command tent and rammed the First Company’s standard into the socket meant for it. There was a heartbeat of silence before Juniper rammed into my side, crushing me under her weight, but then lightning streaked across the sky once, twice.
Victory.
\clearpage
\chapter{Chapter 19: Pivot}

\textit{“Please, do keep digging your own grave. I look forward to your splendidly inevitable demise.”}
– Dread Emperor Benevolent the First

“COMPANIES! SALUTE!”
Two hundred swords rose up in the air, both companies standing at attention in the plain below the hills where a bell ago my band of survivors had been making their desperate last stand. Hakram grinned at me from where he stood in the ranks and I winked back as Ratface and I walked towards Juniper. The orc in question looked like she’d been force-fed a barrel of lemons, but she was pressing on gamely. The Taghreb captain had earlier informed me be there was a ritual involved to the declaration of victory and that I should follow his lead until I learned how it went. Nauk had seemed surprised when Ratface had told the officers of Rat Company I’d be with him during the process, the lot of them exchanging meaningful looks I wasn’t quite sure what to make of.
“Hellhound,” he greeted Juniper as he clasped her arm. “Not how we expected this one to go, huh?”
First Company’s captain growled under her breath.
“Gonna be a while before I live this down,” she replied frankly. “I might have to break Morok’s nose again if he gloats. Let’s get this over with.”
She turned towards her legionaries, unsheathing her sword.
“One sin,” she called out abruptly.
“DEFEAT,” they thundered back
Ratface took out his own blade, facing our men.
“One grace,” he yelled.
“VICTORY,” they chorused back, slapping their swords against their shields with an enthusiasm that drowned out everything else.
The scowl on Juniper’s face was the stuff of nightmares as she handed her blade to Ratface, handle first. The handsome boy took it but, after a heartbeat, handed it to me. There hadn’t been any mention of this in the books but then they were about the Legions themselves, not the College. Silence fell over the crowd until Rat Company burst out in another roaring cheer. My eyes flicked to my captain, whose face was an odd mixture of resignation and amusement.
“Hand it back to her,” he whispered.
I did, and Juniper slammed it back into her scabbard before striding away. We were… done, I guessed? I turned to Ratface.
“So we just head back to Ater, now? Seems anticlimactic,” I mused.
He grinned. “Silly greenie,” he replied. “Now comes the fun part. We spend the night here, and the extra rations should have arrived.”
I raised an eyebrow. “Extra rations?”
He smirked. “Ever tried \textit{aragh}, Callow? There’s a reason us Taghreb aren’t fucking miserable all the time like the Soninke.”

—

Night had fallen, and the site of Rat Company’s original defeat had turned into a giant feast. Fire pits had been dug and entire pigs put to roast while barrels of dark ale flowed freely. Legionaries from both companies mingled freely, clustering around great bonfires. Nobody seemed to be holding grudges over beating each other bloody during the game, which I supposed made sense if they were held every week. I took a sip from the cup of milky white liquor I’d been handed and immediately started coughing, much to Nauk’s amusement.
“Gods Below, what \textit{is} that stuff?” I croaked out.
“We call it dragon’s milk,” the other lieutenant replied, easily polishing off the rest of his cup. “If you drink enough it’s possible to set your breath on fire.”
“Bullshit,” I decided, pulling at it again. It was easier to swallow the second time.
“I tell no lie,” the massive orc laughed. “Some mage from Vulture Company did it last year, had to spend three weeks with the healers to get her throat fixed.”
I snorted.
“People made dragon noises whenever she came into a room for the rest of the year,” Ratface grinned from his seat on the other side of the fire.
“If you think this is hard stuff, you should try orc liquor some time,” Hakram weighed in. “Some sappers use it as cleaning fluid for the catapults.”
“I haven’t been in this company for a week and my sergeant is already trying to kill me,” I mourned.
There was a round of laughter and I smiled at the warmth coursing through my veins. Unlike most of the older girls in my dormitory, I’d never gone drinking on the beach with the guys from the boy’s orphanage down the street. I’d tasted enough drinks at the Nest that the novelty had worn off, and most of the time I had better things to do. Scraping together enough gold for tuition at the College wasn’t going to happen on its own. Still, this was… nice. I wasn’t sure I’d call any of the other three friends, but for all that they were easy to like. \textit{What does it say about me that I find it easier to laugh with the Empire’s freshest batch of killers than my own people?}
“Looking grim there, Callow,” Ratface noted. “Thinking heavy thoughts?”
“Remembering home,” I half-lied.
“You’re from Laure, aren’t you?” Hakram guessed. “You’ve got the accent.”
I raised an eyebrow. “I am,” I agreed. “But how would you know what a Laurean accent sounds like?”
“Our history teacher is from there,” Nauk said. “Used to be part of the Thirteenth.”
Ah, the famous Traitor Legion. \textit{Legio XIII, Auxilia.} It had been raised in the wake of the Conquest, made up mostly of former bandits and mercenaries. Every Callowan with a grudge against the throne had flocked to the banner, and they’d been instrumental in making sure the south surrendered after the fall of the capital – the prospect of that band of armed malcontents sacking their way through the southern cities had been utterly horrifying to the few remaining nobles. Before I could comment on the subject, though, a band of drunken legionaries passed right behind us singing at the top of their lungs.
“- they got a wizard in the West
But no matter how he’s blessed
We got a Warlock in the Tower
Who’ll use his bones for flour

Let them keep their priestly king
Cause no matter how sweet he sings
We’ve got an Empress black as sin
Who’ll take his throne and grin

We’re the Legion and the Terror
They’re in the right but we’re meaner-”
That was perhaps the most horribly sung rendition of the Legionary’s Song I’d ever heard, and I’d heard some pretty bad ones. They continued towards the closest barrel of ale, singing the last couplet until they ended on the customarily yelled \textit{we’re gonna swallow the world whole}. The old marching song had always been popular with the rank and file, penned by some unnamed legionary during the Conquest. From the unsurprised looks on everyone’s face, this was apparently a common event.
“The thing with Praesi,” I started.
Hakram rasped out an amused laugh, biting into his pork, and Ratface rolled his eyes.
“The thing with Praesi,” I pressed on bravely. “Is that you have so many godsdamned rituals. Like that thing with the grace and sin earlier. What was that even about?”
Ratface grinned, which suited him much better than his usual sour expression. He really \textit{was} a handsome one, if a little delicate-looking compared to my usual tastes.
“You’ve never heard of the Speech at the Fields?” he asked. “That’s the thing with Callowans, you always leave out the best parts of history.”
I blinked. “You mean the Fields of Streges?”
Nauk flashed me a double-row of pearly whites.
“Those are the ones. The Black Knight spoke to the Legions, before the battle,” he gravelled. “Every kid knows the words.”
“Today we set aside Good and Evil,” Hakram quoted with reverence. “There is only one sin, defeat. There is only one grace, victory. Everything else is meaningless.”
I sometimes forgot that the man who’d claimed me as his student was the same one from all the legends. Back home the Calamities were the monsters under the bed but here in Wasteland it was different. All of them were treated like giants among men, the epitome of all it meant to be Praesi.
“Huh,” I mused, taking another sip of dragon’s milk. “Well, I learned something today.”
“That and I named you captain of Rat Company,” Ratface continued airily.
I sprayed out the alcohol, to the delight of all the assholes surrounding me.
“\textit{What?!}”
“Why did you think he handed you Juniper’s sword?” Hakram asked, cocking his head to the side. “He was acknowledging it was your victory. No offence, Ratface.”
The olive-skinned boy snorted. “I spent the entire game as a prisoner, Hakram. The truth’s the truth.”
“This is stupid,” I objected vehemently. “All I know about the Legions I learned second-hand. I’ve never even set foot in the College!”
The now former captain of Rat Company shrugged.
“Twelve losses and you lose the captainship. That’s the rule. I didn’t win this, Callow. In fact I lost pretty badly. Your win, your claim. That’s what that entire scene was about, when it comes down to it.”
“You’ve got other lieutenants,” I pointed out. “Who might feel a little slighted they got passed over for the promotion.”
Ratface turned to face Nauk.
“Are you feeling particularly slighted, Lieutenant Nauk?” he asked.
“We ain’t so thin-skinned as you monkeys, taking offence at everything,” the large orc scoffed before addressing me. “Callow, the reason Ratface ended up Captain in the first place was that none of the lieutenants want to be.”
The boy in question shrugged. “Not that I particularly wanted the job either, but my marks are the highest in the company.”
I was about to muster up another denial when Hakram intervened.
“It’s only for two months, Callow,” he grunted. “We’re graduating soon, and our points are so badly in the negatives it’s not like you could do much damage anyway.”
I sighed.
“Fine,” I surrendered. “But I want my objections on the record.”
“To Captain Callow, then,” Nauk toasted, raising his cup.
“May she manage to have us graduate slightly less in the negatives,” Ratface replied cheerfully.
It was a horrible toast, but we all drank anyway.
I wasn’t sure how much time passed when I found myself wandering away from the fire to get my hands on a fresh bottle of \textit{aragh}. Nauk had disappeared at least half a bell ago when he saw Lieutenant Pickler pass by, running off after her while we all jeered at him and Hakram made some very suggestive comments about his canine length. Apparently that was a thing with orcs? He was replaced almost immediately by Sergeant Nilin. The dark-skinned boy was quiet one, compared to the others, but he had a wry sense of humour that was almost Callowan. I supposed it made sense for Nauk’s sergeant to be more grounded, given the large orc’s tendency for impulsive decisions. Ratface passed out by the time we’d polished off our second bottle of dragon’s milk and I was officially mandated by the survivors to get us a new one before we did the same. It hadn’t occurred to anyone, including myself, that I had no idea where to get one. I headed for the latrines first anyway, only to find a grim-looking orc waiting for me when I came out.
“Captain Callow,” Captain Juniper said flatly. “Let’s take a walk.”

—

I followed the Hellhound to the edge of the festivities, too drunk to be nervous but sober enough to be wary. We ended up standing at the top of the tallest slope, where a few bells before Juniper had tried to bury me under an avalanche of logs – the wood in question was still at the bottom of the hill, mostly intact.
“You have a Name,” the captain of First Company spoke.
It was not a question.
“That’s quite an assumption to make,” I replied anyway. “For all you know, my family might have a long tradition of being great jumpers.”
It might even be true, though admittedly the odds weren’t that great.
“I’ve seen Roles in action before,” Juniper denied me sharply. “Don’t take me for an idiot.”
I probably should have put in a little more effort into that parry, I admitted ruefully to myself. I’d been lulled into a sense of false security by the fact that no one had called me out on the fact that I’d done something that bordered on the limits of human capabilities – part of it, I assumed, was that few people had been looking at me except for Juniper and her personal line. For something done in broad daylight, there’d been surprisingly few witnesses.
“Everything’s possible,” I finally said, deciding that vagueness was still the way to go. I’d been supposed to keep a low profile, after all. “Are you here to complain that made the fight unfair?”
The orc eyed me like I’d just sprouted wings.
“This is practice for a real war,” she said slowly. “Fair doesn’t factor in it. Anyhow, I should have seen it coming. An unknown stranger with an obviously fake name takes a rank in the lowest-ranked company on the edge of their twelfth defeat? Name bait. I should have sent two lines to bury you on the first night just in case.”
“Yeah, that would probably have worked,” I admitted.
The greenskin captain’s eyes narrowed.
“So not a Name that’s overwhelmingly strong,” she murmured in that smoky voice of hers. “Something transitional, maybe?”
Juniper, I noticed, did not smell of alcohol at all. Had she been waiting for me to get drunk before we had this conversation? I would have admired that kind of patient ruthlessness, if it hadn’t been directed at me.
“Something that’s supposed to stay \textit{quiet},” I replied briskly.
“You’re the Squire,” the Hellhound realized after a heartbeat. “You’re the girl who set half of Summerholm on fire just to smoke out a hero.”
She eyed me up and down, like she had a hard time reconciling what was apparently my reputation with the person standing before her.
“Why do people keep blaming me for the goblinfire?” I complained, deciding that at his point the deception was so flimsy it wasn’t even worth it to keep trying. “I’m not the one who was throwing munitions around!”
“I’m sure you weren’t,” Juniper replied, clearly not believing a word of what I’d said. “So the Squire, huh. No wonder you ended up being a pivot for Rat Company.”
I really wished people would stop using words out of the blue and somehow keep expecting me to know exactly what they were talking about. It always made me feel like an idiot when I had to ask.
“A pivot,” I repeated, flavouring the words with an invitation to elaborate.
Juniper frowned, which I’d always thought looked strange on orcs – they had no hair on their brows, only thick ridges of skin.
“Your ignorance offends me on a personal level,” the other captain informed me. “How can you not know what a pivot is? It’s basic Name knowledge.”
“Hey! I’m new at this,” I defended myself. “And my teacher’s a bit of an ass. He never tells me anything outright. I think me might be physically incapable of not being cryptic.”
“Did you just call the Black Knight an ass?” Juniper replied, aghast.
“He really is,” I told her frankly.
“Lord Black is the best thing to happen to the Empire in centuries,” the Hellhound glared.
I squinted.
“Are you \textit{blushing}?” I asked. “It’s hard to tell in the dark.”
“You’re seeing things,” Juniper growled. “Fine, I’ll educate you. Names are stories.”
“I do know that much,” I said with a roll of the eyes.
I was familiar with the look she got at that – it was the face someone made whenever they were asking their deities of choice for patience.
“The stories have been around since the dawn of Creation, meaning there’s an endless variety of ways they can go. A pivot is a point in time or a decision where the Named pushes her story in a particular direction. It influences the kind of powers you develop.”
Mhm. Had I ever had one of those? My little talk with Heiress, maybe. Otherwise I couldn’t think of-
“Oh,” I spoke. “\textit{Oh}.”
Juniper frowned.
“What?”
“I fucked up,” I admitted out loud. “Today was the first time in weeks I’ve been able to tap into my Name, and I think I just realized why.”
“That ought to be illuminating,” Juniper sneered. “Do continue.”
“So a pivot is the beginning of a plot in the story, right?” I mumbled.
“Truly, your insight is an awe-inspiring thing,” the Hellhound commented.
I glared at her, but she was magnificently unconcerned.
“So take a boy and a girl, of roughly the same age. They’re on opposite sides. The boy doesn’t take a golden opportunity to finish the girl when he has it, and after she gets her shit together and beats him she also spares him.”
“The girl’s on the side of Evil?” Juniper asked, eyes much too knowing for my comfort.
“Something like that,” I grimaced.
“That’s a redemption story,” the Hellhound opined.
It was. I’d heard a dozen different tales that went that way, all with the same pattern. Spared on the first fight, an even match on the second and the climactic third meeting ended up with the conflicted evildoer changing sides after an impassioned speech by the hero or the heroine. \textit{No wonder my Name threw a shitfit.} I looked back on the way I’d reacted to the hangings in Summerholm, and I could see I’d been… influenced. Not by much: most of the disgust I’d felt then I still felt, but my reaction had been too strong. I’d been nudged just a little to the side of my usual mindset, and the realization sickened me. I’d been pulled by my own mind in two different directions, and the effect had been bad enough I’d ended up weeping my eyes out in an alley.
“I’m going to smother him with his own intestines,” I spoke into the night, tone cold as ice.
The Lone Swordsman had muddled my free will. \textit{Unforgivable.} Not even Mazus had tried to rob me from who I was, and he’d hanged for what he’d done. My fingers clenched and I felt hatred twist my stomach. Juniper’s face was unreadable.
“We’re done here,” she finally said. “Go to sleep, Callow. We’ve got a long march ahead of us tomorrow.”
I stumbled into my tent, my good mood evaporated into thin air. The others would have to soldier on without me, I didn’t feel like keeping company with anyone at the moment. Besides, Juniper was right. The hangover I was headed for would already make the march back to Ater a painful affair, there was no need to add to it. My bedroll was where I’d left it, blessedly unrolled. There was, however, a small bowl next it. I knelt on the ground to take a closer look. It was unadorned wood, full of water and with a small piece of granite incrusted at the bottom. Was it supposed to be symbolic of something, or had someone put it here by mistake? The answer came when the water rippled, the barely-visible reflection of my own face turning into the profile of my teacher as a subtle glow lit up the surface.
“Lieutenant Callow,” Black greeted me, his voice sounding like he was speaking from across the room.
“Black,” I replied, not as surprised as I should have been. “This is new.”
“Long-distance scrying. One of Warlock’s more useful tricks,” he acknowledged. “I hear the war game is over?”
“Pulled off a win at the last minute,” I grinned. “Though you seem to be missing a crucial piece of information.”
His brow rose. “And that would be?”
“You are addressing \textit{Captain} Callow,” I informed him.
His lips twitched. “Well done. We’ll go over your campaign when I return. Which company did you happen to beat?”
“Who do you think? First Company, of course,” I replied haughtily.
“It wouldn’t happen to be headed by an orc girl by the name of Juniper, would it?” he asked.
“You’ve heard of her?” I blinked.
He laughed.
“Istrid keeps bragging about how her eldest is the next Grem One-Eye whenever she gets into her cups,” he murmured. “Well now. Finally I have a retort.”
“\textit{General} Istrid?” I said, surprised. “She never said anything about being her daughter.”
“I imagine it’s not common knowledge,” Black mused. “She’s rather independent-minded, I’ve been given to understand. Doesn’t want to trade in on the family name.”
I could respect that. The orc captain rose up a notch in my esteem.
“How are things in the south?” I asked, changing the subject. “Are the Matrons giving you trouble?”
“Much to the contrary,” he replied. “The situation’s already taken care of. They even sent an envoy to apologize for not catching on before the situation warranted a Red Letter. I should be back in Ater by tomorrow evening.”
“Good to know,” I grunted. “Am I staying in the College even after you’re back? I’d prefer not to leave Rat Company until graduation, if that’s possible.”
He inclined his head. “I’m inclined to grant that, within reason. You won’t be attending most of the classes – we’ll be continuing our lessons instead.”
I nodded. It was what I’d wanted anyway: I was sure the teachers at the College were competent sorts, but I doubted what they had to offer compared to one-on-one tutelage by the Dread Empress’ right hand.
“Did you have time to look into what I asked you to?” I asked after a breath of hesitation.
“The orphanage is untouched,” he replied. “Not a soul missing. A good thing you killed the other claimants in such spectacular manners, I doubt Heiress would have taken you seriously otherwise.”
“That would have been unfortunate,” I murmured. “Because I meant every word.”
He smiled. “You’re beginning to garner enough of a reputation that you can leverage it. Be careful in managing it. Oh, and there’s one last thing.”
“Now why did you have to say that?” I complained, rubbing the bridge of my nose. “This conversation was going so well.”
He snorted. “Keep your evening free tomorrow, you already have plans.”
“Am I allowed to know what those plans are?” I asked sardonically.
“Of course,” he agreed. “Catherine Foundling is being officially introduced to the Imperial Court.”
Well, shit.
\clearpage
\chapter{Chapter 20: Rise}

“\textit{Who reigns up high?}
\textit{A dead man’s sigh}
\textit{What sleeps below?}
\textit{A crown of woe}
\textit{That is the Tower:}
\textit{Learn and cower.}”
– Extract from ‘And So I Dreamt I Was Awake’, Sherehazad the Seer

I tugged at my cloak’s collar for the twentieth time, ignoring Black’s amused look.

I’d been politely abducted by the Blackguards within a bell of entering Ater, to the dismayed surprise of Nauk and Ratface: they’d known better than to press the matter then and there, but I had a feeling I’d be getting asked some fairly pointed questions the moment I got back to the barracks. Apparently the low profile section of my association with the College had come to an end. I’d been smuggled deeper into the city and changed into what would be my attire for the evening under Scribe’s watchful gaze. The aketon and armour I was familiar with, though it had been cleaned and polished since I’d last worn them. The thick black cloak held tight against my shoulders by a woven golden braid was new, though, and I felt like I was getting strangled every time I took a breath. 

There was something odd about the cloth – every now and then, when I moved, the way it caught the light made it look like it was made of pitch black feathers. Sorcery was involved, as far as I could guess, though a purely decorative working seemed… out of character, for Black. There was probably more to it. My teacher was still wearing his usual plain steel plate, though he wore a cloak that was mine writ slightly larger. The implication of our matching clothes was less than subtle. Captain had traded her usual armour for something more ceremonial, her breastplate and greaves decorated with snarling wolf heads. Her cloak was of a brown tone that bordered on red.

“Do you really wear armour every time you come to Court?” I asked as we strolled down a wide – and strangely deserted – avenue.

“Praesi nobility has a regrettable propensity for stabbing,” Black replied.

“And poisoning,” Captain grunted from behind us. “And blood magic. Calling the Tower a snake pit is doing a disservice to snakes: they don’t usually bite unless provoked. Some of the fuckers up there will have you killed for wearing robes that look too much like theirs.”

My fingers closed against the hilt of the sword sheathed at my hip. Since the wrecking of my last blade back in Summerholm, I’d been provided with another goblin-wrought short sword. The grinning goblin’s head the last pommel had been shaped as had been replaced by a stylized version of green flames. My teacher’s sense of humour was ever a twisted thing.

“You think someone’s going to try to kill me?” I asked.



“

Crass, of all the adjectives to use. Sometimes the Praesi seemed the same as us, but then they said something and I was struck by how differently they looked at things. Culturally speaking Ater might have been more Soninke than Taghreb, but the capital of the Dread Empire had developed into something that was entirely different from both. Ater was the touchstone of Praes and at Court murder was considered as much of an art as sculpting or painting. Lack of elegance in the death was more of a sin than the killing itself.

“How can the Empire even function, with the nobles poisoning each other at the drop of a hat?” I wondered. “I always thought the stories about the Imperial Court were exaggerated, but if anything things seem to be worse.”

“

“The Name she had outlawed,” I murmured. “Seems like there’s a story there.”

Pale green eyes flicked to me, then away.

“A long one,” he said. “That will have to be told another day. We’ve arrived.”

I’d thought I’d seen the Tower. 

\textit{ }

I stood before the beating heart of the Dread Empire and felt like an ant.



“I come summoned by the Tyrant,” Black called out into the silence. “Gatekeeper, grant me entrance.”



“The prodigal knight returns,” the abomination drawled. “And with an apprentice in tow.”

“Gods, tell me that thing isn’t going to ask us to solve a riddle,” someone said, and in a moment of horror I realized it had been me.

Black’s hand fell around my arm and I could feel it squeeze painfully even through the armour. I really needed to get a handle on the mouthing-off-in-the-face-of-fear thing. The thing in the gate laughed and I regretted every opening my mouth: it sounded like both the wail of a child and the shattering of a hundred swords.

“Even now, you bring me the most interesting strays,” it spoke. “I grant you entrance, Black Knight.”

The face melted back into the obsidian and I heard a series of locks unlatch through the gate, until it slowly swung open. The antechamber was empty, not a soul haunting the riot of dark marble that preceded the deeper Tower. We stepped inside and my teacher turned on me as soon as the gates closed.

“Don’t ever do that again,” he whispered furiously.

“It let us in anyway!” I whispered back, tone defensive.

“

My blood ran cold. Souls couldn’t be destroyed, the House of Light said, not except by-

“That thing was a demon?” I choked.

“From the Twenty-Third Hell,” he said.

His face was calm again, but his eyes were still sharp as a knife.

“



“You’re a long way from Laure, Catherine,” Black murmured. “The evil that dwells here runs deep and old. It took two empires and a continent-wide rebellion to bring down Triumphant, when Praes was at its peak. There are still shadows of that madness lurking.”

Fuck. I took a deep breath and settled my nerves. I could still do this. Whatever horrors prowled inside the Tower didn’t matter: it was the Court I was here for, and they were just people. People I could deal with, no matter how dangerous they were.

“Got it,” I said through gritted teeth. “Let’s move on.”

The antechamber led to a high-ceilinged room of cold black stone, bare of any tapestries. The only thing that wasn’t polished marble around was the series of mosaics on the walls, strangely patterned in a hundred subtle shades of red and grey. I frowned as we got passed one by, slowing to take a closer look. A large hand came to rest on my shoulder almost immediately, gently pushing me forward.

“Don’t,” Captain murmured, her tanned face expressionless. “If you manage to see the eyes, you’ll be speaking in tongues for weeks.”

I jerked back.

“Is this entire place a death trap?” I asked peevishly.

“Yes,” Black agreed blandly. 

Well, that kind of took the wind out of my sails. Shame, a good rant would have helped to settle my nerves. Two sets of spiralling stairs rose to the first level, the smooth railing guarding them shaped as the tail of a snake. \textit{Yeah, I’m not touching that.} Given how the rest of my visit here had gone the thing might be some sort of animated stone snake just waiting to smother anyone touching it. Black paused as we came to the head of the stairs to the upper floor, turning to grant me a glance.

“Steel yourself,” he spoke. “This part is always… unpleasant.”

Without giving me the time to reply, he stepped through the archway to the next room. My determination to be cool and unflappable in the face of whatever was coming lasted exactly three heartbeats. The long corridor awaiting me was filled with human heads. They hung from the ceiling by silk ropes, kept close to the walls so that they formed a curtain of mutilated flesh covering the entire span of the stone. That alone would have been enough to fill my nightmares for the next few months, but the moment we stepped in they all swivelled to face us. A thousand mouths opened and they started moaning and yelling and begging, words spoken in half a dozen different tongues drowning each other out into incoherence until all that could be heard was one deafening scream of despair and hatred. I flinched back and saw the closest ones were laughing at me now, leering and calling out sentences I couldn’t make out. One in particular stood out to me, a pale-skinned man with a a bushy red beard whose entire face was covered in pockmarks and scars. The derision I saw on that face was the last straw.

“

For the span of a single breath my Name filled the room. The power that surged through my veins winked out of existence as swiftly as it had appeared, but in its wake silence reigned. I felt the weight of a thousand stares on me, but I was too angry to care.

“Interesting,” Black murmured, resuming his walk. “You’ve picked up Speaking after seeing me use it only the once. A decent effort, for a beginner.”

I strode ahead of him, not bothering to reply, and in a matter of moments we were making our way up another flight of stairs.

“What the Hells was that place?” I asked after a long moment.

“The Hall of Screams,” Captain replied. “It’s where people end up, when they try for a Dread Empress’ crown and fail.”

“The necromancy keeping the heads alive goes back to the Declaration,” Black mused. “No one’s been able to reproduce it since, and not for lack of trying.”

“Well isn’t this place just a nice little box full of fucking horrifying surprises,” I growled. “A more specific word of warning would have been nice. Like say ‘Hey, Catherine, there’s a hall full of humans heads just ahead. So you know, heads up!’”

“I was interested in seeing your reaction,” Black admitted shamelessly, and if we hadn’t been in the Tower I would have shown him some of the more insulting gestures I’d learned in the Pit.

“How high up are we going anyway?” I asked, since dwelling on the subject would just have made me angrier.

A little anger would be enough to keep me steady, but if I worked up any more than that I’d lose focus.

“Official Imperial Court functions are held on the twenty-fourth floor,” the green-eyed man replied.

“That doesn’t sound like a coincidence,” I muttered.

“It’s been some time since the numerical value was used to facilitate devil summoning,” Black noted. “The Court still remembers when they came to collect with Nefarious.”

“\textit{ }

The dark-haired man shrugged, though the gesture was hard to make out under his cloak.

“Borrowed power always betrays its user, in the end,” he simply said. “It might gain the one making the deal some short-term victories, but it inevitably turns into a death sentence down the line. It’s as good a way as any to weed out the more foolish elements of the aristocracy.”

“They still have to cause a costly amount of damage when they go crazy,” I replied curiously. “Why don’t you just ban it entirely? It would save resources in the long term.”

The way the green-eyed man talked about making deal with devils implied he found the matter distasteful, and Black wasn’t the kind of man who let traditions linger when they were counterproductive. Was I missing something?

“It already disqualifies mages from service in the Legions,” Captain replied from behind us.

The look my teacher sent me made it clear he knew I was mostly pressing the matter to keep my mind off of the coming evening, but for now he seemed inclined to indulge me.

“There’d be no practical way to enforce the ban,” he explained. “Any half-decent warlock can summon something if they get their hands on the right manuscript. Therefore, Catherine, what would be the consequences of Malicia passing such a decree?”

It was almost reassuring to hear him slip into his teaching voice, given our surroundings.

“An erosion of Imperial authority,” I replied after a moment. “If the Empress can’t enforce her own laws, people are going start breaking more than that single one.”

He nodded, looking satisfied.

“The myth of Imperial omnipotence is what keeps Praes together,” he murmured. “We must manage that illusion carefully.”

We stepped foot on the second floor. After the general level of nightmarishness displayed by the last two I’d expected yet another sight I would wake up screaming about in the coming weeks but it was surprisingly mundane. The entire level, much like the one beneath us, had been carved into a single room but unlike the hallway this one occupied the entire space. There were no real walls, just some spaces between large sculpted archways that led straight into oversized circular balconies. For the first time since we’d entered the Tower there were other people around, guards wearing the same armour-and-mask as those outside standing between the archways in the same creepy silence. There were no stairs for us to go up by, I noticed, and shot the Calamities a quizzical look.

“How are we getting to the twenty-fourth?” I asked.

“Getting a lift,” Captain grunted.

Both of them ignored the silent guards and headed straight for one of the archways to the left – I managed to discern a twenty-four in Miezan numerals in the pattern adorning its stone when we got closer. Stepping out onto the balcony, Black whistled sharply as I stared down. No railing here, and wasn’t that just horrible architectural design? \textit{It’s like they want someone to slip and fall}. I paused for a heartbeat.\textit{ Hells, they actually might. Strike two for the evil architecture school theory.} I was about to ask what we were doing there besides standing and looking like the village idiots when a reptilian shriek resounded from above and a dark shape flew down towards the balcony. A grey-skinned creature with bat wings the size of a small house landed on the edge of the balcony, hissing hatefully at us in a way that displayed its bloody saw-like teeth.

“What is that?” I asked, taking a wary step back. “Some dragon’s inbred cousin?”

“Our ride up,” Black replied amusedly, and I followed his pointed finger to the large saddle placed on the creature’s back.

“You’re a bad man,” I accused. “A bad, bad man.”

“Guilty,” he mused. “Though never charged.”

Against my better judgement, I snorted.

“I’m taking the reins on this one,” Captain spoke up in a tone that brooked no argument. “We’re not having a repeat of last time.”

“I have no idea what you could possibly mean,” Black demurred. “High Lord Nok lingered too long on the landing pad. That accident could have happened to anyone.”

“Everybody heard you telling it to take a bite in the Dark Tongue,” the Taghreb warrior replied, thoroughly unimpressed.

“My pronunciation’s still a little off,” the Knight smiled sardonically. “I was trying to tell it to ‘take a hike’, I assure you.”

\textit{So I’m avoiding the High Lord of Nok, then.} Good to know. Captain climbed onto the beast first, followed by Black who moved much too gracefully for a man wearing plate armour. I took his offered hand to hoist myself up, keeping myself steady by clasping a pair of helpfully placed leather handles on the saddle. The gargantuan warrior-woman spat out a harsh, guttural word in a language I didn’t recognize – immediately the abomination we were riding let out another screech and jumped off the balcony. For a moment we were free falling and I bit my lip to keep myself from screaming. My old fear of heights was coming back with a vengeance. The thing’s enormous wings started beating and it rose through upwards steadily. I close my eyes and clasped the handles hard enough I was sure my knuckles turned white. 

Several eternities later, the creature landed on what I felt to be solid ground. I opened my eyes again and let out a breath of relief when I saw we’d arrived on what looked like a large, gaudier version of the balcony we’d come from. Without waiting for anyone’s permission I jumped down from our ride, dancing out of the way when the creature turned to hiss and snap its teeth at me. The balcony led into a smaller chamber with a handful of wooden benches heavily encrusted with gold and jewels. I eyed a ruby the size of my fist that probably made actually sitting on the bench highly uncomfortable and sighed. There was such a thing as being \textit{too} rich. Golden hooks jutted from the walls, meant for guests to hang their coats on, but I didn’t have any more time to gawk: my companions had dismounted and Black casually adjusted his cape over his shoulders.

“Here we go,” he murmured, and without further ado pushed the doors open.

My first thought was that there was no way the throne room in display could actually fit inside the Tower. It was way too broad and the ceiling was high enough I half-expected there to be clouds trailing the ceiling. The usual theme of black marble hard returned with a vengeance, but this once there was actually a bit of colour around: drapes of red, green and gold cascaded down everywhere like strange cloth pillars. The floor was one single immense mosaic depicting a hundred different scenes – the part I was in front of showed what I was fairly certain was the latter parts of First Crusade. The large army with its myriad of banners laying siege to a stylized Ater was something of a hint. My attention almost immediately left the decor, though: there must have been at least several hundred people standing in the gallery, and all of them were looking at us.

I’d seen very little of Praesi nobility, back in Laure. Besides Mazus and a handful of his hanger-ons, there wasn’t any in the city. But now I was in their natural habitat, and though I despised them on principle I had to admit they were a stunning sight. Tunics and dresses of every colour and every pattern, every one of them more exotic than the last. Silk and brocade, velour and velvet and half a dozen other cloths I didn’t even know the name for. The hair styles for both men and woman were outrageously elaborate, from braids with emeralds woven into them to a closely-cropped head with ever-changing arcane patterns shaved into it. There were Taghreb and Soninke both, and the overwhelming majority of the people inside were humans. There were but a handful of orcs, and no goblins at all. That I could see, anyway. Given their size they might be hiding behind someone else. Black stepped to my side and his face might as well have been carved out of stone. I schooled my own expression into something more neutral as I followed behind him, hearing the music that had been gently sounding in the background trail off as we did. The crowd parted before us as we strode with purpose, until we came to stand a few dozen meters away from the dais in the back of the room where the throne stood.

I barely looked at the throne itself, though it was a thing of legend, for all my attention was commanded by the woman sitting on it. I’d seen some beautiful women in my handful of years. More than most. The Baroness Dormer had visited Laure, when I’d been a child, and I remembered thinking her hair looked like it was spun out of silver. She’d been pale as the moon and just as lovely. I’d served drinks to Yan Tei missionary once and spent most of the evening sneaking looks at her smooth honey-coloured skin and amber eyes. She’d been lean in the way all their warrior-priests were, with the muscles of a swimmer and the mysterious smile of a sage. Heiress, too, had been gorgeous in a way I could only envy: generations of good breeding culminating in a perfect figure and flawless features that not even a sneer could mar. 

Compared to Dread Empress Malicia, they might as well have been pigs.

She was tall, even with her sitting I could see that much, but there was more to it than that. There were statues of ancient warrior-queens in Laure and they’d been… too perfect. Beautiful, but looking at them you knew they were art and not a living thing. The Empress was breathtaking because she was so very \textit{alive}, like a bonfire compared to everyone else’s candle. It didn’t matter that I didn’t usually find sharp Soninke cheekbones like those on her face attractive, they were part of a whole that went beyond its separate parts. I couldn’t pick out a single feature that made her beautiful, she just \textit{was}. Her silk dress was a stream of green and gold that suggested the curves of her body without revealing them, leaving bare her long neck and curling down to caress smooth dark calves. \textit{Black as sin}, the Legionary’s Song called her, and it was impossible \textit{not }to think of something sinful when looking at her. Fluidly, with the easy grace of a hunting cat, she rose to her feet.

“All kneel for Her Most Dreadful Majesty Malicia, First of Her Name, Tyrant of Dominions High and Low, Holder of the Nine Gates, Sovereign of All She Beholds,” a harsh voice rang out.

As one, the nobles filling the throne room dropped to their knees. After a moment Captain’s armour creaked as she did the same, cloak pooling on the ground around her. Without thinking I was halfway to doing the same when a hand fell upon my shoulder.

“We,” Black said, “do not kneel.”

He’d spoken quietly, but in the hush of the room the words reverberated like the crack of a whip. The sentence was heavy with meaning, a claim and a declaration both. \textit{We do not follow the law. We are the law. And if you want me to kneel, come and make me.} There we stood, the two of us clad in steel and black like a pair of crows surrounded by birds of paradise. The only two people still on our feet among a sea of kneelers. I felt a shiver go down my spine at the sight. It felt like power. It felt like a beginning, though of what I was not sure. Dread Empress Malicia smiled as she sashayed toward us – just looking at the quirk of her lips made my heart clench.

“Welcome home, Amadeus,” she said. “I see you brought along your Squire.”
\clearpage
\chapter{Chapter 21: Fall}

“\textit{Victory, most fickle of friends.”}
-Taghreb saying

Gods, even her voice was gorgeous. How was that fair in any way? I knew taking a Name could change your appearance, over time, but somehow I got the feeling that wasn’t the case with Malicia. \textit{I suppose once in a while someone does get born that outrageously good-looking}. With an effort, I forced myself to look away – I certainly wasn’t going to get my head back in the game as long as I was gawping at the Empress like a dumbstruck fool.
“It’s good to be home, Malicia,” Black replied mildly. “If I may introduce Catherine Foundling, formerly of Laure.”
The direct mention was enough to jolt me back into a semblance of attention. I kept my face as blank as I could manage and inclined my head as the Dread Empress’ dark eyes turned to me.
“My dear Knight has long been delaying the taking of an apprentice,” she mused. “I look forward to finding out how you changed his mind. I must confess I have great hopes for you, Squire.”
Smiling in that heartbreaking manner of hers, she cast a warmly fond look at the Court.
“We \textit{all} have great hopes for you,” she asserted, and the nobles effortlessly painted polite agreement over their faces.
I imagine they would have done much the same, if she’d opened me from crotch to throat with a sacrificial knife. One did not openly disagree with the ruler of Praes without consequence – and who would even want to, while she was smiling at them like that?
“I will try to live up to them, Your Majesty,” I replied, and had to force down a cringe when I heard how hesitant my voice sounded.
I might as well have been throwing a barrel of blood in a pond full of sharks. Malicia’s expression was kindly, but I was beginning to have a handle on how striking she was. I was, nominally at least, on Black’s side. That more or less meant I was on hers considering that Black was her staunchest supporter, but I’d been given to understand that there were nuances at play. My teacher had made it clear from the beginning that while he deferred to the Empress he didn’t agree with her every decision. Already I was beginning to regret I hadn’t spent more time asking questions about the current state of Imperial factions at Court – this was a battlefield like any other, but I had no idea who my enemies actually were. Malicia lightly tread around us, forcing us to turn as the kneeling nobles rose to their feet. They were still silent, though, so I got the feeling that the show wasn’t over yet.
“How go the provinces, Black Knight?” the Empress asked, voice carrying clearly across the enormous throne room.
\textit{Provinces}. My face turned properly expressionless for the first time since I’d stepped into this mess. That was how they thought of Callow here, wasn’t it? Uncivilized provinces good only for shaking until gold and other useful materials came out.
“Settled,” my teacher replied calmly. “For now.”
Malicia cast a soulful look at the nobles.
“It is,” she spoke with genteel regret, “a great shame that Governor Mazus forced our hand in such a way. I do dislike ending old bloodlines.”
The Tyrant was the very picture of an aggrieved young woman. Black turned to face the crowd too, and there was no such regret on his face. A hint of the… thing I’d glimpsed in Summerholm was peering out through those unsettling green eyes, offering the aristocrats a smile that bared too many teeth to be anything of the sort.
“That is the ever the way, with those who overreach,” he told them. “It should be remembered that unsightly ambition so often lead to an unsightly end.”
He ran a pale thumb across his throat in a seemingly casual gesture and I saw several silhouettes go still as stone. The casual reminder that in the end Mazus had been robbed of the easy death all those colourfully plumaged vultures thought was their birthright was unsettling them. \textit{None of this is spontaneous,} I instinctively grasped. The easy repartee between the two most powerful individuals in the Empire was too fluid to have been rehearsed, perhaps, but there was still something almost practiced about it. Like they’d been in their respective roles for so long that they no longer needed to plan out the dance, only be who they were supposed to be and let the music lead them.
\textit{So that’s how it is}, I frowned. Malicia was gentle and soft and regretful, respected the importance of the old families and their place in the halls of power – and all the while my teacher stood there reminding them with a smile that if he had his way all of their heads would be in the Hall of Screams. The Empress smiled and casually laid a hand on Black’s arm, four hundred eyes following the gesture. \textit{Look at my monster}, she seemed to be saying. \textit{Isn’t he dangerous? Remember, I’m the only thing standing between you and him. So why don’t you all behave, my darlings? Leashes are such slippery things.}
“Now that the inevitable politics are out of the way,” Malicia announced cheerfully, “we can get back to the part of the evening you’re all actually here for.”
Chuckles and smiles ripped through the crowd, though she hadn’t been being particularly funny. The Empress idly clapped her hands, and immediately the music started playing again. In a heartbeat the court split into a hundred smaller clusters, conversing among themselves and calling over servants carrying trays full of cups. With a last smile at us, the Empress trailed away to mingle.
“You did passably well, for you first time at Court,” Black assessed quietly. “They’ll think you weaker than you are, but that can be useful.”
“I really need some etiquette classes,” I grunted back. “The stuff I learned at the orphanage is useless here.”
“I’ll work it into your schedule,” the dark-haired man murmured. “But don’t forget you have a Name, Catherine. Rudeness is one of the many privileges that affords you.”
I raised an eyebrow. “If I’m gonna be rude to one of them, I want to be on purpose,” I retorted.
He conceded the point with a mild inclination of the head. “You’ll have to mingle on your own,” he said. “Captain will be keeping an eye on you, but she’ll be remaining at a distance.”
“Got an assignment of your own, have you?” I guessed.
Black smiled thinly.
“The High Lady of Kahtan has been making noises about revising the legal number of household troops,” he replied. “She seems to need a reminder as to why she inherited her seat so young.”
“You have fun with that,” I snorted. “Anybody in particular I should talk to?”
“There might we some well-connected cadets from the College in attendance,” Black murmured. “Allies are a useful thing.”
I acknowledged the hint with a nod and turned to face the crowd as he strode away. Where to start? Gods, I’d never been all that good at the social butterfly thing. \textit{All right, let’s get a drink first. Should make the rest of this easier.} I gestured for one of the drinks-carrying servants to come closer and snatched a golden goblet with wine in it. Something fruity, from the smell of it.
“Don’t drink that,” Scribe murmured.
I nearly dropped the cup, cursing under my breath. The plain-faced woman was standing at my side like she’d always been there – and for all I know she’d been. There was a ring of empty space around me for at least twenty feet, which made it all the more ridiculous I hadn’t seen or heard her coming.
“You \textit{really} need to stop doing that,” I complained.
A flicker of amusement went through her eyes, gone in a heartbeat.
“Haven’t seen you since the Blackguards picked me up,” I observed after composing myself. “Where did you go?”
“I had other duties,” she replied, and didn’t elaborate even after I raised an eyebrow.
I sighed and eye the cup of wine wistfully.
“It’s poisoned, isn’t it?” I said with resignation.
“All the drinks are,” she said. “A mild poison, with embarrassing side-effects. Attendees find out what antidote they’ll need in advance: not drinking is seen as a sign of incompetence.”
“Fucking Praesi,” I grunted under my breath. “No offence, Scribe.”
“None taken. I was not born in Praes,” she replied without inflection.
That was the first bit of personal information I’d ever learned about Black’s shadow, and I filed it away for mulling over later. Very little was known about Scribe, given how rarely she made it into the stories. The Empress passed at the edge of my field of vision, laughing throatily at a richly dressed young boy’s jest. From the poleaxed look on his face, he seemed as unable to deal with her as I’d been not too long ago. The Named woman followed my gaze, clicking her tongue against the roof of her mouth.
“Be careful with her,” Scribe said.
I kept my surprise off of my face. She wasn’t usually one to bother with warnings, and to be honest I was a little surprised we were still talking at all: this might very well be the longest conversation the two of us had had since the first time we’d met. I’d never gotten the feeling that Scribe disliked me, per se, she just didn’t seem particularly invested in my general existence.
“I know she’d dangerous,” I replied quietly. “It’ll take more than few smiles to make me forget that.”
“You don’t understand \textit{how} dangerous she is,” the plain-faced woman murmured. “Not even Black does, and he’s known her the longest.”
“They knew each other before she took the throne?” I asked, openly surprised.
I’d heard next to nothing about Dread Empress Malicia before she claimed the Tower. Even how she’d managed that was rather vague: I knew she’d been opposed and a civil war had ensued where Black had served has her general, but details were scarce in the books I’d been provided.
“They met before he claimed his first Name in full,” Scribe said. “When she was still a waitress at her father’s inn in Satus.”
I blinked. “A \textit{waitress}?” I hissed out in disbelief. “The Dread Empress of Praes used to be a \textit{waitress}?”
The other Named folded her ink-stained fingers into her sleeves.
“What do you know about Dread Emperor Nefarious?” she finally asked.
I frowned. “He ruled before Malicia. Went a little cuckoo in the head after he failed to invade Callow and got whipped by the Wizard of the West.”
Scribe’s face was unreadable. “The nature of his fall was less charming than your expression might imply. Nefarious never again left the Tower after he returned, leaving matters of ruling to the Chancellor. He spent his time expanding the ranks of his seraglio.”
Just the word made my skin crawl. I’d known that some of the Dread Emperors – and Empresses – had kept consorts, but from the way Scribe was talking about it Nefarious hadn’t been looking for volunteers.
“Her beauty has little to do with her Name,” she murmured. “The Emperor had his Sentinels scouring the breadth of Praes for beauties and word of her looks had spread beyond the town. Her father protested, so they nailed him to the floor of his own inn.”
I grimaced. I sometimes forgot that the bastards that held the Tower were just as brutal towards their own people as they were towards the other kingdoms.
“So they met when she was taken to Nefarious?” I guessed.
Scribe shook her head. “A few days beforehand. He and Wekesa were still claimants to Squire and Apprentice, back then. They met again when he became the Black Knight and Chancellor summoned him to the Tower.”
“From concubine to Empress,” I muttered. “Weeping Heavens, how did she manage that?”
“Patience,” Scribe said. “Patience, poison and making the right promises.”
That certainly got my attention. “And what did she promise him?”
“What she needed to,” Scribe replied flatly. “Not as much as she should have. They are, after all, friends.”
Her face had remained impassive, but there was no hiding the thick distaste in the way she pronounced the last word.
“You don’t sound very fond of the Empress,” I said very, very quietly.
“Amadeus is a loyal man, in his own way,” Scribe replied. “It’s why we follow him – he’d break the world, for one of us. In some ways he already has. But the blade bites from both sides.”
I cast a shifty look around us, which probably made us look twice as guilty.
“We are not being overheard,” the plain-faced woman said, and the utter certitude in her voice gave me pause. Something related to her Name? “Ranger and I disagreed on many matters, Catherine, but there was one thing we always agreed on.”
“And what’s that?”
Scribe leaned closer.
“We should have an Emperor, not an Empress,” she whispered into my ear.
Without another word, she stepped into the crowd. A drunken noble passed in front of her, tittering with a companion whose hair was shaped like a roaring dragon, and by the time they cleared my field of vision there was no sign of Scribe. She might as well have vanished into thing air, and if I hadn’t know how hilariously disproportionate the amount of magic needed for even the smallest transportation spells was I would have thought she’d teleported. \textit{Well, wasn’t that the most ominous conversation I’ve had all week. If you don’t count the fucking demon doorman, anyways.} It wasn’t every day I got spoken treason to, and there was no way this was anything but treason. Coming from the Named who worked closest with my teacher, to boot.
Scribe’s mention of Ranger had come as something of a surprise, considering the woman in question had left the Empire early into the Conquest – if the stories were true, anyway. So there were Praesi who’d wanted Black to claim the Tower. That wasn’t all that surprising, considering he’d been the face of the Empire’s latest victories. \textit{But he doesn’t seem to want the Tower.} \textit{And I’m not sure he could actually take it, considering he’s pale-skinned.} There were three ethnicities, in the Wasteland. The two largest were the Soninke and the Taghreb, often overshadowing the less-known Duni. Most dark and olive-skinned people who lived in the Green Stretch still considered themselves of the associated culture, but the pale-skinned people who’d trickled into the Stretch from Callow as well as those who had much more ancient Miezan roots were branded with the name of Duni.
The Soninke had some kind of religious grounds for despising them, I’d read – it was associated with the same reason they thought of the Taghreb as a lesser people – but the Taghreb simply hated them for being a visible reminder of the Miezan occupation. Over a thousand years later no living Taghreb had been actually seen a Miezan and the blood of the original settlers who’d remained in Stretch was so diluted as to have nothing in common with their ancestors, but the hatred remained. There had been Black Knights of Duni blood before my teacher and a few Chancellors. But no Warlock, and no one of those roots had ever held the Tower. The very idea was anathema to the beliefs of most of the old nobility.
I wasn’t sure what Black actually wanted, when it came down to it. I’d grown to know the person he presented himself at and even looked the monster he could be in the eye, but his intentions were still a mystery to me. With every passing day I felt more like the only dancer in the ballroom who didn’t know the tune or the steps, and there was only so long I was willing to allow that. I could still hear rope creak and necks break whenever I closed my eyes: those were the consequences, when I took a swing in the dark instead of planning out my actions carefully. \textit{Gods, I really wish I could have a bloody cup of wine at the moment. }There seemed to be food displayed on a table by one of the cloth pillars, and I made my way towards it. Odds were it was just as poisoned as the wine, but I figured I’d at least look whether some people helped themselves to it before writing it off. There was already someone there sniffing around pork cutlets, as it happened. I recognized the silhouette even from a distance: I didn’t know a lot of orcs as tall as Juniper, aside from Hakram.
“Hellhound,” I greeted her, pleasantly surprised. “Didn’t think you’d go for this sort of thing.”
Juniper turned to eye me and then stabbed a cutlet with a fork, dropping it on an ornate gold plate.
“Someone from the family needs to show up at the important stuff,” she grunted. “Mom’s in Summerholm and Dad is taking care of my sisters up north so I got stuck doing it.”
I eyed the cutlet enviously as she took a bite.
“I don’t suppose those are safe?” I asked hopefully.
“Bishara told me what the antidote for tonight was,” Juniper replied with a smirk, flashing her fangs. “Only brought enough for one, I’m afraid. Should have planned this one better, Squire.”
“A common failure of hers, I’ve found,” a female voice casually butted in from behind me.
“The density of smugness in this room has suddenly intensified,” I announced without turning. “I wonder why that is?”
I turned towards the source of the comment and saw a pretty dark-skinned girl smiling at me in a way that never quite reached her eyes.
“Oh, Heiress,” I added cheerfully. “Hadn’t seen you there. Did you say something?”
Juniper snorted.
“It’s rather astonishing what passes as a sense of humour in the provinces,” someone else commented.
My eyes flicked to the pair of girls and the single boy my nemesis – one of them, anyway, and Gods when had I gotten to a point in my life where I’d need to look up the plural for the word nemesis? – had decided to bring along with her. The girls were Soninke, the boy Taghreb. Richly dressed, all of them, in shades of red and gold. Heiress’ long red dress brought a pang of envy from me, if only because of the way it fit around her curves perfectly. I’d yet to grow in any of those to speak of myself, much to my dismay. \textit{At least I don’t have to bind my breasts too hard under plate. Must be Hells on her, when she does.} After a heartbeat to take them in, I addressed Heiress.
“You brought bookends,” I said amusedly. “I didn’t think that was something people actually did. Did you train them to say snappy phrases whenever you signal them? Go on, tug at your earlobe. I’m hoping it’ll make one of them strike a pose.”
“I suppose allowances need to be made for poor breeding,” one of the Soninke girls sighed. “I am Barika Unonti, heiress to the Ladyship of Unonti. You may kiss my hand, Wallerspawn.”
She extended a slender dark-skinned arm, palm facing downward. I eye her dubiously and she sneered. I sighed and my hand snapped out, closing around her little finger. Her eyes widened and she had to bite down a scream when I twisted sharply, breaking the bone without much effort. Soft hands, this one. I let go and smiled pleasantly at the lot of them.
“That’s your first warning,” I said. “You say another thing about breeding of any kind, or reference the fact I’m Callowan, and I’ll take something more drastic. An eye, maybe, since you little shits don’t see to be using them to recognize I am \textit{not somebody to fuck with}.”
Unonti eyed me like I’d turned into a raving madwoman and something arcane in nature flickered around the other girl’s fingers – it felt like lightning, but she did not strike out. The boy’s hand dipped to the bastard sword at his hip and I made eye contact with him, still smiling.
“Draw it,” I said softly. “See where that gets you.”
His hand returned to his side, his face flushed with anger. I returned my attention to Heiress and something I couldn’t quite identify passed through her eyes.
“Barbarity,” she spoke calmly, “is all you are good for. I’m told you couldn’t even manage a win at the College without using your Name.”
“She used all the tools at her disposal,” a gravelly voice interjected. Juniper was onto a second cutlet, eyeing us with mild amusement. “That’s the purpose of the games: training for war. She’d have been an idiot not to use it.”
Well now, an unexpected display of support from the Hellhound. Hadn’t seen that coming.
“Is defeat all it takes to cow one of the Knightsbane’s blood?” Heiress spoke softly.
Juniper’s eyes turned hard and she bared her teeth, pushing herself up to her full height.
“The likes of you don’t get to say shit about my blood, Soninke. We still remember the Night of Red Winds,” she snarled. She rounded up on me immediately afterwards. “And you, don’t you look so pleased. I’m not taking sides in your little pissing contest – I just want you both to to leave your fucking politics out of my Legions. There’s more to this Empire than humans bickering over who gets to be in charge.”
And with that she dropped her plate on the table, walking away with a growl. Heiress smiled and met my eyes. \textit{Ah, she did that on purpose. Burned the bridge for me. But that means…}
“You have now slighted me twice, Catherine Foundling,” the Soninke called out, and her voice carried.
It got the attention of people around us, and they watched with interest – a loose circle of watchers formed.
“Well,” I replied blandly, “you do take things so personally.”
“You have assaulted a guest under my protection,” Heiress announced. “Do you deny this?”
Mhm, how to qualify the feeling in my bones at that moment? \textit{Like a rabbit seeing the noose tighten around its throat.} I could hardly deny breaking Unonti’s finger when it was still, in fact, broken. Besides Heiress had witnesses. Had I been baited? It was starting to look like I had been. \textit{Now time to see for what.}
“Sometimes I see something particularly breakable and I just can’t help myself,” I shrugged, noting the girl in question was still cradling her finger and glaring at me.
“Talk like that will cost you your tongue, \textit{uchaffe},” the boy snarled.
It meant filth, in Mthethwa. I ignored him anyway. He was just Heiress’ mouthpiece, allowing him to distract me would just let her gain more ground.
“You comport yourself like a thug and still expect to rack up honours and commands,” my rival spoke, gracefully circling around me in a stalk. “You have not proved worthy of the promotion you are being given.”
“And what promotion would that be?” I replied flatly. “The one where my company in the College named me captain by acclaim?”
Heiress dismissed that with a contemptuous flick of the wrist.
“I speak, of course, of the request made for your commission as the head of the Fifteenth Legion,” she said.
I kept my face carefully blank. That was the first I was hearing about that. As far as I knew, there was no Fifteenth Legion existing at the moment, or even a Fourteenth. More than that, there was only one person I knew who could have made that request. I resisted the urge to scan the crowd for Black.
“Think you’re the one who deserves it, do you?” I mocked.
Heiress’ smile widened.
“As a matter of fact, I do,” she purred. “What have you done, to deserve such an appointment?”
I felt the crowd move more than I saw it, the sea of aristocrats parting for the bigger fish. Dread Empress Malicia sauntered into the scene, elegance personified.
“My, my,” she murmured. “Such spirited youths we have in attendance tonight. What seems to be the problem, my dears?”
Heiress knelt, and for a heartbeat I almost regretted I couldn’t – wouldn’t – do the same. The display of deference might have been useful, and I could only envy how my rival was turning a mark of lower status into a useful tool.
“Your Majesty,” the Soninke girl spoke before rising back to her feet. “I was merely questioning the fitness of this… Callowan to command Praesi legionaries.”
There was a murmur of approval among the nobles. She really was going to milk my origins for all they was worth, wasn’t she? I’d never been more painfully aware that I had no friends in that crowd.
“The Callowan actually attends the War College, unlike you,” I noted flatly.
“An attendance that has not been marked by successes justifying such a rise in authority,” Heiress retorted smoothly.
“The contrary, if anything,” her Taghreb from earlier contributed with a sneer.
“Captain?”
The voice came from far behind me, to my left, but even at that distance Black’s voice was pitched perfectly to carry across the room.
“Lord?” Captain replied.
“If the boy interrupts again, snap his neck.”
“With pleasure.”
The boy went pale as a ghost, taking a half-step back. Times like these were when I was glad to have the Black Knight in my corner, cryptic jackass or not. Malicia laughed, and the entire world held its breath at the sight of it – it defused the tension that had risen in the crowd easy as snapping your fingers.
“You have a solution in mind, Heiress,” the Empress smiled. “I can see it in your eyes.”
“I do,” my rival agreed. “To keep things interesting, I would propose a wager.”
The Empress cast her an interested look. “You have my attention.”
“Another war game,” Heiress announced. “The College once held grand five-way melees, in older times. Better times. If Squire is to command, I would have her prove her worth. Isn’t that the way of our Legions, Your Majesty?”
My rival’s smile turned sardonic.
“One sin, one grace,” she quoted softly.
I felt my fingers clench around the pommel of my sword.
“And should, Gods forbid,” the Empress prompted, “our Squire lose?”
“I would ask that for the slights she has given me, Catherine Foundling’s appointment be made mine,” she replied, and triumph glinted in her eyes.
\textit{Oh, that bitch. She knows Rat Company is ranked last.} And if Summerholm was any indication, she wouldn’t be above bribing my opponents to make sure I failed.
“That does sound interesting,” Malicia mused, tapping her chin with a slender finger as her eyes raked the crowd.
I could see the intellect behind the beautiful face weighing the advantages and disadvantages, what the throne could gain and lose by allowing this to proceed. A moment later, she returned her attention to us.
“It will be so,” the Empress spoke, and this time there was iron in her voice. “In two days hence, with the outlined stakes.”
“I thank Your Majesty for her wisdom, as always,” my rival said with a low bow.
And just like that, it was done. Malicia drifted away and I felt the eyes of the entire wretched flock on me, mocking. A few splatters of laughter came from different corners of the room. Heiress passed me by, pausing to lean into my ear.
“And all it cost me was a broken finger,” she murmured.
The grip on my sword strengthened until my knuckles were white, my face flushed with humiliation. She’d played me like a fiddle, and everybody in the room knew it. Some of them weren’t even bothering to be subtle about it, eyeing me like I was wearing a fool’s motley. \textit{I suppose I might as well have been, falling for it so easily.} I strode out of the crowd, heading for the closest door I could see. It led straight into an antechamber much like the one I’d come in through, though night had fallen in the lapse of time since I’d first come in. The beginnings of a storm were whipping at the stone with ropes of water. I tightened my cloak around my shoulders and stepped into the rain.
I stood and let the water run down my face, unsure of why I’d thought it would make me feel better. Lightning struck in the distance, streaking the night sky for the barest fraction of a moment. I didn’t feel soothed by the beat of the rain on my head: just wet and cold and still so very humiliated. Ater was sprawled out in the distance around me, the labyrinth of stone dotted by torches all the way to those enormous walls and the famous nine black gates the City of Gates had been named for. I’m not sure how I knew Black had joined me up out on the balcony, but I knew it as sure as I knew my own breath. My Name, probably – the more I learned how to use it the more it changed me, broadened my perceptions in some indescribable way. My teacher came to stand by my side on the edge, standing still and silent like he hadn’t even noticed we were in the middle of a storm.
“They’re always going to get in my way, aren’t they?” I spoke into the silence. “Because I’m from Callow, because I’m a commoner, because I’m not one of them. They’re going to fight me on everything just because they can. Because every time I win when they think I should lose, it insults them.”
Black was silent for a long time.
“Yes,” he agreed, and there was a world of weariness in that single word.
“She beat me,” I said, knowing it to be the truth. “Without lifting a finger. A handful of sentences and she managed to make my every success meaningless in less time than it takes to boil a cup of tea.”
He didn’t move and lay his hand on my shoulder the way I’d seen some fathers do with their daughters. It had never been this way with the two of us, and it never would be. He would not prop me up when I fell, but I’d never expected that from him. I was the Squire and he was the Black Knight, and so instead of comforting me he stood by my side in the pouring rain, waiting for me to rise back up on my own the way I always had. I closed my eyes and raised my head, letting the water flow against my cheeks as I let out a shaky laugh. Lightning struck again and I screamed at the night sky, screamed until my throat was sore and my stomach hurt.
“How do I do it,” I panted afterwards, “how do I beat them?”
And I didn’t mean the other companies. I meant all those dagger-eyed nobles inside, just waiting for me to step wrong so I could be buried in a shallow grave. Black turned towards me and smiled the same wicked smile he had what seemed so long ago, when he’d walked into the palace in Laure and turned a man’s death sentence into a lesson for me. Lighting struck again, casting his pale face in a madman’s light.
“How does a villain deal with enemies? It’s the simplest thing in the world, Catherine. When they get in your way… \textit{step on them}.”
\clearpage
\chapter{Chapter 22: All According To}

“\textit{Diplomacy is the art of selling a deal you don’t want to people you don’t trust for reasons you won’t admit to.”}
-Prokopia Lekapene, first and only Hierarch of the League of Free Cities

“No one goes through the front gate, Callow,” Ratface told me pityingly. “Not unless you have a Name or you’re in disfavour with the Empress.”
“That just bloody figures,” I muttered. “There’s another way in?”
“Try twenty,” Hakram gravelled. “Most of them through tunnels, but the nobles have some fancy gate in the back.”
I scowled, much to the amusement of my officers. I’d missed the communal breakfast for my company, as Black had let me sleep in up to Morning Bell before sending me back. Within moments of setting foot on the grounds my officers had come to ambush me: morning classes had been dismissed because of an announcement that was the talk of the College. A five-way melee had been ordered by the Empress herself, and the participants had been informed in the middle of the meal. We commandeered one of the classrooms to serve as our meeting hall, ushering out the handful of cadets studying inside. There were advantages to Captain rank, even when it was a purely collegial title. My lieutenants clustered together on the same bench as if I was about to start a lesson while Hakram propped himself up on what was likely the teacher’s desk: he was the only sergeant in attendance, since this was theoretically a senior officers’ meeting. No one objected to his presence, not that I would have given in if they had: I’d come to value his advice too much to care if him being around ruffled a few feathers.
“So,” Kilian spoke up, “a five-way melee. Been a while since they organized one of those. I’m guessing it’s not a coincidence that the people in it are the four top companies and little old us?”
I’d paid little attention to the lieutenant of the mage line, when I’d first come across her in Ratface’s tent, and hadn’t see much of her since. Red-haired and pale-skinned, she was an unusual sight this deep in the Wasteland. \textit{Likely there’s a story to that. }Setting aside my curiosity for the moment I grimaced, leaning back against the desk with my arms folded over my chest.
“There’s other forces at play here,” I told them. “My name, as you might have guessed, is not Callow.”
Pickler cocked her head to the side.
“You’re not actually the Duchess of Daoine’s secret bastard offspring, are you?” she asked flatly.
“I-” I opened my mouth, closed it and then opened it again. “I genuinely don’t know how to respond to that.”
“That’s the most popular rumour as to why the Blackguards picked you up,” Ratface informed me in an irritatingly amused tone. “Ran away to Praes so you could learn war from the best. Very romantic stuff. Until the melee everyone was talking about it.”
“I am not, in fact, the hidden heir to the Duchy of Daoine,” I replied patiently, rubbing the bridge of my nose to stem the no-doubt oncoming headache.
Ratface cursed under his breath, handing a smug-looking Kilian a handful of silver denarii.
“Told you it was Name stuff,” she crowed.
“She doesn’t do magic and there’s already a Squire and Heiress running around,” he argued. “What Name could she possibly have?”
I cleared my throat.
“Yeah, funny thing about that,” I admitted.
Surprisingly, Nauk was the first one to get it.
“You were there when Lord Black hung the Governor, huh,” he grunted. “Well, that explains that.”
A ripple of surprise went through the officers. I’d have to remember not to underestimate how sharp the orc lieutenant was just because he was muscled like a bear and liked punching people in the face. It took more than brawn to make his rank.
“Long story short,” I continued, “I got baited by Heiress and now we’re in this mess. You have my apologies for that.”
“Ah, Imperial politics,” Ratface murmured. “Someone always gets screwed, and never the one who deserves it.”
He got sympathetic looks from the others at that and I made a mental note to get the whole story about why from Hakram later. My sergeant seemed to have an inside track into every story going on in the College and displayed absolutely no reluctance in feeding me the juiciest morsels.
“Something like that,” I agreed. “If Heiress continues to make the same kind of plays she has so far, we might have a company – or more – going for us from the beginning. Girl has deep pockets, and she’s not above bribing her way to victory.”
Pickler shook her head.
“Won’t work,” she assessed. “Not here.”
I raised an eyebrow. Hopefully she wasn’t about to make a speech on the strength of Praesi moral fibre, because so far I’d found the subject less than impressive.
“She’s right,” Ratface agreed. “Anyone takes a bribe for this and their career in the Legions is over.”
I hadn’t considered that, actually. True, my teacher could just put in a quiet word with some of his followers and kill someone’s career if he wanted to. Would he? After a heartbeat I decided he would. It’d be seen as Heiress meddling in his backyard, so he’d have to make an example.
“Even then,” I finally said, “expect sabotage. She wouldn’t have put forward those terms if she didn’t think she could affect the odds.”
“Eh,” Nauk shrugged. “As long as they keep that shit off the battlefield it doesn’t matter, does it? We just need to wreck everyone else.”
“He’s right. This isn’t the kind of war game that can be easily stacked, anyhow,” Pickler murmured. “Too many people in play, too many different priorities.”
The almost adoring look Nauk sent her after the comment forced me to bite down on a smile. I’d never really gotten to see the two of them interacting before but I had no trouble at all believing what Hakram had told me about the large orc having a thing for the goblin lieutenant.
“Which brings me to the point of this little chat,” I broke in after having smoothed my face out of any amusement. “There’s four other captains participating and I’m going to need anything on them you can give me.”
“You sure you need us to tell you anything about the Hellhound?” Kilian mused, dark eyes dancing with amusement. “From what I hear you whipped her pretty bad even without us around.”
I smiled but inside I was wondering about the most polite way to nip this in the bud. I didn’t want to antagonize one of my senior officers within the three days of my getting a command, but underestimating Juniper was a sure-fire way to get spanked so hard our grandkids would still be feeling the sting.
“She actually played me like a fiddle from start to finish,” I admitted, deciding that a little self-deprecation was the way to go. It wasn’t like I’d have to lie to get my point across, or even stretch the truth. “If I hadn’t blindsided her by having a Name she would have won – and she nearly did anyway.”
Ratface cleared his throat, breaking in.
“On the bright side, she’d unlikely to hold a grudge,” he mentioned. “She’ll want to win this one too badly to focus on us: she’ll go for victory, not payback.”
“We can focus on Juniper later,” I agreed. “I think I’ve got a decent read on her anyway, it’s the other three that are unknowns. I only know the name of the guy in charge of Fox Company – Captain Snatcher, right?”
Pickler nodded.
“He’s not going to be an immediate threat,” she spoke quietly, “but we can’t afford to give him time to dig in. He’s turned his entire company into defence specialists – made it mandatory for every single one of his cadets to take the sapper classes.”
Defence, huh? Not the flashiest of specialties but it sounded like it could get troublesome. Snatcher might not meet us on an open plain – tough since I had no idea what our battlefield would look like, I had no idea whether we’d even have one of those handy – but recent history was full of stories making it very clear that giving Legion sappers the time to set up surprises always ended nastily for the attacker.
“Anyone assaulting a position he’s fortified is going to take brutal losses,” Hakram gravelled from my side. “That might be enough to lay the groundwork for cooperation with another company, at least until he’s out.”
“Something to think about,” I mused. “What are we looking at, in terms of allies?”
“Captain Aisha Bishara is our best bet,” Ratface contributed immediately, “she runs Wolf Company.”
Bishara. I’d heard the name before – hadn’t Juniper mentioned it last night? There was a wave of snickering by the others. Even Pickler cracked a smile.
“I bet you’d like to \textit{ally} with her, all right,” Nauk grinned.
I raised an eyebrow and sent Hakram a quizzical look.
“They were involved,” my sergeant informed me. “She dumped him a few months back and he’s still in denial.”
“She didn’t \textit{dump} me, you green arse,” Ratface scowled. “We’re just on a break until we’re less busy with things.”
“Like I said,” Hakram continued with a sagely nod. “Still in denial.”
“All right, let’s table further mockery of Lieutenant Ratface for the moment,” I replied with a wry smile. “Who’s our last contender?”
“Captain Morok,” Kilian spoke up. “Head of Lizard Company. They’re second in company rankings, so he’ll be wanting the Hellhound’s head on a pike.”
“They’ve got a feud running?” I asked my officers.
“Not really,” Ratface said. “Well, maybe him – he takes things personally. They’re nearly head to head in points, so if he wins this and Juniper loses he’ll climb up to first rank. It’s his last year before graduation, so he won’t be getting another chance.”
“That’s something I can use,” I muttered, passing a hand through my hair.
I’d braided it into a semblance of order this morning, but I might have to cut it soon. It was getting too long, and it was awkward to wear under a legionary helmet. Hakram cleared his throat, which made him sound like he was retching out half a desert.
“Have you decided how many points we’re going to be bidding, Captain?” he asked.
I frowned.
“Bidding? That’s the first I’m hearing of this.”
Kilian folded her hands together. “Instructor Bolade said we’re supposed to bid a set amount of points. If we win the melee, we’ll gain that many – and if we lose, we’ll lose that many.”
“An exercise in calculating risk, she called it,” Pickler contributed quietly.
I could see how. Company scores, as I understood, were not the affair of a single batch of cadets: they were a legacy inherited by the next one. All scores were set back to zero every decade, but considering the last reset had been two years ago a large bid that failed could haunt a company for a very long time. Nobody wanted to leave a mess like that behind and be remembered as the captain that tried to bite off more than they could chew, screwing over the next two batches of cadets. Which reminded me, I still had no idea what Rat Company’s score actually was.
“I know we’re in the negatives,” I said, “but how far down are we? Seventeen, twenty?”
Ratface closed his eyes, his face flushed.
“Forty-two,” he muttered.
I kept my face smooth, almost grateful for the refresher course in doing exactly that the Court had turned out to be. \textit{Forty-two?} A win in the war games was a two point gain, a defeat a two point loss. A draw was a one point gain for the defender and a one point loss for the attacker. I knew Ratface had lost twelve in a row and that Rat Company hadn’t been doing well even before that, but I hadn’t expected them to be stuck that deep down the well. It meant that even before the Taghreb had been put in charge the company had been losing far, far more often than they won. I could see the embarrassment in the face of my officers, the shame of having let their standing fall so far, but now was not the time for self-recrimination.
“That’s a relief,” I said.
Ratface blinked. “Pardon?” he asked.
I smiled. “With that kind of a handicap, I feel a lot more comfortable in using some of my more… debatable ideas.”
Nauk laughed, apparently delighted at the prospect. Pickler was hard to read, but Kilian looked like she was wondering whether to be insulted or amused.
“Hopefully it doesn’t involve jumping logs this time,” Hakram muttered. “That hasn’t been a winner for me so far.”
I shot my sergeant an amused look.
“I’m sure I could find a drill, if you’d like,” I mused. “Always be prepared, right?”
“I seem to recall having urgent duties anywhere but here,” the tall orc replied. “I really should go see to them.”
I snorted. “All right, dismissed. Get the company ready, we don’t have a lot of time.”
They slid off the bench one by one, saluting before going through the door. Hakram shot me a questioning look, but I gestured for him to go. It was Ratface’s shoulder I clasped to hold him back.
“So you’re our supply guy,” I said, drumming my fingers against the desk, leaning back against it.
Ratface shrugged, his handsome features highlighting the absurdity of his chosen name.
“Something like that,” he agreed. “Usually it’s the captain’s job to handle this stuff, but you have enough on your plate already.”
Didn’t I just?
“I got a sealed letter from the Headmistress this morning, before I got back to the College. It specifies what quantity of stuff we’re allowed to requisition for the melee, with caps for types of goblin munitions,” I told him. “I’m considering our options, and you know your way around the College stocks a lot better than I do.”
The olive-skinned boy straightened his back, interest piqued.
“You’ve got something particular in mind?” he asked.
“We’ll get to that later,” I replied. “When we passed the stocks earlier I noticed that they have a parchment nailed down with what they have available on it. I want you to send someone to copy it. I’m guessing the other captains are doing the same.”
The grey-eyed lieutenant raised an eyebrow.
“You want to know what the others will be taking into the melee,” he said.
“It should give us an idea of the way they intend to go at it,” I acknowledged. “But what I really want to know is if there’s a way to get anything without going through the College stocks.”
Ratface paused, eyeing me very carefully.
“Not… officially,” he said. “But I might know a few people. Why? It’d be a lot of effort, and we can’t take more than allowed onto the field. More than that, the others will notice we haven’t drawn as much from the stocks as we can – they’ll know something is up.”
“They will,” I noted, “unless we draw up to our limit until the last possible moment. Then we return our surplus, and…”
“They’ll go into the match with wrong information about what we’re carrying,” Ratface finished thoughtfully. “I’ll talk with my friends. Get back to me as soon as you have hard numbers.”
I nodded.
“Another two things,” I added. “Send someone to the College archives. I want everything you have on the old melees. There’s also records of more recent games, right?”
Ratface nodded.
“I want a record of every game Juniper was a captain for,” I grunted. “As quickly as possible.”
“Anything else?” the lieutenant asked drily.
“Well, since you asked,” I mused. “I’ll need a guide for the day. I have a few people to meet.”

—

It seemed that having a vicious sense of humour might be a widespread Praesi trait instead of just my teacher’s: the guide Ratface had assigned me was Robber.
“He’ll be easy to recognize, Cap,” the goblin said. “Just look for the ugliest orc in the training yard, can’t miss him.”
The grounds we were headed to weren’t inside the College, though they were close. It was apparently possible to reserve them for a bell if you signed up with one of the instructors, and aside from First Company the Lizards were the company whose name came most often on the list.
“Is that so,” I said neutrally.
“Now, as is well known,” Robber told me in a tone implying he was about to impart a fundamental truth of life, “orcs are the ugliest creatures in Creation as well as the dumbest. But Morok is in a class in and of himself, as is only fitting for a captain. His face has been known to scare goats and make children cry.”
“Isn’t Hakram one of your friends?” I asked mildly. “And, you know, an orc.”
“He’s an honorary goblin,” the yellow-eyed sergeant replied without missing a beat. “One of these days I’ll get around to adopting him into the Rock Breaker tribe as my ugly but still-beloved son.”
I must have been a bad person, deep down, because I actually found the little shit kind of funny. Regardless, we’d arrived. A wall about a man’s height encircled the yard, though I could hear the sound of metal against metal coming from inside. A pair of human cadets flanked the main entrance, eyeing us distrustfully. Or not actually \textit{us}, I noticed after a moment. They were both glaring at Robber.
“What did you do?” I asked with a sigh.
“Nothing,” the goblin sergeant protested.
“I’m sure those rats got into our dormitory all by themselves,” a dark-skinned boy said through gritted teeth.
“They must have heard you lot talking shit about Rat Company and gotten confused,” the small goblin grinned maliciously. “You know how small-brained creatures get, I’m sure.”
The other cadet, Soninke as well, let her hand drop to her sword.
“You utter prick,” she snarled. “One of them bit my-”
I cleared my throat, loudly. “Robber, go wait down the street. Cadets, I’m Captain Callow. I’d like to talk with Captain Morok.”
They exchanged looks. “He said-” the boy started.
“A visit by another Captain qualifies,” the girl grunted. “You might have to wait until he’s done, though.”
I nodded and granted Robber a steady look.
“Try not to get stabbed, Sergeant,” I ordered.
I was halfway through the doorway when I heard him call back “no promises!” I bit my cheek so I wouldn’t smile. The inside of the yard was beaten earth with weapon racks propped against the walls, though lines of ground chalk had been traced to form some patterns I vaguely recognized from my lectures on the Legions. \textit{Formation drills.} There were benches between the racks and most of the hundred or so legionaries inside were sitting on them, watching two people fight in the middle of the yard.
One was a Taghreb girl, the largest I’d seen since Captain – meaty and thick-shouldered where her people were usually slight of frame. The other, who was currently hammering at her shield with his own, was the ugliest orc I’d ever seen. \textit{Godsdamnit, Robber.} He wasn’t wearing his helmet so I could see from the occasional grin that his teeth were yellowish. His eyes were dark and deep-set, and I couldn’t help but notice he had a large brownish mole just above his lip that was almost fascinatingly hideous. Like most orcs Captain Morok was heavily-muscled, but where the likes of Hakram and Nauk were in perfect shape he had something a pot-belly.
Not that it seemed to be hindering him any: he was winning the fight, and pretty handily. Slower than Juniper, I assessed, and his movements were kind of sloppy. But the girl he was fighting looked like she was getting kicked by a horse every time he hit her, and he battered her defence down until she was kneeling in the dirt. There was a cheer when he helped her up afterwards, and I leaned against the wall as another legionary walked up to the pair. They talked, too far away for me to overhear, and Morok glanced in my direction. Spitting on the ground, he shoved his sword and shield in the cadet’s hands before beginning to walk towards me.
“Captain fucking Callow, is it?” he leered, passing me by to pick up a water skin off a bench.
Popping off the cork, he took a long swallow – some of the water trickled off his lips onto his chin, mixing with the sweat already there.
“That’s me,” I agreed.
“You’re a skinny thing, for the heiress to Daoine,” he snorted.
“This is going to be worse than the goblinfire, isn’t it?” I sighed.
The captain’s eyes sharpened. “What’s that?”
“Nothing,” I grunted. “No relation to Duchess Kegan, it’s just a rumour.”
“Sure it is,” he smirked.
It occurred to me then that he was being rude on purpose. Pushing me to see how I’d react, like I’d once done to fighters in the Pit. The thought was comforting: I might have been a long way from home, but some things stayed the same. \textit{And I know how to deal with his type.}
“So, you’re Juniper’s runner-up,” I mused. “Must sting, that she whipped your lot like children when Rat Company pulled off a win.”
Morok smiled, showing off yellow but still very sharp fangs.
“Did your little helper Ratface tell you what I did to your company last time we fought?” he asked. “Didn’t even use munitions and we still took the fort. First time it ever happened, I’m told.”
I now had no problem whatsoever understanding why Robber had flooded their dormitory with disease-carrying rodents. Pushing down the flash of anger, I raised a hand in peace.
“We could do this all day,” I acknowledged, “but we’ve got better things to do.”
“\textit{I} do, anyway,” Morok snickered. “So why the fuck are you here, greenie?”
“Because I beat Juniper,” I stated flatly. “And she’s not the kind of person that takes that lying down.”
The other captain wiggled his hairless brows in a thoroughly horrifying gesture.
“You and the Hellhound lying down, now there’s an image,” he said.
Ripping out one of his teeth and jamming it in that fat ugly mole wouldn’t help me, I told myself. Id’t be deeply satisfying, but it wouldn’t help me.
“You’re second in rankings,” I gritted out. “If anyone else wants a shot at her, it’s you.”
Morok shrugged.
“Could be,” he said. “What’s that got to do with you?”
I narrowed my eyes. He wasn’t an idiot – he wouldn’t be a close second in company scores if that was the case. But he was deliberately ignoring the offer I’d implied. \textit{Why?} My mind raced, and the answer I settled on had me tightening my lips. \textit{He thinks we’ll weaken First Company just enough for him to pick them off afterwards. He’s not interested in working together, he just wants us to tear at each other so his position’s stronger regardless of the result.} Hellgods, I was sick of being used as a piece in other people’s games.
“She’d beat us,” I admitted. It was the truth: in a straight fight, First Company would walk over us like we were a freshly-paved Miezan road. “But Morok, here’s the thing: if I’m going down, I’m taking everyone else with me.”
The fat orc eyed me cautiously.
“I’m not getting into a fight I can’t win,” I said. “So we’ll surrender – and before getting the Hells off that field, I’ll clap her on the back and hand her all our munitions.”
He only half-managed to suppress his wince. Fighting First Company was one thing, but fighting a First Company at full strength with twice the amount of goblin munitions? There wasn’t a force on the field that’d be able to take Juniper then, and we both knew who she’d be headed for.
“It’d take someone with no pride to flop belly-up like that,” he growled.
I shrugged.
“I’m Callowan, Morok,” I spoke in Kharsum. “I’ve spent my entire life with an Imperial boot pushing down on my throat. How proud do you really think I am?”
The captain spat again, the fat gob of saliva coming dangerously close to my boots.
“So we ream her together,” he conceded in the same tongue. “But that’s all, Callow. You’re not riding this one on my coattails. The moment we withdraw from the field, the truce is done.”
“Wouldn’t have it any other way,” I agreed.
I offered up my arm. After a moment, he clasped it.

—

I’d learned from the last trip and left Robber at a street corner close by.
“Tea?”
Captain Aisha Bishara was taller than me, I was chagrined to notice. Was it too much to ask to meet at least one military officer that was shorter? One that wasn’t a goblin, anyway.
“Please,” I replied.
She was rather pretty, in that way some Taghreb were. With a lovely heart-shaped face, tanned skin and wide dark eyes, I could easily see how she would have caught Ratface’s eye. Her hair was cut in short bob, though strictly speaking it was still longer than Legion regulations allowed. \textit{Then again, so’s mine.} Like Morok she’d been rather easy to find: it was common knowledge she had a private room set aside in the Sword and Cup for her personal use. The busy tavern wasn’t the kind of place I would have expected a girl of her apparently noble origins to adopt as her unofficial headquarters, but then I supposed that if she’d been the kind of person who cared for that stuff she would never have gone to the College in the first place. Aisha poured for both of us, elegantly setting aside the porcelain tea cup when she was done. Hospitality was a point of pride for the Taghreb, I remembered Captain telling me. An old tradition from before the days the first Miezan galley had ever reached the Wasteland’s shore, and one that was central to the southern culture in many respects.
“Captain Callow,” the dark-eyed girl mused. “So you’re Ratface’s replacement.”
I felt a flicker of unease at that, though it never reached my face. Her involvement with the boy I’d replaced as captain of Rat Company had been mostly a source of amusement so far, but it occurred to me for the first time that she might have an issue with me replacing her – former? – paramour.
“So they keep telling me,” I said prudently. “Is it going to be an issue?”
She blinked, though that was the only sign of surprise she gave. That was what I hated about dealing with Praesi: you could dump a bucket full of sheep heads on one’s table and you wouldn’t get much more than a frown out of them. Trying to get a read on the nobility of the Wasteland was like trying to dry a godsdamned lake.
“Why would – \textit{Hakram}, you gossipy bitch,” she cursed in a low voice.
I hid a grin. In other circumstances I might have tried to defend my favourite minion but he really \textit{was} a gossip. Aisha let out a frustrated sigh.
“Look, Callow,” she addressed me flatly. “If he was cut out for that kind of command the Rats wouldn’t have lost as much as they did. It was right for him to be replaced. One sin, one grace.”
The last four words she’d said with the fervour of a woman at prayer, which would have gotten a pained grimace out of me if I weren’t already working on keeping my expression neutral. I was as good as apprenticed to the man who’d introduced that philosophy to the Legions, and that was why I could grasp how utterly terrifying it was. Black had indoctrinated the better part of a generation into thinking that morality was irrelevant to the battlefield: the only things that mattered when the swords came out were victory and defeat. When the next war came, and I had no doubt that one was coming, there would no blundering generals at the head of the Legions. The coming generation of Evil would not fall apart on its own. \textit{They’ve been taught that winning matters more than anything else, and they’re not above breaking the world if that’s the only way to own it.}
“So I’ve heard,” I muttered.
“But I doubt you came to speak about my love life, Callow,” Aisha said pleasantly. “What is it you actually want?”
Ah, and now came the tricky part. Time to get my head in the game.
“I’m more interested in talking about what \textit{you} want, Aisha,” I replied with a smile. “I’ve been keeping an eye on the stocks, you see.”
“Quick learner,” the dark-eyed girl said approvingly. “If you’ve been doing that, though, you know your company isn’t the one I’m after.”
Her grabbing as many siege munitions as she could had made that plain enough, true.
“That’s what I’m here about, to tell you the truth,” I told her, sipping at my tea for the first time. Huh, that was the first time I ever tasted that blend – it wasn’t the stuff Praesi usually served. Imported from the Senrima, maybe? That had to cost a fortune. “I’m not keen on letting Snatcher build his walls while the rest of us fight it out.”
Aisha smiled.
“Well now, Captain Callow,” she purred. “It seems like we have a common interest.”
I put down my teacup and my smile broadened.
“Let us talk business, then,” I replied in Taghrebi.

—

After touching base with my officers I’d gone back to Black for my usual lesson and stayed around afterwards, electing to remain in the comfortable solar he’d appropriated in central Ater instead of returning to the College.
“I’ve read through all the reports on games Juniper commanded a company in,” I said after a few hours of silence.
“And?”
I sighed, reaching for the cup of wine he’d poured me earlier and taking a sip.
“She doesn’t make mistakes,” I informed my teacher after swallowing. “Every time she had the necessary information, the calls she made were perfect.”
Black seemed more amused by that than sympathetic.
“Maybe I should have made her my Squire then,” he spoke airily.
I scowled at the bastard.
“You know people only laugh at your jokes because they’re scared of you right?”
He snorted. “I’m assuming you have a point, apart from your apparently upcoming nuptials with Istrid’s daughter.”
I sneered at him as best I could, though compared to the nobility he so often had to deal with I was an amateur at the art. I’d never found orcs particularly attractive, which I’d been informed was a shared opinion from their side of the wall.
“How do you beat someone who always makes the right choices?” I finally asked him.
Morok I could deal with – I’d faced men like him before, fought and beat them. Aisha was trickier, but her focus on Snatcher made it possible. And Snatcher? Well, I was keeping quiet on my way to deal with him. Some cards needed to stay face down until the very last moment. But Juniper? I’d tried to come up with something to trump the Hellhound and come up empty.
In a straight-up fight she’d crush me, I knew that much. She had more command experience, a formal education in tactics and she’d shaped First Company into a heavy combat force my own legionaries would be unable to deal with. Which was fine, anyway: I’d never been all that fond of straight-up fights. I could scrap with the best of them, sure, but there was always someone who was bigger or better at taking hits. The problem was that every single dirty trick I’d manage to think of was present in one of those reports, and \textit{she had beaten every single one of them}.
Her only defeat on record was the one I’d inflicted on her, and it had been a fluke. She’d led me around by the nose the whole time and if she’d suspected I had a Name she might very well have managed to beat me even if I’d somehow managed to tap in my power. A power I couldn’t even count on, anyway, since I hadn’t managed to use my Name since the last game – and not for lack of trying. \textit{Godsdamned Lone Swordsman.}
“Ah,” Black hummed. “She’s that kind of an opponent, then.”
“It’s kind of hateful how good she is at this,” I admitted.
“I’ve had Grem One-Eye under my command for twenty years, Catherine,” he told me dryly. “I can certainly empathize with the feeling.”
That was a pretty jarring admission, coming from a man I’d been told had once toppled the king of one of the Free Cities using only a rowboat, a donkey and a pair of broken shovels. There were stories about Marshall One-Eye too, of course – the Wall had stood firm against the greenskin clans for centuries before he’d somehow managed to take all three of the forts the same night – but they were nothing compared to the outrageous ones they told about the Black Knight. He smiled at me, once again managing to read me like a book despite my best efforts.
“There’s always someone better,” he said. “Nonetheless, in your particular situation there’s one thing that should do the trick.”
I raised an eyebrow, not savouring the suspense as much as he clearly was.
“Are you going to do that thing where you give me cryptic advice that later comes in useful at a critical moment?” I asked, trying to convey how irritating that particular habit was through my tone.
Black took a sip from his cup, though not quickly enough to hide that he’d actually been a little offended by that. I tried not to be openly amused, though not very hard.
“Well not \textit{now}, I’m not,” he muttered. “Fine, you killjoy. Here’s your advice: cheat.”
I eyed him sceptically from across the table.
“So who do I talk to, to trade you in for a better mentor?” I asked.
“There’s no attributed Imperial bureau for uppity Squires, unfortunately,” he sneered at me.
I grinned, smothering a laugh, and even the cold fish that was my teacher deigned to offer a smile to the world.
“So,” I said after a moment. “Cheating, huh. I don’t suppose you’d care to elaborate on that?”
“War games are, ultimately, still games,” he murmured over the rim of his cup. “You’re still trying to win according to the rules, when you should be trying to win despite them.”
I leaned back into my comfortable seat, letting myself enjoy the warmth of the fire and the bellyful of wine as I closed my eyes. The both of us let silence fall over the room as we descended into our own thoughts. \textit{How do you beat someone you can’t beat? }I asked myself\textit{. }My teacher had long left the room when I felt a savage smile stretch my lips. There was a way, maybe. It was underhanded and unfair, not to mention a little immoral around the edges, but then I was a villain wasn’t I?
I supposed it was about time I started acting like one.
\clearpage
\chapter{Chapter 23: Morok’s Plan}

“\textit{Trust is the victory of sentiment over reason.”}
-Extract from the personal memoirs of Dread Emperor Terribilis II

\textit{The High Lord of Kahtan was a skilled general, Black was willing to admit.}
\textit{It was unfortunate those skills were being used against him but expecting fairness of the world was to pave a road towards bitterness. The Taghreb aristocrat had learned the correct lesson from the Burning Cliffs: he’d avoided the narrow passes west of Okoro, taking Chancellor’s army through the flat expanse of Jugomo’s Folly instead. There would be no drowning the superior forces in goblinfire this time, not that he’d expected the trick to work twice. That was fine. Another three clans had been come over to their side in the aftermath of the last victory, bringing them up to a little under four thousand soldiers. Though ‘soldiers’ was a generous term to use for the newly arrived orcs, truth be told. Unlike Grem’s Howling Wolves and Istrid’s Red Shields there was little discipline to these fresh arrivals. Grem had told him in private they’d been on the losing side of the constant raids between the Clans. By throwing their lot in with Dread Empress Malicia they thought to better their fortunes. They might just accomplish that, should this day not end in crushing defeat.}

“\textit{I have them,” Warlock laughed suddenly. “A Wolofite warding scheme, really? Nobody’s bothered to use those since the Second Crusade. All blood and no finesse.”}

\textit{Wekesa had half a dozen water bowls placed in a loose circle around him, the candles in between casting shaky light on the images that had appeared over the surface of the liquid. Black allowed a sharp smile to flicker across his face. High Lord Mawasi might have been a vigilant man, but his mages were subpar. That would come back to haunt him. Istrid crouched by one of the bowls, ignoring Warlock’s warning look, and squinted at the shapes inside.}

“\textit{You were right, Grem,” she grunted. “They split in four.”}

\textit{One-Eye showed no sign of surprise. Black had yet to see the orc’s tactical judgement fail and doubted he ever would.}

“\textit{Mawasi wants to be able to concentrate his forces easily when they make contact,” he gravelled. “If they manage it, we’ll lose.”}

\textit{Chancellor had sent twelve thousand killers into the Steppes to end what the nobility had taken to calling the Whore’s Rebellion. Not that Malicia was actually with them: she’d gone to Thalassina to talk the ruling High Lady into supporting them. }

“\textit{None of the commanders will be willing to commit to a real fight until the others are there,” Ranker murmured, her slight shape stirring in the shadows. Even young as the goblin was, her face was already creased. “The High Lord will have forbidden it.”}

\textit{Black knuckled an old denarii with Dread Empress Vindictive’s face on it, allowing the silver to spin between his fingers.}

“\textit{They will,” the green-eyed man said calmly. “Chancellor made a mistake, when he put a price on my head.”}

\textit{Whoever killed the Black Knight would be granted gold enough for a dozen kings as well as a noble title, such was the word out of Ater. The kind of price men would kill for. The kind of price men would die for – and Black fully intended to see this done.}

“\textit{We start with the eastern division,” he told the others.}

\textit{One-Eye frowned. “You want to bait them. With what?”}

\textit{Black finished spinning the coin with a theatrical flick of the wrist, snatching away the silver.}

“\textit{What they want most, right now,” he replied. “My head.”}

I woke up in Rat Company’s dormitory with a gasp.
The dream had been weaker that the last, the connection not as deep: the ghostly sensations I’d felt in the wake of the other time were missing. Was it because I’d accidentally weakened my Name, or had it always been supposed to be this way? Not for the first time, I wished Black wasn’t so tight-lipped on the subject of Roles. He’d already taught me plenty on the history of Praesi Names and even a few tricks about putting heroes down, but when it came to my own Name he remained frustratingly vague. No doubt there was a reason for it, but that didn’t make it any less irritating. The dreams were meant to teach me lessons, that much I’d divined on my own. Drawing from the experiences of my predecessor, it showed his victories so that I could emulate the ways that had worked and avoid those that hadn’t. \textit{So what was this one meant to teach me?} Defeat in detail, but I’d already known that was the only way I could win the melee. That Warlock could break through scrying wards was an interesting tidbit I’d have to ask Lieutenant Kilian about, but I had a feeling it was related to his Name: it was dubious at best my own mages would be able to replicate the feat. 

\textit{My head}, Black had said. That was where the memory had ended. He’d used the greed of his opponents to bait them into making an ill-advised move. While I’d never gone over the battle with my teacher as we’d done for some others, it was one of the most famous engagements of the civil war: the Battle of the Four Defeats was in every history book that covered the time period, often mentioned as the point where the war started to turn in Dread Empress Malicia’s favour. So how could I apply this to my situation?\textit{ }I pushed my covers aside and sat up in the cot, surrounded by still-sleeping cadets. Dawn had yet to rise. My mind was still sleep-addled and slow, and as I rubbed my eyes I came to the conclusion that this was\textit{ n}ot something I was going to figure until I was more than half-awake.

I slipped out of the bunk and picked up the pair of trousers I’d lazily dropped next to it last night. Not folding my clothes and neatly sliding them in the exact space assigned for them was technically against Legion regulations, but who was going to report me? Every company had two dorms assigned, one for each gender. Which dorm you got changed according to your ranking, meaning that instead of beds and a nice view Rat Company got cots and a former warehouse that still smelled vaguely like olive oil. The part for women was the same size as the one for men, though it wasn’t full. A cursory look at the company’s rolls had told me that about four in ten of my soldiers were women, which was actually slightly under the average for the College. Forcing myself awake, I ran a hand along the ugly red scar that the Lone Swordsman had left me. The skin was strangely sensitive, and sometimes it felt like if I exerted myself too much it would open up again. Sighing, I picked up a roll of cloth and bound my chest. Slipping on a loose cloth shirt over it, I left the dorms before I could wake up anyone. My legionaries would need their sleep.

There was a well in the plaza just outside, easy to make out even in the half-light preceding dawn. Someone was already using it, to my surprise. A half-naked Ratface pulled up the bucket and splashed his face with water as I approached. He turned when I got close, nodding a silent greeting to me.

“Do you mind?” I asked, pointing at the bucket and scrupulously not looking at his muscled chest.

\textit{It would be inappropriate to ogle one of my subordinates}, I reminded myself. \textit{Even if it’s very easy to imagine rivulets of water running down to…} 

“Go ahead,” he replied after flicking the water off his shoulders.

I sharply put the thoughts aside, rinsing my face as I got back my bearings. 

“I got word from my friends,” the lieutenant said as he sat on the edge of the well. “We’ve got the munitions ready for the swap.”

“Good,” I grunted back. “Did Snatcher finally pick his load?”

There were two official munition templates for a company as taught in the College. The first was commonly known as “Siege”, heavy on sharpers and demolition charges. Aisha had claimed one within hours of the melee was announced. The second was called “Field” and was broader in scope, though it had a proportionally large amount of smokers. Hakram had informed me that several manoeuvres were taught in the classroom related to their use, but I hadn’t had the time to look into them. Both Juniper and Morok had gone that route.

“Yeah. He didn’t use one of the templates, though,” Ratface replied. “Brightsticks and demolition charges, mostly, though there’s a few smokers as well. He’s up to something.”

“He’s a goblin,” I murmured. “They’re always up to something.”

He shot me an amused look but said nothing. Silence reigned for a few moments and it was starting to get awkward when I cleared my throat.

“I have a question,” I said. “It’s a little personal, though, so feel free to tell me to bugger off it you want.”

The Taghreb boy raised an eyebrow.

“I’m all ears,” he said.

“Why Ratface?” I asked. “I know you get to pick the name you enrol under, but it seems a little…”

“Insulting?” he replied with faint smile. “That’s the point.”

The lieutenant let out a long breath.

“It’s not like half the College doesn’t know the story already,” he finally spoke. “I”m a bastard, Callow.”

I opened my mouth, but he turned sharp eyes in my direction.

“I’ve already heard all the jokes, so spare me,” he said.

“No idea what you’re talking about,” I lied.

Ratface rolled his eyes, not seeming all that offended.

“My father’s one of the lords sworn to Kahtan. Old family, one of the tribes from before the Miezans,” he continued. “He married late and slept around before he did – hence my existence.”

I grimaced. With a beginning like that it was hard to imagine the story ending well.

“I had a pretty easy childhood, all things considered,” he mused. “Not like I ever lacked for anything. But eventually Father married and spawned a legitimate heir.”

“And that put you in an awkward position,” I murmured.

“My half-sister is ten. Sweet girl, spends a lot of time braiding her pet goat,” he shrugged. “I don’t blame her for any of this. Father eventually decided to simplify the line of succession and one night I woke up to a knife in my back.”

He half-turned, showing me a short crescent mark just a few inches away from his spine.

“The soldier botched the job,” he grimaced. “And panicked when I woke up. I managed to get away, stole enough from the vault to buy my way into a caravan and pay for my first year of tuition here.”

It would have been indiscreet to ask how he’d paid for the other years, so I held my tongue.

“Doesn’t explain why you picked Ratface, though,” I pointed out.

The Taghreb smiled coldly.

“I’m told I’m the spitting image of my father at the same age,” he replied.

I laughed and he cracked a much warmer smile.

“Come on, Callow,” he said. “Let’s grab something to eat. Only a few hours left until they want us ready for the game, and I’m not marching to wherever the Hells we’re going on an empty stomach.”

I stood in the middle of a rocky plain with no recollection of how I’d gotten there.

Dusk was already beginning to darken the sky. Behind me Rat Company was spread out in a marching column – I could see the tracks indicating we’d walked here, but I couldn’t remember actually doing it. To the west the rocks rose in a slope and led into a canyon I could barely make out. There was a forest of tall dragon trees and ferns to the north, getting progressively thicker. The east was closer to what I’d been told to expect of the Wasteland, badlands of silt and shale forming tall rocky outcroppings that cut my line of sight. I felt a little woozy and there was a small cut on the palm of my hand, already mostly healed: I got a strange sensation from it, like a bee buzzing in the back of my head. I took me a moment to recognize the feeling. \textit{Blood magic}. I swore under my breath. \textit{So someone fucked with my memories.} I strode over to my legionaries who were still standing around with blank expressions, though by the time I got close some of them were already snapping out of it. I picked out Hakram near the head of the column – he was still in a trance, so I slapped him across the face. His eyes snapped back into focus and he let out a bestial snarl, the rage only leaving his expression when he realized I was the one standing in front of him.

“Callow?” he gravelled. “Where are we?”

“I have no idea,” I admitted. “Do you remember how we got here?”

The tall orc frowned. “No,” he replied. “And this thing is itching like you wouldn’t believe.”

He showed me his forearm, where a small cut had also been made. Not only me, then.

“Last thing I remember is…” he trailed off.

I forced my mind to focus. “When we shed blood on the tablet,” I finished.

The College instructors had us assemble in front of a large stone tablet, a different one for every company, and drip a few drops of blood on it. The Headmistress had mentioned it was intended to recreate the fog of war, though she hadn’t elaborated. After that it was a blank until just now.

“They sealed our memories,” I grunted. “So we don’t know where we are or where the other companies are starting from.”

“Not entirely true,” a voice intervened softly.

Lieutenant Pickler walked up to us, stride unhurried. In her hand she held a rolled up leather scroll with a broken seal. I picked out crossed swords that were the emblem of the College on the wax pieces, something I shouldn’t have been able to do in the gloom. \textit{Ah, getting the sight back}. About time my Name started making itself useful again.

“Map?” I asked bluntly.

Pickled nodded. “Our starting position is marked, though only ours.”

I accepted the offered scroll and took a look at the inked map. We were in the southernmost part of the area, it seemed. A few miles of flat ground behind us, with the canyon I’d glimpsed earlier snaking its way in an arc towards the northern end. The forest extended for longer than I would have guessed, though eventually it led into another wide plain. The badlands apparently covered the entire eastern half of our battlefield, a labyrinth of hills and depressions. \textit{If one of the companies isn’t setting up fortifications somewhere in there as of this moment, I’ll eat my helmet.} Hakram leaned over my shoulder to take a look with almost insulting ease. Hadn’t one of the Empresses outlawed being taller than her? Maybe it was time to start looking into that.

“We have the worst starting position,” my sergeant assessed bluntly.

He was right. No terrain to fortify unless we marched somewhere else in the dark, which would leave us exhausted tomorrow. Any company with a scout on higher ground would be able to find us within moments, and with the way goblins saw in the dark even nightfall wouldn’t be enough to cover us. \textit{This doesn’t feel like a coincidence}, I grimaced. Could Heiress have meddled with the position I was assigned? I couldn’t remember the process at the moment, so it was hard to tell. \textit{Doesn’t matter. Can’t change the facts now.} It was impossible for me to implement the deals I’d made where we currently were, regardless, which meant we’d have to march past nightfall. \textit{Close to the forest. }

“Lieutenant Pickler, prepare a scouting tenth,” I ordered. “We’re going north as quickly as we can.”

Surprise flickered across the smooth-skinned goblin’s face, but her amber eyes remained calm. She saluted and went to attend her troops. Hakram waited until she was gone before clearing his throat.

“Is that wise?” he asked. “We’re carrying enough \textit{sudis} to make a fortified camp here. If we carry them through a forced march we’ll be slower tomorrow.”

The pair of large wooden stakes carried by every one of my legionaries would start weighing heavy on them after a day’s march, well-drilled or not. He was correct in that. But we couldn’t afford to be where we currently were when dawn came. I took off my helmet and passed a hand through my hair, the pony tail it was kept in unpleasantly soaked with sweat.

“We need to meet up with Morok as quickly as possible,” I told him. “Any company but Snatcher’s catches us on an open plain and we’re done for.”

“You sure we can trust him?” my sergeant gravelled. “He’s Blackspear Clan, Callow. They’ve never made a pact they didn’t break.”

“I wouldn’t trust him with a handful of coppers, Hakram,” I admitted. “But I’ve got a decent read on what he wants right now. Not sure I can answer for what he’ll be thinking in two days, though.”

That was my largest problem at the moment: what I’d planned was time-sensitive. Black had once told me that the great weakness of plans with several stages was the difficulty of getting the timing right. Miss the window of opportunity for one stage due to unexpected complications and the whole thing would come tumbling down. Usually on your head, with the way villain’s luck went. \textit{Better to use several small schemes to stack the odds than a single complicated one giving you a marginal chance at victory}, he’d said. Unfortunately, I couldn’t afford to play the game that way. The odds were stacked against us too badly for a handful of quick tricks to be able to see the company through the fights. I needed to move quickly enough that the circumstances I’d made my pacts in hadn’t changed, because if they did then this was going to turn into an actual melee and Rat Company was basically fucked.

“Get our line moving, Sergeant, we’re taking the lead,” I ordered. “Double-time. If we want to win this, we’re going to have to pay the long price for it.”

He frowned. “Long price?”

I blinked in surprise. \textit{Would have thought that one made it across the border. }

“Callowan expression,” I explained. “A long price is one you have to keep paying for. People use it to mean paying unpleasant dues.”

“Long price, huh,” he grunted thoughtfully. “Well it’ll be a long night, I’ll give you that.”

Our pace was slower than I would have liked, and became slower still when night fell.

Hakram kept my line steady while we moved forward in the marching order I’d let him organize. He’d used what was apparently the standard for Legion expeditions in hostile territory: regulars in the front, sappers and mages in the middle, then a line of regulars in the back again. The line behind the second regulars, Nauk’s, was a little different. They were called heavies: their armour was plate rather than chain mail, and their shields much thicker. I’d taken the time yesterday to inquire what the companies we were up against had in their roster, and been left rather troubled by the answers. 

Snatcher’s Fox Company was in some ways the least dangerous, as almost half of his forces were goblins. Shield wall against shield wall even my soldiers would wreck them. But he had the highest concentration of crossbowmen in the College, and his legionaries always fought from behind fortifications. Aisha and her Wolf Company had borrowed from old Taghreb tactics, putting mobility above all else. They had no heavies at all, but they’d pulled off outrageous victories by hitting the opponent out of nowhere. Lately she’d been drilling her soldiers in siege tactics, determined to take third place in the rankings from Snatcher. 

If the Wolves were all about swiftness, then Lizard Company was about brutal, unrelenting might. Morok’s entire force, save for a tenth of mages, was made of heavies. He had no legionaries formally trained as sappers, which would have made assaulting fortified positions hard if not for his trump card: he had a tenth of ogres. Fifteen feet tall and clad in a small mountain of steel, they were living battering rams that used massive war hammers. First Company was an all-rounder, the traditional company composition for the College. A line of sappers, a line of mages, two of regulars and one of heavies. 

The same as us, except they’d won every battle they’d been in instead of accumulate defeats like Rat Company. Ratface had outright admitted to me that he’d modelled the Rats after Juniper’s company, hoping to recapture some of her success. Doomed to failure, that.\textit{ It works for Juniper because she’s at her most effective when she has a broad toolbox: she uses different lines to solve different problems. But unless you have someone like Juniper giving the orders, all you have is a company with no real strong point. No weak one, either, but that’s not enough to beat an opponent that knows what they’re doing.}

It was hard to tell how long it took us to make it close to the woods. Several hours, at least but how far past midnight we were I had no idea. Robber spent most of the march scuttling about with our scouts, regularly checking in to tell me there was no sign of anyone else. Perhaps the only saving grace of our starting position was that it would be next to impossible for any of the other captains to ambush us. Plenty of ground to see them coming, and while Robber’s tenth was not meant to be a scouting one they’d been used for that purpose often enough to pick up the basics. I had us halt in sight of the canyon’s entrance, near the beginning of the forest. My legionaries dropped their packs to the ground with vocal relief. The break was a short one, though. I had my senior officers in council within moments.

“We should back further away from the canyon,” Ratface opened bluntly. “Or else go entirely into it.”

“Not inside,” Pickler immediately replied. “I could bring that thing down on our heads with an hour’s work, and so could most of the other companies. We \textit{should} move, though. Too easy to sneak up on us here.”

“Callow ain’t an idiot,” Nauk grunted. “You got a reason for this, Cap?”

Pickler graced him with a surprised look, apparently unused to disagreement from the large orc.

“We’re staying here,” I spoke flatly. “This isn’t a mistake, I chose this place specifically.”

Hakram eyed me carefully.

“We’re baiting someone,” he guessed.

I nodded. “We’re waiting on Morok before moving out, so we’ll make camp here. Half-watches for the night. That aside, Kilian, how far up can you shoot a fireball?”

The redhead blinked in surprise. Every mage cadet had to be able to cast two spells by the end of their first year: basic field healing and a standardized fireball. Those that couldn’t were forced to drop the mage curriculum and repurpose as regulars. Older years learned more advanced healing, a few different offensive spells and the most talented were even taught to scry, but those two basic spells were the bread and butter of cadet magery.

“That depends,” she replied after a moment. “If I tweak the incantation to strengthen momentum over power I might be able to manage five hundred feet. Wouldn’t even drop a bird, though – it’d be more warm air and light than fire by that point.”

“I’d still look like a fireball, right?” I confirmed.

She nodded.

“Good,” I grunted. “Send up three in a row.”

There was a moment of utter silence.

“Captain,” Ratface started slowly, “with all due respect, that…”

“Every other company will know exactly where we are,” Pickler finished.

Nauk barked out a laugh. “Now that’s one way to start the party,” he growled. “I like it. Come at us, you fuckers. See what happens.”

“What will happen is we’ll lose,” Pickler hissed at him. “She bid eighty-four points – we screw this up and Rat Company will be in the red for the next eight years. What do you think that will do for our careers? I’m not getting posted in Thalassina with the Thirteenth to break up bickering merchants.”

I took a deep breath, determined not to lose my temper.

“\textit{Enough},” I Spoke, and they went still as statues. “This isn’t the Highest Assembly, and you aren’t Proceran princes. If I give an order it will \textit{damn well be obeyed}.”

I stared them down.

“Do you understand me?”

Whatever was holding them by the throat let go and I received a handful of shaky nods. Kilian eyed me warily – she was probably the only one with enough arcane education to understand how I’d managed this.

“I know exactly who’s coming,” I told them. “I’ve planned for it. We’re all tired and tempers are rough, but if we start arguing about everything we’re as good as done.”

“You’re the captain,” Ratface murmured.

They saluted and all went to attend their lines except for Kilian, who stepped a few feet away and started muttering under her breath. She snapped a hand upwards and a ball of bright red flame went sailing up in the air. It was hard to judge if it had really gone up to five hundred feet, but it’d clearly be visible from everywhere in the area. Another two followed quickly. After a moment, a single ball of blue flame rose in the distance.

“The canyon,” I muttered to myself. 

So that was where Morok was. I’d yet to hear Hakram leave, so I wasn’t surprised when he cleared his throat.

“You’re playing your cards pretty close to the chest, Callow,” he gravelled.

What little I had of it, anyway.

“I had a dream, this morning,” I told him instead of a true reply.

The orc shot me a quizzical look.

“So?”

“It was trying to teach me a lesson,” I mused. “I think I might be getting it, now.”

“Anything useful?” he asked curiously.

“If we’re to win this,” I said, “it won’t be by playing the game. It’s the players I need to play.”

“I take it that made sense in your head,” he snorted, flashing me his fangs in a small smile.

“Something like that,” I agreed. “Before you get to work, I need you to tell two things to Lieutenant Pickler.”

He leaned in close.

I only managed to grab a few hours of sleep before dawn came. Rat Company had formed a square of jutting spikes around its camp, sharp end outwards. There was a large entrance facing the canyon for quick deployment and two smaller ones on the adjacent sides. I’d somehow managed to miss a rock under my bedroll and it had dug into my back the whole time, so it was with a bruised back that I put my armour back on after Robber woke me.

“They’re here,” he told me, biting into a piece of jerky.

“The entire company?” I asked, tightening my sword belt.

“That’s my guess,” he replied. “They’re not deployed in a way that makes it easy to count them.”

I nodded, and to my mild irritation he lingered.

“We’re playing with fire, aren’t we?” he grinned. “Knew you’d make this interesting.”

“Don’t you have things to do, Sergeant?” I grunted.

“Eh, nothing urgent,” he dismissed. “Pickler’s sorry, by the way.”

That got my attention. I glanced at him and for once his face was lacking the usual malicious grin.

“She’s not the kind of person who apologizes,” he continued, “but she knows she stepped out of line. After you made us bury the stuff, she got the same look on her face she usually makes when she screws up a weapon design.”

I passed a hand through my hair, putting the pony tail into a semblance of order.

“I know I’m asking the company to take a lot on faith,” I finally said. “I’m not going to hold grudges over a moment of doubt, as long as it doesn’t happen again.”

“Must be that soft Callowan upbringing that makes you so forgiving. No wonder you lot got conquered,” the little shit grinned. “I’ll pass the message along.”

I flipped him the finger and he scuttled off after a horribly sloppy salute. Inexplicably, I was now in a better mood. In the distance I could see Lizard Company kicking up a trail of dust as they marched out from the canyon. I noted with approval that, now that Morok was less than half a mile away, all my legionaries were up. The last ones to wake were hurrying to put on their armour. I fished out some dried and salted meat from my pack, taking a bite with distaste. \textit{Goat jerky. Ugh. }I left my shield with my cot, strolling towards the middle of the camp: there was slight rise there, and I claimed a flat rock for my throne. Eventually Ratface made his way to me. Without a word, he offered me a water skin: after last night’s confrontation, it felt like something a peace offering. I took it without comment and gulped down some tepid water. We let a long while pass in silence, my soldiers slowly assembling in ranks as Morok’s company marched towards us. In the light of day, it was easier to make out our surroundings. We were a little closer to the forest than I would have liked, though it was too late to do anything about it now. Ratface eyed Lizard Company’s ranks as they came closer, his face settling into a frown.

“He’s got his ogre tenth right behind his first line,” he spoke with a frown. “That’s not standard practice.”

I handed him back his water skin.

“No, it isn’t,” I agreed.

Two hundred feet away Lizard Company paused, its lizard skull standard coming up to the front. And then, without so much as a sound of warning, they charged forward. A stir went through my soldiers, a few of them cursing out loud.

“The fucker’s betraying us,” Ratface bit out. “On the \textit{first day}? Who even does that?”

“He got this look on his face, when I threatened to hand our munitions over to Juniper,” I informed the lieutenant absent-mindedly. “Tried to hide it, but I’ve been dealing with tricky sorts lately. He was thinking about what he could do if he had them.”

Kilian’s line was standing in front of the entrance about to get charged, her ten mages standing behind the ten soldiers with the oversized shield that served as their mobile cover. 

“You’re being very calm about this,” Ratface accused.

Less than a hundred yards now. 

“I’d be hypocritical of me to get angry about him betraying us,” I mused.

I tore off a chunk of jerky and swallowed it. Fifty yards. Too late for Morok to pull out.

“After all,” I continued, “I betrayed him first.”

The moment before the vanguard of Lizard Company stepped foot into our camp, a hundred voices howling like wolves sounded from the woods. Armour shining bright in the morning sun, Wolf Company charged out of cover right into Morok’s flank.
\clearpage
\chapter{Chapter 24: Aisha’s Plan}

“\textit{Grand designs in war are a thing of vanity. Victory goes to the general that blunders the least.”}
– Theodosius the Unconquered, Tyrant of Helike

I’d known from the beginning that the ogres would be the biggest problem. No pun intended. I rather loathed puns, actually. The main two military treatises I’d sunk my teeth into were the \textit{Ars Tactica} and the \textit{Praecepta Militaria}, though the smaller\textit{ Commentaries on the Campaigns of Dread Emperor Terribilis the Second} had been a lot more interesting – and useful – to read. None of the three went into how to deal with a tenth of heavily armoured ogres, though. Good ol’ Terribilis had subdued a band of giants when dismantling the crusader kingdoms, but unlike him I couldn’t afford to put a small city to the flame and shoot anything that crawled out. 

I’d asked Black to find me some of the manuals used under the Kingdom of Callow, but he’d told me that there was no equivalent to the War College in my homeland. Nobles who’d wanted their children to have a military education either had them join a chivalric order or serve in the Order of the White Hand for a few years. Given that the Order had been wiped out with remarkable thoroughness and that chivalric orders were now illegal in Callow, there would be no help coming from that front.

So I’d looked into Juniper’s old games. She’d beat Morok every time they fought, after all, and while Rat Company wouldn’t be anywhere as smooth in executing her techniques we theoretically had the right tools to use them. In short, she outmanoeuvred the tenth. She’d systematically baited Morok into grounds she’d prepared to turn the size of the ogres into a disadvantage or outright mined them with demolition charges. With the tenth dispersed or knocked down, she had her mage line concentrate fire on individuals until they were down for the count. The fact that the Hellhound had never used sharpers on the ogres indicated they probably wouldn’t be effective, something I’d taken heed of. 

That was one of the two reasons that, officially speaking, Rat Company had gone with the Siege template. Morok had been until recently under the impression that his betrayal would come as a surprise to me. \textit{So he won’t be expecting the main entrance to be mined.} That the other munitions we could supposedly bring to bear against him would be ineffective had just been additional bait for him to betray us. The second reason was how I’d managed to have the hundred Wolf Company legionaries running down the hill to flank Lizards. Going with Siege was as good as declaring my intention to go after Snatcher and his fortifications – which had been one of the main conditions Bishara had extracted in exchange for her help against Morok. The other condition was much more costly, but I wouldn’t have to worry about that for a while yet.

“Ratface,” I spoke. “Go back to your line. Things are about to get interesting.”

The Taghreb lieutenant nodded and picked up his shield before leaving, rolling his shoulder to stretch it out. My eyes remained on the skirmish. I’d had Pickler bury demolition charges under the entrance Morok had his company charging through. Though I’d been worried he’s send more expendable troops in first after being burned by Juniper in a similar manner – as he was currently doing with a forward tenth of heavies – she’d told me it wouldn’t be an issue. She’d fiddled with the triggers so that they wouldn’t blow unless a large enough weight pressed down on them: unless she’d made a mistake, the charges should ignore the first ten heavies entirely. With a frown I watched the ten heavily armoured legionaries slow as they got to the entrance, sheathe their swords and reach for- I got to my feet.

“KILIAN,” I yelled out. “FIRE, NOW!”

I saw the redheaded lieutenant glance in my direction, my voice managing to carry over even from where I stood, but by the time she started incanting it was too late. Morok’s heavies sent sharpers rolling over the mined grounds, the clay balls detonating a moment later and triggering our demolition charges. \textit{Fuck.} Ten fireballs sailed right into the ensuing cloud of dust and rock in a mocking aftermath: it was impossible to tell if they’d hit anything. More importantly, the ogre tenth had a free path right into my mages. Aside from my sappers they by far my most vulnerable line. \textit{And if the healers get taken out there’s no one to get my wounded back on their feet.}

“Captain,” a voice came from behind me. “Orders?”

Hakram and the rest our line had come to stand behind me while I was distracted. The tall orc looked unworried even though our first line of defence had just disappeared into literal smoke. His calm soothed my own nerves and I took a deep breath.

“Have Pickler drown the gap in smokers,” I ordered after a heartbeat. “Are Ratface and Nauk in position?”

Getting my legionaries in fighting order without them looking like they were in fighting order had been a tricky proposition. I had Ratface’s line to the left of the main entrance and Nauk’s to the right, hopefully read to close like a jaw on the first men of Lizard Company to pass through. Kilian and her mages were right in front of the enemy, with Pickler’s line close behind them. My own men I’d held back as a reserve to plug gaps or use a possible flanking force, should an opportunity present itself.

“They’re ready,” my sergeant gravelled after sending off a messenger to Pickler.

In the distance I saw the forward heavies charge out of the smoke, unharmed. Godsdamnit, couldn’t Kilian have taken out at least one?

“Have them form a wedge with the point facing us,” I ordered. “Quick.”

That should leave a broad enough kill zone that Kilian’s mages could do damage by continuously pouring flames into the melee. A dozen smokers fell into the gap just as I finished speaking, obscuring the visibility that had just begun to clear. Looking outside the boundaries of my own camp just as Morok’s heavies rammed themselves into Ratface’s line, I saw that Aisha’s men were finally about to hit Lizard Company’s left flank. Mages in the back of her company threw fireballs into the enemy a heartbeat before the lines made contact, Wolf Company’s regulars pouring into the gaps the impacts created to pry open the formation. 

Morok was redeploying his company to secure his left, a line hurriedly moving to extend the flank so that Aisha couldn’t just encircle him. \textit{Come on, you ugly bastard. You know if Aisha manages to go around that you’re done. Sent the ogres in to make a dent in her troops. }The ogres emerged from the smoke, hammers held high. I closed my eyes. What was his play here? He wasn’t committing enough men to do more than hold Wolf Company for a few moments. So he was pushing straight into us. Why? He was an asshole, not an idiot. He wouldn’t go for vengeance in the middle of a melee. 

“He wants the camp, Captain,” Hakram suddenly said. “He’s trying to push us out and use the fortifications to hold off Wolf Company.”

I opened my eyes.

“Ready our line,” I grimaced. “If it goes sour for them, we’re going in.”

Already Ratface’s line was having trouble dealing with the tenth of heavies: they weren’t losing ground, but they weren’t pushing them back either. A flurry of fireballs hit the ogres as they strode forward, but it barely slowed them – Kilian hand’t though to concentrate on a single target. The flames slid off the plate and then the ogres impacted into Nauk’s heavies. \textit{Oh, Weeping Heavens.} Back at the orphanage, I’d once seen a girl drop a heated plate on a block of butter. Seeing the ogres crumple the first rank of heavies with the initial swing was eerily reminiscent of that. Shields broke, legionaries fell and the only reason they were stopped was because the second rank heavies got in close. I saw Nauk take a swing straight in the shield arm and though I couldn’t actually hear the bones break from where I stood my imagination provided a vivid approximate. The lieutenant fell to the ground, dropping his shield, but that was when things got… weird. The large orc spasmed once, then twice, and I heard Hakram breathe in sharply.

“Sergeant,” I began, “what’s-”

Nauk let out a blood curling scream and rose to his feet. I’d once seen him take on two legionaries with his bare hands but there’d been a degree of control to him back then, for all his roaring. There was no trace of that now. He jumped on the back of the ogre who’d struck him, abandoning his weapon, and started hammering into the legionary’s helmet with his bare hands. The first strike saw the hands turn into a bloodied mess and it got worse from there.

“What the actual fuck,” I said in a faint tone.

“You ever wonder why Nauk was never in the running for captain?” Hakram said quietly. “That’s why. He’s got the Red Rage.”

“He’s a berserker?” I asked. 

My sergeant shook his head. “Berserkers can… well, not control it but direct it at least. He can’t. He’ll keep fighting everything until he drops, friend or foe.”

As if to drive the point home Nauk’s armoured boot impacted with the face of one of his own soldiers, sending him sprawling. His line was on the verge of collapse and already more heavies were nearing the camp, aiming to reinforce the tenth locking down my left flank. 

“We performed a lot better against Juniper’s soldiers,” I frowned. “Ratface shouldn’t be doing this badly.”

“They’re not underestimating us anymore, Captain,” Hakram gravelled. “You took the fort with even numbers, last game. People took notice. They’re taking us seriously now.”

“Balls,” I said, feelingly. “Damage control time. We’re going to back up Nauk.”

The greenskin sergeant barked out orders and we set to a brisk walk. Pickler’s line parted for us silently and I allowed my line to pull a little ahead as I stopped for a word with the lieutenant.

“Captain,” the goblin grimaced. “I should have taken sharpers into consideration. This is my mistake.”

“We can do the blame game after this is done,” I grunted back. “Pull out all the stops, Pickler. I want brightsticks and sharpers in the lot of them as soon as they fill the wedge. Wait for my signal.”

She nodded. I felt Robber sneaking behind me before I saw him, turning to fix the diminutive goblin with a steady look. He threw me a sharper and I caught the clay ball with my free hand, raising an eyebrow.

“If you get one under the armour they’ll take one of the big guys out,” he grinned. “Go do your thing, Captain. I’m looking forward to the chaos.”

Of course he was. I was half-tempted to throw the thing right at his head, but now was not the moment to be petulant. I put a spring to my step and caught up with my line just as they got to Nauk’s. I slipped my way through one of the gaps in the ranks right before my regulars filled it, heading straight for the nearest ogre. Was that lieutenant’s stripes I saw on the shoulder? As usual, luck was enjoying pissing all over my day. \textit{All right, Catherine. This is just like sparring with Captain, if she was half a dozen feet taller and intent on really beating me up.} The gargantuan mountain of steel moved in my direction, face impossible to see under the close plate helm. The ogre struck with vicious speed, hammer coming for my shoulder in the blink of an eye. Calmly, carefully, I took a half-step back out of range. My opponent slowed the swing, getting closer, and that was when I pushed forward. All in the timing, the way Black had taught me. I slipped inside my enemy’s guard and slapped the flat of my blade into the ogre’s helm. It bounced off with a sharp ring. 

\textit{Well, that was useless.} I danced around a kick that would have sent me sprawling, trying to get a hit in on the knee joint but being forced to back away by an awkward swing of the hammer. Given the size of the thing, even a weak hit would have enough weight to it to mess me up. My fingers tightened against the sharper Robber had given me as I tried to circle around the ogre, dodging another hammer stroke by the skin of my teeth. The malevolent little sergeant hadn’t given me anything to light it with, I suddenly realized. Not that I had a free hand to use even if he had. \textit{Robber, you asshole.} I snuck a look back at my line and saw they were somehow managing to hold back the enemy advance, swarming the ogres with numbers and taking hard losses as they did. Ahead of me Kilian’s mages were holding off down enemy advance with a near-continuous stream of fireballs but Morok’s heavies were forming into a shield wall and when they managed that would be the end of that. Regulars wouldn’t be able to power through a sorcery barrage, but heavies certainly would.

My inattention was rewarded by the ogre’s hammer clipping my shoulder. It was a glancing hit at best, but it still spun me about like a leaf. I managed to stay on my feet but a moment later I got kicked in the chest. I fell on my knees and absently wished I hadn’t just eaten, because that jerky was doing its level best to resurface. \textit{Did I just feel the chain mail loosen?}

“All right,” I croaked out as I pushed myself back to my feet. “That’s enough.”

The ogre huffed out a metallic laugh. Snatching up the sharper I’d dropped after the kick, I ran in my opponent’s direction. \textit{Come on, these are pretty horrible odds. Doesn’t it count as a Struggle?} My Name stirred slightly, but there was no sudden influx of power. Fine, a trickle was all I needed anyway. Gritting my teeth, I watched the hammer rise and counted down. One, two, three steps and – there it went. Apparently done playing, the ogre swung down in a stroke that would have shattered my shoulders in several smaller and painful bone shards had it landed. Too slow, though. The hammer struck the ground a little to my right and I jumped onto the ogre’s chest, ramming the sharper into the joint between the neck and the shoulder. Hanging on for dear life I forcefully took hold of that small thread of power my Name had granted me, forcefully pushing it into my hand. My fingers crackled with pitch black energy and I punched the sharper as hard as I could.

This was, admittedly, not the most elegant plan I’d come up with.

The impact blew me clean off the ogre. I landed painfully in the dust, breath pushed out of my stomach and my ears ringing. I grinned when I felt the ground shake, opening my eyes to the sight of my toppled opponent. \textit{That’s going to be one nasty concussion, my friend, but that’s what healers are for.} I got to my feet and coughed out a bit of dust, taking a bleary look around. It seemed I’d landed somewhere around the wedge. I glanced to my left and my blood ran cold. I \textit{had} landed in the wedge, I realized. In the middle. Just before Morok’s heavies pushed in with their shield wall.

“That’s their Captain,” I heard a girl’s voice call out from the enemy ranks. “She’s on the priority target list.”

Rat Company replied by sending a volley of fireballs right into the shield wall, though they were noticeably less bright than they’d been at the beginning of the fight. My mages were getting tired. Spitting out a bit of stone stuck in my mouth, I wiped my lips and took a look at the rest of the fight. The ogre tenth was on its last legs, overwhelmed by numbers and the lack of back-up Kilian had managed to accomplish. Two of them were still fighting but my legionaries and Nauk’s were piling up on them so much they could hardly move. I just needed to distract the enemy long enough for them to be taken out.

“Gods, this feels unpleasantly heroic,” I muttered to myself.

I took a deep breath and limbered my fingers.

“CAPTAIN MOROK,” I called out. “COME OUT, YOU WRETCH. YOU AND ME, OUT HERE ON THE FIELD.”

There was a heartbeat of silence.

“She \textit{did }punch a sharper,” someone mused out loud. “That’d scramble anyone’s brains.”

I shot the Soninke boy in question an offended look.There was no need to get personal about this. I snuck another look at the melee to my left – one ogre remaining now, and it was in trouble. \textit{Come on, Morok. You’re one of the proud ones. You can still salvage how this looks by taking me out.}

“LIZARD COMPANY, FORWARD,” the captain in question barked.

And the bait had failed. Godsdamnit, I hated it when my enemies were competent. It made everything so complicated. I took a moment to look suitably defiant at the enemy before praying Pickler was close enough to hear me over the sound of the fighting.

“PICKLER, NOW,” I yelled.

For a moment nothing happened and I looked like a complete imbecile, standing in front of about thirty enemy heavies with my sword pointed forward. Then a dozen clay cylinders arced above me, coming to roll at the feet of Morok’s forward line. I closed my eyes right before the blinding light hit, turning a clean pair of heels to the enemy and getting the Hells out of there before they could run me down. By the time I’d gotten back to my line, the last ogre was down and Pickler’s sappers had tossed a round of sharpers into the enemy ranks. It made me wince to think that we’d wasted at least half of our munitions on what had been supposed to be our easiest battle, but there was no helping it. Lizard Company would not have been so high in the rankings if they were easy to deal with. I saw Hakram drag back an unconscious Nauk behind our lines and drop him none too gently, turning to salute me when he noticed my return.

“How are we doing, sergeant?” I panted out, sheathing my sword as I took cover behind my assembling men.

“Between the rest of the heavies and our own cadets capable of fighting, we make up most of a line,” he gravelled.

That barely qualified as good news, but I’d still take it. I pushed back a sweaty lock of hair that had slipped out from under my helmet.

“Send a messenger to Kilian,” I told my sergeant. “I want her tenth of shields sent to back up Ratface. We need to start pushing them out of camp.”

“I’ll see to it. But it might not even be necessary, Captain,” the tall orc grinned savagely. “Smoke’s clearing out. Look at what Bishara’s up to.”

I did. The handful of smokers I’d ordered thrown into the entrance at the beginning of the battle had finally started to disperse. Wolf Company had slipped around Morok’s extended flank with almost contemptuous ease, flipping an entire line and using the momentum to drive the other one right into the stakes surrounding my camp. Lizard Company had sent another tenth into the mess to try to salvage it, but it was already collapsing under the pressure. In a matter of moments the Wolves would be hitting the back of Morok’s heavies right as they tried pushing their way through my wedge. 

“There’s no way he can swing this,” I realized. “He needs to pull back or he’s out of the game.”

The conditions for the elimination of a company were very straightforward: either every officer in a company of lieutenant rank and above had to be incapacitated, or else eight soldiers out of ten in the company. Rat Company had, by the skin of its teeth, managed to take out a line. Aisha’s legionaries had done the same to another two lines and were getting started on a third. If Morok didn’t pull out now, the Lizards he risked elimination by numbers. Which was exactly my intention, actually. The number of prisoners and enemy wounded this skirmish would result in was so large that the manpower cost of keeping an eye on them would be crippling. We wouldn’t be able to move that many people quickly or easily, and we didn’t have a defendable stronghold where we could put them away. The Lizards needed to be broken here and now, or they’d leave a bloody mess for me to deal with.

Morok seemed to agreed with my assessment. His companu sounded the retreat, the tenth Ratface was still struggling with pulling out in good order. Immediately I ordered my own line to push forward, signalling for the former captain’s to do the same. The grounds were uneven where the demolition charges had been blown, but both lines formed in the best order they could. We held position at the mouth of the entrance as Wolf Company moved to complete their encirclement. \textit{Only a matter of time now.} There was a sudden flash of lightning from Aisha’s mage line and a bolt struck in the middle of the enemy’s formation. I couldn’t see who they’d hit and the effort seemed something of a waste, but a few heartbeats later thunder rumbled in the distance. Lizard Company’s standard appeared as a giant image in the sky, a red streak across it. \textit{Eliminated. She must have aimed for Morok.}

I raised my sword in victory, my company cheering behind me.

Clean up was as much work as the actual fighting.

Legionaries from both victorious companies were picking through the packs of the vanquished one, putting aside the goblin munitions in a great pile we’d distribute later. Aisha had agreed on splitting them half and half when we’d struck our deal, though it had taken a great deal of wheedling on my part. She’d given in in the end, though, since if the both of us were to assault Snatcher’s fortifications then I could hardly be expected to send my cadets into the breach with depleted stores. Mages from all companies were already at work on the wounded, the Rats and Wolves because we’d need to get moving before too long and the Lizards because they needed to be able to march to their pick up point before being escorted back to Ater. The mood was festive on the winning side, legionaries trading good-natured jibes and boasts as I finished taking casualty reports from my lieutenants. 

The butcher’s bill wasn’t as bad as it could have been: Ratface had played it out conservatively and barely had a handful of wounded to his name. Nauk’s line had been the most brutally hit and the orc lieutenant was still out of it. Sergeant Nilin was handling his duties until the healers managed to drag him back to consciousness. Overall there were twenty seven wounded among my men, the majority of which would be back on their feet after a session with our healers. The four that were more severely hurt were still able to march, though they wouldn’t be fighting again in the melee. \textit{That’s fine. It could have been worse, and} \textit{I can still use them for sentries. }I dismissed my officers when I saw Aisha strolling down the main entrance with a handful of her own legionaries escorting her. Ratface cast a long look in her direction before saluting and returning to his line. I only barely refrained from sighing. Now was not the time for the lieutenant to start mooning over the captain of Wolf Company.

“Captain Callow,” Aisha greeted me with a smile. “Well fought.”

I clasped the forearm she offered me. 

“You did most of the heavy lifting on this one,” I acknowledged. “All we did was hold the line.”

“Your inspired trick with the smokers hurt him more than you think,” the Taghreb captain assured me. “It was clever of you to keep him from concentrating his force with the smoke so the fireballs would be able to keep him away.”

I’d done what now? Ordering Pickler to throw the smokers in had been a knee-jerk reaction to Morok blowing the charges, not something I’d given a lot of thought to. I’d originally meant for Lizard Company to fill the wedge I’d made so that my sapper line’s munitions would have the greatest possible effect, though in retrospective I could see how that would have ended badly. If Morok had managed to bring that many troops inside my camp he would have broken through my lines for sure, and it would have been all downhill from there.

“I try,” I replied neutrally, doing my best to hide that my ‘tactical ingenuity’ was news to me. “How were casualties on your side?” 

“Light,” the olive-skinned girl noted. “We’ll be ready to march in a quarter bell.”

I grimaced.

“I’ll need at least twice that,” I replied. “My mages are running out of juice and the ogres did a number on my heavies.”

“They have a way of doing that,” Aisha said sympathetically. “Is that why I’m hearing chatter about you getting so angry you punched an ogre into unconsciousness?”

I closed my eyes and rubbed the bride of my nose, imploring the Heavens for patience. 

“That’s not what happened,” I told her, “I mean, I can understand it might have \textit{looked} like that from a distance but I used a sharper.”

The other captain patted me on the shoulder, dark eyes glittering with amusement.

“It’s all right, Callow, you don’t need to pretend with me,” she consoled me. “There were already rumours about your grudge against them, anyhow, what with you castrating one in single combat.”

“I used to think the girls at my orphanage were the worst gossips in the world,” I sighed, “but then I came to the College.”

The dark-haired girl snorted, though after a moment her face turned serious again.

“I became worried when you were late in giving me the signal,” she said. “What happened?”

“We had a bad starting position,” I grunted. “Middle of the plain to the south.”

Aisha raised an eyebrow.

“And you didn’t manage to get here before sundown? I thought Ratface drilled your cadets better than that.”

“\textit{Before} sundown?” I asked dubiously. “The sun was already setting when we snapped out of the blood magic.”

The Taghreb girl blinked in surprise.

“That’s strange. We were all awake around Afternoon Bell,” she told me.

\textit{Oh, fuck you Heiress. Seriously?}

“Must have been a mistake with the casting,” I grunted, unwilling to give a real explanation.

The other captain looked unconvinced, but she didn’t press the subject.

“Regardless,” Aisha spoke, “it gave me time to scout around thoroughly. First Company was on the plains on the other side of the forest yesterday, though where they are now is anyone’s guess. Morok seems to have started in the canyon, which means Fox Company is east of us.”

“In the badlands,” I grimaced. “Burning Hells. He’ll have fortified wherever he ended up to a ridiculous extent.”

“On one hand,” my temporary ally noted, “it means he won’t have been able to have cut many trees from the forest, if any. But he might have eschewed that entirely and built in rock instead, which would be… troublesome.”

“We need to find him before he ends up making an actual castle, then,” I grunted. “I’ll tell my mages to hurry it up.”

“That would be appreciated,” Aisha nodded. “I’ll have one of my lieutenants handle the distribution of the munitions.”

There was only so much magic Kilian’s minions were able to squeeze out in a day, unfortunately, and their earlier pyrotechnics had used up the lion’s share. Given how physically exhausting casting could be, I wouldn’t even be able to set a fast pace when we marched: after last night’s moonlit stroll and the morning’s fighting they would be physically incapable of moving that fast. I ended up remaining within the bounds of my original prediction of a half bell, though it was a close thing. The entire allied force took a turn towards the south east for the first leg of our journey, Wolf Company being well aware of how easy it would be to charge out of the woods into someone’s flanks after having done that exact thing. I put Ratface’s line in the lead this time and left Hakram to take care of mine, keeping a newly-awakened Nauk company instead. The large orc was sheepish about the entire Red Rage debacle and apologized at least twice before I dismissed the whole thing.

“Hakram told me it’s why you were never in the running for captain,” I told him.

“Can’t have the man in charge fly into rage every time he’s too badly injured,” Nauk grunted. “Been lucky enough to have Nilin with me since my first semester – he knows how to pick up the slack when I lose it.”

“Ratface is too conservative when he commands,” I noted, “and I can see why it might be a liability to have you in charge. Kilian and Pickler, though, why did they never step up?”

It would be a lie to say I hadn’t been appalled by how abysmal Rat Company’s score was. I had a hard time reconciling that with their performance in our first war games, though after the battle we’d just gone through I could see that one of the reasons my band of survivors had been so effective was that we’d been badly underestimated by the First Company. The fact that Ratface’s line of twenty regulars hadn’t managed to drive back a single tenth of heavies was a grim indicator of how my cadets would actually perform in a straight up fight.

“Kilian’s got some kind of condition from her creature blood,” Nauk told me. “Sometimes she draws too much magic and start speaking in tongues.”

Creature blood? Something to ask my sergeant about. Anyhow, that was already half of my senior officers who could find themselves incapacitated if things got a little too hot. \textit{No wonder they fold every time the other companies turn up the pressure..}

“Pickler?” I prompted.

The large orc looked uncomfortable, which would have been an amusing sight on his thick-skinned face if the subject wasn’t so serious.

“She failed out of Advanced Tactics,” he admitted. “If it ain’t related to engineering she doesn’t care for it.”

Of the problems with my officers, that was the least damaging. The goblin served effectively enough as the lieutenant for my sapper line, I just had to ensure she never ended up having to make decisions too broad in scope. I clapped Nauk on the back, carefully avoiding his still-tender arm, and moved back to the head of my column as I chewed over what I’d learned. Flawed officers, but nothing I couldn’t work with. I just had to find the right way to use them.

By the time sundown came we’d gotten fairly deep into the badlands. 

Wolf Company’s scouts had found a day-old trail a few hours back that led straight to the forest – and then another fresher one, with much deeper tracks. Snatcher’s men had brought back timber to wherever he was holed up. The scouts tried to follow the tracks back to his camp but after a patch of bare rock they simply disappeared. \textit{Of course it wouldn’t be that easy.} Robber climbed his way up a rock spire and reported that the slope in the south east went downhill: there was no sign of any camp down there, though of course it was possible Snatcher had hid away behind one of the many stone hills. After conferring with Aisha we decided to head towards the northeast regardless. The grounds got more difficult to navigate in that direction, and that was best sort of territory for Fox Company to settle in.

We made camp right before nightfall, neither of our companies putting in the effort to fortify the hollow we claimed as our spot. I wasn’t sure what Aisha’s reasons were, but I was simply reluctant to put my legionaries through more hard labour after the day they’d had. I needed them as fresh as possible for the assault on Snatcher’s fortifications, the mages especially. Still, I drew the line at ordering half-watches. There were still two other companies marauding about and while I doubted anyone would attack me while my alliance with Wolf Company was still active I wasn’t going to be taking any risks. Not with Juniper still out there. My night of sleep ended up being a short one, as Hakram woke me up while the moon was still out.

“Callow,” he gravelled. “We have a problem.”

I cursed and reached for my sword belt, tossing away my blanket.

“Wolf Company?” I asked immediately.

Without my Name I probably wouldn’t have been able to make out the way my sergeant grimaced.

“I don’t know,” he admitted. “Doesn’t seem like it, but…”

I finished putting on my boots and frowned at him.

“What happened, Hakram?”

“Seven of our sentries have disappeared,” he told me.

The vast majority of my camp was still asleep, and casting an eye around I couldn’t see anything that qualified as unusual activity. Wolf Company wasn’t assembling, so it didn’t seem like they were planning to betray us. \textit{Not yet, anyway.}

“Our munitions are still untouched?” I asked.

“First thing I checked,” the sergeant replied. “Nothing wrong there, Pickler inspected them herself.”

So whoever was behind this wasn’t planning an attack. \textit{Then why are they doing this?} Normally taking out sentries would be a prelude to a night attack, but my opponent wasn’t pressing their advantage.

“Juniper,” I realized suddenly.

“Then why didn’t she raid deeper into the camp?” Hakram wondered.

“Because she’s not after our munitions,” I cursed. “She’s just trying to lower our numbers.”

The Hellhound knew I had a Name, knew what kind of damage those could cause. So to mitigate that advantage she was going to keep grinding down my forces as much as she could before giving battle. What did it matter if I could take a tenth of heavies on my own, if I had a single line to back me up against the entire First Company? 

“Double the watch,” I ordered tiredly. “No one patrols alone and send word to Captain Bishara that First Company has men in the area.”

My sleep was uneasy after the wake-up call, but there were no more abductions that night. There was no more time to worry, anyhow: by Noon Bell the next day, we’d found Snatcher’s camp.
\clearpage
\chapter{Chapter 25: Snatcher’s Plan}

“\textit{The patient knife always strikes true.”}
\textit{– }Soninke saying

I let out a soft whistle. “That doesn’t look like a Legion design.”

“\textit{Bin hamar},” Aisha cursed in a low voice. “He must have had his cadets working through the night.”

I glanced at her curiously. My Taghrebi was still a little iffy, though I recognized the word for donkey in there. Still, Snatcher’s fortifications did warrant quite a bit of cussing. Fox Company had made camp over a hill in the centre of a hollow, though their defences extended quite a bit further than that. The first wall wouldn’t be too hard to take, I assessed. Three feet of stone and sand packed together tightly were topped by a row of sudis, with small openings slits for crossbowmen to shoot through. Demolition charges would punch through those in a matter of moments, though my own company was running a little short on those. Morok hadn’t carried any, and though Rat Company was once more topped off on smokers and brightsticks a shortage of heavier munitions had the potential to be very costly here. From the high grounds where Captain Bishara and I stood, however, we could see that the first wall was the least of our worries.

There were about a hundred feet of open ground after the wall, and one didn’t need my Name-improved sight to see some of it had been freshly dug. \textit{Rubies to piglets that Snatcher mined the Hells out of that.} Too many places had been dug into for all of them to be covering a demolition charge, but there was way to tell which of them really were mined. If any of them were, I thought with a grimace. He might have left the more obvious marks as a feint and dug in his charges less obviously. Should the Wolves and my Rats manage to breach the first wall, then we’d have to charge across the flat grounds through the traps while getting shot at by Fox Company. And then we’d get to the fucking second wall. It was more or less impossible to see the hill the sapper-built fort had been based from, with the stone ramparts ten feet high hiding away the sight of it. The depth of the ditch the Foxes had dug right in front of said ramparts was hard to estimate, but even from where I stood I could glimpse the sight of the sharp wooden stakes jutting out of it.

Some kind of wooden tower had been erected in the middle of the fort, standing above even the ramparts – it looked more like a platform, actually, though its purpose eluded me for now. At the moment most of Fox Company’s legionaries were taking cover behind the first wall, patiently waiting for our own cadets to come into range. No attempt had been made on Snatcher’s side to initiate talks after we’d arrived, and neither Aisha nor I were particularly inclined to attempt them. At this point, giving the other captain more time to dig in would be shooting ourselves in the foot.

“I can have my company ready for the fight fairly quickly,” I grunted. “We’ll be taking the first wave, as agreed.”

That had been the second price I’d agreed to pay for Wolf Company’s assistance against the Lizards. When the time to assault Snatcher came, my soldiers would be the first into the breach – and so would be the ones running into all the nasty little surprises the goblin captain no doubt had in store. Aisha eyed me sideways.

“Rushing our attack might prove more costly than we can afford,” she demurred. “First we set up our camps, then we’ll hash out a planned offensive.”

I clenched my fingers and unclenched them. I could see the sense in what Bishara was proposing, but it did not suit my own plans. 

“The longer we delay, the higher the chances Juniper stabs us in the back while we’re dealing with Snatcher,” I reminded her. “We know she has men in the area, and following our tracks here will be child’s play.”

Hiding away the tracks of two hundred legionaries, some of them in heavy plate, was not something any of us had been trained for. If Juniper wanted to find us, she would. The Taghreb girl’s lovely face was marred by a dubious look.

“It’s unlikely she has more than a single line shadowing us,” she replied. “Regardless, we will not be attacking blindly: I fully intend on scouting our backs before committing to the assault. You can have your men patrol the south-east, if you’re truly worried. Should she bring her whole company to bear, we can take her together before dealing with Snatcher.”

I smiled politely at her words, not believing a word of them. \textit{I trust you to hold up your end of the bargain against the Foxes, Bishara, but against the Hellhound? That’s a whole other story.} Ensuring Snatcher would be knocked out of the melee as quick as possible was a priority for the Wolves, since their company score would hitch them up to third place if the Foxes lost their bid. But everything after that got trickier. Juniper and Aisha were friends, I knew. How much that would weigh in on her decision making I couldn’t be sure, but I did not think the other captain would think twice about selling me out to First Company. She could take on on Snatcher with their help instead of mine, and there was no denying that Juniper’s soldiers would perform better than Rat Company’s in the matter. And yet I couldn’t just tell her that. I sighed.

“We do it your way, then,” I conceded. 

After a silent nod I made my way down the hill, returning to my company’s ranks. Hakram was already waiting for me, wonder of a sergeant that he was, and a few orders to him got my cadets started on making camp. I found Pickler in the midst of the flurry of sudden activity, Robber at her side. Good, I’d needed to talk with the both of them.

“Lieutenant, Sergeant,” I greeted them as they saluted. “I have work for you.”

The yellow-eyed little bastard immediately started grinning, though his commanding officer remained more sedate.

“What do you need, Captain?” Pickler asked.

“I want a tenth out on patrol,” I grunted back. “Start in our south-east quadrant but swing around to the south of Snatcher’s camp afterwards. Keep an eye out for First Company.”

“And if Snatcher makes contact?” Robber slyly inquired.

I held his gaze steadily. “Use your better judgement.”

To the sergeant’s left I saw Pickler wince.

“Dismissed,” I spoke, ending the conversation.

—

By the time Pickler’s patrol came back, half a bell had passed. 

The bare bones of Rat Company’s camp had been laid down, the regulation-spaced wall of sudis spikes rising out of the stony ground. To the west of us Wolf Company had claimed a hill for its own, with Aisha’s tent pitched at the top with the wolf skull standard close by. There was something of a commotion when Robber’s tenth came back, for they had a new addition to their ranks: an unusually large dead goat was being carried by a pair of sappers, neck bloodied where one of them had stabbed it. The corpse was dropped next to my bedroll – I’d elected not to bring a tent, preferring to travel light – as the sergeant strutted around like a victorious conqueror to the cheers of my cadets.

“Fresh meat for the next meal, Captain,” Robber told me proudly. “Hatcher stuck a knife in its neck before it even realized she was there.”

The female goblin he’d just provided me the name for shuffled on her feet, obviously uncomfortable with the attention. I rose from where I’d been sitting going over our only map and clapped the cadet’s armoured shoulder amicably.

“Well done, soldier,” I praised her warmly and bit back a smile when her cheeks flushed darkly.

“Thank you, sir,” she squeaked out, managing a salute before she basically ran away.

I watch her scuttle into the rocks like she was fleeing the scene of a crime, eyebrows raised.

“Shy type, is she?” I asked the sergeant.

“You’re beginning to have a bit of a reputation with the troops, ‘Cap,” Robber replied cheerfully. “You know, what with all that charging into fireballs and punching out ogres.”

“That was only the once, and you know the ogre thing is a filthy lie,” I protested.

“That’s my favourite kind of lie,” the sergeant admitted shamelessly. “Which is probably why I’ve been spreading it every occasion I get.”

“You’re an insubordinate wretch, Robber,” I told him.

“Title of my report card three years running,” the sergeant replied cheerfully, and it took an effort not to be openly amused.

“I don’t suppose you’ve got anything to report aside from your adventures in aggressive goat herding?” I prompted.

“Funny you would say that,” he murmured. “Half the reason we put the goat in front was so that no one would notice we had eleven sappers coming back. Snatcher sent a messenger.”

“I thought he might,” I grunted. “You keeping an eye on him?”

“I’ve got two cadets watching his back,” the sergeant replied. 

“Go get your Lieutenant,” I ordered, “and spread the word I want a senior officer meeting immediately.”

“You got it,” he grinned, sauntering away as he whistled the first few notes of a strangely haunting tune. I’d heard it before, I thought, though I couldn’t remember where.

\textit{They say the third step is the cruelest}

\textit{Walk when the moon is at her clearest:}

\textit{Love ends with the kiss of the knife,}

\textit{Trust is the wager that takes your life}

The words accompanying the tune came back easily enough. Not a song I’d ever heard at the Rat’s Nest, I decided. Might have overheard it in the streets of Laure, or maybe someone had sung it to me when I’d been too young to remember. I mulled over the matter until all my lieutenants were assembled, though a real answer eluded me. Nauk was the first to break the silence when everyone had arrived.

“We hashing out a plan to suggest to Bishara?” he asked.

“Not exactly,” I replied. “It’s time to let you all in on the second step of my plan for the melee.”

Ratface was the first to catch on.

“Gods Below,” he cursed. “We’re betraying Wolf Company to the Foxes, aren’t we?”

“Got it in one,” I replied amusedly. “Snatcher came to have a talk after I first met with Aisha. He had an interesting proposition for me.”

“Is there anyone we \textit{aren’t} betraying?” the Taghreb lieutenant quipped dryly.

I paused, mulling it over, and watch his face turn pale.

“Define betray,” I equivocated.

“\textit{This is not a question that should require this much thought to answer},” he burst out.

Kilian cleared her throat. “Amusing as this is, I’d prefer a little more information. How will this be going down?”

“Ideally we’d split our forces in two for the assault, each half on one of the flanks of Wolf Company,” I explained. “When the signal is given, Snatcher will make a sortie into their centre and we’ll fall on them from both sides.”

“And we’re sure Snatcher will hold up his part of the deal?” Pickler questioned.

“He wants Aisha out of the melee very, very badly,” I grunted. “He knows she won’t stop until one of them is done.”

“It should be enough to keep him honest for now,” Nauk gravelled in approval.

“Speaking of Snatcher,” I continued, “we have a messenger from the man.”

I motioned for the Fox Company sapper to come closer, dismissing his two escorts with a nod.

“Your name, cadet?” Nauk growled.

“Latcher, sir,” the goblin replied serenely.

Even in the heart of another company’s camp, the Fox legionary seemed unruffled. I’d noticed more than once that his eyes never stopped moving, always seeking out additional details he could report to his own captain about the state of my company. A reminder that after Aisha was down for the count we’d be enemies again. The part of his armour where the foxhead stamp revealing where his allegiances lay had been cleverly scratched out, though if anyone from Wolf Company recognized his face that would be a moot point. I’d need to keep him carefully out of sight, and with his helmet on at all times.

“And what message does Captain Snatcher send you with, Latcher?” I prompted.

“Our company will be ready to hit Captain Bishara’s centre the moment yours sounds the horn twice,” he replied.

I hummed thoughtfully, drumming my fingers against my knee.

“I’m not seeing a door in the first wall, cadet,” I pointed out. “How will Fox Company be joining the battle?”

The goblin bobbed his head. “Some parts of the palisade are removable,” he informed us. “That said, most of our company will be staying at a distance to contribute through crossbows. Only our two lines of regulars will be charging into the fight.”

I’d expected about as much. Sending in goblin sappers into a sword fight would result in catastrophic losses for him and little change in the engagement’s outcome.

“It will do,” I grunted. “I expect we’ll be beginning our assault by Afternoon Bell, so you won’t have time to sneak back into your camp. You’ll be staying with Pickler’s line until then. Don’t draw attention to yourself.”

“By your will, Captain,” Latcher agreed softly.

—

Talking Aisha into my formation had been surprisingly easy, considering it was far from the optimal way to attack the wall. My guess was that as a new captain she’d been expecting me to blunder for some time, and that she’d decided Rat Company taking losses here would make us easier to mop up afterwards. I kept Nauk and his heavies in my half, in case there was another Red Rage episode, and put Ratface in charge of the other one. Pickler went with him and Kilian’s line was split in two, with her shields bolstering Ratface’s line while I took the mages and the lieutenant in question. I could glimpse Snatcher’s men behind the palisade, much more heavily concentrated than they had been this morning\textit{.} I watched Ratface position his men just out of crossbow range and prepare his line as Hakram did the same with own with my forces. We’d be ready soon. The Wolves stood in the flat grounds of the hollow, ranks perfectly ordered and ready to move: Aisha had put her mages and sappers in the middle of a tightly-packed square, though given how quickly her company could move that meant very little. Taking the signal horn from my pack, I took a deep breath and prepared to sound the beginning of the battle. \textit{Sorry, Aisha, but this was my best option.} The deep sound thundered across the badlands.

I had not been the one to blow it.

Armour shining in the sun, Wolf Company pivoted with parade-ground perfection to face my separated men and started to charge. Pushing down the urge to curse my heart out, I put my lips to the polished ram’s horn and sounded it twice. Four chunks of the palisade were immediately raised up and put aside, Snatcher’s lines starting to pour through. What the Hells was Aisha’s game here, I wondered. Had she been aware I was about to betray her? No, if she had she would have left more than a line facing the direction Fox Company was currently forming ranks in. It didn’t make sense for her to force a fight with me before we’d assaulted Snatcher’s fortifications. She’d probably beat me, but she’d still take losses and –

“Oh fuck my life,” I spoke out loud.

I turned to look at the northwest, the part of our back Wolf Company’s patrols had been supposed to be covering. A black standard with the silver crossed swords of the War College rose over the crest of the hills, First Company’s forward lines briskly marching in our direction. \textit{Well, that explains why she wanted to wait a bell until the assault. She was giving Juniper time to catch up.} The thought was oddly calm, considering I was panicking at the moment. What should I do? Take a gamble and hope we could rout Aisha before Juniper arrived? No, even then we’d be stuck facing First Company with split forces and I wasn’t sure I could count on Snatcher to stick with me through the fight. He might just withdraw behind the walls and let us fight it out. I threw my helmet on the ground and let out a cry of anger.

I couldn’t let it end here. Not with everything that was at stake.

“Hakram,” I called out.

“Sir?” my sergeant prompted. 

He’d been about to rejoin our line to prepare it for the fight with Aisha’s men, who were less than a hundred feet from us now. I spat on the ground.

“We withdraw,” I told him, the words feeling like ash in my mouth. “Follow Snatcher’s wall to the east, there’s bound to be another way in there.”

The goblin captain wouldn’t refuse me entrance, not when he had two other companies knocking at his gates. He needed the numbers. The real problem was that there was no way to get a message to Ratface to tell him to do the same on the other side. The tall orc saluted without a word, returning to our men to see my bidding done. Gingerly I picked up my helmet, watching as the half of my forces under the command of Rat Company’s former captain prepared to meet the charge of the Wolves. My own soldiers started retreating in their assigned direction a moment later, and I sounded the horn one last time as a warning to the rest of my cadets. It was for naught. The lines met, and over the horizon Juniper’s legionaries turned in their direction. I would have stayed to watch longer, but Wolf Company was getting close and there was a limit to how any people I could take on even with my Name. Fingers clenched, I ran to catch up with my legionaries and we fled.

—

Fox Company opened another chunk of the palisade to let us through long before Wolf Company was in a position to do anything about it, the captain himself coming to meet me almost immediately. Snatcher was tall, for a goblin: the top of his head went up to my chin. His skin was of a paler green than I was accustomed to, smooth and almost entirely without the usual wrinkles. Yellow eyes like Robber’s looked back at me, although his left one had a way of facing away from where he was looking. It made it hard to meet him eye-to-eye.

“Captain Callow,” he rasped out in an ever-surprisingly deep voice for a goblin.

“Captain Snatcher,” I replied tiredly, clasping the offered arm.

“Bit of a mess today,” he sympathized. “Didn’t think Bishara had it in her.”

“Neither did I,” I admitted. “A lesson to remember. Do you know what happened to the rest of my men?”

“They broke and ran when they saw Juniper coming to sweep them,” he replied. “We opened a gate for them on the western side when they fled in that direction. Most of your sappers made it through, as well as a few of Ratface’s cadets. Twenty-three overall.”

With my own survivors, that brought me down to seventy-one legionaries. Not as bad of a disaster as it could have been, but still a crippling defeat. I grimaced. Black had been right, damn his Praesi hide: one step of my plan had failed and now the whole thing was useless. I’d have to start planning from scratch again, and my position was horribly weak.

“Do they show any sign of wanting to assault?” I asked.

Snatcher shook his head. “First Company is taking over your camp. I doubt they’ll try anything until tomorrow morning.”

I frowned. “Why the wait? They still have at least a bell until sundown.”

“Juniper’s forces aren’t all here,” the other captain grimaced. “Her sappers are still missing. Building ladders and a ram, if I had to guess.”

“They’ll still be at a disadvantage going on the offence, even with those,” I noted. “Between your crossbows and my heavies we’ll be able to hold them off even if they attack several spots at the same time.”

“I have a few thoughts about this, as it happens,” the goblin smiled. “Walk with me, Callow.”

For a moment I thought he’d make like a Callowan and offer me his arm to slip into mine but he simply ambled on ahead.\textit{ Probably better that way}, I mused. \textit{Never seen a goblin riding a horse before, so knighthood would be a stretch.} I caught up with him and we strolled next to the wall like this was a Proceran garden viewing.

“As you’ve no doubt noticed,” he started, “ the walls to my second ring of my fortifications are stone and dirt.”

I nodded, curious where he was going with this.

“And yet,” he spoke almost casually, “there is no sign of the digging efforts that would be necessary for such an accomplishment.”

My eyes sharpened. He was right: I’d been so focused on the possible mine field I’d never thought to wonder where the materials making his rampart from had come from. Some of it must have been from the ditch in front of it, but that wasn’t enough to explain ten feet high walls.

“You’ve been digging elsewhere,” I said.

Snatcher’s lazy eye wandered as he bared yellowing needle-like teeth in approval.

“Goblins weren’t always surfacers, you know,” he told me. “We once lived underground, before the dwarves drove us out and into the Grey Eyries.”

I clenched my fingers and unclenched them, letting my other hand rest on the pommel of my sword.

“Tunnels,” I realized. “You’ve been digging tunnels.”

“And they lead right to the two most likely camp sites for a besieging force,” he chuckled. “So tell me, Captain Callow: how would you like to even your score with Bishara?”

My answering smile was a savage thing. “I think you and I will get along very well, Captain Snatcher.”
\clearpage
\chapter{Chapter 26: Juniper’s Plan}

\textit{“Never back the Praesi in a corner, son. That’s when the devil-summoning starts, and it’s all downhill from there.”}
-King Jehan of Callow, addressing the future King Pater the Unheeding

Snatcher had suggested we wait until sundown for the sneak attack, and I wasn’t inclined to disagree.

I had a lot of work before me, as it happened. I needed to get a real headcount of my remaining cadets, go through our stocks to see what we had left munitions-wise and brief my remaining officers on the new plan. We were in no danger of being eliminated through officer attrition, given that my only missing lieutenant was – once again – Ratface but I’d already figured out that numbers were the way Juniper was aiming to take me out. Wise of her, considering I’d take quite a few legionaries to put me down if she cornered me badly enough. My Name was still being a temperamental bitch about coughing out power, but I had a feeling that if the opposition got too overwhelming it would trigger my Struggle aspect again. \textit{Though how much help that would be against a group is still up in the air. }

Though he remained tight-lipped on more general Role lore, I’d managed to get some tips on using my own from Black. He’d told me that aspects always needed specific conditions to be tapped into, and usually had at least one flat limitation. Learn, for example, only applied when I was consciously being taught. Trying to pick up a sword trick in the middle of a duel would fail every time. As for Struggle, he’d been less helpful in puzzling it out: it had not been one of his aspects back when he’d been the Squire, and though he’d made a study of Names their powers had a way of varying wildly from one Named to another. His guess was that the aspect was meant as an equalizer: when I was outclassed, my Name would put me on even footing with my opponent for a short amount of time. There was no way to be sure whether he was right or not until it was put to the test, but his theory had felt… right. Like it fit in a wider pattern.

Names were supposed to respond with who you were, and I’d known from the moment I’d accepted the Calamity’s offer that most of my battles would be uphill ones. That my Name had responded to my desire for a way to even the playing field made perfect sense to me. I was worrying, though, that it would not react the same to multiple opponents. When I’d taken Rashid by surprise and stabbed his sorry ass we’d essentially been duelling. When I’d jumped over the log in the last war game I’d not been tapping into the Struggle, I was pretty sure. Just making use of what little power my damaged connection to my Name had made available at the time. Would the aspect trigger if I was facing multiple opponents that were, strictly speaking, weaker than I? I had my doubts.

Already I knew that it only reacted to direct threats, or it would have reacted when Heiress was outmanoeuvring me in the Tower. I was kind of hoping my third aspect would involve a loud alarm blaring in the back of my head whenever the Soninke noble was fucking me over, but I doubted it would be that easy. There was a sort of twisted duality to my Name and hers, one that brought to mind one of the first afternoon lessons with my teacher. Most of the time we went over my assigned readings and he clarified points or expanded on them, but once in a while he’d strike a debate over a subject and the afternoon was spent discussing it. I’d learn to both dread and look forward to those particular lessons: I always came out having learned something useful, but the conclusions could be… morally flexible, to put it mildly.

That time, the subject had been the nature of power. “Dread Emperor Terribilis once said that power is the ability to see your will done,” he’d begun. “Using that as a touchstone, I would classify power in two broad types: soft power and hard power.” Soft power, he’d elaborated, was the use of indirect methods and influence. Convincing and coercing others to do your bidding through persuasion or social pressure. Though I disliked her on a personal level, on an objective one I could see that Heiress excelled at that kind of work. She’d managed to turn all the other claimants against me back in Summerholm with minimum effort and no risk to herself. When we’d met face to face on the Blessed Isle the use of force had been a backup plan, not the main thrust of her effort: instead she’d offered me something she thought I wanted, in a way that would marginalize me as an obstacle to her plans.

Hard power, by contrast, was where I lived at. Direct application of force to dictate your will on others. The way Black had phrased that made me uncomfortable, but there was some truth to his words. In the end, I was not above imposing what I thought was right and wrong on others at the edge of a sword. Even what could be called my one foray into soft power, when I’d decided to use the Lone Swordsman as a way to set Callow on fire an advance my cause, had been something I’d managed to accomplish by forcefully beating the hero first. I still remembered the way every one of the claimants for Squire had gone about things differently, almost as if the Name was pitting different methods against each other to see which was the most worthy. In that light, I did not think it was a coincidence that Heiress and I used fundamentally different ways of getting what we wanted. We were in a competition, clearly, I just wasn’t sure for \textit{what}.

Not that it changed anything. Heiress had been sharpening knives meant for my back before we’d ever met, and I did not think she was done interfering in the melee yet. The blood magic delay and my shitty starting position felt like her hand at work, but that could not be the only string to her bow. The two incidents I suspected she was behind had damaged my performance, yes, but so far she’d always gone for more thorough plots than that. All the moves she’d made before had the potential of taking me entirely out of the equation, which meant there was likely a third stroke coming for my neck. \textit{But from where? }So far she’d interfered through the College, which made sense: it was an old institution, one where her family was likely to have pre-existing contacts. Pickler had already killed my initial guess of her bribing one of the participating captains, which left… outside interference?

That seemed unlikely, with the way Black was bound to be watching all of this like a hawk. Heiress was good, but not good enough to pull the wool over the eyes of one of the fucking Calamities. I sighed and put the matter aside. It was an unfortunate fact that I had a lot more difficulty predicting Heiress than she apparently did predicting me. \textit{One who prefers soft power is weak to direct confrontation}, I remembered Black murmuring over a cup of wine, \textit{but one who uses only hard power is easy to entrap. As in all things, balance is paramount.} It didn’t matter, I decided as I clenched my fingers tightly. However sharp the jaws of the trap my rival would have closing on me, I would pry them open and throw the whole bloody contraption at her head. Adjusting my sword belt – it had loosened a bit while running away from Wolf Company – I put my helmet back on and returned to my cadets.

My initial count of seventy-one legionaries had been overly optimistic. I had that many cadets present, certainly, but not all of them were in fighting shape. Damnably, most of the legionaries unfit to fight were in my heavies. Getting trampled by a tenth of ogres was not something you recovered from in a day, and though Kilian’s mages were fairly talented they were nowhere close to the kind of ability you’d need to truly heal broken bones. They could put them back into place and patch them up, but any hard impact would break them right back – and make them that much harder to heal the second time. Flesh could only soak in so much magic before it became saturated, the redheaded lieutenant explained to me. Trying to push in sorcery past that point would lead to… bad things. All in all, I had about fifty-five soldiers in fighting shape. Most of my own line, the mage half of Kilian’s and miraculously all of Pickler’s sappers. The goblin lieutenant did have a talent for ducking out of the way before trouble reached her, one probably helped along by the way her sergeant snuck around and compulsively eavesdropped on everything.

“We don’t have the numbers to overwhelm Wolf Company anymore,” I told my remaining officers. “Not even a surprise attack will change that.”

“We’re going for the officers, then,” Hakram graveled.

“Finding them will be the real problem,” I grunted back. “Even if we manage to penetrate the camp quietly, which isn’t a given, we’ll only have so much time before the alarm is sounded.”

Pickler gently cleared her throat. “There shouldn’t be a problem, Captain. Aisha’s sapper line is lacking, so they largely stick to the book. Their camp layout is Legion standard.”
I frowned.

“I’m not seeing the significance of that,” I admitted.

Nauk snorted out a laugh. “It means their officer tents are in designated spots for quick assembly,” he grinned savagely. “If we move quick enough, we could have all their senior officers out before the pack wakes.”

Well now. I’d been due some good news, and this seemed to qualify.

“I’ll need four other people to sneak in with me,” I decided. “One per target officer. Any of you have recommendations?”

“Sergeant Robber,” Pickler immediately offered, not noticing the disgruntled look taking hold of Nauk’s face. “He’s good at quiet work, and you won’t find anyone better at taking out sleeping soldiers.”

Her tone seemed to imply that the last part of that sentence had been a compliment. \textit{Goblins}. The Tribes had very definite ideas about the way wars should be fought, and most of them would have the knights of Old Callow sputtering in mortal outrage. Thankfully, I’d never been afflicted by that whole chivalrous ethics mess. The Fields of Streges had made it very clear which way worked better when it counted, and in the end that was all that mattered.
“That’s two,” I noted. “Anyone else?”
“I’ll give you Nilin,” Nauk grunted. “My line’s not gonna be seeing action anyway, so he shouldn’t be needed.”
I nodded.
“Hakram?” I prompted.
“I’d go myself,” my sergeant graveled, “but someone needs to attend our line. Take Nomusa – not too tall, for a Soninke, and she packs a punch.”

I turned my eyes to Kilian and found her frowning.

“I’ll come,” she finally said. “You might need a mage, and I can be quiet if I need to.”
I hesitated before accepting that. Two sergeants, a lieutenant and the company’s captain were quite a few assets to risk on a strike that might very well fail. \textit{On the other hand, if we don’t succeed we’re pretty much fucked anyways. All or nothing, huh? Should I be worried how often that ends up being my play?}

“Nauk, you’ll be in command in my absence,” I ordered, tacitly accepting Kilian’s offer.
The orc in question cleared his throat. “Where do you want Rat Company deployed, then?” he asked. “Not to get too obvious, but the moment the Wolves are out Snatcher no longer needs us.”

And there lay the thorniest of the thorns in my godsdamned side. Fox Company needed us to bolster their ranks on the walls only so long as there were two companies besieging them. If there were only Juniper and I left, I couldn’t be sure Snatcher wouldn’t decide to take his chances with the Hellhound and backstab Rat Company. As things stood, with most of my troops already behind the first wall I was pretty sure I could take his fort from him. But there’d be casualties, and then I’d be stuck in the same position he’d let me in to avoid: alone on the hill with Aisha and Juniper out for my blood. Not a feasible option, especially considering there were tunnels connecting to both their camps. The plan Snatcher had proposed was that I would strike at the Wolves under the cover of night while he made his move against First Company. On the surface that seemed to be on the level, but he’d left himself a door. He’d have the option of pulling out after Aisha was done and leave me to deal with a pissed off Juniper, shutting the tunnels down behind me. Something to avoid as much as possible.

My options were either to leave my survivors inside with him and have them ready for a fight in case he betrayed me or to have Rat Company bail out the moment I headed into Aisha’s camp. I was leaning more towards the second: even if this whole thing went south, I’d still have enough troops left to find another angle to victory. \textit{And if I manage to drop Aisha while leaving the Foxes mostly intact behind their pretty little walls? I’m not sure it’s me Juniper will be pointing her blade at.} That the Hellhound got to work cracking open Fox Company’s defences while I found a better position for the final confrontation was the best outcome I could hope for. Not that there was any chance of me getting there \textit{now}, since just by thinking that I’d pretty much sent an engraved invitation to the Gods asking them to piss all over my plans.

Still. It was worth a try.

“Wait fifteen Hails after my team moves out and then take the company north,” I told him after chewing over my options a little longer. “Avoid fighting.”

The large lieutenant shot me a bewildered look.

“What the Hells are ‘Hails’,” he growled.

Kilian snorted. “It’s the time it takes to recite one of their fancy House of Light hymns,” she explained, eyeing me amusedly. “Wrong gods for this neck of the woods, Captain.”

“Right,” I coughed, somewhat embarrassed. “I, er, don’t know the equivalent for the Gods Below.”

“About six basic line drills,” the redheaded lieutenant said after pausing an instant to close her eyes and think. “The Hellgods don’t really go for hymns, as it happens. Probably safer to stick with Legion exercises.”

Clearly I’d need to actually learn those at some point. My lessons had been rather sparse in that regard, as it happened. After teaching me the bare essentials of fighting as a legionary, Captain and Black had focused on other kinds of swordsmanship. I’d never actually seen my teacher use a scutum outside of those first few mornings: Black usually favoured a smaller kite shield with his short sword and taught me with the same.

“Duly noted,” I grunted. “That should be it for the moment, unless anyone else has a point to raise?”

No one did, and they took heed of the implied dismissal. I motioned for Kilian to stick around as the others started leaving, not bothering to vocalize the order. The pale-skinned girl looked surprised but she sat back down without a comment. I waited for the other officers to be at a safe distance before clearing my throat.

“There’s a thing I’d like clarified before we head into combat,” I told her. “I’ve heard you can be incapacitated if you draw too much on magic – something about creature blood?”
The lieutenant sighed, fine lashes fluttering over hazel eyes.

“Hakram?” she asked in a resigned tone.

I snorted. “Surprisingly enough, no. Got it out of Nauk.”

“Like he’s one to talk, the bloody failed berserker,” she muttered.

“I don’t mean to pry into personal matters,” I said. Not strictly true, but I figured I might as well pretend not to be nosy. “I just want to know how it might affect things.”

Either she bought that or she was polite enough to pretend to. Pushing back a strand of red hair into the sides of her pixie cut, the lieutenant took a deep breath.

“My grandmother was one of the Fae,” she said.

I blinked in surprise. “Like the ones in the Waning Woods, or does that mean something different in Praes?”

She eyed me cautiously. “I keep forgetting you’re Callowan,” she admitted. “The Fae are… not popular around here, even in the Green Stretch.”

I raised an eyebrow. “I mean, they kill Callowans too whenever one’s stupid enough to go too deep into the forest but it’s not exactly a big deal. They never wander out and the path to Refuge is supposed to be safe.”

“The benefits of having a former Calamity ruling your city,” Kilian noted. “The blood’s pretty diluted, but I still got some things out of it. Mostly the unusual hair and some mage tricks that require control beyond what most humans can manage.”

“I’m not really seeing downsides, so far,” I pointed out. “Well, besides the racism. But that was kind of given already, what with you being Duni.”

“Isn’t it just?” she replied bitterly. “You’d think with the fucking \textit{Black Knight} being one of us they’d start holding their tongues, but it doesn’t seem to have changed anything.” She took another deep breath, forcing herself to return to the original subject. “Anyway. You’ll note I don’t have wings, which Fae are supposed to have. Whenever I draw in too much power my body tries to make some, which fucks with my head and occasionally makes me lose control over the magic.”

“That sound bad,” I contributed helpfully.

“Pretty bad,” she agreed with the ghost of a smile.

“But you know your limits?” I probed.

“Learned them the hard way,” Kilian grimaced.

“All I needed to know,” I told her, clapping her shoulder in reassurance. “I’ll let you brief your tenth, I need to have a talk with Captain Snatcher.”

She nodded and I rose to my feet, rolling my shoulder under the chain mail. Wearing it for so long was killing my muscles, especially without a proper aketon under to soften the weight. Legionaries were issued something thinner than the padded jacket I was used to, though admittedly mine was meant to be worn with mail.

“Captain,” Kilian suddenly called out.

I half-turned to meet her eyes. “Lieutenant?”

“Thank you,” she said, looking away.

“Any time, Kilian,” I replied quietly.

I hated the part of myself that coldly noted she was more loyal to me now than ever before, but I did not ignore it. \textit{Guilt is fine. Healthy, even. But I will not let it stop me}. Thumb rubbing the hilt of my sword, I went to find Snatcher. There were still details to hash out, and all of my ambitions would be for naught if I lost today.

Arranging a meeting ended up a more complicated matter than I would have thought. Snatcher was inside the fort, and that meant going across the – possibly – mined field. I asked one of the sergeants still at the wall and he informed me that my fellow captain had left instructions that I be escorted to him if I asked. I was guided across on a hilarious overcomplicated path by a cadet in what I suspected was far from the most efficient route. I did my best to commit it to memory anyway: for all I knew, I might need to use it before the melee was done. To my surprise, I came to find the goblin captain doing manual labour. The wooden platform I’d glimpsed earlier today was being linked to the ground by a minimalist ramp: Snatcher was part of a group of half a dozen goblins laying the finishing touches on it. He gestured for one of the sentries to replace him when he saw me, patting down his clothes to get some of the dust out of them.

“Captain Callow,” he greeted me. “I take it you’re done briefing your officers?”

“They’ll be read when the time comes,” I agreed. “Just one last thing to go over with you – I’ll be taking a small team through the tunnels, not the entire company. Lieutenant Nauk will be taking most of my cadets north while I’m targeting Aisha’s officers.”
I did not phrase it as a request because it was not up for debate. Snatcher studied me with a calm face.

“Fair enough,” he conceded. “I’ll notify my officers. One of my cadets has volunteered to guide you through the tunnels.” He paused. “If I may say so, Captain Callow, you’re a rather quick study. It has been a pleasure to work with you.”

“The same to you,” I replied, somewhat surprised to find I meant it.

Snatcher was a pleasant enough sort, and by far the politest goblin I’d ever come across. Talking with General Sacker had been like having a knife at my throat the whole time, I couldn’t help but think that Pickler was only ever half-listening when I spoke and the less said about Robber the better. I enjoyed the malevolent little sergeant, true, but if he ever met politeness in a dark alley he’d knife it and rob the corpse.

“All of the Deoraithe attending the College show promise,” the other captain noted. “It’s a shame so few of you actually serve in the Legions afterwards.”

I’d had no idea whatsoever that there were any of the People around, but I kept my surprise off of my face. \textit{Why the Hells would Deoraithe go through a Praesi officer school?}

“You’re the first Praesi I’ve heard referring to them as anything other than Wallerspawn,” I replied instead, subtly steering the subject away from my ignorance.
Snatcher shrugged.

“The Grey Eyries are a long way from the Wall,” he replied. “Unlike the Clans, the Tribes have no bloody history with the Duchy of Daoine and no grudge to go along with it.”
I nodded slowly. That was good to know. It was hard to break the habit of thinking of the Empire as a monolithic entity: even now that I’d learned of the different forces at work inside of it I still had a tendency to assume general opinions remained the same regardless of ethnicity. I considered leaving the conversation at that, but my eyes flicked to the platform and I decided to push my luck.

“If you don’t mind my asking,” I spoke, “what is that thing for? I’ve been wondering since Rat Company first set camp.”

Snatcher smiled a tad nastily, though the nastiness did not feel like it was directed at me.
“My little surprise for Juniper,” he replied. “Did you pay attention to the stocks?”

I nodded. “Though I don’t recall anything shedding light on this.”

“It’s a common mistake to only keep track of the munitions,” the goblin said. “It leads people to miss things like my requesting a large bowstring, nails and iron plate.”
A large bowstring? What would he use that for? I frowned. Fox Company was, at its core, a sapper company. The function of the sappers in the broader Legion was the use of goblin munitions, the building of fortifications and…

“I thought siege weaponry was forbidden,” I said.

“Bringing one is forbidden,” Snatcher corrected me. “The regulations say nothing about \textit{building} one.”

Another detail fell into place.

“So that’s why my scouts found tracks coming from the woods. You were bringing back materials to work with.”

“It was a gamble,” Snatcher admitted. “There was no way of telling whether or not our battlefield would have lumber on it, and I must admit the ballista we’ve cobbled together is rather crude.”

A \textit{ballista}. Weeping Heavens, and to think I’d believed his company would be the easiest to deal with. And since the better part of his company was goblins, starting bombardment during night time would make no difference to him. He interpreted my silence as worry, and to be honest he wasn’t entirely wrong – I really hoped Juniper was the one who ended up having to take this fort, because I didn’t think my own men could pull it off.

“No cause for alarm,” he assured me. “We’ll only begin firing after either you’ve taken out Wolf Company or conspicuously failed in doing so.”

“Very kind of you,” I faintly replied.

Thanks all the Hells I hadn’t stuck to my original deal with Aisha: it would have been a bloody rout.

—

I already knew all of my team except for Nomusa.
I recognized her from my line when she met us at the head of the tunnel, but we’d never actually talked before. She was Soninke, like Hakram had said, and only a head taller than me – which qualified as short by the standards of her people. She was missing a finger and there was a nasty burn mark in the hollow of her cheek I decided not to ask about. Nilin I already knew, having shared drinks with him in the aftermath of the last game, and smiled at him when he arrived. Robber had already been there when I’d arrived, skulking around and managing to look suspicious without actually doing anything concrete. It was a skill he’d perfected through years of hard work, or so he’d informed me cheerfully. Kilian was the last to show up, slightly out of breath. When she fell behind me in silence our guide for the night finally opened his eyes and rose to his feet.

“My name is Hatcher,” he informed us curtly. “I see none of you brought your scutum, which is good – the tunnel is tight enough without dragging along a shield. It’ll be dark in there, so keep close to me.”

Without further ado he scuttled into the hole in the ground. I was the first to follow and a short drop later I was on solid ground again, crawling on my knees. For once in my life I was glad of my height: even Nilin would find the tunnel a tight fit, and Hakram wouldn’t have managed more than a few feet before getting stuck. We waited until everyone dropped and so began our wriggling in the dark. Progress was damnably slow and the air felt thin, but after an eternity of making like worms the tunnel broadened a bit and Hatcher told us to take a break.

“We’ve passed the first wall,” he told me. “Only a bit further now.”

“Do you know where in the camp we’ll be coming out?” I muttered back.

“The tunnel splits around there in four different directions,” he replied. “Most are close to the middle, but you’ll be going in blind.”

“Lucky us,” I grunted.

Without my Name I would not have seen him glare at me in the dark. Soon after we resumed the crawl, and around what I estimated to be the tenth Hail the tunnel broadened again, splitting in the directions as he’d mentioned. Hatcher tapped a hand against the wall of the centre one.

“That one’s the best situated,” he spoke. “You should send two people there, split the others.”

“You heard the man,” I murmured. “Nilin and Kilian, take that one.”

“The rightmost tunnel goes a bit further,” Hatcher told me. “I’ll show you the way.”

Presumptuous of him to assume I’d take that one, but I saw no point in arguing. Robber and Nomusa headed into theirs while I followed the Fox Company legionary. The tunnel tightened again, much to my dismay, and our progress slowed. I peered over Hatcher’s soldier and my blood ran cold when I saw that up ahead was a dead end. \textit{Trap. Shit.}

“Just a moment,” Hatcher spoke. “Something wrong with the ceiling here, I need to have a closer look.”

His hand slowly moved towards a small hole in the wall ground under him, where I glimpsed clay balls. My hand went for my sword and slowly, silently, I unsheathed it.

“You ever been to Summerholm, Captain?” Hatcher asked.

“Only the once,” I replied, shifting around to get a better angle to strike.

“Never been, myself,” he casually spoke. “But my cousin did. She never came back, Squ-”

I rammed the pommel of my sword into the back of his head before he could finish the monologue covering his motivation. \textit{Amateur}. He yelped but the angle had been awkward and he wasn’t knocked out. He dropped the sharper though, and that was what mattered. He threw himself at me but I was ready – releasing my sword I caught his hands and forced him down. Hissing furiously, he bared his teeth and tried for my throat but I head-butted him violently. His nose broke and I did it again, twice as hard. He screamed but his struggling weakened, eventually ceasing entirely.

“I’m guessing you’re talking about Chider,” I spoke quietly.

“\textit{Murderer},” he garbled out.

“The hero was the one to kill her, actually,” I replied. “Though I won’t deny I would have done it myself if it came down to it.”

“They’ll get you,” he sneered through the blood. “Sooner or later, someone will. Little Callowan playing the Squire. You’re a joke and everyone knows it.”

“Let me guess,” I sighed. “You got the information through an anonymous source right before the beginning of the melee?”

A flicker of doubt went through his eyes but, as desperate sorts are wont to do, he doubled down instead of folding.

“No idea what you’re talking about,” he mocked.

How many other knives had Heiress pointed at me this way, I wondered? How many other legionaries in the melee were out to kill me if they could? I’d need to watch my back very, very closely.

“The part that confuses me is how you thought you’d get away with this,” I admitted. “The College is scrying this whole thing as it happens.”

“Can’t scry underground, you ignorant sow,” he spat.

“Ah,” I said softly. “That changes things.”

There was a look in the goblin’s eyes I recognized from the Pit. The one sore losers got, the kind of opponents who knew they’d lost the fight but were already thinking of the next one. He wasn’t going to stop. He’d come for me again. Not tonight, not even tomorrow but one day he would try his luck a second time.

“You know, the first night I met him, he told me it didn’t get easier,” I told the goblin softly.

A trickle of power ran through me as my Name stirred, strengthening my grip. Hand moving with swift purpose, I broke Hatcher’s neck.

“It was,” I decided, “a very kind lie.”

Softly, I closed the cadet’s eyes and let out a long breath. I picked up my sword and sheathed it, turning around to crawl back the way I’d come from. I still had a game to win. And no time to think about what a stupid, meaningless way it had been for that cadet to die.

—

I surfaced after having taken the tunnel I’d sent Nilin and Kilian through, the one closest to the centre of the camp.
The exit was hidden behind a stone much too large to move easily, covered so it wouldn’t be seen at a casual glance. I pushed myself out and knelt in the dirt, holding my breath to hear there were any sentries close by. A few heartbeats later, satisfied there were none, I rose up to a half-crouch and took a better look at my surroundings. I was a little to the south of where I needed to be, if I remembered Pickler’s drawing correctly. The captain’s tent was supposed to be in the very centre of the camp, where the two main avenues crossed. Aisha had been the target I’d chosen for myself, as she was the most likely to have guards around her – I had a few trump cards at my disposal that the rest of my team didn’t if things got out of control. Admittedly the cards were fickle and still rather displeased with me at the moment, but they were still nominally in my hand.

Wolf Company seemed to be largely asleep and there shouldn’t be any sentries this deep inside the camp, but I still moved carefully. I passed by two rows of tents nestled close to each other, pausing when I saw torchlight lighting up the space ahead. I peered around the corner of a tent and grimaced when I saw that there was still light in what looked like Aisha’s tent. Worse, there was a pair of legionaries standing next to the entry flaps – orcs, and not small ones either. Would it be worth it to circle around and try my way by the back? The longer I waited the higher the chance of getting caught, of course, but it might be wiser to take a chance than go for the noisy front assault. I was late already, thanks to Hatcher’s failed assassination plot, but I shouldn’t be a problem as long as – I tensed, waiting for the alarm to ring. Silence.

\textit{Huh}, I mused. \textit{This might actually go as planned}.

A horn sounded a heartbeat later and I decided that if I ever came face to face with a god I was going to stab it somewhere painful. Casually I started walking in the direction of Bishara’s tent, not quite hurrying but definitely not slowly. The guards had snapped to full attention the moment the horn sounded, and \textit{fuck} had one of my legionaries failed? This wouldn’t work if we didn’t get all of the senior officers. I saw the closest orc glance at me and then to something in the distance – \textit{that’s right, nothing to see here, just one of your legionaries assembling} – but the gaze snapped back.

“INTRUDER!” she yelled, but I was already running. “TO THE CAPTAIN!”

She barely had the time to bring her shield up before I bodily slammed into it, knocking her back. The other guard tried to strike my neck but I angled my head and it bounced off my helmet. The hit still hurt, but I gritted my teeth and stumbled through the flaps to the tent. Aisha was inside, tightening her sword belt without having even bothered to put on a shirt.

“\textit{Callow}?” she squawked. “What the-“

The flat of my blade, swung two-handed, struck her on the temple before she could reach for her sword. A moment later someone struck me in the back and I was thrown to the ground, rolling to get to my feet as a very angry orc tried to bash my head in with their shield. I ducked behind Aisha’s cot, sneaking a look at Wolf Company’s captain while a pair of furious orcs turned the wooden frame to kindling. She was out like a light, most likely concussed.

“This has been great,” I told the legionaries, backing away to the edge of the tent, “but this is getting a little serious for me. I’m not sure I’m ready for that kind of commitment.”

“I’m going to take this out of your hide, \textit{Rat},” the male orc spoke in a surprisingly mellow voice.

And that was my cue to make a daring escape. I kicked the tent pole I’d managed to position myself next to. It did not fall.

“Dug into the ground, huh,” I spoke into the incredulous silence. “Bummer.”

Well, what was going to follow was not going to be pleasant. I could already hear reinforcements closing in. Actually, I could hear them screaming. In dismay.

“I don’t suppose one of you could check the sky?” I asked. “I think-“

Thunder rumbled. Sheathing my sword, I raised my hands up in surrender and carefully walked back out of the tent – one of the orcs shouldered me as I went by, but I was a magnanimous winner and so allowed it to pass without comment. The night sky was streaked with the beautiful image of Wolf Company’s standard, a red streak across it. The sweet taste of victory was a little harder to enjoy with a crowd of hostile legionaries gathering around me, but after a moment Nilin pushed his way through them and to me with a wide grin on his face.

“Captain,” he said, sounding almost disbelieving. “We did it. I mean, I thought maybe we could pull it off, but we \textit{actually pulled it off}.”

His babbling was actually somewhat endearing. I clapped his shoulder with a smile of my own.

“We should have one Hell of a spectacle starting soon, sergeant,” I told him. “Captain Snatcher’s minions made a ballista, and by now they should be ready to bombard First Company.”

“So that’s what the platform was for,” he mused. “I’d been wondering.”

Kilian came around a corner and I waved her over, ignoring the multitude of glares coming in my direction. She put a spring to her step and joined us, Wolf Company parting for her as they started dispersing.

“Lieutenant Kilian,” I grinned. “Come on, we need to find a good vantage point.”
She raised an eyebrow. “Why would we-”

Thunder rumbled. \textit{What?} I looked up, and next to the red-slashed wolf a fox glared back down on me. Ignoring my legionaries, I headed for the peak of the hill Wolf Company had built their camp on. First Company’s camp looked untouched, the few fires surrounded by tents in it slowly dying down. What had happened? Snatcher hadn’t so much as thrown a stone. \textit{Wait, where are the sentries?} Not a single legionary was patrolling the perimeter. There should have been someone, if only because of the ruckus my team had made hitting the Wolves. Slowly I felt my stomach sinking and I turned my eyes to Fox Company’s walls. In the distance, over the fort’s ramparts, a standard bearing crossed silver swords flapped lazily in the night breeze.

“Well,” I said. “That’s going to be a problem.
\clearpage
\chapter{Chapter 27: Callow’s Plan}

\textit{“What Foundling does isn’t thinking outside the box so much as stealing the box and hitting her opponents with it until they stop moving.”}
– Extract from “A Commentary on the Uncivil Wars”,  by Juniper of the Red Moon Clan

I crouched down and peered into the dark.
I couldn’t see where it linked up with the tunnels dug by Snatcher’s sappers but there was no doubt that it did: there’d been no assault on the walls and I hadn’t heard any munitions being used. Most likely First Company had taken the Foxes while they were spread out and preparing an assault of their own, decapitating the leadership before they could muster up a real fight.
“Hurried work,” Pickler noted from where she was crouching next to me, “but still stable. Juniper makes up for limited sapper assets by quality.”
First Company’s camp – the one my own legionaries had built – had been empty. Tents and bedrolls were still in place and often with rocks and debris slipped in so from a distance it would look like they were full, but there was not a living soul among the rocks. I sent Robber to link up with the rest of Rat Company as soon as I saw Juniper’s banner on the walls and went to follow the tracks coming out of the back of the camp. They led to the entrance of a tunnel hidden behind a nearby hill, freshly dug. \textit{Which solves the mystery of where First Company’s sappers had been holing up.} I sighed and forced myself back up. The night’s excitement was already catching up with me, though the ever-expanding list of issues I had to solve would keep me far away from my bedroll for the foreseeable future.
“Collapse the tunnels, Lieutenant,” I finally said. “That trick isn’t going to work for anyone twice.”
Unclasping the cheek flaps of my helmet, I set it down and took a moment to straighten up my ponytail. The part of the helm that covered my neck kept pushing down the leather strip keeping it together, though I usually didn’t notice until the fighting was done\textit{. I might have to get it cut soon}, I thought. It kept getting in the way, and I didn’t have the time to straighten the knots with my old beaten-up comb the way I’d used to: the whole mess was so tangled up it could have been used as a rope. \textit{Or a noose.}
“It’ll be done in a quarter bell,” Pickler spoke quietly. “A little more, if you want us to be thorough.”
“Thorough is good,” I grunted. “Have Robber do the same for the tunnels leading in Wolf Company’s camp, I’m not giving Juniper multiple ways out of that fortress.”
Sure, I could have used the tunnels too. But now that the element of surprise was gone she would just drop a handful of smokers in them whenever she caught sight of us and let us choke our lungs out in the dark before sweeping up whoever was still standing. Well, crawling. The point still stood.  I didn’t think she’d risk an assault herself, considering we could do the same to her, but I wasn’t going to be taking chances with the Hellhound. Snatcher evidently had, and how had that ended up for him? I made my way up the hill, ducking around a stone spire that looked a little too unstable for my tastes and allowed myself to drop on the ground after checking the close-by bush for snakes.
Ratface had informed me that pretty much everything out in the Wasteland was either poisonous or out to eat your liver – and possibly your soul – before he’d been taken prisoner. Something about how everyone who took over the Tower let out the experiments of the last Tyrant into the wilds, which seemed like a horrible idea to me and therefore entirely in line with the usual Praesi way of doing things. I closed my eyes and lay back against the rock, taking comfort in the fact that I was out of sight and therefore none of my troops could see me totally at a loss for what to do. Nauk had pulled out of Fox Company’s fortifications before Juniper had taken them and been entirely unaware of their taking over when Robber had made contact with him. I’d ordered him to take our survivors in the hills beyond either of the already-made camps as soon as he finished looting Wolf Company’s supplies.
It would have been more comfortable to stay in one of the camps instead of pitching our tents out in the wilds, but by now Juniper was bound to have gotten her hands on the ballista. I wasn’t sure what the range on that thing was, but Snatcher had believed it could reach First Company’s camp and that meant we weren’t sticking around. Not that ducking out of sight was going to accomplish anything in the long term: Juniper was still holed up in that \textit{fucking} fortress, with only token casualties and a godsdamned siege weapon to point at my company should it attack. There was no sign of the prisoners taken during our little betrayal reach around from earlier, though I’d found the tents where they’d been kept, so I was still down in the fifties when it came to my effective fighting force. \textit{Which nearly half of is sappers, and those are worthless in a melee.}
What did I have that Juniper did not? She had more men, a better position, and considering she must have ransacked Snatcher’s stocks like I had Aisha’s we should be about even on munitions. I’d have more demolition charges, considering Wolf Company had taken a Siege inventory, but my cadets would have to get close to use those. \textit{And I’ll eat my helmet if she didn’t grab all the crossbows she could from Fox Company’s men.} My plan had been an elegant thing, when we’d started out the melee. Betray Morok to Aisha, betray Aisha to Snatcher and betray Snatcher to use his fortifications against Juniper. The moment Wolf Company had turned on me, though, it had all gone up in smoke. I’d been on the back foot ever since, and the moment I’d thought I was getting a modicum of control again the Hellhound had turned the entire thing on its head by ending Fox Company in one swift blow.
Gods, I was tired. Tired and out of ideas to use against a captain who it was becoming obvious was just better at Legion tactics than I was. It shouldn’t have come as a surprise, really. Juniper had trained for years in the College and she was the daughter of one of the most talented generals in the Empire. And yet, on some level, I’d still expected things to turn out to my advantage. They had back in Laure, when my murder had turned into an apprenticeship to Black, and once again in Summerholm when the cock up with the Lone Swordsman had turned into a mess I’d been the most effective at exploiting. Chaos was something I was good at dealing with: rolling with the punches was a skill I’d perfected through my years in the Pit and it served me well when things spun out of control.
The hard truth was that, right now, my bag of tricks was empty. None of the things I’d learned on my own were of any use, and what had Black taught me since I’d become the Squire? A lot of history, some generalities and the basics of swordsmanship. My Name was a recalcitrant little brat and even if it had been cooperating I barely even knew how to use it. I closed my eyes and forced myself to think about nothing, letting the cool night breeze lick at my face. This was the most restful thing I could manage short of actually napping, and I was too wired for that right now. How long passed as I drifted away I couldn’t be sure, but eventually I heard someone make their way up the hill through the same path I had. I opened my eyes but didn’t bother to get up. Hakram eventually found me, raising a hairless brow when he saw me sprawled without even the pretence of dignity.
“Taking a break?” he asked.
“This is my thinking pose,” I lied.
The tall orc snorted, then took a seat next to me.
“Anything urgent?” I murmured.
“Not right now,” he grunted. “First Company’s not moving and Pickler is finishing up with the tunnels. You should probably call an officer meeting soon.”
“And tell them what?” I scoffed. “That I have no idea how to get us how of this mess?”
It helped that we weren’t looking at each other. I wasn’t sure I would have managed to admit that if we’d been face-to-face. I liked Hakram, probably the most out of all of my officers. He had a steadiness to him that I found soothing, and even outside the games he was good company.
“Nobody’s expecting miracles out of you, Callow,” he finally said. “You already got us much farther than anyone else would have.”
“I’m also the one who got Rat Company in this mess in the first place,” I replied bitterly. “Pickler was right. If I screw this up your careers are going to suffer, all because I thought I was better at this than I actually am.”
It was oddly relieving to admit that out loud. I hadn’t quite grasped the kind of damage putting Rat Company’s score so horribly in the negatives would do to my cadet’s placement in the Legions. And yet I could be honest enough with myself to admit that even if I had, I would have made the same gamble.
“You knew the risks,” my sergeant gravelled. “And took the chance anyway. Why?”
There was nothing confrontational about the orc’s tone. He was, from looks of it, genuinely curious. Trusting implicitly that I’d had a good reason for what I’d done.
“We win this and I’ll get command of the Fifteenth Legion,” I confessed quietly.
He did not point out that there was no Fifteenth Legion currently in existence, or even a Fourteenth for that matter. I was grateful for it: I was still vague on the details myself, and did not feel like having to explain any of it.
“And if you lose?” Hakram asked instead.
“Heiress gets it,” I replied. “She played me, in the Tower. Called it a wager when it was the most one-sided deal I’ve ever heard of – and I lived under the rule of Governor fucking Mazus.”
“That’s how they do things, Callow,” the orc breathed out slowly. “They give you one out to have the pretence of fairness and then tighten the screws. Then they smile and ask how can it be their fault, when you had a way to win but failed?”
There was something bitter in the orc’s voice, an old anger that might not have ruled him but was never far from the surface. It was something I could relate to.
“You ever want to change the world, Hakram?”
He laughed quietly. “World’s always changing, Callow. We roll the boulder up the mountain until it falls down the other slope, and then we start again. If you’re lucky, it doesn’t crush anything you care for on the way down.”
“And that’s all we can hope for?” I grimaced. “Not to be crushed?”
“For people like me?” Hakram gravelled. “Yeah. It is. But you’re not like me, Callow. For some reason, you seem to think you can fix this mess. I don’t know if you really can. Hells, I don’t know if anyone can.” I could feel him smile without looking. “But I’d like to see you try.”
He pushed himself up and offered me a hand.
“So get off your ass, Callow, and start scheming again. We’re not down for the count yet, and I’ll be damned if we don’t go out making a bloody mess of it.”
I looked into the orc’s dark eyes and felt a spike of guilt through my stomach. It had been easier to think of the legionaries I wanted to command as tools before I got to know them. I took his hand and let him drag me up.
“Catherine,” I finally said. “Call me Catherine.”
We made our way back down the hill and I got my head back in the game. I called a meeting as soon as I found a runner, though I didn’t bother to limit it to senior officers this time. There were few enough of us left, and I’d had my own sergeant attend every one of them so far anyhow. Kilian’s sergeant had been taken prisoner with Ratface but the former captain’s own second-in-command was still with us, a stocky female orc named Tordis. She’d remained quiet so far, her brown-red eyes shifting from one lieutenant to the other as they finished giving their reports.
“We set up everyone on half-watches since it’s unlikely the Hellhound will move again tonight,” Nauk finished in a grunt. “Camp’s not fortified, but with our position it’ll be hard for them to sneak up on us.”
Nilin looked exhausted, I noticed. His eyelids drooped every few moments and twice now I’d seen him pinch his own wrist. Pickler and Kilian seemed in a better state, though it was admittedly hard to tell with the goblin. As for the sapper lieutenant’s main minion, he’d been chewing on something through all the reports which I took mean he was just fine.
“We won’t be doing anything until the sun is up either,” I told them. “Rest up your cadets as much as possible, we’ve got a rough patch ahead of us. That said, Robber, what the Weeping Heavens are you eating?”
The small goblin noisily swallowed.
“Goat,” he replied. “The one we hunted. First Company roasted it and left some scraps when they moved out.”
I raised an eyebrow but passed no further comment. Rations wouldn’t be a problem for us: we’d taken both Morok’s and Aisha’s, so we should have enough for at least another four days. More, actually, considering we weren’t at full strength. I’d given thought to trying to starve Juniper out of the fortifications, given that there was no time limit in this melee, but we’d come to a head long before that. Hunting for more game would be unnecessary, though fresh meat might improve morale if I had the time. Huh. Fresh meat.
“You’re a brilliant little bastard, Robber,” I told him.
“One of the fundamental truths of Creation,” he agreed without missing a beat.
I ignored his gloating. “We’ll be sending hunting parties out with dawn,” I told my officers. “As many as we can.”
Pickler eyed me like I’d grown a second head.
“May I ask why, Captain?” she said hesitantly.
I clenched my fingers and unclenched them. “I’m going to fell some trees to make some carts.”

—

By Noon Bell the next day I had laid out in front of me three goats, a pretty mangled antelope and what looked like a rabbit with horns. Wait, did it also have \textit{fangs}? Why would – no, it didn’t matter. Trying to figure out why a Dread Emperor had created a breed of carnivorous rabbits would gain me nothing except a splitting headache. The creature would be useless for my purposes anyway, though I supposed that was my own fault for not being more specific.
“I don’t know where this is going,” Robber announced cheerfully, “but the fact that step one involves slaughtering the local wildlife has filled me with great expectations. Sir.”
In an entirely predictable turn of events, my praise had gone to Robber’s head with swift efficiency. The better part of my sapper line was standing in the sun looking at the line of corpses with politely confused expressions. I’d seen Pickler open her mouth and then close it without saying a word several times from the corner of my eye.
“One of the goats first,” I muttered to myself.
I knelt next to the closest corpse and closed my eyes, reaching for my Name. It felt faraway still, but not as much as it once had – the last few weeks had begun to repair the bridge I’d damaged, one morally dubious decision at a time. This was different in nature to tapping into one of my aspects, where I let the power flow through me and harnessed it for my own purposes. I was submerging myself into my Role, reaching for those cool depths I’d touched only twice before. For a moment nothing happened, but then I felt it. That great weight pushing against me, the coldness unnatural to Creation that somehow managed not to feel \textit{wrong}. I smiled and felt a sharp prick against the palm of my hand, like I’d been jabbed by a needle. The coldness spread to the goat’s corpse. I got back on my feet and, after a heartbeat, so did the goat. I tugged at a string and its head turned to look at me. Another exertion of will and it stepped forward, then back.
“Necromancy,” Pickler spoke after a blink of surprise. “I did not know you were a mage.”
“I’m not,” I admitted. “This is Name shenanigans, I’m not entirely clear on how it works.”
The goblin lieutenant was openly dubious but managed to rally valiantly. “So we now have a goat. This is… progress?”
“You’re going to carve it up,” I told her. “And put munitions in it.”
There was a moment of silence until Robber’s convulsive laughter filled it.
“Oh Gods,” he gasped. “Juniper’s got a fortress and our answer is \textit{suicide goats}.”
“I’m not sure if that’s technically accurate,” I frowned. “I mean, they’re already dead.”
Another burst of laughter. “Undead suicide goats,” he corrected himself breathlessly. “Very sorry, Captain. For the record, I don’t care whether we lose this one anymore. This is already a victory in every way that matters.”
Engaging him any further would just be seen as encouragement, I decided. I turned to Pickler, who looked like she wasn’t sure whether to be appalled or impressed. I had a feeling it was not the last time in my career a subordinate was going to be looking at me this way.
“I want the first one to have enough munitions stuffed in that it can blow cleanly through the palisade,” I told the lieutenant.
Pickler cleared her throat. “Punching our way through the first wall will be pointless if the entire First Company is arrayed behind it,” she pointed out. “We’ll still be outnumbered and outclassed.”
“We’re not going to be fighting them, Lieutenant,” I grunted. “The only thing we have going for us right now is a ridiculous amount of munitions and the ability to make expendable carriers for them. I intend to abuse that as much as possible.”
She nodded, uncertain but unwilling to argue.
“We’ll still need to get a mage in range to detonate the… goats,” she reminded me.
It took a visible effort to speak the last word of that sentence.
“I’ll escort Kilian onto the field,” I replied. “I need line of sight myself for fine – \textit{Robber stop godsdamned touching it}.”
I could feel the goblin’s fingers poking experimentally at the corpse’s skin, which added that layer of additional creepiness to an already eerie feeling. The sergeant grinned unrepentantly in my direction.
“Permission to name the goats, sir?” he asked.
“Denied,” I replied without so much as a speck of hesitation.
“Both Morok’s Revenge and I are very disappointed in your decision, Captain,” he told me, patting the goat’s head comfortingly.
“Morok’s Revenge?” I repeated, already regretting the quizzical intonation before I’d even finished saying the words.
“It’s the ugliest and least impressive of the three,” Robber provided cheerfully.
I really needed to have a closer look at Legion regulations. It was an Evil institution, there was bound to be a loophole that allowed you to strangle irritating minions in the bylaws.
“Well. He’s not wrong,” another of the goblins muttered.
“Oh, we can have another one referring to Bishara,” a third contributed excitedly. “Something like ‘Aisha’dnt Have Done That’.”
The meeting quickly devolved into my sappers throwing around progressively more absurd names for our secret weapons.
“Pickler,” I spoke flatly, turning to the embarrassed-looking lieutenant who was watching the madness spread through her cadets. “I expect you to find a truly vicious punishment for the one that made the pun.”
Without a single look back I walked away, massaging the bridge of my nose and ignoring the indignant cry of “we’re not naming it ‘Ratface’s Ex’, he’s not even here to hear about it” for the sake of my sanity. \textit{Sappers. Mad, every last one of them.}

—

Keeping my tenth in a ramshackle testudo formation meant we could only move slowly, but it was necessary nonetheless: I didn’t want any of the soldiers on the wall to see our trump card until it was too close for them to do anything about it.
“Incoming,” Kilian hissed, a streak of fear in her voice.
I popped my head out from behind the cover of the shields, immediately seeing the stone sailing across the clear afternoon sky. First Company had overshot – it was in no danger of hitting us and landed on the hill behind my tenth. The geyser of sand and stone caused by the impact made it very clear that none of us would be getting back up if Juniper landed a shot properly, though.
“Pick up the pace, cadets,” I ordered.
From the looks of it Juniper had put two lines up on the palisade Snatcher had helpfully built for her, which wouldn’t have been as much of a problem if even from where I stood I hadn’t been able to glimpse that the cadets were armed with crossbows. I knew the Hellhound could easily have fit twice as many legionaries behind the wall, which probably meant she was trying to bait me into an assault. If I’d truly been in straits as desperate as the ones she believed, it might even have worked.
“Another thirty feet, then we disperse,” I told the legionaries in a whisper.
A few of us would probably get shot by crossbow bolts – we were already in range, actually, but limited ammunition meant Juniper had likely ordered her legionaries to hold off until they could make the bolts count – but if it was a choice between that and continuing to present a good ballista target then there was no need to think about it twice.
“Even a glancing hit will set it off,” I reminded Kilian in a murmur. “The demolition charge alone would have done the trick but they added a few sharpers just in case.”
The sappers had spent quite some time tinkering with the munitions after carving up the corpse. I’d become a little curious about what it would look like when Morok’s Revenge went out in a blaze of glory.
“Ten feet,” I warned my cadets after peeking out from behind the shields.
I counted my breaths in silence, glancing at Kilian every few moments to verify the ballista wasn’t about to make us a moot point. The redhead’s face remained outwardly calm, tough the way her fingers held the grip of her sword so tightly her knuckles were paling was something of a giveaway for her true state of mind.
“On my word, disperse,” I whispered.
My legionaries immediately scattered, leaving Kilian and I standing beside an already moving undead. The mage lost no time in chanting her incantation as I willed the goat to move more quickly, crossing the last dozen feet separating it from the palisade in moments. There was a cry of alarm from the soldiers behind it but it was late, too late, and the fireball flew from Kilian’s outstretched hand. It clipped the side of the animated creature, and that was enough. There was a flash of light and then thunder struck, the explosion outright shattering a chunk of the palisade at least ten feet wide. The redheaded lieutenant and I started legging it without missing a beat, though a part of me wanted to stop and gape. Neither of us stopped before we were well in cover behind another hill: I dropped down, catching my breath and making a quick headcount. None of my cadets had been shot, it seemed. Lucky us.
“The explosion should not have been that large,” I got out breathlessly. “Or that intense.”
“It’s because of the Name, I think,” Kilian panted. “Munitions are alchemy, they can feed on other power sources.”
I closed my eyes. So, my trump card was more effective than previously anticipated. I could work with that.
“Send Nauk a runner,” I told the lieutenant. “We start phase two immediately.”
\clearpage
\chapter{Chapter 28: Win Condition}

\textit{“Our doctrine is one of cost-efficiency. Any officer who believes extermination of the enemy is a valid path to victory should immediately be demoted back to the ranks.”
–}Marshal Ranker

“What makes you think she’ll abandon the first wall?”

Kilian’s breath was steadier now that she’d had a few moments to catch it. Running in chain mail could really take it out of you, and if Captain hadn’t made a habit of drilling me in plate it might have been as hard on my lungs as the redhead’s. I cast her a sideways look.

“Having doubts, Lieutenant?” I asked.

She shook her head. “I’m trying to understand where your certainty is coming from,” she replied.

“It took me a while to get it, but Juniper’s actually somewhat predictable,” I grunted.

Now there \textit{definitely} was scepticism on the pretty mage’s face.

“Predictable is, uh, not a word I’d use for the Hellhound. Sir,” she said delicately.

“She always makes the correct choice,” I pointed out, closing my eyes. “When she has the necessary information, she makes the best decision she could make.”

Kilian frowned. “So you’re saying…” she trailed off, evidently not too sure about what I was saying.

Couldn’t blame her, really. This wasn’t something I’d figured out using wits and logic – it had been instinctual. Similar to the way I’d read opponents in the Pit, only applied to warfare instead of breaking a single person’s legs.

“If I know what the best move for her to make is, I can be fairly certain it’s the one she’ll make,” I replied, opening my eyes and turning on my belly to crawl my way closer to the crest of the hill.

The redheaded lieutenant did the same, joining me in taking a peek over the dust and stone. Like I’d predicted, First Company’s lines were preparing to retreat back across the mine field. One of Juniper’s sappers casually tossed a smoker into the hole I’d blown through the palisade a moment later, preventing me from getting a look at the path they were using. \textit{Ugh. I mean, I was pretty sure they’d do that but it’s still going to be a pain to figure out the way through.}

“It’s limited in scope, Kilian,” I told her as I pushed myself back into cover. “I have no reliable way of knowing what she does and doesn’t know, so it’s still very much a guessing game. But if I have the initiative, then I can predict some of her reactions.”

I waved vaguely in the direction of what had once been Fox Company’s stronghold.

“What she knows right now is that I have access to munitions that can blow through her first wall and some sort of expendable creature minions to deliver them,” I grunted. “So she’s going to pull back behind the rampart until she can figure out how I managed that. It’s not like she’s losing anything, anyway: even if we manned the first wall from the other side we don’t have the strength to hold it against her. She could just claim it back whenever she wants.”

By now the runner I’d sent to Nauk should have gotten the remnants of my company moving. Keeping out of sight as long as possible, they’d wait until the last moment to run across the ballista’s killing field until they could take shelter behind the enemy’s own palisade. Pickler had assured me that the same platform Snatcher had built to ensure the siege engine would have a clear shot at the enemy camps meant that once we got close enough Juniper wouldn’t be able to adjust the angle low enough to aim at us. There was something mildly absurd about using the enemy’s fortifications as cover against them, but the situation I was in was beyond the ability of orthodox tactics to salvage.

Pretty much the only advantage on my side at this point was that by holing up in the fortress Juniper had given up the initiative. It was, I believed, a conscious decision on her part. She could have assaulted us almost immediately after taking out Snatcher, but the Hellhound was aware of what kind of fuckery Names could pull when you put their backs up against the wall. She was doing all she could to avoid outright cornering me while still stacking the odds on her side. If I’d decided to pull out and head into the wilds, then she would have simply followed in her own time: First Company functioned at its best when on the field, so it wasn’t like she’d have been giving me much of an edge there. Regardless, after hitting the bottom of the barrel last night I’d bounced back into the semblance of a plan. My largest mistake so far was that I’d been trying to beat Juniper as a captain when the fact was that she was just \textit{better} at this than I was.

She was a better tactician and her company was flatly superior to mine – which shouldn’t have come as a surprise, considering Ratface had tried to make Rat Company a knock-off version of hers. If I played this game the way it was meant to be played, I’d lose every time. Like Black had told me in his usual semi-cryptic jackass advice session, I had to win despite the rules instead of according to them. The suicide goats were a first step towards that, as a method of attack that had no real precedent in the war games. The necromantic constructs weren’t significant because of how effective they were, although it looked like they’d be pretty damned effective, but because by pulling out a new trick I’d been able to seize the initiative. As long as I had Juniper reacting instead of acting, the Heavens were on my side.

“Although I guess technically they’re on neither of our sides,” I muttered to myself. “Probably should stop calling on them period.”

Kilian shot me a curious look but passed no comment. I glanced at my tenth and was pleased to see they appeared to have recovered from the run. Whatever his flaws as a captain, Ratface had drilled his legionaries into very good shape.

“As soon as Nauk gets out of cover, we’ll be running across,” I called out, making sure all of them acknowledged the reminder before turning my attention back to more pressing matters.

Crawling my way back up the hill, I scanned the distance for the rest of my company. Couldn’t see any sign of them, which I put down as another mark in Nauk’s favour: the large lieutenant was a highly competent officer, when he wasn’t in the throes of the Red Rage. Overly aggressive in his tactics, maybe, but for a frontline commander that wasn’t always a bad thing. Captain had mentioned General Istrid was also considered a little too bloodthirsty and she was one of the most respected military commanders in the Empire. After the three Marshals, she was one of the household names forged during the Conquest. I waited in silence for Rat Company to appear, and my patience was eventually rewarded: without so much as a word of warning, sixty-odd legionaries started running downhill towards the palisade.

“That’s our cue, ladies and gentlemen,” I called out, pushing myself up.

I picked up my shield and waited a few heartbeats before starting to sprint back across the grounds I’d covered only moments ago. There was no point in having my legionaries form up: if anything, it would be a liability. A tenth moving slowly and clustered together was prime ballista bait. Feeling my lungs burn as I forced my body to move, I jumped over a low-riding bush and only barely managed not to trip as my foot got snagged into a root. Whirling on myself I steadied my footing at the last minute and continued to push through. My tenth wasn’t far behind and before I’d managed to catch my breath at the foot of the palisade the majority of them were already at my side.

“We got everyone?” I panted.

Kilian nodded, too out of breath to get any actual words out. Gods, I hated running in armour. I’d heard no impact in the distance, which meant First Company either hadn’t been ready to shoot in time or that we’d offered them no target worth the effort. Nauk’s soldiers were milling by the palisade further to the south-east, slowly spreading out, and I gestured for my own tenth to join them. We walked, taking our time – there was no need to hurry this part of the operation, and going in unprepared was likely to see us brutally spanked. The lieutenant with the still-broken arm found me easily. There was a restless way to him, like he had an itch he couldn’t quite scratch.

“Callow,” Nauk greeted me. “Divided the lot of them like you told me. We’ll be ready to move as soon as Kilian reclaims her tenth.”

From the corner of my eye I could see the redhead heading for her mages, soldiers moving out of her way as she did.

“Good,” I grunted. “Pickler managed to make all the screens?”

“They’re ready,” the orc nodded. “Shame we don’t have vinegar to soak them in, but we’ll make do.”

I’d been more than happy to delegate the whole affair to the sapper lieutenant, having no experience whatsoever in crafting the likes of it myself. To be honest, my skillset largely considered of “bashing people’s heads in” and “ordering people to bash other people’s heads in”. It was a good thing that for all their quirks my officers had a knack for their area of expertise, because what I knew about sapper’s work would fit into a thimble. And not even a very big one.

“Wish I could do more than stand around like a waste of flesh,” Nauk admitted. “I’ve been useless to you since the scrap with Morok.”

I clapped his shoulder. “I don’t need someone to break skulls right now, Nauk,” I told him honestly. “I need someone to watch over the company while I try to outmanoeuvre Juniper, and you’ve done that just fine.”

The large orc shuffled his feet uncomfortably. He looked pleased – or hungry. It could be hard to tell with orcs.

“Wade in their blood, Captain,” Nauk gravelled. “I’ve been looking forward to this part since you told us the plan.”

So had I. It was about time we got to be the ones causing trouble. I left the orc lieutenant to it and went to check on the walking absurdity that was my trump card. Unsurprisingly, Robber was the one watching over Ratface’s Ex. My legionaries insisted on calling the goat by the verbal abomination that was the other proposed name, but I refused to humour them in this. A girl had to have \textit{some} principles, and I drew the line at puns.

“Everything ready, Sergeant?” I asked.

“On our part, sure,” the goblin replied, eyes still fixed on the unmoving goat. “Can’t answer for Lieutenant Kilian’s merry parade of magical minions.”

I let the dig pass without comment, since he’d at least bothered to tack on Kilian’s rank to it. Kneeling next to the corpse, I touched its forehead and with an exertion of will had it rise to its feet. To my surprise I’d manage to raise all of the carcasses provided by my men without any real trouble, though I’d yet to figure out how to manipulate more than one at a time. The corpses remained still unless I willed it otherwise, and I’d found that after leaving one alone for too long I needed physical contact to make it work properly again. There would be no zombie army for me, it seemed, and Weeping Heavens when had I reached a point in my life where I was using the words “zombie army” without a hint of irony?

“Tell Pickler to get the line in position,” I told another sapper standing close by. “We won’t have much time between the first hit and the second.”

The female goblin saluted and scuttled off without a word as I returned my attention to the zombie. My main obstacle at the moment was the mine field. Assaulting the rampart was nothing more than a daydream as long as my company hadn’t secured a way across it. That we weren’t in the ballista’s angle of fire anymore was one problem dealt with, but the fact remained that any people I sent through would be getting peppered with crossbow fire the whole time. I could more or less deal with that by putting my cadets in a testudo formation, but packing them that tightly as they made their way through a field line with demolition charges would lead to horrific casualties. My first step, then, was to be clearing a safe path for my company. Thankfully, I had expendable assets to send into the grinder.

Ratface’s Ex dutifully followed me as I passed through the gap I’d had blown into the palisade, coming to stand at the edge of the killing field and gazing at the rampart. As expected the top of it was bristling with enemy legionaries, all of them armed with Snatcher’s crossbows. I couldn’t see Juniper, but I had no doubt that she was standing somewhere she could see the whole battlefield. Behind me my sapper line trickled through the hole, the front ranks carrying large screens of leather framed by repurposed sudis. All of the components had been cannibalized from Aisha’s camp, the leather coming from her tents and the wood and nails taken from her first line of defence. In the absence of the second tenth of my mage line and their large shields this ramshackle kind of cover would have to serve – much to my displeasure, every single member of that tenth had been taken prisoner with Ratface. Kilian’s mages spread out among the sappers in groups of three, the redhead in question coming to stand by my side in silence. I cracked my fingers and took a deep breath\textit{. Time to get the stone rolling.}

Before I could get so much as a word out, Robber broke formation and strolled to the edge of the field. Straightening his back, he stood as high as his four feet and a half of height allowed him and slowly unsheathed his sword. Face solemn, he brandished the blade at First Company.

“\textit{Unleash the goat},” he commanded, clearly relishing every word coming out of his mouth.

“Remind me to stick him with latrine duty for at least a month,” I told Kilian in an aside.

The mage snorted. With a sigh, I willed the goat to move forward. The pace I set was fast, though not enough to damage the corpse’s integrity, and I set it to a path that passed straight through the middle of the field. It was facing the only part of the ramparts that wasn’t ten feet high: instead of packed rock and dirt there was a palisade there serving as a makeshift gate. More importantly, it was the only part of the fortifications that wasn’t barred by the ditch. The goat made it about fifteen feet before the sand under it detonated. I grimaced. It was a good thing that my ability to sense through the creature’s skin numbed pretty quickly after I raised it, otherwise that would have been a bitch of a backlash. I focused on my connection to the necromantic construct and noted that while it was damaged it was still, in fact, capable of moving. \textit{Makes sense. Snatcher’s not going to use a munition grade that risks actually killing other cadets.} No doubt a living creature would have been knocked unconscious or, barring that, been incapacitated by the shattered bones. Fortunately, Ratface’s Ex had no such limitations. Mustering vague memories of when I’d done the same to my own fingers, I pulled at strings and popped the goat’s bones back into place. It slowly got back to its feet and started limping forward the field. It managed to make it to fifty feet before the first fireball from the rampart struck it. Another three followed almost a heartbeat later, hitting the goat almost simultaneously.

“Gotcha,” I grinned sharply.

“NOW,” Kilian called out.

My three clusters of three mages immediately fired back fireballs of their own straight at the source of the enemy magic. All but one of the enemy casters were drowned in a storm of flame before they could get back in cover. One fireball they might have weathered without too much damage, but three? Those three mages had been knocked out of the melee for now. Unfortunate that I’d had to split my mage line in clusters of three instead of pairs, but Kilian had informed me she couldn’t promise a sure takedown if she couldn’t concentrate the magic at least that much. First Company was superbly trained: before I could count five heartbeats the rest of its mage line was returning fire at my now exposed mages. \textit{Too late, Hellhound.} My sappers moved their screens forward and the mages ran to take cover behind the stretched out leather. I frowned as the flame impacted Pickler’s screens: two of them held up admirably, but the third’s frame splintered as fire spread across its surface. Kilian cursed and I followed her gaze to a lone silhouette on the rampart, where a mage’s raised hand was slowly wreathing itself in bolts of blinding energy\textit{. Shit.} I hadn’t anticipated Juniper would have any mages capable of calling down lightning. If they managed to hit the screen that had already been damaged…

“No you don’t,” the Duni growled.

The redhead bit her thumb as I blinked in surprise, drawing blood and swiping a line of it across her cheek.

“I am the root and the crown, the source and the flow, the storm and the calm,” she murmured. “Power is purpose, purpose is will. Gods of my mother, take this offering and \textit{grant me the wrath of Heaven}.”

The last words were an angry hiss, and she threw her hand forward in a snap. A gauntlet of lightning burst into existence around her fingers, a thick thread of it streaking forward across the air with a violent crackle and colliding with the bolt thrown by the enemy mage maybe four feet above my fleeing soldiers. The magic impacted with a deafening howl but Kilian’s spell held, both streaks of lightning flickering out of existence after the clash. My lieutenant’s cheeks were flushed and she was panting, the streak of blood on her cheek somehow turned to ash.

That had been… impressive. And, if I was to be entirely honest, just a little bit arousing. Seeing her harness that kind of power with nothing more than a handful of words and being pissed off… I coughed and turned my attention back to the now-smouldering Ratface’s Ex. Now was definitely not the time to wonder what the redhead looked like out of her armour.

Unfortunately, my zombie was no longer in a state fit for running. I willed it to crawl forward anyhow and it made it another ten feet before a last fireball destroyed it beyond even my ability to control. I clenched my fingers and unclenched them. \textit{Sixty feet out of a hundred, not bad.} The question was, was there another charge buried in those last forty feet? The path I’d cleared was the easiest, quickest way to the fort’s entrance. If there was somewhere to mine, that was definitely it. On the other hand, Snatcher might have thought that no one would be stupid enough to go further in a straight line after running into a charge fifteen feet in. Out of my four undead, two were already unusable. The remaining goat and the gazelle were loaded with munitions I couldn’t afford to lose on a mine: I needed that gate blown up, and quickly.

“Well, Snatcher,” I murmured to myself. “Here’s hoping you decided to get tricky on our asses.”

Pickler had brought the next goat forward when she’d moved in her sappers, propping it up against the palisade like it was a poorly-built bookshelf. It took no more than a few moments to re-establish my connection with the undead, the animated corpse skipping back with me when I returned to Kilian’s side.

“Give the signal,” I ordered her. “We’re beginning phase three.”

“Operation Fainting Goat is a go,” she murmured, and I shot her a genuinely betrayed look.

Kilian had been one of the few strongholds of sanity left when the undead suicide goat plan had spread to the rank and file, that she would get on the wagon now was treachery of the worst sort. That Hakram had been the one to dryly suggest the name was even worse. Regardless, the mage raised her hand and with a few mangled syllables created the Miezan numeral for three out of flames. A moment later half of my sappers got moving, escorted by the surviving tenth of Ratface’s line: Sergeant Tordis led from the front, shield raised high. This would be the tricky part, when it came down to it. I should have made Juniper wary of using her mages by making it clear my own would immediately retaliate but she had other options. Risking one of my remaining tenths in fighting shape left a foul taste in the mouth yet it was necessary if the sappers were to get within range without getting put down by crossbow fire.

The first bolts hit when they’d made it twenty feet in through the path I’d cleared. Immediately my regulars tightened their ranks and the sappers crouched behind them, the lot of them still pushing forward at a glacial pace. When Juniper’s mages popped out my own were ready to pre-empt them, but she was ready for us this time: every one of First Company’s spellcasters had a pair of soldiers covering them with their shields. Not even concentration of fire managed to break through it. I grimaced when the enemy’s own fireballs impacted Sergeant Tordis’ group, knocking three cadets out of formation and immediately seeing them shot.

“Kilian,” I spoke up. “That thing you did with the lightning; could your mages do the same with enemy fireballs?”

“No,” she admitted. “The spell they teach us at the College isn’t precise enough for that.”

“Godsdamnit,” I cursed, watching as another two members of Tordis’ tenth bit the dust. “This is going to cost us.”

They were in position now, at least. The sappers wasted no time in throwing their smokers ahead, their whole position becoming obscured by the thick smoke in a matter of moments. They started backing up almost immediately, another regular getting hit by a blindly-thrown fireball but managing to shake it off since it wasn’t immediately followed by getting shot. The sappers dragged back our unconscious cadets, the entire formation managing to get back safely out of enemy range without any further trouble. From fifty feet into the path to the very bottom of the enemy rampart was now covered in smoke, but there was no time to waste. Smokers didn’t last as long when the space they filled was that broad, and though the day wasn’t particularly windy it wasn’t absent of wind either. Without so much as my looking in its direction, the goat started running forward.

“So what’s this one called, anyway?” I absently asked Kilian.

I could feel her smile through the tone, though my attention was still on my zombie.

“Snatcher’s Cousin,” she replied.

“That feels mildly racist,” I mused.

“Can it really be racist if goblins are the ones who named it?” she wondered out loud.

I didn’t answer the question, as the Cousin had finally entered the smoke. I’d ordered the obscuration of the battlefield to ensure Juniper couldn’t blow the zombie before I did, but the obvious downside was that I couldn’t see where it was going either. All my Name was giving was a vague sense of where it was standing and how its parts were moving. It would have been useful if I’d been able to see through the zombie’s own eyes but when it came down to it what my ability could create was little more than an elaborate flesh puppet. All I could do was send it in a straight line and hope for the best. With a silent tug of the strings I had the goat halt at what I estimated was about eighty feet, returning a portion of my attention to Kilian.

“I can have it at the gate in about six breaths,” I told her. “Tell me when to get it moving.”

The redhead frowned but nodded, eyes faraway as she tried to puzzle out the timing. Aiming for perfection here would be overestimating ourselves but we couldn’t let it stand in front of the gate too long either: I couldn’t take the risk Juniper had figured out a way to deal with it without blowing it up. Frankly, just sending out a legionary to pick it up and run back inside might do the trick if they were fast enough. The mage softly started chanting and I kept an eye on her as red-orange flames started forming around her hand. Suddenly she nodded and instead of replying I set my construct moving, the ball of flames shooting into the smoke a moment later. A few heartbeats later I felt the goat run into something solid. The explosion that struck a moment later was, once again, deafening. While I couldn’t see the effect of it through the smoke, I had a hard time believing it wouldn’t have wrecked the gate. There were twice as many sharpers stuck inside the goat as last time, after all. Hopefully none of Juniper’s soldiers had been standing right behind the gate, because that would have been pretty brutal to go through.

“Now what?” Kilian asked, peering into the distance.

“Now we-“

Before I could finish the sentence a flash of lightning came out of the smoke. I reacted on instinct, trying to get Kilian down, but she pushed away my hand and thrust out her arm. I felt goose bumps on my arms as she spat out a word in that strange tongue mages used, sorcery meeting sorcery once again. Whatever it was she’d done, it stopped the better part of the lightning:  a shudder run through me but that was the only effect I could feel. The redhead fell on her knees and I made to help her up when I noticed her hair had turned… strange. It looked more like fire than dark red locks, and when she turned to face me her eyes had turned from hazel to an inhumanly vivid green. Her body had a spasm, her back arching like something was trying to break out of it, and I wasn’t sure whether I should try to hold her down or let it happen. Thankfully, after a moment it stopped.

“Fuck,” she cursed, the words coming thick and slow on her tongue. “I hate it when that happens.”

I helped her back to her feet. “Too much magic?” I guessed.

“Tried to abshorb – \textit{absorb} – the hit to keep it from splashing,” Kilian replied.

She took a deep breath, then stood on her own.

“I’ll be fine, Captain,” she told me. “Bit of a headache, that’s all, and I’ll keep the spells simple for a while.”

I clapped her shoulder. “Take a break, Lieutenant,” I ordered. “Nothing’ll happen until the smoke clears anyway.”

I let her limp away without comment, deciding it was about time I relocated myself. Whoever had said lightning never struck the same place twice obviously had little experience with mages.

—

By the time the smoke cleared I’d returned to my old vantage point, the undead gazelle idling by my side. Robber had informed me it had been dubbed ‘Stealth Goat’ by popular acclaim at which point I’d informed \textit{him }that he was going to find me a stool or I would be dragging him along for the ride as my official footrest. I took great satisfaction in the fact that he looked genuinely worried by the threat. To my surprise he reappeared later with a fold-up stool apparently looted from Aisha’s camp. I blithely pretended I hadn’t been sending him on a fool’s errand and assured him he was safe from my feet for at least the next few days. The first thing I noticed when the ramparts came into sight again was that the new batch of munitions had \textit{definitely} been more powerful than the last. There was no trace of the former gate and even the tightly packed sand and stone surrounding it had been damaged.

I stood in sight of the walls for a long time, letting the lazy breeze fall on my face. Juniper must have believed I was baiting her mages, because there was no repeat of the lightning incident. I didn’t think it would have been enough to take me out anyway. I’d punched a sharper two days ago and all my fingers had gotten out of the experience was a set of bruises. Squires were a hard breed to kill, apparently. After remaining in the open long enough that there could be no doubt Juniper had seen me, I left Stealth Goat behind and casually strolled down the path I’d cleared earlier. I left my shield behind, keeping the folded stool under my arm instead. My soldiers milled uncomfortably behind me as I kept walking, stopping about halfway through without anyone from the ramparts trying anything. I was close enough to see that two full lines had crossbows pointed at me, but for now they refrained from shooting. Calmly, I unfolded the stool and placed it on the ground. I plopped myself on it and waited.

Juniper didn’t make me wait long. The tall female orc strode out of the gate-hole without a shield or a helmet, though like me she’d kept her sword at her side. I was amused to note she’d brought a stool of her own, of identical make. Must have been Legion-issue. Her face was inscrutable as she made her way towards me, setting up her own seat to face mine barely a few feet away. The wooden frame creaked under the weight of her when she sat down, still silent. A moment passed, then she turned to the side and spat in the dirt.

“So you want a draw,” she flatly stated.

I raised an eyebrow. “That obvious, huh,” I said, not denying the truth of it.

“I looked up the old rules too, Callow,” she grunted. “Two-way draw means we keep half the points we bid. Probably shouldn’t have bid twice what Rat Company has in the negatives if you wanted to keep it quiet.”

The idea had struck me when the cadets Ratface had sent to scour the College archives for old five company melees had dug up a record three-way draw. When the instructors had outlined the rules for the melee they’d said nothing about draws of any sort, meaning they hadn’t specifically denied the old ruling. It was sketchy as Hells, but I was pretty sure I could swing it. There were advantages to having the Black Knight on your side, and if Heiress wasn’t above using family connections to her advantage then I wasn’t above pulling rank through my teacher.

“Figured it was a good thing to have as a back up, if things went south,” I admitted.

“You’d lose the bet,” Juniper pointed out.

“Ah, but here’s the thing,” I smiled. “The Dread Empress specifically phrased so that Heiress only got the appointment if I \textit{lost}. A draw isn’t a defeat, it’s just not a victory.”

\textit{And should, Gods forbid, our Squire lose}? Those had been her exact words. I’d wondered in the aftermath of court why a woman who was supposed to be the political patron of Black hadn’t seen fit to give me a helping hand when I was his de facto apprentice. It was only the night before the melee I’d realized that she’d subtly steered the terms of the bet to give me a better chance.

“Very clever,” Juniper smiled unpleasantly, flashing her fangs at me. “Now tell me, why exactly should I give a fuck?”

“Because it could go either way, right now,” I told her frankly. “I still have some of my little minions and I can make more.”

“You’ll run out of munitions eventually,” she growled.

“You’ll run out of \textit{soldier}s eventually,” I replied. “The munitions won’t take you out of the game, sure, but then I still have fighting men left.”

“Who’ll have to cross an open field while getting shot at,” the Hellhound snarled.

“They will,” I shrugged. “Which is why I’ll put my wounded in the front to soak up the crossbow fire.”

The orc’s eyes narrowed. “Some of them could be crippled for life. It messes up mage healing if you break the bones again too quick.”

My answering smile was a cold, cold thing. “You underestimate how badly I want this, Hellhound. If you have moral qualms about crippling cadets, then don’t shoot your fucking crossbows at them.”

That was the thing with scruples: they could so very easily be thrown back at the person throwing them at you. Juniper looked at me like it was the first time we’d ever met. In a sense, it was. My little interlude at the War College had been a pleasant diversion and I’d picked up useful skills, but there was a reason I’d come here in first place. I was not so much of a hypocrite that I’d flinch in the face having people crippled when I’d signed the death warrant of thousands by letting the Lone Swordsman go. The other captain rolled a shoulder calmly, chewing it over.

“No deal,” she finally said. “Nothing in this for me, Callow. Could go either way, sure. Means I could win.”

I sighed. “You know, I wondered what company scores were for when I first heard about them,” I told her.

She’d been about to get up but when I continued speaking she stilled. If she was confused by my interjection, then she showed no sign of it.

“Get your officers to brief you,” she grunted. “It affects placement in the Legions when you graduate.”

“I know that now,” I replied. “Didn’t seem like a big deal to me at the time, but then I remembered I had a dream.”

The orc bared her teeth mockingly. “You going to tell me you have all these big plans so I should let you win? For shame, Callow. You were almost starting to be tolerable.”

“Not that kind of dream,” I said softly. “I mean the Name kind.”

That got her attention, sure enough. Her mouth closed with a snap.

“The gist of it, I think, was that sometimes you have to give to get,” I mused. “So that had me wondering: what do you \textit{want}, Juniper?”

“You getting to a point would be nice,” she growled.

“See, I keep hearing all these things about you,” I continued. “The Hellhound, never lost a game. Best tactician to grace the College since the Reforms, top of the class in every class.”

I could see her mustering what was no doubt a pretty scathing retort but I interrupted her.

“The one thing I didn’t hear about you,” I spoke softly, “was that you‘re Istrid Knightsbane’s daughter.”

The orc’s meaty hand closed around the hilt of her sword.

“You threatening my mother, Callow?” she snarled.

I shook my head.

“It’s telling, that you don’t bring the family name into this,” I told her. “Means you want to make it on your own merits. Means you’re ambitious.”

“It’d be a pretty nice feather in my cap to waste you, you know,” the orc grinned nastily, “If I beat a Named on the field I’d join as a tribune, or at the very least senior captain.”

“You take your chances and try for that,” I agreed. “Or you could make a draw with me right now, and be named the highest-ranked officer in the Fifteenth Legion.”

She gaped at me and I really enjoyed the sight of it more than I should.

“You can’t promise that,” she growled.

“Sure I can,” I retorted flatly. “The whole thing with being a villain, Juniper, is that you can basically do whatever the Hells you want unless someone stops you. And who’s going to stop me in this? Black? If I know anything, he’s doing that vicious smile thing he does as he eavesdrops on us right now.”

The other captain got her bearings back after a few moments, her now calm face creasing with a frown.

“I’d be under your command,” Juniper said.

“You’ll be under someone’s command whatever happens,” I shrugged. “Do you want to serve under the shadow of someone who earned their spurs during the Conquest, or forge an entirely new legion with me?”

I could see the conflict in her eyes, and that meant I was winning.

“You’re bribing me,” she accused.

“Shamelessly so,” I admitted. “But the fact that I have to bribe you means you’re worth bribing.”

That got a snort out of her.

“All a draw means is that I’m admitting that, right here and right now, we’re equals,” I said, meeting her eyes. “I’m not too proud for that. Are you?”

I offered up my arm. After a long moment, she leaned forward and clasped it.

“Draw,” she grunted.

“Draw,” I echoed.

Thunder clapped twice and both our standards appeared in the sky, orange-red. We rose to our feet and I looked aside.

“\textit{Despite the rules}, you said. See? I do listen, sometimes,” I whispered.
\clearpage
\chapter{Epilogue}

\textit{“What say you, Empress of Praes? }
\textit{Here you lie upon the blood-soaked ruins of your dominion, surrounded by the corpses of the legions that once swarmed over the world.  Hundreds of thousands dead for the sake of your wretched ambition, your mad design to bring to heel the kingdoms of man. In all the history of Creation no one woman has been so wicked as you, and I will have my answer. }
\textit{Why, o Empress of Ruins?”}
\textit{She shrugged.}
\textit{“Why not?”
}– Last lines of the “The Fall of Empress Triumphant, First and Only of Her Name”



A year ago, the commander would have given him trouble. Now? William tore the Penitent’s Blade out of the orc’s throat with a casual flick of the wrist. The sword keened mournfully, taking the greenskin’s life with it as it withdrew. The officer had died bravely, as bravely as one of his filthy species could, but with the orc’s blood on the floor the last of the resistance was over. It was to the Countess’ credit that she’d managed to turn a force of mercenaries and peasant levies into a coherent fighting force in less than a month – though it had certainly helped that their first battlefield had been her own fiefdom. If only all the allies he’d gathered were so competent. The Duke of Liesse had yet to set foot in the city, remaining with the baggage train under the impatient protection of the Exiled Prince.

The hero in question had been miffed he wouldn’t get to blood his men on Praesi legionaries today, but Countess Elizabeth had been correct when she’d pointed out that his troops were singularly unsuited to surprise attacks. No doubt the Duke would insist on a triumphant victory parade when the time came for him to enter, and for that the polished lancers of the Silver Spears would serve perfectly. They’d make a stirring enough image, and the story would spread: the Duke of Liesse had returned, to free the Kingdom from the yoke of the Tower.

Putting a complete imbecile on the throne of Callow was something William was going to have to live with, unfortunately. Oh, the Duke did have a sort of low cunning – he’d left Callow before Laure had even fallen, during the Conquest, and taken his treasury with him – but it was the kind of cunning a cockroach would have. He was a master of survival and little else, not to mention hopelessly self-important. That he was the First Prince’s creature walked the fine line between a virtue and a liability: this entire rebellion was being bankrolled by Proceran silver, but William was not so much of a fool as to be unaware the cold-eyed woman had designs on Callow herself. That was fine.

He was already leading a rebellion against the Empire, and he was more than willing to lead one against the Principate if it came down to it.

The Kingdom Under was a much greater worry. That two thousand hardened dwarven veterans had suddenly decided to form a mercenary company in Mercantis just when he’d been buying up every contract he could get his hands on was not a coincidence. The dwarves had a history of sending troublemakers up to the surface to die in other people’s wars, but the Sons of Stone were not your usual malcontents. If the King Under the Mountains was meddling in topside affairs William was going to have to keep a very, very close eye on it. Over two thirds of Calernia stood above dwarven tunnels and cities: no single nation had a military whose size equalled even the tenth of what the dwarves could muster if they felt like it.

It would not matter, in the end.

Only eight months had passed since his defeat at the hands of the Squire, but her words still rang whenever he closed his eyes. \textit{Run and hide and muster your armies in the dark. Make deals you’ll regret until you have nothing left to bargain with. I’ll be waiting for you, on the other side of that battlefield.} The dismissal had been a lash on his back all the way to Refuge, where he’d knelt at the feet of the Lady of the Lake and asked to be taken as a pupil. She’d denied him, not unkindly. After the defeat at Summerholm, that had almost been enough to break him.

What could you say, when the great swordswoman in Creation told you you weren’t good enough to beat her old pupil? The sword was all he was good for. His Name was a paradox, in a way: heroes were supposed to galvanize others into something greater than themselves, but his Role thrived on being solitary. The Eyes of the Empire had failed to find him because he’d never been part of a band of heroes, eschewing more blatant heroics for quiet work in the dark. He’d found his answer through pure happenstance, that blessed golden luck that smiled on heroes from above.

He’d found the gates to Arcadia Resplendent, and petitioned the Lady for the right to use them. This boon she’d seen fit to grant, and so began his year in the realm of the Fae. A full year he’d spent fighting for his life against the denizens of that eldritch place, hunted for sport by the horrors of the Wild Hunt. But he’d survived, and learned. There was no comparing his power now to what it had been in Summerholm. On the last day of the year, the gates had opened to let him leave and he’d returned to Creation. Barely a month had passed outside of Arcadia: he would crush the Squire when they next met, and they \textit{would }meet. The pattern had been set, there was no avoiding it. And when the time came, he would cram her words back down her sneering throat before raising the banner of a liberated Kingdom over her corpse.

Sheathing his sword, the Lone Swordsman left the room and stepped down the stairs. Countess Marchford should have set things up by now, assembling her peasantry in the city square. It was a shame the woman was so ambitious, but as far as commanders went she was by far the best the nobility had to offer. She’d stalemated a Marshal for an entire month during the Siege of Summerholm, holding out until the Legions landed a force on the other side of the Hwaerte and finished the encirclement. Had Grem One-Eye not been driving his army into the depths of the Duchy of Daoine at the same time, it would have been long enough for the Deoraithe to come relieve the siege.

\textit{And now she wants to be Queen of Callow, as she would have been had the Shining Prince not died at the Fields.} Less of a bitter pill to swallow than the Duke having the best claim to the throne, all in all. She would not be any more inclined to trade a Praesi occupation for a Proceran one than William himself. The streets were full of dead legionaries, the fighting having gotten brutal in its last gaps. A full quarter of the Twelfth Legion had spat in the face of offered surrender, eerily singing that damned Legionary’s Song as they made their last stand against thrice their number. In a person that kind of courage would have been worthy of respect, but greenskins were barely more sentient than animals. Just another horror crafted by the Hellgods to plague Creation, an endless horde of foot soldiers carrying the banner of Evil.

His steps took him all the way to the central market, where the citizens of Marchford stood as an uneasy crowd in front of the gallows erected by the Legions. Fifty prisoners, goblins and orcs and humans, already stood on the wooden platform with nooses around their necks. His idea, that: William had not forgotten Summerholm, and neither would those fucking Praesi butchers. He hopped onto the gallows and with a few lazy strides he stood in front of the people, whispers of his Name spreading among the crowd when they recognized his white-gilded armour. There’d been a time where he would have avoided such glaringly heroic garments like the plague, but the time for subtlety was long past. Eyes staring down the masses, the hero took a deep breath.

“Twenty years ago, Praesi boots broke the spine of this nation,” he said, and the words carried perfectly.

Utter silence greeted him.

“They were strong, we told ourselves,” he continued. “Too strong. What could we possibly have done?”

His eyes narrowed.

“\textit{Cowardice},” he barked.

The crowd flinched as if he’d lashed them.

“There is no bargaining with Evil,” he thundered. “No truce with the Enemy. That we ever gave in to the Tower is a stain on the history of this Kingdom.”

Slowly, William unsheathed his sword.

“But we are not yet beyond redemption,” he told them. “Shame can be expunged. Today, for the first time in two decades, some of us rose to our feet.”

His Name burned within him, a cold flame that turned his blood to smoke and dust.

“Tell me, Callowans, do you want to spend the rest of your life kneeling?”

He could feel it swelling up. He could see it in their eyes, the light ground out by decades of occupation. His power spread through the air, thick and lingering.

“Do you want to continue licking the Empress’ boot, and let your children inherit that life?” he bellowed.

The whisper first came from the back, twisting and winding and gaining strength as it made its way to the first row and the answer came out as a \textit{NO} that clapped like thunder.

“Neither do I,” he admitted when silence returned. “Take heart, citizens of Callow. Today the Kingdom is born again, and I make you this oath.”

Green eyes burned.

“CALLOW WILL BE FREE.”

Behind him the legionaries dropped, one after another, the cheer from the crowd drowning their dying struggles out. William closed his eyes, letting the sound wash over him, and smiled. There could be no defeat. The Heavens, after all, were on his side. Why else would they have granted him Triumph as an aspect?

—



Akua had never particularly enjoyed playing shatranj, though she was skilled at it. The only reason she was currently playing Barika was that, traditionally speaking, it was expected of her to play shatranj while discussing the demise of her enemies. The way the Unonti heiress played was too conservative, much like the girl herself. Had she not been so reliably loyal, she would never have made it as high in Akua’s council as she currently stood. That was the problem with many of the Trueblood’s children. The old nobility was too stiff, too set in its ways, and it had transmitted that disease to their inheritors. Thankfully her own mother was much more flexible in her ways, and had raised her as such. The truth was that the Empire was no longer the same as it had been in ages past. The Reforms had granted rights to the greenskins, and there would be no withdrawing those without a civil war – one the nobility might not win, given that the vast majority of the current generations of orcs and goblins were Legion-trained.

The old truth that greenskins were inferiors to the Soninke in every way was no longer valid, and so had to be discarded. The aristocrats who refused to admit this were betraying the guiding rule of all Praesi: truth was mutable, and changed according to one’s purposes. Akua was not above using orcs and goblins as tools, though she found the matter distasteful. More importantly, the old hatreds some Soninke still held against humans had to be set aside. Taghreb inferiority, while a fact, was marginal enough in nature it should be ignored. Even the Duni had proved they could have worth, by spawning the most viciously dangerous Black Knight the Empire had seen in centuries. It was a shame the man had declined to take her a pupil, and she truly regretted that she had come to be at cross-purposes with him. Removing Foundling should neuter that liability cleanly enough, and the Knight was much too pragmatic to hold a grudge over such a trifling matter.

“I do not understand why you let the goblin’s death pass without making an issue of it,” Barika said, moving a legionary forward in an unwise gambit that was going to cost her a priest in three moves.

“I tried to press the issue through Court,” Akua noted. “Before I could, a member of the Blackguard dropped a basket with the head of my proxy in it at the mansion gates.”

The warning had been clear enough, and she’d never particularly expected that particular plot to bear fruit anyway. She’d had four people out for Foundling’s blood in the melee, but the goblin had been the only one to get close enough for an attempt. The scheme had been worth making, and had cost her nothing of worth to implement – much like the entire war games affair. Blackmailing the instructor to change Squire’s beginning position and meddle with the memory magic might have been a more expensive endeavour, had the man in question not been caught trying to escape the city and been crucified for his troubles. A rather mild reaction, by the standards of the Black Knight. The last time he’d caught a noble meddling in College business, he’d had their entire family eaten alive by spiders. Malicia was tightening his leash, as she had been for several years.

“Then it was a failure,” Barika said, barely hiding a wince when she lost her priest and found her chancellor trapped in a corner.

“You’re assuming that the point of this enterprise was to deny Foundling the appointment,” Akua said. “While it would have been the optimal result, it was not my main objective.”

In the long term, there was no real way to ensure that Squire did not get to lead troops. She was, ironically enough, too well-connected for that. At best the process could be delayed, and Akua’s assessment of the cost of keeping her out of the Legions for another year had been too much to stomach. And so she’d planned with the eventuality of failure in mind. By making this a public play through the Court, she’d forced her support in the nobility to be open in their backing. The minor loss of face that ensued from Foundling’s victory had caused her fair-weather friends to immediately withdraw their support, allowing Akua to separate the wheat from the chaff. She’d immediately move on those and made examples of them, of course.

Her position in Court was now stronger than it had ever been.

And while Squire had been tearing out her hair over inconsequential collegial games, she’d prepared to place agents in the Fifteenth Legion. \textit{That} plot, the one that mattered, had been a success. That one of Foundling’s senior officers had become a spy before they were even appointed to the rank had been a source of great amusement to her over the last few months. It was unfortunate that she’d been unable to find leverage on the officers of the former Rat Company, as they seemed to be Squire’s most trusted. Ratface’s familial situation had seemed promising but the boy had flatly told her intermediary that if the subject was ever broached again blades would come out. Legate Juniper’s open distaste for what she called “human squabbling” made her a lost cause in this regard, and had she not been the daughter of a general Akua would already have her had assassinated. A shame, that such talent would be put to work in her rival’s favour. Barika knocked over her empress in a concession of defeat, letting out a sigh.

“So,” she murmured. “Are you finally going to tell me what was in the letter that came this morning?”

Heiress smiled.

“Every major city in the south of Callow has risen in rebellion,” she replied.

“\textit{What?}” the other girl replied, openly aghast.

Akua pretended she hadn’t seen the loss of composure, for her childhood companion’s sake.

“The Sixth and the Ninth Legion are to be deployed to put the unrest down,” she informed the other Soninke. “The Fifteenth will be joining them, still at half-strength.”

The purpose behind keeping the numbers of Foundling’s legion at two thousand legionaries only still eluded her, in truth. Part of it must have been the fact that Fourteenth was being raised simultaneously and the recruitment pool was limited, but that answer was too… obvious. There was always more than one angle, when one dealt with the Calamities.

“So that’s why you’ve been recruiting mercenaries,” Barika suddenly breathed.

Akua’s smile broadened, never quite reaching her eyes. Mercenaries were, technically speaking, illegal in Praes. It would have been too obvious of a way for the High Lords to get around the household troops restrictions put into place by Malicia. But the moment southern Callow had risen in rebellion, it had stopped legally being Praesi territory. The roughly four thousand troops she’d hired in Mercantis would be able to operate there without consequence.

“It won’t be enough,” a third voice rasped from the corner of the room.

Akua’s eyes flickered to the mangled goblin. Half of her face was missing, chopped off by a brutal – and lethal sword wound. Various parts of her body had been snapped by falling rubble and even now still remained at unnatural angles, barely functional. Not even the best necromancers on her payroll had been able to restore Chider to something palatable to look at.

“That would be where you come in, Commander Chider,” Heiress replied softly.

The goblin let out a horrible rasp Akua took a moment to recognize as a laugh. Raising a mere enemy of Foundling from the dead would have been a waste of gold, but Heiress had no interest in the greenskin’s skills. It was her nature that was of import. Raising a Claimant from the dead, on the other hand, had been worth every denarii. Picking up her own empress, the Soninke aristocrat felt her Name coil inside of her silently, like a snake preparing to strike. She’d wondered, when she’d first come into her Role, what exactly it meant. It was a question every Heir and Heiress had to answer on their own. Was she the inheritor of the stewardship of the Empire, the return of the forbidden Name of Chancellor? Was she the next warlord of Praes, the successor of its Black Knight? Or was hers to be the hand that cast down Dread Empress Malicia, the woman still hated behind closed doors? Wrong, all wrong. Paltry ambitions of lesser souls.

She was Akua Sahelian, and she would inherit all of Creation.

—



Black put down the letter, face expressionless.

The rebellion was not, all in all, unexpected. He’d moved Istrid and Sacker further south to deal with the eventuality, assigning the Eleventh to Summerholm instead. More importantly, Ranker and her Fourth were keeping an eye on the Deoraithe. Scribe’s agents had found out the Duchess had placed an observer with the rebels, but according to the rest of the network that was the only move she’d made. His personal assessment of Kegan had been accurate, then: she would not take action unless the Liesse Rebellion looked like it had decent chances of succeeding. That Afolabi had lost a full thousand at Marchford would be a black mark on the general’s record, but it was a tactical defeat and not a strategic one. No rebel force had yet to dare move north of Vale, and he’d already sent Catherine orders to mobilize her Fifteenth: by dawn tomorrow they’d be moving for the Blessed Isle to join the muster in central Callow.

“So that was your gamble, then,” the dark-haired man murmured into the silence.

He’d wondered about the exact form his Squire’s actions had taken, back in Summerholm. Obviously she’d let the Lone Swordsman go when she could have killed him – the damaged connection to her Name betrayed as much – but it seemed she’d freed the hero for a specific purpose. The boy had shown no inclination to gather large-scale strength before his encounter with the orphan, and such a sudden change in doctrine would have had to be Name-enforced. \textit{She branded instructions on his Name as the price for sparing him, then} \textit{let him disappear into the wilds.} Black had not even bothered to try tracking the Swordsman after his run-in with Catherine: the confrontation had initiated a pattern of three, and the hero was therefore beyond his reach. The only person who could feasibly kill him now was Squire, unfortunate as that was.

Still, none of this was beyond the parameters he’d set. The rebellion would have happened anyway, there was no denying that. The numbers did not lie: in the last decade the number of heroes appearing had shot up from once every several years to at least two a year. They were all dead now, of course, but that wasn’t the point. Sooner or later, one of his people would make a mistake. When he’d put down the Unconquered Champion last year, he’d been stuck in a pocket realm for what had ended up being three days in Creation proper. Within that lapse of time he’d been impossible to reach, and the Calamities had… not reacted well. Captain had slaughtered an entire village in a fit of blind rage and Warlock had actually mutilated the soul of an informant in his search for answers. He shuddered to think of what might have happened had Assassin or Ranger gotten involved.

No, the rebellion had always been a given. All it meant was that he had to have measures in place so that the event benefitted the Empire instead of weakened it, and he had managed that much. Barely. Catherine’s intervention had the uprising beginning ahead of schedule, and had he not spent the last twenty years preparing the Dread Empire for war it might have been taken by surprise. As things stood, the rebellion would be crushed before the next harvest and Catherine would blood her troops on real battlefield in the process.  The inevitable losses would teach her some valuable lessons and temper her reckless streak as well as strengthen her emotional attachment to her soldiers – and by extension the Empire.

“Not a bad plan at all,” he decided.

Trading a weakened Name for a few months against an opportunity to advance through the ranks in wartime was bold but not overly so. She wouldn’t have known she was damaging her connection to her Role by letting the Lone Swordsman go, of course. He had, after all, carefully kept her in the dark about the way Names functioned. The results of that spoke for themselves. Not even a year into her power and she was already beginning to Speak. She had absolutely no idea how absurd that kind of progress was, no inkling that it had taken Black several years into the same Role before managing it. Ignorance on the subject of what she could and couldn’t do with her Name had allowed her to progress through leaps and bounds instead of a slow grind. It was fortunate that this approach was the best available to him, because Black had no real idea how to teach her.

He’d become the Squire when there was no Black Knight and most of what he knew was either self-taught or derived from Name dreams. He’d had two teachers in his lifetime and both tutelages had been purely related to swordsmanship: first his mother, when he’d been young, and then Ranger later in his career. Deciding how to treat Catherine had been something of a problem for him, in all honesty. He could not treat her as an equal, the way he and Ranger had been, but treating her purely as a subordinate was doomed to failure. In the end he’d settled for moulding her instead of teaching her, carefully exposing her to specific influences so that she would grow through them.

And grown she had, in the eight months he’d known her. The reports from his agent in the orphanage had indicated she had potential, but they’d underestimated how much. It was a good thing he hadn’t had her smothered in her sleep, as the local overseer’s recommendation had originally been. \textit{Morals too heroic in nature}, the assessment had stated. He’d been ready to tie up that particular loose end should it prove necessary when he’d gone to deal with Mazus, but their unexpected meeting had opened a better alternative.

The dark-haired smiled, rising to his feet and coming to stand by the window. The view offered from the Tower’s one hundredth floor was breath-taking, but he’d become inured to the sight over the years. Black had been amused, when Catherine had mentioned that she felt her Name like a living, breathing beast. The way a Named felt their Role revealed much about them. Warlock said his own was akin to opening floodgates, for he rightfully feared the capricious nature of his power. Malicia compared her own to slipping on a pair of gloves, perfectly fitted to her. And him? Gears. An enormous machine made up of a hundred thousand gears, all of them turning. Slowly. Coldly. Implacably.

The moment his agents had gotten him the news he’d felt his Name react\textit{. Lead. Conquer. Destroy}. All three of his aspects were awake. He hadn’t felt this alive in decades, and even as the south of the kingdom he’s conquered resumed the war he’d won he felt a strange joy welling up inside of him. Interesting years were ahead. And this once, just this once, he was willing to break a rule of his. Baring his teeth at the Heavens, Black dared them to deny him.

“Just as planned,” he said.
\clearpage
\end{document}